### 2017-01-26 sources/Math/Handout.BinomialCoefficient.tex
math handouts

\documentclass[]{article}
\usepackage{amsmath,amssymb,amsthm}

\begin{document}

	The notation (nk) for the binomial coefficient was introduced by Andreas Freiherr von Ettingshausen in his 1826 work Die combinatorische Analysis.

	It appears to have become the de facto standard in recent years.

\begin{align}
	\binom{N}{K} &= \binom{N - 1}{K - 1} + \binom{N - 1}{K}\\ 
	\binom{N}{0} &= 1
\end{align}

Identities 
\begin{align}
	\binom{n}{k} &= \frac {n}{k} \binom{n-1}{k-1}
\end{align}
proof
\begin{align}
	\binom{n}{k} &= \frac {n!}{k!(n-k)!}\\
	&= \frac{n*(n-1)!}{k*(k-1)!(n-k)!}\\
	u &= n-1\\
	z &= k-1\\
	u-z &= (n-1)-(k-1)\\
	&= n-1-k+1\\
	&= n-k\\
	&= \frac{n}{k} * \frac {u!}{z!(u-z)!}\\
	&= \frac{n}{k} * \binom{u}{z}\\
	&= \frac{n}{k} * \binom{n-1}{k-1}
\end{align}

\end{document}

### 2017-01-26 sources/Math/Handout.LinearRegression.tex
math handouts

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\begin{document}
	\begin{align*}
		&=\sum_{i=0}^{N}{[y_i-(w_1*x_i+w_0)]^2}\\
		&=\sum_{i=0}^{N}{[y_i^2-2*y_i*(w_1*x_i+w_0)+(w_1*x_i+w_0)^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2-2*y_i*w_1*x_i-2*y_i*w_0+(w_1*x_i+w_0)^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2-2*y_i*w_1*x_i-2*y_i*w_0+(w_1*x_i)^2+2*w_1*x_i*w_0+w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-\sum_{i=0}^{N}{[2*y_i*w_1*x_i-2*y_i*w_0+(w_1*x_i)^2+2*w_1*x_i*w_0+w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-\sum_{i=0}^{N}{[2*y_i*w_1*x_i]}-\sum_{i=0}^{N}{[2*y_i*w_0+(w_1*x_i)^2+2*w_1*x_i*w_0+w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-2*w_1*\sum_{i=0}^{N}{[y_i*x_i]}-\sum_{i=0}^{N}{[2*y_i*w_0+(w_1*x_i)^2+2*w_1*x_i*w_0+w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-2*w_1*\sum_{i=0}^{N}{[y_i*x_i]}-\sum_{i=0}^{N}{[2*y_i*w_0]}+\sum_{i=0}^{N}{[(w_1*x_i)^2+2*w_1*x_i*w_0+w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-2*w_1*\sum_{i=0}^{N}{[y_i*x_i]}-2*w_0*\sum_{i=0}^{N}{[y_i]}+\sum_{i=0}^{N}{[(w_1*x_i)^2+2*w_1*x_i*w_0+w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-2*w_1*\sum_{i=0}^{N}{[y_i*x_i]}-2*w_0*\sum_{i=0}^{N}{[y_i]}+\sum_{i=0}^{N}{[(w_1*x_i)^2]}+\sum_{i=0}^{N}{[2*w_1*x_i*w_0+w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-2*w_1*\sum_{i=0}^{N}{[y_i*x_i]}-2*w_0*\sum_{i=0}^{N}{[y_i]}+w_1^2*\sum_{i=0}^{N}{(x_i)^2}+\sum_{i=0}^{N}{[2*w_1*x_i*w_0+w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-2w_1\sum_{i=0}^{N}{[y_ix_i]}-2w_0\sum_{i=0}^{N}{[y_i]}+w_1^2\sum_{i=0}^{N}{(x_i)^2}+\sum_{i=0}^{N}{[2w_1x_iw_0+w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-2w_1\sum_{i=0}^{N}{[y_ix_i]}-2w_0\sum_{i=0}^{N}{[y_i]}+w_1^2\sum_{i=0}^{N}{(x_i)^2}+\sum_{i=0}^{N}{[2w_1x_iw_0]}+\sum_{i=0}^{N}{[w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-2w_1\sum_{i=0}^{N}{[y_ix_i]}-2w_0\sum_{i=0}^{N}{[y_i]}+w_1^2\sum_{i=0}^{N}{(x_i)^2}+2w_1w_0\sum_{i=0}^{N}{[x_i]}+\sum_{i=0}^{N}{[w_0^2]}\\
		&=\sum_{i=0}^{N}{[y_i^2]}-2w_1\sum_{i=0}^{N}{[y_ix_i]}-2w_0\sum_{i=0}^{N}{[y_i]}+w_1^2\sum_{i=0}^{N}{(x_i)^2}+2w_1w_0\sum_{i=0}^{N}{[x_i]}+w_0^2N\\
		\\
		&\frac{\sum_{i=0}^{N}{y_i^2}}{N}=\bar{y}\\
		&\sum_{i=0}^{N}{y_i^2}=\bar{y}*N
	\end{align*}
\end{document}

### 2017-01-26 sources/Math/Handout.LinearRegression.tex
linear regression handout

@@
 \usepackage{graphicx}
+\usepackage{blindtext}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.9}
+\newcommand*\mean[1]{\overline{#1}}
 \begin{document}
+	Squared Error Line
 	\begin{align*}
-		&=\sum_{i=0}^{N}{[y_i-(w_1*x_i+w_0)]^2}\\
+		SE_{line}&=\sum_{i=0}^{N}{[y_i-(w_1*x_i+w_0)]^2}\\
 		&=\sum_{i=0}^{N}{[y_i^2-2*y_i*(w_1*x_i+w_0)+(w_1*x_i+w_0)^2]}\\
@@
 		&=\sum_{i=0}^{N}{[y_i^2]}-2w_1\sum_{i=0}^{N}{[y_ix_i]}-2w_0\sum_{i=0}^{N}{[y_i]}+w_1^2\sum_{i=0}^{N}{(x_i)^2}+2w_1w_0\sum_{i=0}^{N}{[x_i]}+w_0^2N\\
+		\end{align*}
+		\begin{align*}
+		&\frac{\sum_{i=0}^{N}{y_i^2}}{N}=\mean{y^2}\\
+		&\sum_{i=0}^{N}{y_i^2}=\mean{y^2}*N
 		\\
-		&\frac{\sum_{i=0}^{N}{y_i^2}}{N}=\bar{y}\\
-		&\sum_{i=0}^{N}{y_i^2}=\bar{y}*N
+		&=\mean{y^2}N-2w_1\sum_{i=0}^{N}{[y_ix_i]}-2w_0\sum_{i=0}^{N}{[y_i]}+w_1^2\sum_{i=0}^{N}{(x_i)^2}+2w_1w_0\sum_{i=0}^{N}{[x_i]}+w_0^2N\\
+		&=\mean{y^2}N-2w_1\mean{yx}N-2w_0\sum_{i=0}^{N}{[y_i]}+w_1^2\sum_{i=0}^{N}{(x_i)^2}+2w_1w_0\sum_{i=0}^{N}{[x_i]}+w_0^2N\\
+		&=\mean{y^2}N-2w_1\mean{yx}N-2w_0\mean{y}N+w_1^2\sum_{i=0}^{N}{(x_i)^2}+2w_1w_0\sum_{i=0}^{N}{[x_i]}+w_0^2N\\
+		&=\mean{y^2}N-2w_1\mean{yx}N-2w_0\mean{y}N+w_1^2\mean{x^2}N+2w_1w_0\sum_{i=0}^{N}{[x_i]}+w_0^2N\\
+		&=\mean{y^2}N-2w_1\mean{yx}N-2w_0\mean{y}N+w_1^2\mean{x^2}N+2w_1w_0\mean{x}N+w_0^2N\\
+		SE_{line}&=N\mean{y^2}-2Nw_1\mean{yx}-2Nw_0\mean{y}+Nw_1^2\mean{x^2}+2Nw_1w_0\mean{x}+Nw_0^2\\	
 	\end{align*}
+
+	\begin{tikzpicture}[
+	declare function = {
+		N = 5;
+		YSB = (1+4+9+16+25)/N;
+		YXB = (1+4+9+16+25)/N;
+		YB = (1+2+3+4+5)/N;
+		XSB = (1+4+9+16+25)/N;
+		XB = (1+2+3+4+5)/N;
+		q(\x) = \x - 1;
+		Z(\x,\y) = N*YSB -2*N*\y*YXB - 2*N*\x*YB + N*\y^2*XSB + 2*N*\x*\y*XB + N*\x^2;
+	}
+	]
+	\begin{axis}
+	[
+	axis lines=center,
+	enlargelimits,
+	tick align=inside,
+	domain=-0.5:0.5,
+	domain y=0.5:1.5,
+	samples=20,
+	minor tick num=5,
+	width=500
+	]
+	\addplot3 [surf, opacity=0.5] {Z(x,y)};	
+	\end{axis}
+	\end{tikzpicture}
+
+	Now to find the line that minimizes the squared errors we can take the partial directives in relation to $w_0$ and $w_1$
+
+	First partial derivative in relation of $w_0$
+	\begin{align*}
+		MSE_{line}&=\frac{d}{dw_0}[N\mean{y^2}-2Nw_1\mean{yx}-2Nw_0\mean{y}+Nw_1^2\mean{x^2}+2Nw_1w_0\mean{x}+Nw_0^2]\\
+		&=\frac{d}{dw_0}[N\mean{y^2}]-\frac{d}{dw_0}[2Nw_1\mean{yx}]-\frac{d}{dw_0}[2Nw_0\mean{y}]+\frac{d}{dw_0}[Nw_1^2\mean{x^2}]+\frac{d}{dw_0}[2Nw_1w_0\mean{x}]+\frac{d}{dw_0}[Nw_0^2]\\
+		&=-\frac{d}{dw_0}[2Nw_1\mean{yx}]-\frac{d}{dw_0}[2Nw_0\mean{y}]+\frac{d}{dw_0}[Nw_1^2\mean{x^2}]+\frac{d}{dw_0}[2Nw_1w_0\mean{x}]+\frac{d}{dw_0}[Nw_0^2]\\
+		&=-\frac{d}{dw_0}[2Nw_0\mean{y}]+\frac{d}{dw_0}[Nw_1^2\mean{x^2}]+\frac{d}{dw_0}[2Nw_1w_0\mean{x}]+\frac{d}{dw_0}[Nw_0^2]\\
+		&=-2N\mean{y}+\frac{d}{dw_0}[Nw_1^2\mean{x^2}]+\frac{d}{dw_0}[2Nw_1w_0\mean{x}]+\frac{d}{dw_0}[Nw_0^2]\\
+		&=-2N\mean{y}+\frac{d}{dw_0}[2Nw_1w_0\mean{x}]+\frac{d}{dw_0}[Nw_0^2]\\
+		&=-2N\mean{y}+2Nw_1\mean{x}+\frac{d}{dw_0}[Nw_0^2]\\
+		&=-2N\mean{y}+2Nw_1\mean{x}+2Nw_0\\
+	\end{align*}
+
+	Now the derivative in relation to $w_1$
+	\begin{align*}
+		MSE_{line}&=\frac{d}{dw_1}[N\mean{y^2}-2Nw_1\mean{yx}-2Nw_0\mean{y}+Nw_1^2\mean{x^2}+2Nw_1w_0\mean{x}+Nw_0^2]\\
+		&=\frac{d}{dw_1}[N\mean{y^2}]-\frac{d}{dw_1}[2Nw_1\mean{yx}]-\frac{d}{dw_1}[2Nw_0\mean{y}]+\frac{d}{dw_1}[Nw_1^2\mean{x^2}]+\frac{d}{dw_1}[2Nw_1w_0\mean{x}]+\frac{d}{dw_1}[Nw_0^2]\\
+		&=-\frac{d}{dw_1}[2Nw_1\mean{yx}]-\frac{d}{dw_1}[2Nw_0\mean{y}]+\frac{d}{dw_1}[Nw_1^2\mean{x^2}]+\frac{d}{dw_1}[2Nw_1w_0\mean{x}]+\frac{d}{dw_1}[Nw_0^2]\\
+		&=-2N\mean{yx}-\frac{d}{dw_1}[2Nw_0\mean{y}]+\frac{d}{dw_1}[Nw_1^2\mean{x^2}]+\frac{d}{dw_1}[2Nw_1w_0\mean{x}]+\frac{d}{dw_1}[Nw_0^2]\\
+		&=-2N\mean{yx}+\frac{d}{dw_1}[Nw_1^2\mean{x^2}]+\frac{d}{dw_1}[2Nw_1w_0\mean{x}]+\frac{d}{dw_1}[Nw_0^2]\\
+		&=-2N\mean{yx}+2Nw_1\mean{x^2}+\frac{d}{dw_1}[2Nw_1w_0\mean{x}]+\frac{d}{dw_1}[Nw_0^2]\\
+		&=-2N\mean{yx}+2Nw_1\mean{x^2}+2Nw_0\mean{x}+\frac{d}{dw_1}[Nw_0^2]\\
+		&=-2N\mean{yx}+2Nw_1\mean{x^2}+2Nw_0\mean{x}\\		
+	\end{align*}
+
+	Now we must solve the lienar system
+
+	\begin{align*}
+		\begin{cases}
+			-2N\mean{y}+2Nw_1\mean{x}+2Nw_0=0\\
+			-2N\mean{yx}+2Nw_1\mean{x^2}+2Nw_0\mean{x}=0
+		\end{cases}\\
+		&& \text{divide first 2N}\\
+		\begin{cases}
+			-\mean{y}+w_1\mean{x}+w_0=0\\
+			-2N\mean{yx}+2Nw_1\mean{x^2}+2Nw_0\mean{x}=0
+		\end{cases}\\
+		&& \text{divide second 2N}\\
+		\begin{cases}
+			-\mean{y}+w_1\mean{x}+w_0=0\\
+			-\mean{yx}+w_1\mean{x^2}+w_0\mean{x}=0
+		\end{cases}\\
+		\begin{cases}
+			w_1\mean{x}+w_0=\mean{y}\\
+			w_1\mean{x^2}+w_0\mean{x}=\mean{yx}
+		\end{cases}\\
+		\begin{cases}
+			w_1\mean{x}+w_0=\mean{y}\\
+			w_1\frac{\mean{x^2}}{\mean{x}}+w_0\frac{\mean{x}}{\mean{x}}=\frac{\mean{yx}}{\mean{x}}
+		\end{cases}\\
+		\begin{cases}
+		w_1\mean{x}+w_0=\mean{y}\\
+		w_1\frac{\mean{x^2}}{\mean{x}}+w_0=\frac{\mean{yx}}{\mean{x}}
+		\end{cases}\\
+	\end{align*}
+
+	This means that the line that minimizes the squared error pass through the points
+	\begin{align*}
+		\big(\mean{x},\mean{y}\big)\\
+		\big(\frac{\mean{x^2}}{\mean{x}},\frac{\mean{yx}}{\mean{x}}\big)\\
+	\end{align*}
+
 \end{document}

### 2017-03-05 sources/Math/GeometricInterpretationOfCovarianceMatrix.Rmd
eigenvector interpretation

---
title: "Untitled"
author: "Daniel Frederico Lins Leite"
date: "5 March 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{R}
library(scales)
library(MASS)

generateData <- function (u, sdx, sdy){
  size <- 1000
  x0 <- rnorm(mean = u, sd = sdx, n = size)
  x1 <- rnorm(mean = u, sd = sdy, n = size)
  X <- matrix(x0, ncol = 1)
  cbind(X, matrix(x1, ncol = 1))
}

plotMatrix <- function(X){
  xdf <- data.frame(X)
  plot(xdf, ylim=c(-10, 10), asp=1, col = alpha("black",0.5))
}

plotEigenvectors <- function(X){
  C <- covarianceMatrix(X)
  eigenC <- eigen(C, symmetric = TRUE)
  dimensions <- eigenC$vectors %*% diag(sqrt(eigenC$values))
  arrows(0,0,dimensions[1,1],dimensions[2,1], lwd = 4, col = "red")
  arrows(0,0,dimensions[1,2],dimensions[2,2], lwd = 4, col = "blue")
}

rotationMatrix <- function(angle){
  matrix(c(cos(angle),sin(angle),-sin(angle),cos(angle)), nrow = 2, ncol= 2)
}

covarianceMatrix <- function(X){
  mu <- matrix(colMeans(X), nrow = 1)
  t(X)%*%X * (1/(nrow(X)-1)) - (t(mu)%*%mu)
}
```

# Theory

The eigenvectors of the covariance matrix should form a new basis perpendicular to variation of the data.

```{R}
C <- diag(1,2,2)
eigenC <- eigen(C)
dimensions <- eigenC$vectors %*% diag(eigenC$values)
C
eigenC
dimensions
```

# White Data

A white data (Gaussian with mean = 0 and Standard Deviation = 1) should have its eigenvector as near as possivle to the default basis.

```{R}
X <- generateData(0,1,1)
plotMatrix(X)
plotEigenvectors(X)
```

# Scaled Gaussian

A Scaled Gaussian should have one bigger eigenvector pointing to the variation of the data.

```{R}
X <- generateData(0, 4, 1)
plotMatrix(X)
plotEigenvectors(X)
```

# Scaled and Rotated Gaussian

The Scaled and Rotated Gaussian should have its eigenvectors rotated adn poiting to new variation direction.

```{R}
X <- generateData(0, 4, 1)
rot45 <- rotationMatrix(-pi/4)
X <- X %*% rot45
C <- covarianceMatrix(X)
eigenC <- eigen(C)
plotMatrix(X)
plotEigenvectors(X)
```

# Covariance Matrix is the Linear Transformation Squared

The Scaled and Rotated Gaussian can be generated from a White Data Gaussian using two Linear Transformations:
1 - Scale Transformation
2 - Rotation Transformation

```{R}
X <- generateData(0,1,1)
R <- rotationMatrix(-pi/4)
S <- matrix(c(4,0,0,1), nrow=2, ncol=2)
plotMatrix(X)
```

The complete transformation can be aggregated in the Matrix:

```{R}
T <- R%*%S
```

In thos case the covariance matrix is:

```{R}
#R is a orthonormal matrix so t(R) = ginv(R)
C <- T%*%t(T)
```

The final data is identical

```{R}
plotMatrix(X%*%S%*%R)
```

In this case its eigenvectors can be calculated as:

```{R}
eigenVectors <- t(R)%*%S
plotMatrix(X%*%S%*%R)
arrows(0,0,eigenVectors[1,1],eigenVectors[2,1], lwd = 4, col = "red")
arrows(0,0,eigenVectors[1,2],eigenVectors[2,2], lwd = 4, col = "blue")

# These matrices should be as near as zero as possible
eigenC$vectors - t(R)
diag(sqrt(eigenC$values), 2, 2) - S
```

### 2017-03-21 sources/Math/MaximumLikelihood.rmd

---
title: "Maximum Likelihood"
author: "Daniel Frederico Lins Leite"
date: "19 March 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Gaussian

```{R}
x <- seq(-4, 4, length=100)
hx <- dnorm(x)
plot(x, hx, type="l", lty=2, xlab="x value", ylab="Density", main="Normal Gaussian(u=0,sigma=1)")
```

## Percentage

```{R}
plotGaussian <- function(u, sigma, color = "black"){
  x <- seq(-4, 4, length=100)
  hx <- dnorm(x, mean = u, sd = sigma)
  plot(x, hx, type="l", lty=2, xlab="x value", ylab="Density", main="Gaussian", col = color)
}
plotArea <- function(u, sigma, sigmaSize, color){
  x <- seq(-4, 4, length=100)
  hx <- dnorm(x, mean = u, sd = sigma)
  l <- -(sigma*sigmaSize)
  r <- (sigma*sigmaSize)
  i <- x >= l & x <= r
  polygon(c(l,x[i],r), c(0,hx[i],0), col=color)
}

plot.new()
plotGaussian(0,1)
plotArea(0,1,3,"green")
plotArea(0,1,2,"blue")
plotArea(0,1,1,"red")
```

## Density Simulation

```{R}
hist(rnorm(n = 10, mean = 0, sd = 1))
hist(rnorm(n = 100, mean = 0, sd = 1))
hist(rnorm(n = 1000, mean = 0, sd = 1))
hist(rnorm(n = 10000, mean = 0, sd = 1))
```

## Likelihood

Suppose we have an observation and two possible distributions that can be considered as the source distributions of this observations. We want to choose the best option: in this case the most probable source distribution.

Options:  
Gaussian #1  
u = -2  
sd = 1

Gaussian #2  
u = 2  
sd = 1

```{R}
plotGaussian(-2,1,"red")
par(new=TRUE)
plotGaussian(2,1, "blue")
```

Observations  
A = -0.25  
B = -1  
C = 0.45

To choose the best distribution we will choose the distribution whose density is bigger in that particular point. For example, for observation A:

Probability of observing A from Gaussian #1 (u-2,sd=1) = `r dnorm(-0.25,-2,1)`    
Probability of observing A from Gaussian #2 (u=2,sd=1) = `r dnorm(-0.25,2,1)`

In this case the best option is Gaussian #1. It is more likely/probable that the observation #A comes from Gaussian #1 than Gaussian #2.

```{R}
plotGaussian(-2,1,"red")
arrows(-0.25,0,-0.25,dnorm(-0.25,-2,1), col = "red")
par(new=TRUE)
plotGaussian(2,1, "blue")
arrows(-0.25,0,-0.25,dnorm(-0.25,2,1), col = "blue")
```

We can use the same calculations to the others observations.

Probability of observing B from Gaussian #1 (u-2,sd=1) = `r dnorm(-1,-2,1)`      
Probability of observing B from Gaussian #2 (u=2,sd=1) = `r dnorm(-1,2,1)`   
Probability of observing C from Gaussian #1 (u-2,sd=1) = `r dnorm(0.45,-2,1)`      
Probability of observing C from Gaussian #2 (u=2,sd=1) = `r dnorm(0.45,2,1)`

```{R}
plotGaussian(-2,1,"red")
arrows(-1,0,-1,dnorm(-1,-2,1), col = "red")
arrows(0.45,0,0.45,dnorm(0.45,-2,1), col = "red")
par(new=TRUE)
plotGaussian(2,1, "blue")
arrows(-1,0,-1,dnorm(-1,2,1), col = "blue")
arrows(0.45,0,0.45,dnorm(0.45,2,1), col = "blue")
```

So we can sau that:  
The likelihood of u = -2 and sd = 1 for a observation -1 is `r dnorm(-1,-2,1)` because the probability of seeing a value -1 from a Gaussian with u = -2 and sd = 1 is `r dnorm(-1,-2,1)`.  
In others words:  
The likelihood of theta, the gaussian parameters, given x is `r dnorm(-1,-2,1)` because the probability of x given theta is `r dnorm(-1,-2,1)`.  
Or:  
L(theta|x) = p(x|theta)

## Maximum Likelihood

### Maximum Likelihood of just one point

Imagine now that we do not have two options predertimined. We have all possible Gaussians and we want to find the best gaussian to each observation, first one-by-one, and them as a set.
The best gaussian for observation A is the Gaussian with the maximum likelihod. So our problem can be described as:

maximize theta in L(theta|x)

We saw that this is the same as

maximize theta in p(x | theta)

Se given x, which is a known value, we must find the theta that maximize the function. theta in this particular case is the set {u,sd}. So given X, we must find u and sd that will maximize p(x|u,sd).

For this trivial case we will have a problem, that will be shown later. For now let fix sd =1 and try to maximize just for u. So we have:

maximize u in p(x | u, sd = 1)

Well... looking again  to the Gaussian distribution we see that the maximum value is at u. So if we want to maximize p(x | u, sd = 1), we just have to make u = x.

So in this case we have:

```{R}
plotGaussian(-1,1,"red")
arrows(-1,0,-1,dnorm(-1,-1,1), col = "red")
```

But we still have one problem. We can improve the likelihood in this case decreasing the sd. If we chose a sd = 0.5, for example, we will have:

```{R}
plotGaussian(-1,0.5,"red")
arrows(-1,0,-1,dnorm(-1,-1,0.5), col = "red")
```

Actually we can always improve the likelihood by decreasing the sd in this particular case, because we just have one point.

### Likelihood of two points

### 2017-03-22 sources/Math/MaximumLikelihood.rmd
maximum likelihood pdf

@@
 ### Likelihood of two points
+
+For the likelihood of two points we are going to use the same method to find the best Gaussian distribution to explain both observations together.
+
+This means:
+
+L(theta|x) = L(theta|x1,x2) = p(x1,x2|theta)
+
+To simplify let start optimizing this function for u first. So we have:
+
+p(x1,x2|u) = p(x1|x2)p(x2) = p(x2|x1)p(x1)
+
+We generraly assume that both observations are independent because in this way we have that
+
+p(x2|x1) = p(x2)  
+p(x1|x2) = p(x1)
+
+so
+
+p(x1,x2|u) = p(x1)p(x2)
+
+This means that the we must optimize the product of the probability density function.
+
+First let plot this product value for various u values. With this plot we can clearly see that the function is optimized when the product is maximized.
+
+```{R}
+A <- -0.25  
+B <- -1
+obs <- c(A,B)
+r <- seq(-5,5, by = 0.1)
+plot(r,sapply(r, function(x) {dnorm(A, mean = x, sd = 1)}), col = "red")
+points(r,sapply(r, function(x) {dnorm(B, mean = x, sd = 1)}), col = "blue")
+points(r,sapply(r, function(x) {dnorm(A, mean = x, sd = 1)*dnorm(B, mean = x, sd = 1)}))
+arrows(A,0,A,dnorm(A,A,1), col = "red")
+arrows(B,0,B,dnorm(B,B,1), col = "blue")
+```
+
+So, first lets try to optimize the function numeracally:
+
+```{R}
+A <- -0.25  
+B <- -1
+f <- function (x) {dnorm(A, mean = x, sd = 1)*dnorm(B, mean = x, sd = 1)}
+xmax <- optimize(f, c(-5, 5), tol = 0.0001, maximum = TRUE)
+
+A <- -0.25  
+B <- -1
+obs <- c(A,B)
+r <- seq(-5,5, by = 0.1)
+plot(r,sapply(r, function(x) {dnorm(A, mean = x, sd = 1)}), col = "red")
+points(r,sapply(r, function(x) {dnorm(B, mean = x, sd = 1)}), col = "blue")
+points(r,sapply(r, function(x) {dnorm(A, mean = x, sd = 1)*dnorm(B, mean = x, sd = 1)}))
+arrows(A,0,A,dnorm(A,A,1), col = "red")
+arrows(B,0,B,dnorm(B,B,1), col = "blue")
+arrows(xmax$maximum,0,xmax$maximum,xmax$objective, col = "green")
+```
+
+So now we now that:
+L(theta|x)    
+  = L(theta|x1,x2)  
+  = p(x1,x2|theta) (for simplicity theta={u})   
+  = p(x1|x2)p(x2) for Gaussian(u,sd = 1)  
+  = p(x1)p(x2) for Gaussian(u,sd = 1)
+
+argmax(u) in p(x1)p(x2) for Gaussian(u,sd = 1)  
+  maximum at `r xmax$maximum`
+
+so the best distribution is: Gaussian(u = `r xmax$maximum`, sd = 1)

### 2017-03-23 sources/Math/MaximumLikelihood.rmd
maximum likelihood pdf

@@
 
+L(u = `r xmax$maximum`, sd = 1) = `r xmax$objective`
+
 so the best distribution is: Gaussian(u = `r xmax$maximum`, sd = 1)
+
+But we have more than one parameter to optimize. Maybe it is possible to optimize even futher the function by using other values of sd.
+
+Let try some values:
+
+```{R}
+A <- -0.25  
+B <- -1
+x = seq(-2, 1, length= 20)
+y = seq(-1, 2, length= 20)
+f = function(x, y) { dnorm(A, mean = x, sd = y)*dnorm(B, mean = x, sd = y) }
+z = outer(x, y, f)
+z[is.na(z)] = 0
+library(RColorBrewer)
+contour(x,y,z,col=rev(brewer.pal(11, "RdYlBu")), nlevels = 11)
+abline(h=1, lty=2)
+points(xmax$maximum, 1)
+```
+
+We have analyzed the problem with sd fixed as 1, and searched for the maximum likelihood in this scenario.
+If we analyze the above plot we will see that we searched the maximum following the dashed line and found it on the circled point.
+
+Now it is clear that we hace now actually found the best solution to the problem.
+
+```{R}
+A <- -0.25  
+B <- -1
+f = function(x) { dnorm(A, mean = x[1], sd = x[2])*dnorm(B, mean = x[1], sd = x[2]) }
+max = optim( c(xmax$maximum,1), f ,control=list(fnscale=-1))
+
+contour(x,y,z,col=rev(brewer.pal(11, "RdYlBu")), nlevels = 11)
+abline(h=max$par[2], v = max$par[1], lty=2)
+```
+
+OK! So now we have the best Gaussian distribution for our two observations.
+
+Gaussian
+
+L(theta|x)    
+  = L(theta|x1,x2)  
+  = p(x1,x2|theta) (theta={u,sd})   
+  = p(x1|x2)p(x2) for Gaussian(u,sd)  
+  = p(x1)p(x2) for Gaussian(u,sd)
+
+argmax(u,sd) in p(x1)p(x2) for Gaussian(u,sd)  
+  maximum at (u = `r max$par[1]`, sd = `r max$par[2]`)  
+L(u = `r max$par[1]`, sd = `r max$par[2]`) = `r max$value`
+
+So taking sd into consideration we improved out likelihood from `r xmax$objective` to `r max$value`
+
+# Likelihood Interpretation
+
+OK. We have a likelihood of `r max$value`, but what this means?
+We know that L(theta|x) = p(x|theta). So this means that we have calculated the probability of the product of two variables sampled from a distribution with the found configuration to be A*B.
+
+Let us see if this is true.
+
+```{R}
+A <- -0.25  
+B <- -1
+AB <- A * B
+samples <- rnorm(100000, mean = max$par[1], sd = max$par[2])*rnorm(100000, mean = max$par[1], sd = max$par[2])
+h <- hist(samples, freq = FALSE)
+h$counts=h$counts/sum(h$counts)
+plot(h)
+abline(v = AB, lty=2)
+```

### 2017-03-25 sources/Math/MaximumLikelihood.rmd
intro to olavos work

@@
 AB <- A * B
-samples <- rnorm(100000, mean = max$par[1], sd = max$par[2])*rnorm(100000, mean = max$par[1], sd = max$par[2])
-h <- hist(samples, freq = FALSE)
-h$counts=h$counts/sum(h$counts)
-plot(h)
-abline(v = AB, lty=2)
+samples <- rnorm(100000, mean = max$par[1], sd = max$par[2])/max$par[2]*rnorm(100000, mean = max$par[1], sd = max$par[2])/max$par[2]
+hist(samples, freq = FALSE, breaks = 50)
+abline(v = AB / max$par[2], lty=2)
 ```

### 2017-03-25 texts/philosophy/introolavo.tex
intro to olavos work

\documentclass[10pt,a4paper]{book}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\begin{document}
	\title{Introduction to Olavo de Carvalho´s Work}
	\author{Daniel Frederico Lins Leite}

	\maketitle

	\tableofcontents

	\chapter{Introduction}
	\section{Moral Basis for Philosophy}
	\subsection{Sincerity}
	\subsection{Love}
	\subsection{Science}
	\section{Idea versus Reality}
	\subsection{Reality}
	\subsection{Idea}
	\section{Philosopher Maturity}
	\subsection{Impression of Reality}
	\subsubsection{Senses}
	\subsubsection{Limited Structure of the Reality}
	\subsection{Unification}
	\subsubsection{Reality Unification}
	\subsubsection{Conscience Unification}
	\subsubsection{12 layers of personality}
	\subsubsection{Cognitive Parallax}
	\subsection{Expression of Reality}
	\subsubsection{4 modes of discourses}
	\subsubsection{Poetic}
	\subsubsection{Rhetoric}
	\subsubsection{Dialectic}
	\subsubsection{Logic}

	\chapter{Applications}
	\section{Philosophy}
	\subsection{Status Quo}
	\subsection{History of the History of Philosophy}
	\subsection{Greek Philosophy}
	\subsection{Christian Philosophy}
	\subsection{Muslim Philosophy}
	\subsection{Modern Philosophy}
	\subsection{Current Philosophy}
	\section{Politics}
	\subsection{Status Quo}
	\subsection{Inversion of the Evolution of the State}
	\subsection{Conscience of Transcendent}
	\subsection{Messianic Discourse}
	\subsection{Revolutionary Mentality}
	\section{Science}
	\subsection{Status Quo}
	\subsection{Inversion of Modern Cosmological Views}
\end{document}

### 2017-03-30 texts/dev/PapersILove.tex
development material

\documentclass{article}
\usepackage{hyperref}

\begin{document}

\title{Papers I Love}
\author{Daniel Frederico Lins Leite}

\maketitle

\tableofcontents

\section{Computer Science}

\subsection{Algorithms}

\subsubsection{Analysis}
\begin{enumerate}
	\item {Recursive Algorithms in Computer Science Courses: Fibonacci Numbers and Binomial Coefficients\\
\url{http://venus.cs.qc.edu/~waxman/cs211%20spring%202009/why%20is%20recursive%20fibonacci%20so%20slow.pdf}}
	\item {Binomial Coefﬁcient Computation: Recursion or Iteration?\\
\url{http://delab.csd.auth.gr/papers/SBI02m.pdf}}

\end{enumerate}

\subsubsection{Compression}
\begin{enumerate}
\item {Data Compression Using Long Common Strings\\
\url{http://www.cs.brandeis.edu/~dilant/cs175/%5BSiying-Dong%5D.pdf}}
\end{enumerate}

\subsubsection{Hash}
\begin{enumerate}
	\item {SHA-1 and the Strict Avalanche Criterion\\
\url{https://arxiv.org/pdf/1609.00616.pdf}}
\end{enumerate}

\subsubsection{Data Structures}
\begin{enumerate}
\item {Bitlist New Full-Text Index for Low Space Cost and Efficient Keyword Search\\
\url{http://www.vldb.org/pvldb/vol6/p1522-rao.pdf}}
\end{enumerate}

\subsubsection{Elections + Consensus}
\begin{enumerate}
	\item {Elections in a Distributed Computing System\\
\href{http://academic.research.microsoft.com/Publication/716253/elections-in-a-distributed-computing-system}{http://academic.research.microsoft.com/Publication/716253/elections-in-a-distributed-computing-system}\\
\url{http://homepage.cs.uiowa.edu/~ghosh/Bully.pdf}}
	\item {The Part-Time Parliament\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/lamport-paxos.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/lamport-paxos.pdf}}
	\item {In Search of an Understandable Consensus Algorithm\\
\href{https://ramcloud.atlassian.net/wiki/download/attachments/6586375/raft.pdf}{https://ramcloud.atlassian.net/wiki/download/attachments/6586375/raft.pdf}}
\end{enumerate}

\subsection{Architectures}

\subsubsection{Computer Architecture}
\begin{enumerate}
	\item {Quantifying the Cost of Context Switch\\
\url{http://www.cs.rochester.edu/u/cli/research/switch.pdf}}
	\item {What Every Programmer Should Know About Memory\\
\url{https://people.freebsd.org/~lstewart/articles/cpumemory.pdf}}
\end{enumerate}

\subsubsection{Multi Tenancy}
\begin{enumerate}
	\item {Enabling Multi-Tenancy an Industrial Experience Report\\
\href{http://swerl.tudelft.nl/twiki/pub/Main/TechnicalReports/TUD-SERG-2010-030.pdf}{http://swerl.tudelft.nl/twiki/pub/Main/TechnicalReports/TUD-SERG-2010-030.pdf}}
	\item {Multi-Tenant Saas Applications: Maintenance Dream or Nightmare\\
\href{http://swerl.tudelft.nl/twiki/pub/Main/TechnicalReports/TUD-SERG-2010-031.pdf}{http://swerl.tudelft.nl/twiki/pub/Main/TechnicalReports/TUD-SERG-2010-031.pdf}}
	\item {Towards an Elastic and Autonomic Multitenant Database\\ \url{http://research.microsoft.com/en-us/um/people/srikanth/netdb11/netdb11papers/netdb11-final8.pdf}}
\end{enumerate}

\subsubsection{REST}
\begin{enumerate}
	\item {Architectural Styles and the Design of Network-Based Software Architectures\\
\href{http://academic.research.microsoft.com/Publication/1309313/architectural-styles-and-the-design-of-network-
	based-software-architectures}{http://academic.research.microsoft.com/Publication/1309313/architectural-styles-and-the-design-of-network-
	based-software-architectures}\\
\url{http://www.ics.uci.edu/~fielding/pubs/dissertation/top.htm}}
\end{enumerate}

\subsubsection{SEDA}
\begin{enumerate}
	\item {An Architecture for Highly Concurrent, Well-Conditioned Internet Services\\
\href{http://academic.research.microsoft.com/Publication/112151/seda-an-architecture-for-well-conditioned-scalable-internet-services}{http://academic.research.microsoft.com/Publication/112151/seda-an-architecture-for-well-conditioned-scalable-internet-services}\\
\url{http://www.eecs.harvard.edu/~mdw/papers/mdw-phdthesis.pdf}}
\end{enumerate}

\subsubsection{Servers}
\begin{enumerate}
	\item {Flash an Efficient and Portable Web Server\\
\url{https://www.usenix.org/event/usenix99/full_papers/pai/pai.pdf}}
\end{enumerate}

\subsubsection{Other Architectures}
\begin{enumerate}
	\item {The Monad Manifesto\\
\url{http://www.jsnover.com/Docs/MonadManifesto.pdf}}
	\item {The Hla Tutorial\\
\url{http://www.pitch.se/hlatutorial}}
\end{enumerate}

\subsubsection{Patterns}
\begin{enumerate}
	\item {Active Object: An Object Behavioral Pattern for Concurrent Programming\\
\url{http://www.cs.wustl.edu/~schmidt/PDF/Act-Obj.pdf}}
	\item {Plop Half-Sync/half-Async: An Architectural Pattern for Efficient and Well-Structured Concurrent I/o\\
\url{http://www.cs.wustl.edu/~schmidt/PDF/PLoP-95.pdf}}
\end{enumerate}

\subsubsection{Overlay Networks}
\begin{enumerate}
	\item {Architectures for an Event Notification Service Scalable to Wide-Area Networks\\
\href{http://academic.research.microsoft.com/Publication/314658/architectures-for-an-event-notification-service-scalable-to-wide-area-networks}{http://academic.research.microsoft.com/Publication/314658/architectures-for-an-event-notification-service-scalable-to-wide-area-networks}\\
\url{http://www.inf.usi.ch/carzaniga/papers/phd_thesis.pdf}}
\end{enumerate}

\subsubsection{Distributed Systems}
\begin{enumerate}
	\item {Time, Clocks and the Ordering of Events in a Distributed System\\		
\href{http://academic.research.microsoft.com/Publication/775212/time-clocks-and-the-ordering-of-events-in-a-distributed-system}{http://academic.research.microsoft.com/Publication/775212/time-clocks-and-the-ordering-of-events-in-a-distributed-system}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html#time-clocks}{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html\#time-clocks}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}}
	\item {Distributed Snapshots: Determining Global States of Distributed Systems\\
\href{http://academic.research.microsoft.com/Publication/803548/distributed-snapshots-determining-global-states-of-distributed-systems}{http://academic.research.microsoft.com/Publication/803548/distributed-snapshots-determining-global-states-of-distributed-systems}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html#chandy}{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html\#chandy}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/chandy.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/chandy.pdf}}
	\item {Your Coffee Shop Doesn’t Use Two-Phase Commit\\
\href{http://www.enterpriseintegrationpatterns.com/docs/IEEE_Software_Design_2PC.pdf}{http://www.enterpriseintegrationpatterns.com/docs/IEEE\_Software\_Design\_2PC.pdf}}
	\item {A Brief History of Process Algebra\\
\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
	\item {Life Beyond Distributed Transactions: An Apostate’s Opinion\\
\url{http://www.ics.uci.edu/~cs223/papers/cidr07p15.pdf}}
\end{enumerate}

\subsubsection{Event Based Architecture}
\begin{enumerate}
	\item {Design of a Scalable Event Notification Service Interface and Architecture\\
\href{http://academic.research.microsoft.com/Publication/312680/design-of-a-scalable-event-notification-service-interface-and-architecture}{http://academic.research.microsoft.com/Publication/312680/design-of-a-scalable-event-notification-service-interface-and-architecture}\\
\url{http://www.inf.usi.ch/carzaniga/papers/CU-CS-863-98.pdf}}
	\item {Fast Forwarding for Content-Based Networking\\
\href{http://academic.research.microsoft.com/Publication/7217/fast-forwarding-for-content-based-networking}{http://academic.research.microsoft.com/Publication/7217/fast-forwarding-for-content-based-networking}\\
\href{http://www.inf.usi.ch/carzaniga/papers/cucs-922-01-r1.pdf}{http://www.inf.usi.ch/carzaniga/papers/cucs-922-01-r1.pdf}}
	\item {Real-Time Modelling of Dds for Event-Driven Applications\\
\url{http://www.ctr.unican.es/publications/hpt-jjg-2012a.pdf}}
\end{enumerate}

\subsubsection{Resiliency}
\begin{enumerate}
	\item {Adaptive Overload Control for Busy Internet Servers\\
\href{http://academic.research.microsoft.com/Publication/634136/adaptive-overload-control-for-busy-internet-servers}{http://academic.research.microsoft.com/Publication/634136/adaptive-overload-control-for-busy-internet-servers}\\
\url{http://www.eecs.harvard.edu/~mdw/papers/control-usits03.pdf}}
\end{enumerate}

\subsection{Programming Paradigms}
\subsubsection{Object Oriented}
\begin{enumerate}
	\item {A Theory of Objects\\
\url{http://academic.research.microsoft.com/Publication/1354440/a-theory-of-objects}\\
\url{http://lucacardelli.name/Talks/1997-06\%20A\%20Theory\%20of\%20Object\%20(ECOOP\%20Tutorial).pdf}}
	\item {Traits: Composable Units of Behaviour\\
\url{http://scg.unibe.ch/archive/papers/Scha03aTraits.pdf}}
	\item {Applying Traits to the Smalltalk Collection Hierarchy\\
\url{http://www.researchgate.net/publication/2564879_Applying_Traits_to_the_Smalltalk_Collection_Hierarchy}}
	\item {A Laboratory for Teaching Object-Oriented Thinking\\
\url{http://www.inf.ed.ac.uk/teaching/courses/seoc/2007_2008/resources/CRC_OOthinking.pdf}}
\end{enumerate}
\subsubsection{Double Dispatch}
\begin{enumerate}
	\item {Design and evaluation of C++ open multi-methods\\
\url{https://parasol.tamu.edu/~yuriys/papers/OMM10.pdf}}
\end{enumerate}

\subsection{Database}
\begin{enumerate}
	\item {The Ubiquitous B-Tree\\
\url{http://people.cs.aau.dk/~simas/aalg06/UbiquitBtree.pdf}}
	\item {Generalized Search Trees for Database Systems\\
\url{http://db.cs.berkeley.edu/papers/vldb95-gist.pdf}}
	\item {Concurrency and Recovery in Generalized Search TreeS\\
\url{http://db.cs.berkeley.edu/papers/sigmod97-gist.pdf}}
	\item {Data Cube: A Relational Aggregation Operator Generalizing Group-By, Cross-Tab, and Sub-Totals\\
\url{http://research.microsoft.com/pubs/69578/tr-95-22.pdf}}
	\item {Query Optimization in Microsoft Sql Server PDW\\
\href{http://academic.research.microsoft.com/Publication/56916436/query-optimization-in-microsoft-sql-server-pdw}{http://academic.research.microsoft.com/Publication/56916436/query-optimization-in-microsoft-sql-server-pdw}}
	\item {Druid: A Real-Time Analytical Data Store
\url{http://static.druid.io/docs/druid.pdf}}
	\item {Map-Reduce: Simplified Dataprocessing on Large Clusters\\
\url{http://static.googleusercontent.com/media/research.google.com/en/us/archive/mapreduce-
	osdi04.pdf}}
	\item {Google’s Mapreduce Programming Model — Revisited\\
\url{http://www.idt.mdh.se/kurser/cd5100/ht06/MapReduce/Ralf-Laemmel-paper/paper.pdf}}
	\item {Cassandra - a Decentralized Structured Storage System\\
\url{http://www.cs.cornell.edu/projects/ladis2009/papers/lakshman-ladis2009.pdf}}
	\item {Bigtable: A Distributed Storage System for Structured Data\\
\url{http://static.googleusercontent.com/media/research.google.com/en//archive/bigtable-osdi06.pdf}}
	\item {Dynamo: Amazon’s Highly Available Key-Value Store\\
\url{http://s3.amazonaws.com/AllThingsDistributed/sosp/amazon-dynamo-sosp2007.pdf}}
	\item {Solving Big Data Challenges for Enterprise Application Performance Management\\
\url{http://vldb.org/pvldb/vol5/p1724_tilmannrabl_vldb2012.pdf}}
\end{enumerate}

\subsection{Data Fusion}
\begin{enumerate}
	\item {A Generic Architecture for Fusion-Based Intrusion Detection Systems\\
\url{https://rcdeboer.home.xs4all.nl/rcdb_thesis.pdf}}
\end{enumerate}

\section{Mathematics}
\subsection{Real Analysis}
\begin{enumerate}
	\item {COISAS QUE O LUÍS PRECISA APRENDER\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
\end{enumerate}

\section{Economy}
\subsection {Political Economy}
\subsubsection{Taxes}
\begin{enumerate}
	\item {The Laffer Curve Past, Present, and Future\\
\url{http://s3.amazonaws.com/thf_media/2004/pdf/bg1765.pdf}}
	\item {Dynamic Revenue Estimation\\
\url{https://ideas.repec.org/a/aea/jecper/v10y1996i1p141-57.html}}
	\item {Dynamic Scoring an Introduction to the Issues\\
\url{https://www.aeaweb.org/annual_mtg_papers/2005/0107_1430_1304.pdf}}
\end{enumerate}

\end{document}

### 2017-04-01 texts/math/Handout.Series.tex
moving math files

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel} 
\usepackage{amsmath,amssymb,amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\title{Mathematics Handout - Logaritmics}
\author{Daniel Frederico Lins Leite}
\date{July 2016}
\begin{document}
\section{Introduction}
\maketitle

\[{x_n}\] is a sequence of real numbers
Th sequence converge if:
$$\exists a \in Re$$
$$\exists \epsilon \in R such that \epsilon > 0$$
$$\exists N_a \in I such that N_a > 0$$
$$\forall n > N_a, |a - x_n| < \epsilon$$

if for example exists another 
$$\exists b \in Re$$ such that
$$\exists N_b \in I such that N_b > 0$$
$$\forall n > N_b, |b - x_n| < \epsilon$$

then

$$|a-b| = |a - x_n + x_n - b|$$

Given that the $$R^n$$, the space of the elements of the sequence is a normed vector space, we can apply the Triangle Inequality. So

$$|a - x_n + x_n - b| <= |a - x_n| + |x_n - b|$$

given that $$|x_n - b|$$ is a even function
$$f(x) = f(-x)$$ we have that
$$|x_n - b| = -1 * |x_n - b| = |-x_n + b| = |b - x_x|$$

so we have

$$|a - x_n| + |x_n - b| < |a - x_n| + |b - x_n| <= \epsilon + \epsilon <= 2\epsilon$$

So

$$ 0 <= |a - b| <= 2\epsilon$$

So $|a-b|$ is squeezed between this two function. Given that this is true for every $\epsilon$, if $\epsilon -> 0$
we will have that:
$$|a-b| = 0$$ and $$a=b$$

The value a is called the limit of the sequence.

The

$$S = \sum_{i=0}^{\inf} {x_i}$$ is called the series associated with se sequence.

The partial sum is

$$S_n = \sum_{i=0}^{n} {x_i}$$

So

${S_n}$ is also a sequence. In the same way it can converge and have a limit.
If the sequence converge, we say that the series converge and that the limit is

$$limit of {S_n} =  \sum_{i=0}^{\inf} {x_i}$$

If we have two convergent series:

$$S_1 = \sum_{i=0}^{\inf} {a_i}$$
$$S_2 = \sum_{i=0}^{\inf} {b_i}$$

then

$$\sum_{i=0}^{\inf} {(a_i + b_i)} = \sum_{i=0}^{\inf} {a_i} + \sum_{i=0}^{\inf} {b_i}$$

\end{document}

### 2017-04-01 texts/math/MITOpenCourseWare/Calculus/Lecture001.tex
moving math files

\documentclass{article}
\title{MITOpenCourseWare - Lecture 1}
\author{Daniel Frederico Lins Leite}
\date{September 2016}
\begin{document}
\maketitle

1 - Move the red slider to x = −0.75; we’ll investigate the slopes of secant lines passing through the point (−0.75,f(−0.75)).
(a) Use the yellow slider to find the value of Δy when x = −0.75 and Δx Δx has each of the following values: −0.5, −0.25, 0.25, 0.5.

\[
-0.50 = 0.56
-0.25 = 0.18
0.25 = -0.39
0.50 = -0.58
\]

(b) Use the Tangent checkbox to find the (approximate) slope of the tangent line to the graph of f(x) at x = −0.75.

slope is $$-0.14$$

(c) Find a value of Δx for which the value of Δy/Δx
is within 0.1 units of Δx the slope of the tangent line.

when $$\delta x < 0.01$$

2 - Now use the red slider to set x = 0.
(a) Find Δy when x = 0 and Δx has the values: 
Δx

\[
−0.5 = 0.44
−0.25 = 0.2425
0.25 = -0.2425
0.5 = -0.44
\]

(b) Find the slope of the tangent line to the graph of f(x) at x = 0.

slope is $$-1$$

(c) Find a value of Δx for which the value of Δy is within 0.1 units of Δx the slope of the tangent line.

when $$\delta x < 0.01$$

3 - Let x = 0.75. Δy 
(a) Find Δy/Δx when x = 0.75 and Δx has the values:
\[
−0.5 = -0.59
−0.25 = -0.41
0.25 = 0.16
0.5 = 0.53
\]
(b) Find the slope of the tangent line to the graph of f(x) at x = 0.75.

when slope is $$-0.16$$

(c) Find a value of Δx for which the value of Δy is within 0.1 units of Δy/Δx the slope of the tangent line.

$$0.01$$

4. Compare your answers to the previous problems.
(a) Was your answer to part (c) the same for each problem?

yes

(b) For some values of x, Δx was close to the slope of the tangent line when Δx was 0.5. For others it was not. Can you make any conjec­tures about when you need a very small value of Δx in order for Δy/Δx to be close to the slope of the tangent line?

You need very small values when the function is "very different" around the point. If for example the function is very similar to a linear function the Δx can be bigger.

\end{document}

### 2017-04-02 texts/philosophy/introolavo.tex
olavo intro
resumo curso teoria do estado

@@
 	\subsection{Status Quo}
+	\subsection{Scientist versus Agent}
 	\subsection{Inversion of the Evolution of the State}
+	Aula 1
+	O que é Conceito
+	O que é Símbolo Auto-explicativo
+	Cinco Funções da Idéia
+	1 - Descrição da Realidade
+	2 - Símbolos Auto-Justificadores
+	3 - Influenciar outras pessoas
+	4 - Influenciar a si próprio
+	5 - Transmitir ao outro uma imagem do que ele pensa que é
+
+	Centro da Ciência Política: Origem e Natureza das Justificações das Instituições de Poder que permitem a existência de uma sociedade
+
+	Teoria do Goverbo = Anglo-Saxão
+	Teoria do Estado = Germânico
+	Ciência Política = Francesa
+
+	Dizem que Maquiavel foi o primeiro a dar uma descrição da realidade, porém Maquiavel fez um projeto político e não um estudo científico do estado como ele o encontrou na realidade.
+
+	Aula 2
+	Estado não é um fenômeno primário
+	Estado é um fenômeno secundário, uma modalidade
+
+	Fenômeno primário é reconhecido apenas por descrição
+
+	Rede de relações humanas se dá através da linguagem
+	Início da sociedade humana é através da ordem dada. O tempo imperativo. O imperativo existe em todas as linguas. Animais não dão ordem.
+
+	Imperativo demanda uma relação temporal e espacial. Até mesmo um "por favor" é uma ordem.
+
+	Organização Social é um sistema de ordem que possui retorno garantido (obediência garantida). Ele estabelece a curva de tempo. Esta obediência necessita uma promessa de lealdade.
+
+	Esta ordem não pode ser dada na base da força apenas, ela necessita da lealdada. Para isso será necessário o fascínio.
+
+	A obediência não pode ser dada pela supremacia física pois esta é transitória. Autoridade surge do fascínio que tem que formar numa relação de mando.
+
+	Segundo Eric Voegelin a História da Ordem é a própria Ordem da História.
+	A consciência é ela mais um dos fatos da realidade.
+	Segundo Schelling, o homem não é só um observador, mas é parte do universo. Não posso me colocar de fora do universo para observá-lo. Participação Anamnética.
+
+	Aula 3
+	Camadas de Significado. Focar na experiência e não nas palavras.
+	A experiência do Faraó e a interpretação moderna que se dá para as palavras/experiência do Faraó.
+
+	Por exemplo, o discurso do Faraó que o identificava como a própria divindade era na verdade um discurso ideológico.
+Ou como tentamos entender a ordem social do Faraó como uma forma de Estado.
+Quando na verdade deveríamos entender o Estado como uma ordem social.
+
+	Isso acontece muita vezes pois todos somos educados numa estrutura onde as disciplinas já estão separadas e organizadas de certo modo.
+E quando o aluno depois de muito esforço para dominar um ou mais campos já se ve preso dentro deste modelo.
+
+	Ordem Cosmológica
+	Não havia de um lado o estado do Faraó montado e de outro uma série de mitos criados apenas para sua legitimização ideologica existência do Faraó ou do Estado.
 	\subsection{Conscience of Transcendent}

### 2017-04-02 sources/course-edx-datamining/hw2_classification.py

@@ -24,23 +24,22 @@ YtrainM = numpy.loadtxt(open(ytrain, "rb"), dtype=numpy.int64, delimiter=",", sk
 XtestM = numpy.loadtxt(open(xtest, "rb"), delimiter=",", skiprows=0)
 
 #class prior probabilities 
-pihatCount = numpy.size(YtrainM)
-pihat = numpy.divide(numpy.bincount(YtrainM), pihatCount)
+YtrainMCount = numpy.size(YtrainM)
+def classpercentage(k):
+    indices = numpy.where(YtrainM == k)
+    yk = YtrainM[indices]
+    count = numpy.size(yk)
+    return (count * 1.00) / (YtrainMCount * 1.00)
+pihat = {k:classpercentage(k) for k in numpy.unique(YtrainM)}
 
 #class specific MLE estimate
 def mle(k):
     indices = numpy.where(YtrainM == k)
     xk = XtrainM[indices]
-    xksize = numpy.size(xk, axis=0)
-    muhatml = numpy.mean(xk, axis=0)
-    def sigmahatmlsummationitem(xi):
-        ximinusmuhatml = numpy.matrix(xi - muhatml)
-        return numpy.dot(numpy.transpose(ximinusmuhatml),ximinusmuhatml)
-    def sigmahatml():
-        items = [sigmahatmlsummationitem(xk[i]) for i in range(0,xksize)]
-        itemssum = numpy.sum(items, 0)
-        return itemssum * (1.0/xksize)
-    return [muhatml,sigmahatml()]
+    muhat = numpy.mean(xk, axis=0)
+    centeredxk = xk - muhat
+    sigmahat = numpy.dot(numpy.transpose(centeredxk), centeredxk)
+    return [muhat, numpy.mean(sigmahat, axis=0)]
 
 classes = numpy.unique(YtrainM) 
 mlEstimates = {k:mle(k) for k in classes}
@@ -55,11 +54,15 @@ def pofxgivenmuandsigma(x,mu,sigma):
 
 #predict
 def pforeachclass(i):
-    return [pofxgivenmuandsigma(XtestM[i], muhat(k),sigmahat(k))
+    return [pofxgivenmuandsigma(XtestM[i], muhat(k),sigmahat(k))*pihat[k]
             for k in classes]
+def normalizepofeachclass(ps):
+    #sumps = numpy.sum(ps)
+    #return ps / sumps;
+    return ps
 
 XtestMRows = numpy.size(XtestM, axis=0)
[…]

### 2017-04-03 texts/dev/PapersILove.tex
process algebra paper
j armstrong paper on forecasting
process algebrapaper

@@
 \href{http://www.enterpriseintegrationpatterns.com/docs/IEEE_Software_Design_2PC.pdf}{http://www.enterpriseintegrationpatterns.com/docs/IEEE\_Software\_Design\_2PC.pdf}}
+	\item {Life Beyond Distributed Transactions: An Apostate’s Opinion\\
+\url{http://www.ics.uci.edu/~cs223/papers/cidr07p15.pdf}}
+\end{enumerate}
+
+\subsubsection{Process Algebra}
+\begin{enumerate}
 	\item {A Brief History of Process Algebra\\
 \url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
-	\item {Life Beyond Distributed Transactions: An Apostate’s Opinion\\
-\url{http://www.ics.uci.edu/~cs223/papers/cidr07p15.pdf}}
+	\item {Some of My Favourite Results in Classic Process Algebra (Version of September 9, 2003)\\
+\url{https://www.researchgate.net/publication/228785318_Some_of_My_Favourite_Results_in_Classic_Process_Algebra_Version_of_September_9_2003}}
 \end{enumerate}
@@
 \subsection{Programming Paradigms}
+\subsubsection{Process Theory}
+\begin{enumerate}
+	\item {A Brief History of Process Algebra\\
+\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
+\end{enumerate}
 \subsubsection{Object Oriented}
@@
 \end{enumerate}
+\subsection{Forecast}
+\begin{enumerate}
+	\item {Forecasting Global Climate Change\\
+\url{https://faculty.wharton.upenn.edu/wp-content/uploads/2015/02/GlobalClimateChange-FWP-(2)_2.pdf}}
+\end{enumerate}
 

### 2017-04-19 texts/dev/PapersILove.tex
reactive system paper
Design Patterns for Generic Programming in C++

@@
 \url{https://www.researchgate.net/publication/228785318_Some_of_My_Favourite_Results_in_Classic_Process_Algebra_Version_of_September_9_2003}}
+	\item {Reactive Systems: Modelling, Speciﬁcation and Veriﬁcation\\
+\url{https://www.semanticscholar.org/paper/Reactive-Systems-Modelling-Specification-and-Aceto-Larsen/454e1c72efc65270649e10efb11f4390606b7ea7}}
 \end{enumerate}
@@
 \subsubsection{Resiliency}
+
 \begin{enumerate}
@@
 \end{enumerate}
-\subsubsection{Double Dispatch}
+
+\subsubsection{Generic Programming}
+	\begin{enumerate}
+	\item {Design Patterns for Generic Programming in C++\\ \url{https://www.lrde.epita.fr/dload/papers/coots01.htmls}}
+	\end{enumerate}
+\subsubsection{Dynamic Dispatch}
 \begin{enumerate}

### 2017-04-29 texts/math/TheElementsofStatisticalLearning.exercises.tex
naive bayes classifier analitically boundary

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{bbm}
\author{Daniel Frederico Lins Leite}
\begin{document}
	\section{Exercise 2.1}
	Suppose each of K classes has an associated target $t_k$, which is a vector of all zeros, except a one in the k-th position. Show that classifying to the largest element of \^{y} amounts to choosing the closest target, $argmin_k ||t_k - \hat{y}||$, if the elements of \^{y} sum to one.

	\subsection{Interpretation}
	This problem can be interpreted as a "target coding scheme". This specific target coding is can be found in the following papers:

	\url{http://ieeexplore.ieee.org/document/88570/}\\
	\url{https://www.researchgate.net/publication/3191927_Optimized_feature_extraction_and_the_Bayes_decision_in_feed-forwardclassifier_networks}
	\begin{quote}
		This may be viewed as a gain matrix in which the gain of
		assigning to class j a pattern which belongs to class i is zero
		($i \ne j$) , but is unity for correct classification.
	\end{quote}

	\url{http://personal.ie.cuhk.edu.hk/~ccloy/files/aaai_2015_target_coding.pdf}
	\begin{quote}
		The 1-of-K coding, containing vectors of length K, with the k-th element as one and the remaining zeros, is typically used along with a softmax function for classification. Each element in a 1-of-K code represents a probability of a specific class. 
	\end{quote}

	This paper also contains a more general definition of target coding, but it is not necessary for this exercise.

	Following, we can say that:

	\begin{align*}
		t = \left[ \begin{array}{c}
		t_1 \\
		t_2 \\
		\vdots \\
		t_K \end{array} \right] = \left[ \begin{array}{cccc}
		1 & 0 & \dots & 0 \\
		0 & 1 & \dots & 0 \\
		\vdots & \vdots & \ddots & \vdots \\
		0 & 0 & \dots & 1 \end{array} \right]
	\end{align*}

	In the problem, $\hat{y}$ can be considered as the prediction of a vector $x$ such that $y_k$ is the probability of $x$ being of the class $k$. That is why the sum of $y_k$ is equal to $1$.This also demands that $y_k$ are greater than $0$, although this does not make difference for this particular exercise.

	And now we arrive to the proof part: the k in which the $\hat{y}_k$ is the greatest, the class that we would choose in our prediction is the same $k$ of the $t_k$ that is nearer to the $\hat{y}$. In mathematical symbols:

	\begin{align*}
		\arg\min_k ||\hat{y}-t_k||\\
	\end{align*}

	\subsection{Solution}

	\begin{align*}
		K &> 0\\
		\\
		x &\in \Re^N\\
		y &= f(x)\\
		&	\sum_{i=1}^{K}{y_i} = 1\\
		&	y_i \ge 0, i \in {1,...,K}\\
		\\
		1 &\ge k \ge K\\
		t_k &= (t_{k1},...,t_{ki},...,t_{kK}), t_{ki} = \begin{cases}
			0 &\mbox{if } i \neq k\\
			1 &\mbox{if } i = k
		\end{cases}
		\\
		\arg\min_k||t_k - \hat{y}|| &= \arg\min_k||y-t_k||^2\\
		&= \arg\min_k\sum_{i=1}^{K}{(y_i-t_{ki})}^2\\
		&= \arg\min_k\sum_{i=1}^{K}{(y_{i}^2-2y_{i}t_{ki}+t_{ki}^2)}\\
		&= \arg\min_k\big[\sum_{i=1}^{K}{y_{i}^2}+\sum_{i=1}^{K}{(-2y_{i}t_{ki}+t_{ki}^2)}\big]
	\end{align*}
	Since $\sum_{i=1}^{K}{y_{i}^2}$ is a constant and does not depend on k
	\begin{align*}
		&= \arg\min_k \sum_{i=1}^{K}{(-2y_{i}t_{ki}+t_{ki}^2)}\\
		&= \arg\min_k\big[\sum_{i=1}^{K}{(-2y_{i}t_{ki})}+\sum_{i=1}^{K}{t_{ki}^2}\big]\\
	\end{align*}
	Since $\sum_{i=1}^{K}{t_{ki}^2} = 1$
	\begin{align*}
		&= \arg\min_k\big[\sum_{i=1}^{K}{(-2y_{i}t_{ki})}+1\big]
	\end{align*}
	Since $\sum_{i=1}^{K}{y_{i}t_{ki}} = y_k$, because $t_k$ is zero in all but $i=k$ position.
	\begin{align*}
		&= \arg\min_k\big[-2*\sum_{i=1}^{K}{y_{i}t_{ki}}+1\big]\\
		&= \arg\min_k\big[-2y_k+1\big] &&\mbox{(argmax plus constant)}\\
		&= \arg\min_k\big[-2y_k\big] &&\mbox{(argmax times constant)}\\
		&= \arg\min_k\big[-y_k\big] &&\mbox{(argmax inverse argmin)}\\
		&= \arg\max_k\big[y_k\big] &&\mbox{(argmax inverse argmin)}
	\end{align*}

	Which give us that:
	\begin{align*}
		\arg\min_k ||\hat{y}-t_k|| &= \arg\max_k\big[y_k\big]
	\end{align*}

	This problem can be interpreted as the proof of why in book the author says:
	\begin{quote}
		With the 0-1 loss function [...] the solution is known as the Bayes classifier, and says that
		we classify to the most probable class, using the conditional (discrete) distribution $Pr(G|X)$.
	\end{quote}

	\section{Exercise 2.2}

	From the previous exercise, we know that the Bayes Classifier, will classify the point to the most probable class. So, the boundary is located exactly where there is no clear most probable class. 
	To simplify let us imagine that we have just 2 classes.

	\begin{align*}
		P(K_1|X) = P(K_2|X)\\
		\frac{P(K_1,X)}{P(X)} = \frac{P(K_2,X)}{P(X)}\\
		\frac{P(X|K_1)P(K_1)}{P(X)} = \frac{P(X|K_2)P(K_2)}{P(X)}\\
	\end{align*}

	$P(X|K_i)$ is the same as the likelihood of seeing X using a generative model from the i-th class. If we suppose that all classes come from a Gaussian Distribution, this simplify to:

	\begin{align*}
		\frac{\mathcal{L}(\theta_1|X)P(K_1)}{P(X)} = \frac{\mathcal{L}(\theta_2|X)P(K_2)}{P(X)}\\
	\end{align*}

	To calculate $P(X)$ we can marginalize $X$ over all possibilities, in this case two, so:

	\begin{align*}
		P(X) &= \sum_{k\in K}{P(X|K=k)}\\
		&= \sum_{k\in K}{\mathcal{L}(\theta_k|X)}
	\end{align*}

	So now we have:

	\begin{align*}
		\frac{P(X|K_1)P(K_1)}{\sum_{k\in K}{\mathcal{L}(\theta_k|X)}} = \frac{P(X|K_2)P(K_2)}{\sum_{k\in K}{\mathcal{L}(\theta_k|X)}}\\
	\end{align*}

	But we can simplify it.

	\begin{align*}
		P(X|K_1)P(K_1) = P(X|K_2)P(K_2)\\
	\end{align*}

	We can do the same for $P(K_1)$

	\begin{align*}
		P(K_1) &= \int_{x\in X}{P(K_1|X)P(dx)}\\
		&= \int_{x\in X}{P(K_1|X)P(dx)}\\
		&= \int_{x\in X}{\mathcal{L}(X|\theta_1)P(dx)}
	\end{align*}

	Which give us the final formula:

	\begin{align*}
			P(X|K_1)\int_{x\in X}{\mathcal{L}(X|\theta_1)P(dx)} = P(X|K_2)\int_{x\in X}{\mathcal{L}(X|\theta_2)P(dx)}\\
	\end{align*}

	The first possible simplification is to estimate $P(K_i)$ and two possible ways:
	- First, we can say that they both have the same probability;
	- Second, if we have a dataset we can calculate them by
	\begin{align*}
		P(K_1) = \frac{\sum_{y_i\in Y}{\mathbbm{1}(y_i = k_1)}}{N}\\
		P(K_2) = \frac{\sum_{y_i\in Y}{\mathbbm{1}(y_i = k_2)}}{N}\\
	\end{align*}

	Equal Prior Distributions:

	In this case the equality can be simplified to

	\begin{align*}
	P(X|K_1) = P(X|K_2)\\
	\end{align*}

	For futher simplification we can imagine a two dimensional X:

	\begin{align*}
	P(x_1,x_2|K_1) = P(x_1,x_2|K_2)\\
	\end{align*}

	if we choose another simplification, that x1 and x2 and independent, we arrive at a Naive Bayer Classifier, and the equation become:

	\begin{align*}
	P(x_1|K_1)P(x_2|K_1) = P(x_1|K_2)P(x_2|K_2)
	\end{align*}

	with two classes and Gaussian distribution:
	Different mean, same variance = line/plane
	Same mean, different variance = circle/elipse
	general case = parabolic curve

	with more than two cases will be a piecewise combination of the above three cases.

	\begin{align*}
(\frac{1}{\sqrt{2\pi\sigma_1^2}}e^{-\frac{(x_1-\mu_1)^2}{2\sigma_1^2}})(\frac{1}{\sqrt{2\pi\sigma_1^2}}e^{-\frac{(x_2-\mu_1)^2}{2\sigma_1^2}}) &= (\frac{1}{\sqrt{2\pi\sigma_2^2}}e^{-\frac{(x_1-\mu_2)^2}{2\sigma_2^2}})(\frac{1}{\sqrt{2\pi\sigma_2^2}}e^{-\frac{(x_2-\mu_2)^2}{2\sigma_2^2}})\\
(\frac{1}{\sqrt{2\pi\sigma_1^2}})^2(e^{-\frac{(x_1-\mu_1)^2}{2\sigma_1^2}})(e^{-\frac{(x_2-\mu_1)^2}{2\sigma_1^2}}) &= (\frac{1}{\sqrt{2\pi\sigma_2^2}})^2(e^{-\frac{(x_1-\mu_2)^2}{2\sigma_2^2}})(e^{-\frac{(x_2-\mu_2)^2}{2\sigma_2^2}})\\
	A &= (\frac{1}{\sqrt{2\pi\sigma_1^2}})^2\\
	B &= (\frac{1}{\sqrt{2\pi\sigma_2^2}})^2\\
	C &= -\frac{1}{2\sigma^2}\\
	A(e^{\frac{(x_1-\mu_1)^2}{C}})(e^{\frac{(x_2-\mu_1)^2}{C}}) &= B(e^{\frac{(x_1-\mu_2)^2}{C}})(e^{\frac{(x_2-\mu_2)^2}{C}})\\
	A\frac{(e^{\frac{(x_1-\mu_1)^2}{C}})}{(e^{\frac{(x_1-\mu_2)^2}{C}})} &= B\frac{(e^{\frac{(x_2-\mu_2)^2}{C}})}{(e^{\frac{(x_2-\mu_1)^2}{C}})}\\
	Ae^{\frac{(x_1-\mu_1)^2}{C}*\frac{C}{(x_1-\mu_2)^2}} &= Be^{\frac{(x_2-\mu_2)^2}{C}*\frac{C}{(x_2-\mu_1)^2}}\\
	Ae^{\frac{(x_1-\mu_1)^2}{(x_1-\mu_2)^2}} &= Be^{\frac{(x_2-\mu_2)^2}{(x_2-\mu_1)^2}}\\
	ln(Ae^{\frac{(x_1-\mu_1)^2}{(x_1-\mu_2)^2}}) &= ln(Be^{\frac{(x_2-\mu_2)^2}{(x_2-\mu_1)^2}})\\
	ln(A)ln(e^{\frac{(x_1-\mu_1)^2}{(x_1-\mu_2)^2}}) &= ln(B)ln(e^{\frac{(x_2-\mu_2)^2}{(x_2-\mu_1)^2}})\\
	A'=ln(A)\\
	B'=ln(B)\\
	A'\frac{(x_1-\mu_1)^2}{(x_1-\mu_2)^2} &= B'\frac{(x_2-\mu_2)^2}{(x_2-\mu_1)^2}\\
	A'(\frac{x_1-\mu_1}{x_1-\mu_2})^2 &= B'(\frac{x_2-\mu_2}{x_2-\mu_1})^2\\
	(\frac{x_1-\mu_1}{x_1-\mu_2})^2 &= \frac{B'}{A'}(\frac{x_2-\mu_2}{x_2-\mu_1})^2\\
	\frac{x_1-\mu_1}{x_1-\mu_2} &= \sqrt{\frac{B'}{A'}(\frac{x_2-\mu_2}{x_2-\mu_1})^2}\\
	\frac{x_1-\mu_1}{x_1-\mu_2} &= (\frac{x_2-\mu_2}{x_2-\mu_1})\sqrt{\frac{B'}{A'}}\\
	C' = \sqrt{\frac{B'}{A'}}\\
	\frac{x_1-\mu_1}{x_1-\mu_2} &= C'(\frac{x_2-\mu_2}{x_2-\mu_1})\\
	\end{align*}

	We can simplify the left side of the equation, because:

	\begin{align*}
		\frac{x-\mu_1}{x-\mu_2} &= \frac{x-\mu_2+\mu_2+\mu_1}{x-\mu_2}\\
		&= \frac{x-\mu_2}{x-\mu_2}+\frac{\mu_2+\mu_1}{x-\mu_2}\\
		&= 1 + \frac{\mu_2+\mu_1}{x-\mu_2}
	\end{align*}

	and

	\begin{align*}
	\frac{x_2-\mu_2}{x_2-\mu_1} &= \frac{x_2-\mu_1+\mu_1-\mu_2}{x_2-\mu_1}\\
	&= \frac{x_2-\mu_1}{x_2-\mu_1}+\frac{\mu_1-\mu_2}{x_2-\mu_1}\\
	&= 1 +\frac{\mu_1-\mu_2}{x_2-\mu_1}
	\end{align*}

	\begin{align*}
	\frac{x_1-\mu_1}{x_1-\mu_2} &= C'(\frac{x_2-\mu_2}{x_2-\mu_1})\\
	1 + \frac{\mu_2+\mu_1}{x_1-\mu_2} &= C'(1 +\frac{\mu_1-\mu_2}{x_2-\mu_1})\\
	\frac{\mu_2+\mu_1}{x_1-\mu_2} &= C'(1 +\frac{\mu_1-\mu_2}{x_2-\mu_1}) - 1\\
	\frac{1}{x_1-\mu_2} &=\frac{C'(1 +\frac{\mu_1-\mu_2}{x_2-\mu_1}) - 1}{\mu_2+\mu_1}\\
	x_1-\mu_2 &=\frac{\mu_2+\mu_1}{C'(1 +\frac{\mu_1-\mu_2}{x_2-\mu_1}) - 1}\\
	x_1 &=\frac{\mu_2+\mu_1}{C'(1 +\frac{\mu_1-\mu_2}{x_2-\mu_1}) - 1} + \mu_2\\
	x_1 &=\frac{\mu_2+\mu_1}{\sqrt{\frac{ln(B)}{ln(A)}}(1 +\frac{\mu_1-\mu_2}{x_2-\mu_1}) - 1} + \mu_2\\
	x_1 &=\frac{\mu_2+\mu_1}{\sqrt{\frac{ln( (\frac{1}{\sqrt{2\pi\sigma_2^2}})^2)}{ln((\frac{1}{\sqrt{2\pi\sigma_1^2}})^2)}}(1 +\frac{\mu_1-\mu_2}{x_2-\mu_1}) - 1} + \mu_2\\
	\end{align*}

\end{document}

### 2017-04-29 sources/cppserver/Win32Project1/Server/main.cpp

@@ -1,0 +1,31 @@
+#include <Windows.h>
+
+BOOL WINAPI DllMain(HMODULE hinstDLL, DWORD fdwReason, LPVOID lpvReserved)
+{
+	switch (fdwReason)
+	{
+		case DLL_PROCESS_ATTACH:
+			break;
+		case DLL_PROCESS_DETACH:
+			if (lpvReserved == NULL)
+			{
+				//FREE RESOURCES
+			}
+			else
+			{
+
+			}
+			break;
+		case DLL_THREAD_ATTACH:
+		case DLL_THREAD_DETACH:
+			break;
+	}
+
+	return TRUE;
+}
+
+extern "C" __declspec (dllexport) bool example()
+{
+	MessageBoxA(NULL, "OK", "test4", NULL);
+	return true;
+}

### 2017-04-29 texts/dev/DesignPatterns.tex

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\begin{document}

\section{Object Oriented Patterns}
\subsection{GOF Patterns}
\subsubsection{Bridge}
\begin{enumerate}
	\item {Design Patterns for Generic Programming in C++\\ \url{https://www.lrde.epita.fr/dload/papers/coots01.html}}
	\item {Generic programming in POOMA and PETE\\ \url{https://www.researchgate.net/publication/221024955_Generic_programming_in_POOMA_and_PETE}}
\end{enumerate}

\section{Functional Parsers}
\subsection{Monoid}
\begin{enumerate}
	\item {\url{https://fsharpforfunandprofit.com/posts/monoids-without-tears/}}
\end{enumerate}

\subsection{Monad}
\subsubsection{Parsers Combinators}
\begin{enumerate}
	\item {\url{https://fsharpforfunandprofit.com/posts/understanding-parser-combinators/}}
\end{enumerate}

\end{document}

### 2017-04-29 texts/dev/PapersILove.tex
POOMA paper about c++ patterns and patterns index

@@
 \subsection{Programming Paradigms}
+\subsubsection{Language Analysis}
+\begin{enumerate}
+	\item {Evaluating the Design of the R Language\\ \url{http://r.cs.purdue.edu/pub/ecoop12.pdf}}
+\end{enumerate}
 \subsubsection{Process Theory}
@@
 	\begin{enumerate}
-	\item {Design Patterns for Generic Programming in C++\\ \url{https://www.lrde.epita.fr/dload/papers/coots01.htmls}}
+	\item {Design Patterns for Generic Programming in C++\\ \url{https://www.lrde.epita.fr/dload/papers/coots01.html}}
 	\end{enumerate}

### 2017-05-07 texts/dev/PapersILove.tex
.

@@
 \subsection{Data Fusion}
+
 \begin{enumerate}
@@
 
+\subsection{Artificial Intelligence}
+\begin{enumerate}
+	\item {Computing Machinery and Intelligence\\ \url{http://orium.pw/paper/turingai.pdf}}
+\end{enumerate}
+
+\subsection{Text Mining}
+\begin{enumerate}
+	\item {Text Mining Infrastructure in R\\ \url{https://www.jstatsoft.org/article/view/v025i05}}
+\end{enumerate}
+
+\subsection{VIPs}
+\begin{enumerate}
+	\item {Richard Bellman's contributions to computer science\\\url{http://www.sciencedirect.com/science/article/pii/0022247X86901460}}
+\end{enumerate}
+
 \section{Mathematics}
@@
 \begin{enumerate}
-	\item {COISAS QUE O LUÍS PRECISA APRENDER\\
+	\item {Coisas que o Luís precisa aprender\\
 \url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
@@
 
+\section{Science}
+\subsection{Research}
+\begin{enumerate}
+	\item {Why Most Published Research Findings Are False\\
+	\url{http://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0020124}}
+\end{enumerate}
+
 \section{Economy}

### 2017-05-07 sources/cousera-datascience/capstone/capstone.R

@@ -1,0 +1,92 @@
+url <- "https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip"
+destfile <- "coursera-switftkey.zip"
+
+setwd("C:/github/xunilrj-sandbox/sources/cousera-datascience/capstone")
+
+print(destfile)
+if (!file.exists(destfile)) {
+  print("\tdownloading file...")
+  download.file(url, destfile = destfile)
+  print("\tdone.")
+}else{
+  print("\tfile already exists.")
+}
+
+if(!dir.exists("final")){
+  unzip(destfile, exdir = ".")
+}
+
+maxagg <- function(current, newvalue){
+  if(newvalue > current){
+    newvalue
+  }else{
+    current
+  }
+}
+
+countagg <- function(current, newvalue){
+  if(current==0){
+    current = c(0,0,0)
+  }
+  current + newvalue
+}
+
+mapLines <- function(con, f, agg){
+  current <- 0
+  while (TRUE) {
+    line = readLines(con, n = 1)
+    lengthline <- length(line)
+    if(lengthline == 0){break}
+    newvalue <- f(line[[1]])
+    current <- agg(current, newvalue)
+  }
+  current
+}
+
+mapFiles <- function(l,f,agg){
+  lapply(l, function(i){
+    con <- file(i, "r")
+    results <- mapLines(con, f, agg)
+    close(con)
+    results
+  })
+}
+
+library(stringi)
+
+setwd("C:/github/xunilrj-sandbox/sources/cousera-datascience/capstone/final/en_US")
+
+files <- c("en_US.blogs.txt","en_US.news.txt","en_US.twitter.txt")
+#longest line
+#biggers <- mapFiles(files, function(l){nchar(l)}, maxagg)
+#love-hate ratio
+#lovehateratio <- mapFiles(files, function(l){
+#  if(stri_detect_fixed(l,"love")){
+#    result <- c(1,0,1)
+#  }else{
+#    if(stri_detect_fixed(l, "hate")){
+#      result <- c(0,1,1)
+#    }else{
+#      result <- c(0,0,1)
+#    }
+#  }
+#  result
+#}, countagg)
+
+con <- file("en_US.twitter.txt", "r")
+files <- readLines(con)
+grep("biostats",files)
+
+#howmany computers
+howmany <- mapFiles(c("en_US.twitter.txt"), function(l){
[…]

### 2017-05-09 texts/philosophy/Guide.Plato.tex
.

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Daniel Frederico Lins Leite}
\begin{document}
	\maketitle
	\begin{chapter}

	\end{chapter}

Laws, Books 7-12
Laws, Books 1-6
Critias
Timaeus
The Republic 
Menexenus 
Ion 
Hipias Mayor 
Lesser Hippias 
Meno 
Gorgias 
Protagoras 
Lysis 
Laches 
Charmides 
Lovers 
Theages 
Hipparchus 
Alcibiades 2 
Alcibiades I 
Phaedrus 
Symposium 
Philebus 
Parmenides 
Statesman 
Phaedo 
Sophist (Annotated) 
Theaetetus 
Cratylus 
Euthyphro

Socrates: A Man for Our Times Johnson, Paul 
Platão  Reale, Giovanni
Storia della filosofia greca e romana vol. 3 - Platone e l'Accademia antica Reale, Giovanni
Toward a New Interpretation of Plato Reale, Giovanni
Plato and Aristotle Voegelin, Eric

\end{document}

### 2017-06-26 texts/dev/PapersILove.tex
.

@@
 \url{http://www.cs.wustl.edu/~schmidt/PDF/PLoP-95.pdf}}
+	\item{EASTL -- Electronic Arts Standard Template Library \url{http://www.open-std.org/jtc1/sc22/wg21/docs/papers/2007/n2271.html}}
 \end{enumerate}
@@
 	\item {Text Mining Infrastructure in R\\ \url{https://www.jstatsoft.org/article/view/v025i05}}
+	\item {Checkers Is Solved\\ \url{http://www.eecs.wsu.edu/~holder/courses/CptS570/fall07/papers/Schaeffer07.pdf}}
+	\item{Mastering the Game of Go with Deep Neural Networks and Tree Search  \url{https://gogameguru.com/i/2016/03/deepmind-mastering-go.pdf}}
 \end{enumerate}
@@
 \url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
+	\item{TEACHING SURVEY SAMPLING WITH THE ‘SAMPLING’ R PACKAGE  \url{http://iase-web.org/documents/papers/icots8/ICOTS8_4J1_TILLE.pdf}}
 \end{enumerate}

### 2017-06-26 sources/courses/columbia-ia/8puzzle/driver_3.py

@@ -1,5 +1,12 @@
 # -*- coding: utf-8 -*-
 """
+Created on Wed May 24 02:30:33 2017
+
+@author: Daniel Leite
+"""
+
+# -*- coding: utf-8 -*-
+"""
 Created on Sun May 21 19:46:36 2017
 
 @author: xunil
@@ -7,16 +14,16 @@ Created on Sun May 21 19:46:36 2017
 
 import sys
 from collections import deque
-import copy
+from queue import PriorityQueue
 #import resource
 
 algo = sys.argv[1]
 initialcsv = sys.argv[2]
 
-print("args")
-print("-------------------")
-print("algorithm: {0}".format(algo))
-print("initial state: {0}".format(initialcsv))
+#print("args")
+#print("-------------------")
+#print("algorithm: {0}".format(algo))
+#print("initial state: {0}".format(initialcsv))
 
 def printProgressBar (iteration, total, prefix = '', suffix = '', decimals = 1, length = 80, fill = '█'):
     percent = ("{0:." + str(decimals) + "f}").format(100 * (iteration / float(total)))
@@ -26,89 +33,205 @@ def printProgressBar (iteration, total, prefix = '', suffix = '', decimals = 1, 
     # Print New Line on Complete
     if iteration == total: 
         print()
-
-initialpos = [int(x) for x in initialcsv.split(",")]
-
+    
 w=3
-def isGoal(x):
-    return all(map(lambda xx: xx[0]==xx[1], zip(range(0,9),list(x[0]))))
-def getMoves(x):
-    zeroi = x[0].index(0)
+def isGoal(y):
+    return y == 912345678
+def getMoves(state,strstate):
+    zeroi = strstate.index("9") 
     zerox = zeroi % w
     zeroy = int(zeroi / w)
     if(zeroy > 0):
-        yield "Up"
-    if(zerox > 0):
-        yield "Left"
-    if(zerox < (w-1)):
-        yield "Right"    
+        yield 1#"Up"
     if(zeroy < (w-1)):
-        yield "Down"   
-def swap(x,mov):
-    newstate = copy.deepcopy(x[0])
-    zeroi = newstate.index(0)
-    newzeroi = 0
-    if(mov == "Right"):
-        newzeroi = zeroi + 1
-    if(mov == "Left"):
-        newzeroi = zeroi - 1
-    if(mov == "Down"):
-        newzeroi = zeroi + w
-    if(mov == "Up"):
[…]

### 2017-06-26 sources/cousera-datascience/server.r

@@ -1,5 +1,0 @@
-library(shiny)
-shinyServer(
-  function(input, output) {
-  }
-)

### 2017-07-04 sources/courses/johnhopkins-datascience/3dgaussianmixturemodel.rmd

---
title: "Gaussian Mixture Model"
author: "Daniel Frederico Lins Leite"
date: "21 April 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
library('MASS')
```

## Gaussian Mixture Models

- First we will generate 2000 points from two different multivariate Gaussian distributions.
- Then we will generate a 2d histogram of this data and render in 3D the possible approximation of the Gaussian, a result that we could have achieved from a Gaussian Mixture Model.

## Code

```{r, warning=FALSE, }
simulation.g1 <- mvrnorm(n = 1000, c(0,0), diag(2))
simulation.g2 <- mvrnorm(n = 1000, c(-3,-3), diag(c(0.3,10)))
simulation <- rbind(simulation.g1, simulation.g2)
qtd <- kde2d(simulation[,1], simulation[,2])
```

## Plot

```{r, warning=FALSE}
plot_ly(x = qtd$x, y = qtd$y, z = qtd$z) %>% add_surface()
```

### 2017-07-04 texts/dev/PapersILove.tex

@@
 \url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
-	\item{TEACHING SURVEY SAMPLING WITH THE ‘SAMPLING’ R PACKAGE  \url{http://iase-web.org/documents/papers/icots8/ICOTS8_4J1_TILLE.pdf}}
+	\item{TEACHING SURVEY SAMPLING WITH THE ‘SAMPLING’ R PACKAGE
+	\url{http://iase-web.org/documents/papers/icots8/ICOTS8_4J1_TILLE.pdf}}
+	\item{Data Mining and Statistics: What's the Connection\\ \url{http://docs.salford-systems.com/dm-stat.pdf}}
 \end{enumerate}

### 2017-07-04 texts/philosophy/introolavo.tex

@@
 	\section{Idea versus Reality}
+	Como muita da educação hoje é o consumo das idéias já consolidadas, a maioria esmagadora dos estudiosos tomam as Idéias pelos conceitos reais. Ver aplicações políticas.
+	[Ver a relação disto com o descarte do A Históri das Idéias Políticas do Eric Voegelin pela estrutura do Ordem e História.]
 	\subsection{Reality}
@@
 	\subsection{Scientist versus Agent}
+	\subsection{Inversion of the Concepts}
+	É muito comum, praticamente 100\% dos estudiosos, tomam democracia, livre mercado, socialismo, parlamento etc...
+como conceitos básicos, como mônadas políticas, porém, o primeiro poder real que todo ser humano passa é o poder da mãe, depois do pai, irmãos, familiares, poder de pessoas/amigos mais fortes etc...
 	\subsection{Inversion of the Evolution of the State}

### 2017-07-21 texts/philosophy/COF.tex
IA projects

\documentclass[10pt,a4paper]{book}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Daniel Frederico Lins Leite}
\begin{document}

Aula 1

Amizade = idem velle idem nolle
São Tomás

Aristóteles: a amizade é a base política.

Exercício do Necrológio: a idéia é encontrar a "voz" mais alta dentro de você mesmo que será aquela que irá lhe julgar, lhe direcionar. Seria a "voz" da confissão Católica.

filosofia como: unidade do conhecimento na unidade da consciência

filosofia se constitui com afficcionados como Socrates, Platao e Aristoteles. Porém na idade média se profissionaliza, o que abre uma ótima oportunidade porém vai aumenta a exigência sociais dos filósofos profissionais que vai matando a filosofia em si. Pois o professor vai tendo que cuidar da faculdade, economicamente, administrativamente, socialmente etc... E de algum modo isso vai influenciar a proprie produção filosófica, mesmo que os filósofos não percebam. Isso faz uma série de filosofias que não são conscientes das suas condições sociais.
Um dos exemplos mais óbvios é que um professor universitário, dentro de um curso, normalmente já está limitado pela delimitação do próprio curso, sem nunca se perguntar se a realidade pode ser descrita por esta limitação.

Em Socrátes a filosofia começa como filosofia política. A situação social da Grécia e dos interlecutores.
\end{document}

### 2017-07-21 sources/courses/columbia-ia/sklearn/problem3_3.py

@@ -1,0 +1,136 @@
+
+import sys
+import pandas as pd
+#import numpy as np
+from sklearn import svm
+from sklearn.linear_model import LogisticRegression
+from sklearn.cross_validation import train_test_split
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.grid_search import GridSearchCV
+from sklearn import tree
+from sklearn.ensemble import RandomForestClassifier
+#import matplotlib.pyplot as plt
+
+#import matplotlib as mpl
+#import matplotlib.pyplot as plt
+#from mpl_toolkits.mplot3d import Axes3D
+
+inputfile = "input3.csv"
+try:
+    inputfile = sys.argv[1]
+except:
+    inputfile = "input3.csv"
+outputfile = "output3.csv"
+try:
+    outputfile = sys.argv[2]
+except:
+    outputfile = "output3.csv"  
+    
+df = pd.read_csv(inputfile)
+dftrain, dftest = train_test_split(df, test_size = 0.4, stratify=None)
+
+#def runSVM(kernel, c, gamma):
+#    clf = svm.SVC(kernel=kernel,C=c,gamma=gamma)
+#    model = clf.fit(dftrain[["A","B"]].as_matrix(), dftrain["label"].as_matrix())
+#    score = model.score(dftrain[["A","B"]].as_matrix(), dftrain["label"].as_matrix())
+#    print(score)
+#    amin = df["A"].min()
+#    amax = df["A"].max()
+#    bmin = df["B"].min()
+#    bmax = df["B"].max()
+#    h = .02
+#    xx, yy = np.meshgrid(np.arange(amin, amax, h), np.arange(bmin, bmax, h))
+#    zz = clf.predict(np.c_[xx.ravel(), yy.ravel()])
+#    print(zz)
+#    zz = zz.reshape(xx.shape)
+#    plt.contourf(xx, yy, zz, cmap=plt.cm.coolwarm, alpha=0.8)
+#    plt.scatter(dftest["A"], dftest["B"], c=dftest["label"], cmap=plt.cm.coolwarm)
+#    plt.xlabel('Sepal length')
+#    plt.ylabel('Sepal width')
+#    plt.xlim(xx.min(), xx.max())
+#    plt.ylim(yy.min(), yy.max())
+#    plt.show()
+    
+def runLinear(file):
+    parameters = [
+      {'C': [0.1,0.5,1,5,10,50,100], 'kernel': ['linear']}
+    ]
+    classifier = svm.SVC()
[…]

### 2017-08-02 sources/courses/DataStructuresAndAlgorithmsUniversityOfCaliforniaSanDiego/assignment001/gcd/gcd.cpp
c++ algorithms for san diego course

@@ -1,0 +1,52 @@
+#include <iostream>
+
+int gcd_naive(int a, int b) {
+  int current_gcd = 1;
+  for (int d = 2; d <= a && d <= b; d++) {
+    if (a % d == 0 && b % d == 0) {
+      if (d > current_gcd) {
+        current_gcd = d;
+      }
+    }
+  }
+  return current_gcd;
+}
+
+int gcd(int a, int b)
+{
+  if(b == 0) return a;
+  if(b > a) return gcd(b,a);
+  return gcd(b, a % b);
+}
+
+
+#ifdef UNITTESTS
+
+#define CATCH_CONFIG_MAIN
+#include "../../catch.hpp"
+
+TEST_CASE("GCD must work", "[gcd]")
+{
+    REQUIRE(gcd(2,1) == 1);
+    REQUIRE(gcd(18,35) == 1);
+    REQUIRE(gcd(1344,217) == 7);
+    REQUIRE(gcd(28851538, 1183019) == 17657);
+}
+
+TEST_CASE("GCD corner cases", "[gcd]")
+{
+    REQUIRE(gcd(1,1) == 1);
+    REQUIRE(gcd(2*1000000000, 1) == 1);
+    REQUIRE(gcd(std::numeric_limits<int>::max(), 1) == 1);
+}
+
+#else
+
+int main() {
+  int a, b;
+  std::cin >> a >> b;
+  std::cout << gcd(a, b) << std::endl;
+  return 0;
+}
+
+#endif

### 2017-08-02 sources/courses/DataStructuresAndAlgorithmsUniversityOfCaliforniaSanDiego/assignment001/lcm/lcm.cpp

@@ -1,0 +1,61 @@
+#include <iostream>
+
+long long lcm_naive(int a, int b)
+{
+  for (long l = 1; l <= (long long)a * b; ++l)
+    if (l % a == 0 && l % b == 0)
+      return l;
+
+  return (long long)a * b;
+}
+
+int gcd(int a, int b)
+{
+  if(b == 0) return a;
+  if(b > a) return gcd(b,a);
+  return gcd(b, a % b);
+}
+
+long long lcm(int a, int b)
+{
+  //keep the biggest number as a
+  //because it is the one divided
+  //in the calculation.
+  //avoiding overflows
+  if(b > a) return lcm(b,a);
+  long long lla = a;
+  long long llb = b;
+  long long llgcd = gcd(a,b);
+  return (a/llgcd)*(b);
+}
+
+#ifdef UNITTESTS
+
+#define CATCH_CONFIG_MAIN
+#include "../../catch.hpp"
+
+TEST_CASE("GCD must work", "[gcd]")
+{
+  REQUIRE(lcm(6, 8) == 24);
+  REQUIRE(lcm(28851538, 1183019) == 1933053046);
+}
+
+TEST_CASE("GCD corner cases", "[gcd]")
+{
+  REQUIRE(lcm(1, 1) == 1);
+  REQUIRE(lcm(1, 2*1000000000) == 2*1000000000);
+  REQUIRE(lcm(2*1000000000,1) == 2*1000000000);
+  REQUIRE(lcm(2*1000000000,2*1000000000) == 2*1000000000);
+}
+
+#else
+
+int main()
+{
+  int a, b;
+  std::cin >> a >> b;
+  std::cout << lcm(a, b) << std::endl;
+  return 0;
+}
+
+#endif

### 2017-08-02 sources/courses/DataStructuresAndAlgorithmsUniversityOfCaliforniaSanDiego/assignment002/dot_product/dot_product.cpp

@@ -1,0 +1,58 @@
+#include <algorithm>
+#include <iostream>
+#include <vector>
+
+using std::vector;
+
+int sortDescending(const int & l, const int & r){
+    return l > r;
+}
+
+long long max_dot_product(vector<int> a, vector<int> b) {
+  std::sort(a.begin(),a.end(),sortDescending);
+  std::sort(b.begin(),b.end(),sortDescending);
+
+  // write your code here
+  long long result = 0;
+  for (size_t i = 0; i < a.size(); i++) {
+    result += ((long long) a[i]) * b[i];
+  }
+
+  return result;
+}
+
+#ifdef UNITTESTS
+
+#define CATCH_CONFIG_MAIN
+#include "../../catch.hpp"
+
+TEST_CASE("dot_product must work", "[dot_product]")
+{
+  REQUIRE(max_dot_product({23},{39}) == 897);
+  REQUIRE(max_dot_product({1,3,-5},{-2,4,1}) == 23);
+}
+
+TEST_CASE("dot_product corner case", "[dot_product]")
+{
+  REQUIRE(max_dot_product({-100000,100000},{-100000,100000}) == 20000000000);
+
+  auto ads = std::vector<int>(1000);
+  REQUIRE(max_dot_product(ads,ads) == 0);
+}
+
+#else
+
+int main() {
+  size_t n;
+  std::cin >> n;
+  vector<int> a(n), b(n);
+  for (size_t i = 0; i < n; i++) {
+    std::cin >> a[i];
+  }
+  for (size_t i = 0; i < n; i++) {
+    std::cin >> b[i];
+  }
+  std::cout << max_dot_product(a, b) << std::endl;
+}
+
+#endif

### 2017-08-02 sources/courses/DataStructuresAndAlgorithmsUniversityOfCaliforniaSanDiego/assignment002/fractional_knapsack/fractional_knapsack.cpp

@@ -1,0 +1,82 @@
+#include <iostream>
+#include <vector>
+#include <algorithm>
+#include <functional>
+
+using std::vector;
+
+double unitValue(int w, int v)
+{
+  return (double)v/(double)w;
+}
+
+double get_optimal_value(int capacity, vector<int> weights, vector<int> values) {
+  double value = 0.0;
+  auto order = std::vector<int>(weights.size());
+  std::iota(order.begin(), order.end(), 0);
+  std::sort(order.begin(), order.end(), [&](const int& l, const int& r){
+    return unitValue(weights[r],values[r]) < unitValue(weights[l],values[l]);
+  });
+  for(auto i: order)
+  {
+    if(capacity <= 0)
+    {
+      break;
+    }
+    auto w = weights[i];
+    auto v = values[i];
+    if(capacity >= w)
+    {
+      capacity -= w;
+      value += v;
+    }
+    else
+    {
+      auto partial = (double)capacity / (double)w;
+      value += v*partial;
+      capacity = 0;
+    }
+  }
+  return value;
+}
+
+#ifdef UNITTESTS
+
+#define CATCH_CONFIG_MAIN
+#include "../../catch.hpp"
+
+TEST_CASE("fractional_knapsack must work", "[knap]")
+{
+    REQUIRE(get_optimal_value(50, {20,50,30}, {60,100,120}) == 180.0);
+    REQUIRE(get_optimal_value(10, {30}, {500}) == Approx(166.66666));
+}
+
+TEST_CASE("fractional_knapsack corner cases", "[knap]")
+{
+    REQUIRE(get_optimal_value(1000, {2*1000000}, {2*1000000}) == 1000);
+
+    auto weigths = std::vector<int>(2*1000000);
+    auto values = std::vector<int>(2*1000000);
+    REQUIRE(get_optimal_value(1000, weigths, values) == 0);
+}
+
+#else
+
+int main() {
+  int n;
+  int capacity;
+  std::cin >> n >> capacity;
+  vector<int> values(n);
+  vector<int> weights(n);
+  for (int i = 0; i < n; i++) {
+    std::cin >> values[i] >> weights[i];
+  }
+
+  double optimal_value = get_optimal_value(capacity, weights, values);
+
+  std::cout.precision(10);
+  std::cout << optimal_value << std::endl;
+  return 0;
+}
+
+#endif

### 2017-08-02 sources/courses/DataStructuresAndAlgorithmsUniversityOfCaliforniaSanDiego/assignment002/largest_number/largest_number.cpp

@@ -1,0 +1,70 @@
+#include <algorithm>
+#include <sstream>
+#include <iostream>
+#include <vector>
+#include <string>
+
+using std::vector;
+using std::string;
+
+string largest_number(vector<string> a) {
+  std::sort(a.begin(), a.end(), [](const string & l, const string & r){
+      long long lint;
+      long long riint;
+      std::stringstream lstr;
+      lstr << l << r;
+      lstr >> lint;
+      lstr.clear();
+      lstr << r << l;
+      lstr >> riint;
+
+      return lint > riint;
+  });
+  //write your code here
+  std::stringstream ret;
+  for (size_t i = 0; i < a.size(); i++) {
+    ret << a[i];
+  }
+  string result;
+  ret >> result;
+  return result;
+}
+
+#ifdef UNITTESTS
+
+#define CATCH_CONFIG_MAIN
+#include "../../catch.hpp"
+
+TEST_CASE("largest_number must work", "[largest_number]")
+{
+  REQUIRE(largest_number({"21","2"}) == "221");
+  REQUIRE(largest_number({"9","4","6","1","9"}) == "99641");
+  REQUIRE(largest_number({"23","39","92"}) == "923923");
+}
+
+TEST_CASE("largest_number corner cases", "[largest_number]")
+{
+  REQUIRE(largest_number({"1000","1"}) == "11000");
+  
+  auto numbers = std::vector<string>(100);
+  for(int i = 0; i < numbers.size(); ++i)
+  {
+    numbers[i] = "1";
+  }
+  auto expected = std::string(100,'1');
+  REQUIRE(largest_number(numbers) == expected);
+}
+
+#else
+
+int main() {
+  int n;
+  std::cin >> n;
+  vector<string> a(n);
+  for (size_t i = 0; i < a.size(); i++) {
+    std::cin >> a[i];
+  }
+  std::cout << largest_number(a);
+}
+
+#endif

### 2017-08-02 sources/courses/DataStructuresAndAlgorithmsUniversityOfCaliforniaSanDiego/assignment003/inversions/inversions.cpp

@@ -1,0 +1,140 @@
+#include <iostream>
+#include <vector>
+
+using std::vector;
+
+std::ostream & tab(int size)
+{
+	return (std::cout << std::string(size * 3, ' '));
+}
+
+void printVector(const std::vector<int> &a)
+{
+  std::cout << "[";
+  for(auto i : a)
+  {
+    std::cout << i << ",";
+  }
+  std::cout << "]" << std::endl;
+}
+
+long long get_number_of_inversions(vector<int> &a, vector<int> &b, size_t left, size_t right, int depth) {
+	// tab(depth) << "[" << left << "," << right << "]";
+	long long number_of_inversions = 0;
+	if (right <= left)
+	{
+		// std::cout << "{" << a[left] << "," << a[right] << "}" << std::endl;
+		return number_of_inversions;
+	}
+	else
+	{
+		// std::cout << std::endl;
+	}
+
+	size_t ave = left + (right - left) / 2;
+	
+	number_of_inversions += get_number_of_inversions(a, b, left, ave, depth + 1);
+	number_of_inversions += get_number_of_inversions(a, b, ave+1, right, depth + 1);
+
+	// tab(depth) << "merging [" << left << "," << ave << "] & [" << ave+1 << "," << right << "]" << std::endl; 
+	// tab(depth);
+	// printVector(b);
+	int target = left, il = left + 0, ir = ave + 1;
+	while(il <= ave && ir <= right)
+	{
+		if(a[il] <= a[ir])
+		{
+			// tab(depth) << "l[" << a[il] << "," << a[ir] << "]";
+			b[target] = a[il];
+			// printVector(b);
+			il++;
+		}
+		else
+		{
+			auto invscore = ir - target;
+			number_of_inversions += invscore;
+			// tab(depth) << "r[" << a[il] << "," << a[ir] << "]{+" << invscore << "}";
+			b[target] = a[ir];
+			// printVector(b);
+			ir++;
+		}
+		target++;
+	}
+	while(il <= ave)
+	{
+		// tab(depth) << "l[" << a[il] << "]";
+		b[target] = a[il];
+		il++;
+		target++;
+		// printVector(b);
+	}
+	while(ir <= right)
+	{
[…]

### 2017-08-02 sources/courses/DataStructuresAndAlgorithmsUniversityOfCaliforniaSanDiego/assignment003/sorting/sorting.cpp

@@ -1,0 +1,238 @@
+#include <iostream>
+#include <fstream>
+#include <iterator>
+#include <vector>
+#include <cstdlib>
+#include <tuple>
+
+using std::vector;
+using std::swap;
+
+void printVector(const std::vector<int> &a)
+{
+  std::cout << "[";
+  for(auto i : a)
+  {
+    std::cout << i << ",";
+  }
+  std::cout << "]" << std::endl;
+}
+
+std::tuple<int,int> partition2(vector<int> &a, int l, int r) {
+  int x = a[l];
+  int j = l;
+  for (int i = l + 1; i <= r; i++) {
+    if (a[i] <= x) {
+      j++;
+      swap(a[i], a[j]);
+    }
+  }
+  swap(a[l], a[j]);
+  return std::make_tuple(j,j);
+}
+
+std::tuple<int,int> partition3(vector<int> &a, int l, int r) {
+  // std::cout << "PART " << l << " " << r << std::endl;
+  int x = a[l];
+  int lt = l;
+  int gt = r;
+  for (int i = l ; i <= gt; i++) {
+    // std::cout << "-----------------------" << std::endl;
+    // printVector(a);
+    // std::cout << i << "," << x << "," << lt << "," << gt << std::endl;
+    if (a[i] < x) {
+      // std::cout << a[i] << " smaller " << x << std::endl;
+      swap(a[i], a[lt]);
+      lt++;      
+    }
+    else if(a[i] > x)
+    {
+      // std::cout << a[i] << " bigger " << x << std::endl;
+      swap(a[i], a[gt]);
+      gt--;
+      i--;  
+    }
+    else
+    {
+      // std::cout << a[i] << " equal " << x << std::endl;
+    }
+    // printVector(a);
+    // std::cout << "-----------------------" << std::endl;
+  }
+  // std::cout << "x" << "," << x << "," << lt << "," << gt << std::endl;
+  return std::make_tuple(lt,gt);
+}
+
+template<typename Partition>
+void randomized_quick_sort(Partition p, vector<int> &a, int l, int r) {
+  if (l >= r) {
+    return;
+  }
+
+  int k = l + rand() % (r - l + 1);
+  swap(a[l], a[k]);
+
+  int m1,m2;
[…]

### 2017-08-10 texts/philosophy/introolavo.tex
edit distance algo in cpp using dynamic programming

@@
 	\subsection{Idea}
+	Do Facebook do Olavo
+
+	-"Mapa da ignorância" é um conjunto esquemático de interrogações pelo qual tomamos consciência daquilo que nos falta saber para compreender melhor aquilo que sabemos numa determinada fase da nossa evolução cognitiva.
+	"Horizonte de consciência" é o limite daquilo que compreendemos nessa fase. 
+	Um "mapa da ignorância" pobre ou vazio assinala um horizonte de consciência fechado e incapaz de ampliar-se. 
+	Qualquer doutrina filosófica insinua automaticamente, pela sua própria existência, seu respectivo mapa da ignorância.
+O problema é: aos olhos de quem?
+Do próprio filósofo ou do seu leitor apenas?
+O filósofo está consciente dos problemas principais e imediatos que precisaria resolver para dar plena razão da sua doutrina, ou simplesmente a apresenta como auto-suficiente, como se o seu horizonte de consciência fosse o limite da consciência humana na sua época?
+Os problemas que uma filosofia sugere imediatamente ao leitor foram incorporados pelo filósofo no seu mapa da ignorância, ou fazem parte apenas da sua inconsciência?
 	\section{Philosopher Maturity}

### 2017-08-10 sources/courses/DataStructuresAndAlgorithmsUniversityOfCaliforniaSanDiego/assignment004/edit_distance/edit_distance.cpp

@@ -1,17 +1,282 @@
 #include <iostream>
 #include <string>
+#include <algorithm>
+#include <numeric>
+#include <tuple>
+#include <map>
 
 using std::string;
 
-int edit_distance(const string &str1, const string &str2) {
-  //write your code here
-  return 0;
+void print(int *array, int w, int h, int cx, int cy){
+  auto at = [&](int x,int y){return x+(y*(w));};
+  for (int j = 0; j < h; j++){
+    for (int i = 0; i < w; i++){      
+        if(i == cx & j == cy ){
+          std::cout << "[" << array[at(i,j)] << "] ";
+        }
+        else{
+          std::cout << array[at(i,j)] << " ";
+        }
+      }
+      std::cout << std::endl;
+  }
+  std::cout << std::endl;
 }
+
+bool contains(std::string& s, char c)
+{
+  auto result = s.find(c);
+  return result != std::string::npos;
+}
+
+int edit_distance_dynamic(const string str1, const string str2) {
+  auto w = str1.size();
+  auto h = str2.size();
+  auto solutions = std::vector<int>(w*h);
+  auto at = [&](int x,int y) {return (x-1)+((y-1)*w);};
+  
+  //bases cases
+  auto strj = str2.substr(0,1);
+  for(int i = 1;i <= str1.size();++i)
+  {
+    // print(&solutions[0], w, h, i-1, 0);
+    auto stri = str1.substr(0,i);
+    if(stri == strj)
+    {
+      solutions[at(i,1)] = 0;
+    }else
+    {
+      auto stri_contains_j = contains(stri, str2[0]);
+      auto score = stri_contains_j ? i-1 : i;
+      solutions[at(i,1)] = score;
+    }
+  }
+  auto stri = str1.substr(0,1);
+  for(int j = 1;j <= str2.size();++j)
+  {
+    auto strj = str2.substr(0,j);
+    // print(&solutions[0], w, h, 0, j-1);
+    if(stri == strj)
+    {
+      solutions[at(1,j)] = 0;
+    }else
+    {
+      auto strj_contains_i = contains(strj, str1[0]);
+      auto score = strj_contains_i ? j-1 : j;
+      solutions[at(1,j)] = score;
+    }
+  }
+
+  for(int i = 2;i <= str1.size();++i)
+  {
+    for(int j = 2;j <= str2.size();++j)
+    {
[…]

### 2017-08-24 texts/philosophy/introolavo.tex
san diego alg course in cpp

@@
 Os problemas que uma filosofia sugere imediatamente ao leitor foram incorporados pelo filósofo no seu mapa da ignorância, ou fazem parte apenas da sua inconsciência?
+
+	Como princípio metodológico em psicologia -- e excluindo provisoriamente a psicopatologia e a psicologia espiritual --, adotei a regra de que não posso explicar as condutas de ninguém por fatores gerais que não expliquem as minhas próprias, aí incluída a conduta de tentar explicá-las.
+	Uma explicação que pretenda valer para todas as ações humanas tem de valer, também, para o ato de explicá-las.
+De Maquiavel a Michel Foucault, passando por Marx, Darwin, Nietzsche.
+Freud e não sei mais quantos, todos os belos explicadores do mundo ignoraram essa regra elementar incontornável.
+
+	Um método é um conjunto de proposições auto-evidentes (ou provadas com base nelas) que delimitam um objeto e os meios de conhecê-lo.
+	O bom método não define o seu objeto, mas recebe essa definição de uma prévia descrição fenomenológica.
 	\section{Philosopher Maturity}
@@
 	\subsubsection{12 layers of personality}
+
+	As castas são tipos psicológicos e não classes sociais.
+Elas existem em toda sociedade, independentemente da estrutura de classes.
+Sempre foi assim e sempre será assim, exceto naquele dia de são nunca sonhado por Karl Marx, em que cada cidadão será operário ou lavrador de manhã, comerciante depois do almoço, guerreiro ao entardecer e filósofo de noite, sem contar umas composições musicais, uns quadros e esculturas, alguns feitos extraordinários de donjuanismo, além de uma pescaria, um torneio de xadrez e um joguinho de futebol de vez em quando.
+
 	\subsubsection{Cognitive Parallax}
@@
 como conceitos básicos, como mônadas políticas, porém, o primeiro poder real que todo ser humano passa é o poder da mãe, depois do pai, irmãos, familiares, poder de pessoas/amigos mais fortes etc...
+
+	Há muitos princípios auto-evidentes que podem orientar uma boa previsão histórico-política. Dois deles:
+	1) A difusão dos fatos produz novos fatos.
+	2) Ninguém age onde não enxerga.
 	\subsection{Inversion of the Evolution of the State}

### 2017-08-24 sources/courses/coursera-sandiego-algorithms/algorithmic-toolbox/assignment004/lcs3/lcs3.cpp

@@ -1,0 +1,163 @@
+#include <iostream>
+#include <vector>
+#include <tuple>
+#include <algorithm>
+
+using std::vector;
+
+
+
+long long lcs2(vector<long long> &a, vector<long long> &b, int i, int j)
+{
+  if((i == -1)||(j==-1))
+  {
+    return 0;
+  }
+  else if (a[i] == b[j])
+  {
+    return 1 + lcs2(a,b, i-1,j-1);
+  }
+  else
+  {
+    auto r1 = lcs2(a,b,i-1,j);
+    auto r2 = lcs2(a,b,i,j-1);
+    return std::max(r1,r2);
+  }
+}
+
+long long lcs2(vector<long long>& a, vector<long long>& b)
+{
+  auto h = a.size()+1;
+  auto w = b.size()+1;
+  auto solutions = std::vector<long long>(h*w);
+  auto at = [=](const int row, const int column) { return column+(row*w);};
+
+  for(auto y = 0; y < h;++y)
+  {
+    for(auto x = 0; x < w;++x)
+    {
+        if((x==0)||(y==0))
+        {
+          solutions[at(y,x)] = 0;
+        }
+        else
+        {
+          if(a[y-1] == b[x-1])
+          {
+            solutions[at(y,x)] = solutions[at(y-1,x-1)] + 1;
+          }
+          else
+          {
+            auto r1 = solutions[at(y-1,x)];
+            auto r2 = solutions[at(y,x-1)];
+            solutions[at(y,x)] = std::max(r1,r2);
+          }
+        }
+    }
+  }
+  auto r = solutions[at(a.size(),b.size())];
+  return r;
+}
+
+long long lcs3(vector<long long> &a, vector<long long> &b, vector<long long> &c) {
+  // auto ab = lcs2(a,b);
+  // auto bc = lcs2(b,c);
+  // auto ac = lcs2(a,c);
+  // return std::min(std::min(ab, bc), ac);
+  auto h = a.size()+1;
+  auto w = b.size()+1;
+  auto d = c.size()+1;
+  auto solutions = std::vector<long long>(h*w*d);
+  auto at = [=](const int row, const int column, const int depth) { return column+(row*w)+(depth*w*h);};
+
[…]

### 2017-08-24 sources/courses/coursera-sandiego-algorithms/algorithmic-toolbox/assignment004/placing_parentheses/placing_parentheses.cpp

@@ -1,0 +1,430 @@
+#include <iostream>
+#include <cassert>
+#include <string>
+#include <sstream>
+#include <vector>
+#include <stack>
+#include <algorithm>
+#include <functional>
+#include <tuple>
+
+using std::vector;
+using std::string;
+using std::max;
+using std::min;
+
+template<typename T>
+void permutations(vector<T>& set, std::function<void(std::vector<T>)> f) {
+   do {
+        f(set);
+    } while(std::next_permutation(set.begin(), set.end()));
+}
+
+long long eval(long long a, long long b, char op) {
+  if (op == '*') {
+    return a * b;
+  } else if (op == '+') {
+    return a + b;
+  } else if (op == '-') {
+    return a - b;
+  } else {
+    assert(0);
+  }
+}
+
+struct node{
+  bool digit;
+  union{
+    long long number;
+    char op;
+  };
+};
+
+node digit(long long d)
+{
+  auto n = node();
+  n.digit = true;
+  n.number = d;
+  return n;
+}
+
+node digit(char d)
+{
+  auto n = node();
+  n.digit = true;
+  n.number = (long long)(d-48);
+  return n;
+}
+
+node op(char op)
+{
+  auto n = node();
+  n.digit = false;
+  n.op = op;
+  return n;
+}
+
+node make_node(char c)
+{
+  if((c == '+')||(c == '-')||(c == '*'))
+  {
+    return op(c);
+  }
+  else
+  {
+    return digit(c);
+  }
+}
+
+#include <memory>
+template <template <typename, typename> class Container, 
+          typename Allocator=std::allocator<node> >
+std::ostream & operator << (std::ostream & o, Container<node,Allocator> nodes)
+{
+  o << "[";
+
+  for(auto current : nodes)
+  {
+    if(current.digit){
+      o << "(" << current.number << "),";
+    }else{
+      o << "(" << current.op << ")";
+    }
+  }
+
+  return o << "]";
+}
+
+template <template <typename, typename> class Container, 
+          typename Value,
+          typename Allocator=std::allocator<Value> >
+std::ostream & operator << (std::ostream & o, Container<Value,Allocator> v)
+{
+  o << "[";
+
+  for(auto current : v)
+  {
+    o << current << ",";
+  }
+
+  return o << "]";
+}
+
[…]

### 2017-08-24 sources/courses/coursera-sandiego-algorithms/data-structures/assignment001/check_brackets_in_code/check_brackets.cpp

@@ -1,0 +1,244 @@
+#include <iostream>
+#include <stack>
+#include <string>
+#include <regex>
+#include <tuple>
+
+struct Bracket {
+    Bracket(char type, int position):
+        type(type),
+        position(position)
+    {}
+
+    bool Matchc(char c) {
+        if (type == '[' && c == ']')
+            return true;
+        if (type == '{' && c == '}')
+            return true;
+        if (type == '(' && c == ')')
+            return true;
+        return false;
+    }
+
+    char type;
+    int position;
+};
+
+std::tuple<bool,int> IsBracketMatched(std::string text)
+{
+    std::stack<Bracket> opening_brackets_stack;
+    const char open[] = "([{";
+    const char close[] = ")]}";
+    auto expected_open = [&](char closec){
+        auto begin = std::begin(close);
+        auto pos = std::find(begin, std::end(close), closec);
+        auto index  = pos - begin;
+        return open[index];
+    };
+    for (int position = 0; position < text.length(); ++position) {
+        char next = text[position];
+
+        // std::cout << next;
+        
+        if (next == '(' || next == '[' || next == '{') {
+            // std::cout << " +";
+            opening_brackets_stack.emplace(next,position);
+        }
+
+        if (next == ')' || next == ']' || next == '}') {
+            // std::cout << " -";
+
+            if(opening_brackets_stack.size() == 0)
+            {
+                return std::make_tuple(false,position+1);
+            }
+
+            auto top = opening_brackets_stack.top();
+            if(top.type == expected_open(next))
+            {
+                opening_brackets_stack.pop();
+            }
+            else
+            {
+                // std::cout << " expected " << expected_open(next);
+                return std::make_tuple(false,position+1);
+            }
+        }
+
+        // std::cout << std::endl;
+    }
+
+    // std::cout << "ok";
+
+    if(opening_brackets_stack.size() == 0)
+    {
+        return std::make_tuple(true,0);
+    }
+    else
+    {
+        return std::make_tuple(false,opening_brackets_stack.top().position+1);
+    }
+}
+
+#ifdef UNITTESTS
+
+#define CATCH_CONFIG_MAIN
+#include "../../catch.hpp"
+
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <dirent.h>
+
[…]

### 2017-09-09 texts/dev/PapersILove.tex
update in papers
san diego alg course in cpp
.

@@
 \subsubsection{Dynamic Dispatch}
+\subsubsection{Functional Programming}
+\begin{enumerate}
+	\item {Monadic Parser Combinators\\
+\url{http://www.cs.nott.ac.uk/~pszgmh/monparsing.pdf}}
+\end{enumerate}
 \begin{enumerate}
@@
 \url{http://db.cs.berkeley.edu/papers/sigmod97-gist.pdf}}
+
 	\item {Data Cube: A Relational Aggregation Operator Generalizing Group-By, Cross-Tab, and Sub-Totals\\
@@
 \section{Mathematics}
+\subsection{Linear Algebra}
+\begin{enumerate}
+	\item {Basic Linear Algebra Subprograms for Fortran Usage\\
+\url{https://ntrs.nasa.gov/archive/nasa/casi.ntrs.nasa.gov/19780018835.pdf}}
+	\item{FLAME: Formal Linear Algebra Methods Environment\\
+\url{http://tinyurl.com/ycxkmzw7}}
+	\item{The Five Greatest Applications of Markov Chains\\
+\url{http://langvillea.people.cofc.edu/MCapps7.pdf}}
+\end{enumerate}
 \subsection{Real Analysis}

### 2017-09-09 sources/courses/coursera-sandiego-algorithms/data-structures/assignment002/job_queue/job_queue.cpp

@@ -1,10 +1,154 @@
 #include <iostream>
 #include <vector>
 #include <algorithm>
+#include <tuple>
 
 using std::vector;
-using std::cin;
-using std::cout;
+
+template <typename T1, typename T2>
+std::ostream& operator << (std::ostream& out, std::tuple<T1,T2> t)
+{
+  return out << std::get<0>(t) << "," << std::get<1>(t);
+}
+
+template <typename T, typename F>
+class heap{
+public:
+  heap(std::vector<T>& v, F f) : c(v), getkey(f)
+  {
+  }
+
+  void insert(T item)
+  {
+    auto s = c.size();
+    c.push_back(item);
+    SiftUp(s);
+  }
+
+  T top() const 
+  {
+    if(c.size() > 0) return c[0];
+    //ERROR
+  }
+
+  T pop()
+  {
+    auto result = c[0];
+    c[0] = c[c.size() - 1];
+    c.pop_back();
+    SiftDown(0);
+    return result;
+  }
+
+  void printTree(int i = 0, int depth = 0)
+  {
+      std::cout << std::string(depth*2, ' ') << getkey(c[i]) << std::endl;
+
+    auto lindex = lchild_of(i);
+    if(lindex < c.size())
+    {
+      printTree(lindex, depth + 1);
+    }
+    
+    auto rindex = rchild_of(i);
+    if(rindex < c.size())
+    {
+      printTree(rindex, depth + 1);
+    }
+  }
+private:
+  int parent_of(int i) const{
+    return ((i+1)/2)-1;
+  }
+
+  int lchild_of(int i) const{
+    return (2*(i+1)) - 1;
+  }
+
+  int rchild_of(int i) const {
+    return (2*(i+1));
+  }
+
+  template <typename T1>
+  bool compare(T1& l, T1& r) const {
+    // std::cout << "compare " << std::endl;
+    return l < r;
+  }
+  
+  void SiftUp(int i)
+  {
+    while(true)
+    {
+      if(i < 0) return;
+
+      // std::cout << "siftinUp " << i << std::endl;
+      auto ivalue = getkey(c[i]);
+      auto pindex = parent_of(i);
+
+      if(pindex < 0) return;
+      
+      auto pvalue = getkey(c[pindex]);
+      
+      if(compare(ivalue,pvalue))
+      {
+        std::swap(c[i], c[pindex]);
+        i = pindex;
+      }
+      else
+      {
+        break;
+      }
+    }
[…]

### 2017-09-09 sources/courses/coursera-sandiego-algorithms/data-structures/assignment002/merging_tables/merging_tables.cpp

@@ -3,9 +3,9 @@
 #include <vector>
 #include <algorithm>
 #include <iostream>
+#include <sstream>
+#include <memory>
 
-using std::cin;
-using std::cout;
 using std::endl;
 using std::max;
 using std::vector;
@@ -16,6 +16,22 @@ struct DisjointSetsElement {
 	DisjointSetsElement(int size = 0, int parent = -1, int rank = 0):
 	    size(size), parent(parent), rank(rank) {}
 };
+
+std::ostream& operator << (std::ostream& out, const DisjointSetsElement& x)
+{
+	return out << "{" << x.size << "," << x.parent << "," << x.rank << "}";
+}
+
+template <template <typename,typename> typename C, typename T, typename A = std::allocator<T>>
+std::ostream& operator << (std::ostream & out, const C<T,A>& v)
+{
+	out << "[";
+	for(auto x : v)
+	{
+		out << x << ",";		
+	}
+	return out << "]";
+}
 
 struct DisjointSets {
 	int size;
@@ -28,39 +44,120 @@ struct DisjointSets {
 	}
 
 	int getParent(int table) {
-		// find parent and compress path
+		auto originalTable = table;
+		auto x = sets[table];
+		while(x.parent != table)
+		{
+			table = x.parent;
+			x = sets[table];
+		}
+
+		sets[originalTable].parent = table;
+		return table;
 	}
 
 	void merge(int destination, int source) {
+		// std::cout << sets << std::endl;
+		// std::cout << "merge " << destination << " " << source << std::endl;
+
 		int realDestination = getParent(destination);
 		int realSource = getParent(source);
 		if (realDestination != realSource) {
+			auto& d = sets[realDestination];
+			auto& s = sets[realSource];
+			if(d.rank >= s.rank)
+			{
+				d.size += s.size;
+				s.parent = realDestination;
+				if(d.rank == s.rank) ++d.rank;
+
+				if(d.size > max_table_size) max_table_size = d.size;
+			}
+			else
+			{
+				s.size += d.size;
+				d.parent = realSource;
+
+				if(s.size > max_table_size) max_table_size = s.size;
+			}		
+			
 			// merge two components
 			// use union by rank heuristic
-                        // update max_table_size
+			// update max_table_size
 		}		
 	}
 };
 
-int main() {
[…]

### 2017-10-03 texts/philosophy/Guide.Plato.tex
.
columbia robotic course using ROS and python

@@
 
-Laws, Books 7-12
-Laws, Books 1-6
+Laws
+
+[Eric Voegelin - Order and History - Plato and Aristotle]
+
+The Laws has only one major, external incision?
+the one that separates the first three books from the subsequent
+nine. And this incision serves precisely the purpose of articulation
+through dominant motifs inasmuch as the first three books marshal
+the motifs, while Books IV?XII apply them to the exposition of the
+nomoi of the polis. Within the nine books the subject matter itself
+is distributed in a roughly systematic sequence from the choice of
+site and population for the polis, through social institutions, mag-
+istracies, education, and festivals, to civil and criminal law?but
+this systematic order is subordinated to the order of the dominant
+motifs.
+
+The high points of this internal organization are to be found
+in Books VII (Education) and X (Religion) with the recurrence of
+the principal motif of Book I, that is, with the symbol of the God
+who plays the game of order and history with man as his puppet.
+
+This
+Summa of Greek life embraces in its amplitude the consequences
+of the Trojan War and the Doric invasion, it analyzes the failure
+of the Doric military kingship and the horrors of Athenian the-
+atrocracy, it reflects on the effects of harem education on Persian
+kings and on the preservation of art styles in Egypt, on the con-
+sequences of enlightenment and the inquisitorial enforcement of a
+creed, on the ethos of musical scales as well as on the undesirability
+of fishing as a sport
+
+The Laws develops fully the religious position of Plato; the polis
+whosefoundationandorganizationisdescribedmaybecharacterized
+as a theocratic state. In the liberal era a work of this kind could only
+arouse grave misgivings among scholars for whom the separation
+of church and state was a fundamental dogma, and for whom a
+theory of politics had to be defined in terms of the secular state.
+
+The second of these elementary misconceptions crystallizes in
+the formula that the Laws is a treatise on ?jurisprudence.? The as-
+sumption is not entirely wrong. The Laws, indeed, contains sections
+that have to be classified as jurisprudence in the modern meaning
+of the word
+
+The error is in part induced by the translation of
+the title Nomoi as Laws with the implication that the laws of Plato
+mean laws in the sense in which the word is used in modern legal
+theory. Plato?s nomos, however, is deeply imbedded in the myth of
+nature and has an amplitude of meaning that embraces the cosmic
+order, festival rites, and musical forms. The assumption that the
+Laws is a treatise on ?jurisprudence? ignores this range of meaning
+and inevitably destroys the essence of Plato?s thought.
+
+A third group of misconceptions touches a more complex problem.
+ItconcernsPlato?sdesignationoftheLawsasthesecond-bestplanfor
+a polis. We hear that Plato had developed in the Republic his plan for
+theidealstate,thathisprojectwasutterlyunrealistic,thathehimself
+became convinced of its Utopian character, and, finally, that in the
+Laws he developed an ideal that took into account at least some of
+the exigencies of human nature. Moreover, the Laws is distinguished
+from the Republic by its recognition of historical traditions and
+customs as well as of the necessity of legal institutions. While the
+Republic still envisaged something like a dictatorial government
+without laws, the Laws embodies the more mature conception of a
+constitutionalgovernmentunderthelaws.
+
+The plan of a second-best polis seems to imply a transition from
+the ?ideal? of dictatorship by the philosopher-king to the ?ideal? of
+a government by law with constitutional consent of the people. In
+thisinstancewehavetounravelawholeseriesofmisunderstandings.
+
+The Republic is
+written under the assumption that the ruling stratum of the polis
+will consist of persons in whose souls the order of the idea can
+become reality so fully that they, by their very existence, will be the
+permanent source of order in the polis.  the Laws is written under the
+assumption that the free citizenry will consist of persons who can
+be habituated to the life of Arete under proper guidance, but who are
+unabletodevelopthesourceoforderexistentiallyinthemselvesand,
+therefore, need the constant persuasion of the prooemia as well as
+the sanctions of the law, in order to keep them on the narrow path
+
+[Herbert Marcuse - The Af?rmative Character of Culture ]
+
+ Platonic philosophy still contended with the social order of commercial Athens.
+Plato?s idealism is interlaced with motifs of social criticism.
+What appears as facticity from the standpoint of the Ideas is the material world in which men and things encounter one another as commodities.
+The just order of the soul is destroyed by
+
+ the passion for wealth which leaves a man not a moment of leisure to attend to anything beyond his personal fortunes.
+So long as a citizen?s whole soul is wrapped up in these, he cannot give a thought to anything but the day?s takings.7
+
+ And the authentic, basic demand of idealism is that this material world be transformed and improved in accordance with the truths yielded by knowledge of the Ideas.
+Plato?s answer to this demand is his program for a reorganization of society.
+This program reveals what Plato sees as the root of evil.
+He demands, for the ruling strata, the abolition of private property (even in women and children) and the prohibition of trade.
+This same program, however, tries to root the contradictions of class society in the depths of human nature, thereby perpetuating them.
+
 Critias
@@
 
+Good Articles:
+"I read two dialogues of Plato, the ?Timaeus? and the ?Parmenides.? These are among Plato?s longer and more difficult dialogues ? the first about creating the world, and the second about the One."
+http://www.crisismagazine.com/2011/what-plato-advises
+
 \end{document}

### 2017-10-03 sources/courses/columbia-robotic/proj03/catkin_ws/build/catkin_generated/generate_cached_setup.py

@@ -1,0 +1,30 @@
+# -*- coding: utf-8 -*-
+from __future__ import print_function
+import argparse
+import os
+import stat
+import sys
+
+# find the import for catkin's python package - either from source space or from an installed underlay
+if os.path.exists(os.path.join('/opt/ros/kinetic/share/catkin/cmake', 'catkinConfig.cmake.in')):
+    sys.path.insert(0, os.path.join('/opt/ros/kinetic/share/catkin/cmake', '..', 'python'))
+try:
+    from catkin.environment_cache import generate_environment_script
+except ImportError:
+    # search for catkin package in all workspaces and prepend to path
+    for workspace in "/home/vagrant/proj03/catkin_ws/devel;/home/ubuntu/catkin_ws/devel;/opt/ros/kinetic".split(';'):
+        python_path = os.path.join(workspace, 'lib/python2.7/dist-packages')
+        if os.path.isdir(os.path.join(python_path, 'catkin')):
+            sys.path.insert(0, python_path)
+            break
+    from catkin.environment_cache import generate_environment_script
+
+code = generate_environment_script('/home/vagrant/proj03/catkin_ws/devel/env.sh')
+
+output_filename = '/home/vagrant/proj03/catkin_ws/build/catkin_generated/setup_cached.sh'
+with open(output_filename, 'w') as f:
+    #print('Generate script for cached setup "%s"' % output_filename)
+    f.write('\n'.join(code))
+
+mode = os.stat(output_filename).st_mode
+os.chmod(output_filename, mode | stat.S_IXUSR)

### 2017-10-03 sources/courses/columbia-robotic/proj03/catkin_ws/build/catkin_generated/installspace/setup.sh

@@ -1,0 +1,93 @@
+#!/usr/bin/env sh
+# generated from catkin/cmake/template/setup.sh.in
+
+# Sets various environment variables and sources additional environment hooks.
+# It tries it's best to undo changes from a previously sourced setup file before.
+# Supported command line options:
+# --extend: skips the undoing of changes from a previously sourced setup file
+
+# since this file is sourced either use the provided _CATKIN_SETUP_DIR
+# or fall back to the destination set at configure time
+: ${_CATKIN_SETUP_DIR:=/home/vagrant/proj03/catkin_ws/install}
+_SETUP_UTIL="$_CATKIN_SETUP_DIR/_setup_util.py"
+unset _CATKIN_SETUP_DIR
+
+if [ ! -f "$_SETUP_UTIL" ]; then
+  echo "Missing Python script: $_SETUP_UTIL"
+  return 22
+fi
+
+# detect if running on Darwin platform
+_UNAME=`uname -s`
+_IS_DARWIN=0
+if [ "$_UNAME" = "Darwin" ]; then
+  _IS_DARWIN=1
+fi
+unset _UNAME
+
+# make sure to export all environment variables
+export CMAKE_PREFIX_PATH
+if [ $_IS_DARWIN -eq 0 ]; then
+  export LD_LIBRARY_PATH
+else
+  export DYLD_LIBRARY_PATH
+fi
+unset _IS_DARWIN
+export PATH
+export PKG_CONFIG_PATH
+export PYTHONPATH
+
+# remember type of shell if not already set
+if [ -z "$CATKIN_SHELL" ]; then
+  CATKIN_SHELL=sh
+fi
+
+# invoke Python script to generate necessary exports of environment variables
+# use TMPDIR if it exists, otherwise fall back to /tmp
+if [ -d "${TMPDIR}" ]; then
+  _TMPDIR="${TMPDIR}"
+else
+  _TMPDIR=/tmp
+fi
+_SETUP_TMP=`mktemp "${_TMPDIR}/setup.sh.XXXXXXXXXX"`
+unset _TMPDIR
+if [ $? -ne 0 -o ! -f "$_SETUP_TMP" ]; then
+  echo "Could not create temporary file: $_SETUP_TMP"
[…]

### 2017-10-03 sources/courses/columbia-robotic/proj03/catkin_ws/build/catkin_generated/order_packages.py

@@ -1,0 +1,5 @@
+# generated from catkin/cmake/template/order_packages.context.py.in
+source_root_dir = "/home/vagrant/proj03/catkin_ws/src"
+whitelisted_packages = "".split(';') if "" != "" else []
+blacklisted_packages = "".split(';') if "" != "" else []
+underlay_workspaces = "/home/vagrant/proj03/catkin_ws/devel;/home/ubuntu/catkin_ws/devel;/opt/ros/kinetic".split(';') if "/home/vagrant/proj03/catkin_ws/devel;/home/ubuntu/catkin_ws/devel;/opt/ros/kinetic" != "" else []

### 2017-10-03 sources/courses/columbia-robotic/proj03/catkin_ws/build/forward_kinematics/catkin_generated/pkg.installspace.context.pc.py

@@ -1,0 +1,8 @@
+# generated from catkin/cmake/template/pkg.context.pc.in
+CATKIN_PACKAGE_PREFIX = ""
+PROJECT_PKG_CONFIG_INCLUDE_DIRS = "".split(';') if "" != "" else []
+PROJECT_CATKIN_DEPENDS = "rospy;sensor_msgs;tf;urdfdom_py".replace(';', ' ')
+PKG_CONFIG_LIBRARIES_WITH_PREFIX = "".split(';') if "" != "" else []
+PROJECT_NAME = "forward_kinematics"
+PROJECT_SPACE_DIR = "/home/vagrant/proj03/catkin_ws/install"
+PROJECT_VERSION = "0.0.0"

### 2017-10-03 sources/courses/columbia-robotic/proj03/catkin_ws/build/lwr_robot/lwr_defs/catkin_generated/pkg.installspace.context.pc.py

@@ -1,0 +1,8 @@
+# generated from catkin/cmake/template/pkg.context.pc.in
+CATKIN_PACKAGE_PREFIX = ""
+PROJECT_PKG_CONFIG_INCLUDE_DIRS = "".split(';') if "" != "" else []
+PROJECT_CATKIN_DEPENDS = "xacro".replace(';', ' ')
+PKG_CONFIG_LIBRARIES_WITH_PREFIX = "".split(';') if "" != "" else []
+PROJECT_NAME = "lwr_defs"
+PROJECT_SPACE_DIR = "/home/vagrant/proj03/catkin_ws/install"
+PROJECT_VERSION = "0.0.1"

### 2017-10-03 sources/courses/columbia-robotic/proj03/catkin_ws/build/robot_mover/catkin_generated/pkg.develspace.context.pc.py

@@ -1,0 +1,8 @@
+# generated from catkin/cmake/template/pkg.context.pc.in
+CATKIN_PACKAGE_PREFIX = ""
+PROJECT_PKG_CONFIG_INCLUDE_DIRS = "".split(';') if "" != "" else []
+PROJECT_CATKIN_DEPENDS = "".replace(';', ' ')
+PKG_CONFIG_LIBRARIES_WITH_PREFIX = "".split(';') if "" != "" else []
+PROJECT_NAME = "robot_mover"
+PROJECT_SPACE_DIR = "/home/vagrant/proj03/catkin_ws/devel"
+PROJECT_VERSION = "0.0.0"

### 2017-10-15 sources/courses/coursera-sandiego-algorithms/algorithms-on-graphs/assignment002/toposort/toposort.cpp
graph topological sort using c++, graph connected components using c++, more calculus notes for the handout

@@ -1,32 +1,155 @@
 #include <iostream>
-#include <algorithm>
 #include <vector>
+#include <algorithm>
+#include <unordered_set>
+#include <vector>
+#include <functional>
 
 using std::vector;
 using std::pair;
 
-void dfs(vector<vector<int> > &adj, vector<int> &used, vector<int> &order, int x) {
-  //write your code here
-}     
+template <typename T, typename TValue>
+class map_greater
+{
+public:
+  map_greater(std::function<TValue(const T&)> f) : getValue(f)
+  {
+  }
+
+  bool operator () (const T& l, const T& r) const
+  {
+    auto lvalue = getValue(l);
+    auto rvalue = getValue(r);
+    return lvalue > rvalue;
+  }
+private:
+  std::function<TValue(const T&)> getValue;
+};
+
+struct VertexPrePos
+{
+  int Vertex;
+  int Pre;
+  int Pos;
+};
+
+template <typename T, typename TValue>
+map_greater<T,TValue> make_greater(std::function<TValue(const T&)> f)
+{
+  return {f};
+}
+
+class Graph
+{
+public:
+  Graph(vector<vector<int> > adjList) : adj(adjList), r(false)
+  {
+  }
+
+  std::vector< VertexPrePos > DFS() const
+  {
+    int pos = 0;
+    auto prepos = std::vector<VertexPrePos>(adj.size()); 
+
+    auto visited = std::unordered_set<int>();
+    std::function<void(const int&)> visit;
+    visit = [&](const int& vi){
+      if (visited.find(vi) != visited.end())
+      {
+        return;
+      }
+
+      visited.insert(vi);
+      prepos[vi] = {vi, pos, 0};
+      ++pos;
+
+      auto vadj = adj[vi];
+      for(auto other_vertex : vadj)
+      {
+        visit(other_vertex);
+      }
+      
+      prepos[vi].Pos = pos;
+      ++pos;
+    };
+    
+    for(int i = 0; i < adj.size();++i) visit(i);
+    return prepos;
+  }
+private:
+  vector<vector<int> > adj;
+  bool r;
+};
 
 vector<int> toposort(vector<vector<int> > adj) {
   vector<int> used(adj.size(), 0);
   vector<int> order;
-  //write your code here
+  
+  auto g = Graph{adj};
+  auto prepos = g.DFS();   
[…]

### 2017-11-04 texts/philosophy/introolavo.tex
matlab algebra linear for invert matrix using GaussJordan

@@
 	\subsubsection{Limited Structure of the Reality}
+	Kantism is not a philosophy. It`s a practical joke.
+	Kant had to be VERY stupid to not understand that our apprehending only the phenomenic appearances, and not the thing in itself, is not a limitation in us, but of the things in themselves.
+If he had noticed this, he would have realized that his theory DOES NOT MEAN ANYTHING.
+	All modern science is based on a phenomenist metaphysics, in which there are no real beings, just measurable appearances.
+It is so because no real entity is exhausted on which a science, or all of them together, can say about it.
+Besides, each one only asks questions about the object that pertain to its own methodology and not about the ontological structure of the object itself.
+This structure remains outside the reach of each science in particular and cannot be reengineered by the mere articulation of a number of the sciences.
+The experience of REALITY is an anterior necessity for the possibility of any science, which they just complement with specific details.
+This same experience of reality remains outside of epistemological control of any science.
+	No scientific explanation refers to the fact in itself, as small as it may be, and even less accounts for its causes.
+It just highlights the aspects of the fact that correspond to the methodological perspective of that science in particular.
+"Reality" is entirely out of all that.
+Ninety-nine point ninety-nine percent of science professionals ignore that this is how things are.
+	Practicing any science without the constant critical examination of its epistemological pillars, and therefore of its own limitations, causes a state of hypnotic hallucination.
+In such a state the person denies the validity of his spontaneous perception of things - which is the foundation of any science - and substitutes it for some hypothetical system that gives him the impression of being scientific.
+Many scientists end up becoming like Felix, the Cat ( https://www.youtube.com/watch?v=amGbBFsiuzc ), living in a world drawn by themselves.
+	When a science professor says there is no significant genetic differences between a monkey and a three-year-old, he imagines that this difference really does not exist, and not that it is his genetic perspective that is insufficient to apprehend it.
+	Ultimately, the sciences as they exist today are not meant to know the world, but to fabricate it as an industrialized product.
+	Olavo de Carvalho
 	\subsection{Unification}

### 2017-11-04 sources/courses/university-of-texas-linear-algebra/GaussJordanInv3x3.m

@@ -1,0 +1,28 @@
+function result = GaussJordanInv3x3( A )
+    appended = [A eye(size(A))];
+    G0 = [
+        1 0 0
+        -A(2,1)/A(1,1) 1 0
+        -A(3,1)/A(1,1) 0 1
+    ];
+    A1 = G0*appended;
+    G1 = [
+        1 -A1(1,2)/A1(2,2) 0
+        0 1 0
+        0 -A1(3,2)/A1(2,2) 1
+    ];
+    A2 = G1*A1;
+    G2 = [
+        1 0 -A2(1,3)/A2(3,3)
+        0 1 -A2(2,3)/A2(3,3)
+        0 0 1
+    ];
+    A3 = G2*A2;
+    D = [
+        1/A3(1,1) 0 0
+        0 1/A3(2,2) 0
+        0 0 1/A3(3,3)
+    ];
+    A4 = D*A3;
+    result = A4(:, 4:6);
+endfunction

### 2017-11-16 texts/philosophy/introolavo.tex
more olavos facebook for his intro

@@
 	\subsection{Inversion of Modern Cosmological Views}
+
+	Existe alguém, entre os luminares da esquerda nacional, especialmente na mídia, que esteja capacitado para discutir a teoria dos quatro discursos, o círculo de latência, a perspectiva rotatória, a psicologia espiritual, a fenomenologia do milagre, a teoria do império, a minha interpretação das filosofias de Maquiavel, René Descartes e Kant ou o método filosófico tal como o resumi em ?A Filosofia e Seu Inverso?, enfim, algo daquilo que se pode chamar de ?filosofia do Olavo de Carvalho??
+A resposta é um decidido NÃO.
+
+	Uma das teses principais da minha filosofia é que a vocação filosófica se realiza menos na busca das grandes verdades gerais do que na compreensão da experiência real ao nosso alcance, onde aques verdades aparecem como que em filigrana, mais insinuadas do que proclamadas.
+	Tudo o que escrevi sobre a política ou sobre a sociedade brasileira são apenas exercícios destinados a ilustrar essa tese.
+
+	Fabio Florence Professor, bom dia.
+Gostaria de tirar uma dúvida sobre a "Filosofia Política" de Eric Weil.
+No último capítulo, o autor fala positivamente da ideia de Estado mundial.
+Na sua avaliação, ele defendia um projeto análogo ao da elite globalista ou pensava em algo bem diferente do que estamos vendo hoje?
+	LikeShow more reactions
+	·
+	8
+	· 8 hrs
+	Manage
+	Olavo de Carvalho
+	Olavo de Carvalho Weil nunca entrou em detalhes sobre esse ponto, nem creio que formar projetos políticos fosse um dos seus objetivos.
+Apenas afirmou que o Estado Mundial era a conclusão lógica inevitável de toda a sua fllosofia política.
+Essa filosofia, por sua vez, é uma longa e rigososa dedução a partir de princípios universais abstratos -- precisamente o oposto do que penso que uma filosofia política deva ser.
 \end{document}

### 2017-12-05 sources/csharp/CSharpFeatures/Tuples.cs
.

@@ -217,4 +217,39 @@ namespace CSharpFeatures
             return Task.FromResult(await t);
         }
     }
+
+    class Program2
+    {
+        static void Main2(string[] args)
+        {
+            var (id, name) = !Dto1.From((Guid.NewGuid(), ""));
+            //TODO: test serialization and deserialization
+        }
+    }
+
+
+    public class Dto1 : Record<Dto1, (Guid id, string Name)>{}
+
+
+    public class Record<T, TValues> where T : Record<T, TValues>
+    {
+        public static T From(TValues values)
+        {
+            dynamic instance = System.Runtime.Serialization.FormatterServices.GetUninitializedObject(typeof(T));
+            instance.Value = values;
+            return (T)instance;
+        }
+
+        protected TValues Value;
+
+        public static TValues operator !(Record<T, TValues> item)
+        {
+            return item.Value;
+        }
+
+        public static explicit operator Record<T, TValues>(TValues values)
+        {
+            return From(values);
+        }
+    }
 }

### 2018-01-01 texts/dev/PapersILove.tex
monadic task for c# (maybe) working with async await
calculus limit proof
.
fundamentals of matrix computations exercises

@@
 \href{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}}
+	\item {Paxos Made Simple\\
+	\url{https://www.microsoft.com/en-us/research/publication/paxos-made-simple/}}
 	\item {Distributed Snapshots: Determining Global States of Distributed Systems\\
@@
 	\item {Life Beyond Distributed Transactions: An Apostate’s Opinion\\
-\url{http://www.ics.uci.edu/~cs223/papers/cidr07p15.pdf}}
+\url{http://www-db.cs.wisc.edu/cidr/cidr2007/papers/cidr07p15.pdf}}
 \end{enumerate}
@@
 \end{enumerate}
-
 \subsubsection{Generic Programming}
@@
 \begin{enumerate}
+	\item{The essence of functional programming \\
+\url{http://homepages.inf.ed.ac.uk/wadler/papers/essence/essence.ps.gz}}
 	\item {Monadic Parser Combinators\\
@@
 \section{Mathematics}
+\subsection{Geometry}
+\begin{enumerate}
+	\item {An Elementary Course in Synthetic Projective Geometry}
+\end{enumerate}
 \subsection{Linear Algebra}

### 2018-02-07 texts/math/Handout.BinomialCoefficient.tex
.

--- 2017-01-26 sources/Math/Handout.BinomialCoefficient.tex
@@
 \usepackage{amsmath,amssymb,amsthm}
+\usepackage{hyperref}
 
@@
 
-	The notation (nk) for the binomial coefficient was introduced by Andreas Freiherr von Ettingshausen in his 1826 work Die combinatorische Analysis.
+	The notation $\binom{N}{K}$ for the binomial coefficient was introduced by Andreas Freiherr von Ettingshausen in his 1826 work "Die combinatorische Analysis".
 
-	It appears to have become the de facto standard in recent years.
-
+	It appears to have become the de facto standard in recent years.\\
+	\\
+	Definition:
 \begin{align}
-	\binom{N}{K} &= \binom{N - 1}{K - 1} + \binom{N - 1}{K}\\ 
-	\binom{N}{0} &= 1
+	\binom{n}{k} &= \frac {n!}{k!(n-k)!}\\
+\end{align}
+	Recursive Definition:
+\begin{align}
+	\binom{n}{k} &= \binom{n - 1}{k - 1} + \binom{n - 1}{k}\\ 
+	\binom{n}{0} &= 1
 \end{align}
@@
 
+See More:
+\url{https://www.khanacademy.org/math/precalculus/prob-comb/combinations/v/introduction-to-combinations}
+\url{https://www.khanacademy.org/math/algebra2/polynomial-functions/binomial-theorem/v/binomial-theorem}\\
+
 \end{document}

### 2018-02-07 texts/math/Statistics/MaximumLikelihood.rmd
.

--- 2017-03-23 sources/Math/MaximumLikelihood.rmd
@@
   maximum at (u = `r max$par[1]`, sd = `r max$par[2]`)  
-L(u = `r max$par[1]`, sd = `r max$par[2]`) = `r max$value`
+L({u = `r max$par[1]`, sd = `r max$par[2]`}|x1,x2) = `r max$value`
 
@@
 B <- -1
-AB <- A * B
-samples <- rnorm(100000, mean = max$par[1], sd = max$par[2])*rnorm(100000, mean = max$par[1], sd = max$par[2])
-h <- hist(samples, freq = FALSE)
-h$counts=h$counts/sum(h$counts)
-plot(h)
-abline(v = AB, lty=2)
+
+x = seq(-2, 1, length= 20)
+y = seq(-2, 0.5, length= 20)
+f = function(x, y) { dnorm(x, mean = max$par[1], sd = max$par[2])*dnorm(y, mean = max$par[1], sd = max$par[2]) }
+z = outer(x, y, f)
+z[is.na(z)] = 0
+library(RColorBrewer)
+contour(x,y,z,col=rev(brewer.pal(11, "RdYlBu")), nlevels = 11)
+abline(h=A,v=B)
+points(B, A)
 ```

### 2018-02-07 sources/cpp/debugtest/main.cpp

@@ -1,0 +1,11 @@
+
+int test1(int x)
+{
+    return x+1;
+}
+
+int main()
+{
+    int x = test1(1);
+    return 0;
+}

### 2018-02-11 texts/philosophy/Guide.Aristotle.tex
gas problem using R

\documentclass[10pt,a4paper]{book}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Daniel Frederico Lins Leite}
\title{Guide to Aristotle}
\begin{document}
	\chapter{Modern Scholars}

	\section{Giovanni Reale}

	\section{Jonathan Barnes}

	Books\\
	Aristotle: A very short introduction\\
	\\
	No man before him had contributed so much to learning. No man after him might aspire to rival his achievements.\\
	\\
	In one of his later works, the 	Nicomachean Ethics, Aristotle argues that ?happiness? ? that state of 	mind in which men realize themselves and flourish best ? consists in a 	life of intellectual activity. Is not such a life too godlike for mere 	mortals to sustain? No; for ?we must not listen to those who urge us to 	think human thoughts since we are human, and mortal thoughts since 	we are mortal; rather, we should as far as possible immortalize 	ourselves and do all we can to live by the finest element in us ? for if in bulk it is small, in power and worth it is far greater than anything else?.
	\\
	A good way of reading him is this: Take up 	a treatise, think of it as a set of lecture notes, and imagine that you now have to lecture from them. You must expand and illustrate the argument, and you must make the transitions clear; you will probably decide to relegate certain paragraphs to footnotes, or reserve them for another time and another lecture;
	\\
	The Cambrigde Companion to Aristotle\\
	The Cambridge History of Hellenistic Philosophy\\
	The Complete Works of Aristotle

	\chapter{Timeline}

	Spring 322: Retire to Chalcis (Euboea Island)
\end{document}

### 2018-02-11 texts/math/Statistics/CarOutGas/generate.data.r

@@ -3,28 +3,28 @@ type = c(1,2)
 homeWork = rnorm(260, mean=10, sd=1.5)
 workHome = rnorm(260, mean=10, sd=2.0)
 
-consuption = data.frame(days, type, consumption = c(homeWork, workHome))
-write.csv(file="consumption.csv", x=consumption)
+consumption = data.frame(days, type, consumption = c(homeWork, workHome))
+#write.csv(file="consumption.csv", x=consumption)
 
 consumption = read.csv("consumption.csv")
 
-homeWork = consumption[comsumption$type == 1,]
-workHome = consumption[comsumption$type == 2,]
+homeWork = consumption[consumption$type == 1,]
+workHome = consumption[consumption$type == 2,]
 
 png(filename="homeWork.plot.png")
-plot(homeWork$day, homeWork$consumption)
+  plot(homeWork$day, homeWork$consumption)
 dev.off()
 
 png(filename="homeWork.hist.png")
-hist(homeWork$consumption)
+  hist(homeWork$consumption)
 dev.off()
 
 png(filename="workHome.plot.png")
-plot(workHome$day, workHome$consuption)
+  plot(workHome$day, workHome$consumption)
 dev.off()
 
 png(filename="workHome.hist.png")
-hist(workHome$consuption)
+  hist(workHome$consumption)
 dev.off()
 
 normal.lik<-function(mu,sigma,y){
@@ -56,12 +56,7 @@ plotMLE <- function(data, x, y, steps = 20, levels = 10000) {
 png(filename="homeWork.likelihood.png")
   plotMLE(homeWork$consumption, x=c(5,15),y=c(0,5), levels = 2000)
 dev.off()
-
-
 optim(c(12,4),normal.lik.muvar,y=homeWork$consumption,method="BFGS") 
-
-
-
 png(filename="homeWork.likelihood.withlines.png")
   plotMLE(homeWork$consumption, x=c(5,15),y=c(0,5), levels = 2000)
   abline(h=1.70105, lty=2)
@@ -73,9 +68,56 @@ plotGaussian <- function(start = -1, end = 1, u, sigma, scale, color = "black"){
   hx <- dnorm(x, mean = u, sd = sigma)*scale
   lines(x, hx, type="l", lty=2, xlab="x value", ylab="Density", main="Gaussian", col = color)
 }
[…]

### 2018-02-12 texts/philosophy/Syllogisms.tex
.

\documentclass[10pt,a4paper]{book}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Daniel Frederico Lins Leite}
\title{Syllogisms}
\begin{document}

	\maketitle

	\section{TODO}

	TODO: Aristotle
	TODO: Theophrastus
	TODO: Eudemos

	\index{entry}

	\begin{enumerate}
		\item Categorical Syllogisms
		\item Hypothetical Syllogisms
	\end{enumerate}

	\chapter{Aristotle}
	\chapter{Theophrastus}
	\chapter{Alexander of Aphrodisias}
	\chapter{Ioannes Philoponos}
	\chapter{Eudemos}	
	\chapter{Boethius}

	\chapter{References}

	from "The Propositional Logic of Boethius : Studies in Logic and the Foundations of Mathematics"\\ 
	page 4	\\
	Boethius speaks to a certain Symmachus who is named in the title of the work.\\ 
	"What I have found in a few Greek authors brief and confused and in no Latin authors, that I dedicate to your insight, after its having been completed by our long, but successful exertions. When you had acquired a comprehensive knowledge of categorical syllogisms, you often desired information about hypothetical syllogisms, concerning which Aristotle wrote nothing. Theophrastus, a man versed in every science, works out only the main points. Although Eudemos touches on the subjects more broadly, lie proceeds in such a fashion that he seems to have only thrown out a few seeds without having harvested any of the fruit."\\
	(Cf. Boe. p. 606). 
	\\
	"In his article "Zur Geschichte der Aussagenlogik", Jan Lukasiewicz opposed propositional logic to the logic of names (Cf. Lu. p. 111). If we adopt this usage, we can say: The theory of categorical 
	syllogisms is the logic of names and the theory of hypothetical syllogisms is propositional logic."\\
	\\
	page 5\\
	Boethius relates the theory of hypothetical syllogisms with Theophrastus and Eudemos; it is unmistakable that he regards these two peripatetics as the first to develop this kind of logic. 
	This last fact is significant, because according to the interpretation now represented by Jan Lukasiewicz and Heinrich Scholz, which we may call the modern interpretation, the Stoics either founded 
	propositional logic or at least developed it to a higher level (Cf. Lu. p. 112 and Sch. p. 31). This raises the question of the relation between Boethius and the Stoic logic.
	page 6\\
	In order to establish what the theory of the older peripatetics was, we are directed to the information to be found in Greek commentaries on Aristotle's Prior Analytics. Aristotle speaks, in several places, of hypothetical syllogisms. These remarks give the commentators occasion to point out what the doctrines of the older peripatetics on hypothetical syllogisms were. There are two commentaries to be taken into consideration, namely: 
	(1) The commentary of Alexander of Aphrodisias. 
	(2) The commentary of Ioannes Philoponos.

\end{document}

### 2018-02-15 texts/math/Handout.Probability.tex
.

\documentclass[10pt,a4paper]{book}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\author{Daniel Frederico Lins Leite}
\title{Probability}
\begin{document}
	\section{Introduction}
	$w$ is a "sample point".\\
	$S$ is a "sample space" if\\
		\tab $w$ is a "sample point and $w \in S$;\\
		\tab and $\forall_{i,j}{(w_i \cap w_j = \emptyset \text{, if } i \neq j)}$;\\
		\tab and $w_1 \cup w_2 \cup ... \cup w_n = S$.\\
		A is a "family of events" if is a set of "sample points"\\
		\tab $A = \{w\}$ where $w$ is a "sample point"\\
		\tab $A^\complement = \{w : w \notin A\}$\\
		\tab $A \cup B = \{w: w \in A \lor w \in B\}$\\
		\tab $A \cap B = \{w: w \in A \land w \in B\}$\\
		\tab $S^\complement = \emptyset$\\
		\tab $A \cup A^\complement = S$\\
		\tab $A \cap A^\complement = \emptyset$\\
		\tab $A \cap S = A$\\
		\tab $A \cup S = S$\\
		\tab $A \cup \emptyset = A$\\
		\tab $\cup$ is commutative, associative, distributive\\
		\tab $\cap$ is commutative, associative, distributive\\
		P is a "probability measure" if is a mapping between S and the "real numbers" with the following properties:\\
		\tab $P = f: S \mapsto {\rm I\!R}$\\
		\tab $P(A) = f(A)$\\
		\tab $f(S) = \sum_{\forall i}{f(A_i)} = 1$\\
		\tab $0 <= f(A) <= 1$\\
		\tab if $A \cap B = \emptyset$ then $f(A \cup B) = f(A) + f(B).$\\
		\\
		The triplet (S,A,P) defines a "probability system", a consistent axiomatic theory of probability of finite "sample spaces".
		\\
		"Conditional probability" is the probability of "family of events" A, given that the "family of events B" occurred.\\
		$$P(A|B) \triangleq \frac{P(A \cap B)}{P(B)}$$\\
		$A$ and $B$ are "statistical independent" if:\\
		$$P(A \cap B) = P(A)*P(B)$$
		wich can be extended to:\\
		$$ P\big(\bigcap_{\forall i}{ A_i}\big) = \prod_{\forall i}{P(A_i)} $$\\
		Given the last two properties we have that the "conditional property" of two "statistical independent" "family of events" is:\\
		$$ P(A|B) = \frac{P(A \cap B)}{P(B)} = \frac{P(A)*P(B)}{P(B)} = P(A) $$.
		The "Theorem of total probability" states that:\\
		$$P(B) = \sum_{\forall i}{P(A_i|B)}$$
\end{document}

### 2018-02-17 courses/coursera-princeton-algorithms-1/karatsubamultiplication.tex
.

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\begin{document}
	\section{Karatsuba Multiplication}

	Two numbers $l$ and $r$, can be written in the following way:	
	\begin{align*}	
	l &= a*10^N + b\\  
	r &= c*10^N + d\\
	\end{align*}
	In this case their multiplication can be written
	\begin{align*}
	l*r &= (a*10^N + b)*(c*10^N + d)\\ 
	&= (a*c*10^{2N})+(a*d*10^N)+(b*c*10^N)+(b*d)\\  
	&= (a*c*10^{2N})+([(a*d)+(b*c)]*10^N)+]+(b*d)  
	\end{align*}
	but $(a*d)+(b*c)$ is equal to
	\begin{align*}
	&= (a*d)+(b*c)\\
	&= (a+b)*(c+d) - ac - bd\\
	&= a*c + a*d + b*c + b*d - a*c - b*d\\
	&= a*d + b*c
	\end{align*}
	now we can change two multiplications $(a*d)$ and $(b*c)$ to just one: $(a+b)*(c+d)$, given that we have already calculated $a*c$ and $b*d$.

	This gives us the final form:	
	\begin{align*}
	l*r &= (a*c*10^{2N})\\&+([(a+b)*(c+d) - a*c - b*d]*10^N)\\&+(b*d)
	\end{align*}

	See:\\
	\url{https://academic.microsoft.com/#/detail/204623740}\\\\
	\url{https://scholar.google.co.uk/scholar?q=Multiplication+of+Many-Digital+Numbers+by+Automatic+Computers&btnG=&hl=en&as_sdt=0%2C5}\\\\
	\url{http://cstheory.stackexchange.com/questions/21564/why-did-kolmogorov-publish-karatsubas-algorithm}\\
	\\
	The Art of Computer Programming, Volume II, page 294, section 4.3.3
\end{document}

### 2018-02-17 courses/johnhopkins-datascience/london.rmd
.

---
title: "London Tube"
author: "Daniel Frederico Lins Leite"
date: "21 April 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
library(jsonlite)
library(RCurl)
library(dplyr)
```

## Realtime London Underground Position

page created at 2017-04-21 by Daniel Leite

```{r}
raw_data <- getURL("http://traintimes.org.uk/map/tube/data/london.json")

data <- fromJSON(raw_data, flatten = TRUE)
trains <- data$trains
trains["lat"] <- sapply(data$trains$point, function(x) x[1])
trains["long"] <- sapply(data$trains$point, function(x) x[2])

subicon <- makeIcon("http://cdn2.iconfinder.com/data/icons/circle-icons-1/64/train-32.png", 32, 32)
trains %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup = trains$title, icon = subicon)
```

### 2018-02-17 texts/dev/PapersILove.tex
.

@@
 \subsubsection{Elections + Consensus}
+
 \begin{enumerate}
@@
 \href{https://ramcloud.atlassian.net/wiki/download/attachments/6586375/raft.pdf}{https://ramcloud.atlassian.net/wiki/download/attachments/6586375/raft.pdf}}
+\end{enumerate}
+
+\subsubsection{Computer Graphics}
+\begin{enumerate}
+	\item {Bresenham's Algorithm\\
+\url{http://graphics.idav.ucdavis.edu/education/GraphicsNotes/Bresenhams-Algorithm.pdf}}
 \end{enumerate}
@@
 \url{http://www-db.cs.wisc.edu/cidr/cidr2007/papers/cidr07p15.pdf}}
+	\item {Conﬂict-free Replicated Data Types\\ \url{https://hal.inria.fr/inria-00609399/document}}
 \end{enumerate}
@@
 \section{Science}
+
 \subsection{Research}
@@
 \end{enumerate}
-
+\section{Physics}
+\begin{enumerate}
+	\item {Seven Possible Alternative Interpretations of the ‘cosmological Red Shift’ Which Can do Away with the Dark Energy\\
+\url{http://www.vixra.org/pdf/1403.0005v1.pdf}}
+\end{enumerate}
 \section{Economy}

### 2018-02-17 texts/math/Handout.Probability.tex
.

@@
 	\section{Introduction}
+	\subsection{Subset}
+
+	\subsection{Population}
+	A \textbf{population} is defined as a collection of statistical units of the same nature whose quantifiable information we are interested in.
+The 	population constitutes the reference universe during the study of a given statistical problem.
+	\subsection {Sample}
+	A \textbf{sample} is a \textit{subset} of a \textit{population} on which statistical studies are made in order to draw conclusions relative to the \textit{population}.
 	$w$ is a "sample point".\\
@@
 		$$P(B) = \sum_{\forall i}{P(A_i|B)}$$
+
+		\section{Reference}
+		\begin{enumerate}
+			\item {The Concise Encyclopedia of Statistics - Yadolah Dodge}
+		\end{enumerate}
+
 \end{document}

### 2018-02-17 books/FundamentalsMatrixComputations/exercise.01.002.017.m
.

@@ -1,0 +1,40 @@
+warning('off','all');
+pkg load symbolic
+
+function result = newxi(i) result = sym(["u" num2str(i)]); endfunction
+x = arrayfun(@newxi, 0:8);
+
+l1 = ((x(4)-x(1))/0.1) - ((x(1)-x(2))/0.5)
+l2 = ((x(1)-x(2))/0.5) - ((x(5)-x(2))/0.5) - ((x(2)-x(3))/0.2)
+l3 = ((x(2)-x(3))/0.2) - ((x(6)-x(3))/0.1)
+l4 = ((x(7)-x(4))/0.2) - ((x(4)-x(5))/0.1) - ((x(4)-x(1))/0.1)
+l5 = ((x(4)-x(5))/0.1) + ((x(5)-x(2))/0.5) - ((x(8)-x(5))/0.1) - ((x(5)-x(6))/0.5)
+l6 = ((x(5)-x(6))/0.5) + ((x(6)-x(3))/0.1) - ((x(9)-x(6))/0.2)
+l7 = ((x(8)-x(7))/0.2) - ((x(7)-x(4))/0.2)
+
+function result = Add(A,x,m,i,Eq)
+    for ic = 1:m
+        item = Eq;
+        for ic2 = 1:m
+            if(ic!=ic2)
+                item = subs(item,x(ic2),0);
+            endif
+        end
+        A(i,ic) = subs(item,x(ic),1);
+    end
+    result = A;
+endfunction
+
+A = zeros(9,9) * x(9);
+A = Add(A,x,9,1,l1);
+A = Add(A,x,9,2,l2);
+A = Add(A,x,9,3,l3);
+A = Add(A,x,9,4,l4);
+A = Add(A,x,9,5,l5);
+A = Add(A,x,9,6,l6);
+A = Add(A,x,9,7,l7);
+A = Add(A,x,9,8,x(8));
+A = Add(A,x,9,9,x(9));
+A
+b = [0,0,0,0,0,0,0,9,0]'
+A \ b

### 2018-02-27 books/category4programmers/1.1.main.hs
.

@@ -1,0 +1,7 @@
+f :: Float -> Int
+f x = round x
+g :: Int -> String
+g x = show x
+composed :: Float -> String
+composed = g . f
+main = print $ composed 11.0

### 2018-02-27 courses/columbia-cg-animation/week01/FOSSSim/TwoDScene.cpp

@@ -1,0 +1,6 @@
+#include "TwoDScene.h"
+
+scalar TwoDScene::computeKineticEnergy() const
+{
+    return -1.0;
+}

### 2018-02-27 courses/columbia-cg-animation/week01/include/eigen/Eigen/src/Core/Transpositions.h

@@ -1,0 +1,292 @@
+// This file is part of Eigen, a lightweight C++ template library
+// for linear algebra.
+//
+// Copyright (C) 2010 Gael Guennebaud <gael.guennebaud@inria.fr>
+//
+// Eigen is free software; you can redistribute it and/or
+// modify it under the terms of the GNU Lesser General Public
+// License as published by the Free Software Foundation; either
+// version 3 of the License, or (at your option) any later version.
+//
+// Alternatively, you can redistribute it and/or
+// modify it under the terms of the GNU General Public License as
+// published by the Free Software Foundation; either version 2 of
+// the License, or (at your option) any later version.
+//
+// Eigen is distributed in the hope that it will be useful, but WITHOUT ANY
+// WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+// FOR A PARTICULAR PURPOSE. See the GNU Lesser General Public License or the
+// GNU General Public License for more details.
+//
+// You should have received a copy of the GNU Lesser General Public
+// License and a copy of the GNU General Public License along with
+// Eigen. If not, see <http://www.gnu.org/licenses/>.
+
+#ifndef EIGEN_TRANSPOSITIONS_H
+#define EIGEN_TRANSPOSITIONS_H
+
+/** \class Transpositions
+  *
+  * \brief Represents a sequence of transpositions (row/column interchange)
+  *
+  * \param SizeAtCompileTime the number of transpositions, or Dynamic
+  * \param MaxSizeAtCompileTime the maximum number of transpositions, or Dynamic. This optional parameter defaults to SizeAtCompileTime. Most of the time, you should not have to specify it.
+  *
+  * This class represents a permutation transformation as a sequence of \em n transpositions
+  * \f$[T_{n-1} \ldots T_{i} \ldots T_{0}]\f$. It is internally stored as a vector of integers \c indices.
+  * Each transposition \f$ T_{i} \f$ applied on the left of a matrix (\f$ T_{i} M\f$) interchanges
+  * the rows \c i and \c indices[i] of the matrix \c M.
+  * A transposition applied on the right (e.g., \f$ M T_{i}\f$) yields a column interchange.
+  *
+  * Compared to the class PermutationMatrix, such a sequence of transpositions is what is
[…]

### 2018-02-27 courses/columbia-cg-animation/week01/include/eigen/bench/benchFFT.cpp

@@ -1,0 +1,128 @@
+// This file is part of Eigen, a lightweight C++ template library
+// for linear algebra. Eigen itself is part of the KDE project.
+//
+// Copyright (C) 2009 Mark Borgerding mark a borgerding net
+//
+// Eigen is free software; you can redistribute it and/or
+// modify it under the terms of the GNU Lesser General Public
+// License as published by the Free Software Foundation; either
+// version 3 of the License, or (at your option) any later version.
+//
+// Alternatively, you can redistribute it and/or
+// modify it under the terms of the GNU General Public License as
+// published by the Free Software Foundation; either version 2 of
+// the License, or (at your option) any later version.
+//
+// Eigen is distributed in the hope that it will be useful, but WITHOUT ANY
+// WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+// FOR A PARTICULAR PURPOSE. See the GNU Lesser General Public License or the
+// GNU General Public License for more details.
+//
+// You should have received a copy of the GNU Lesser General Public
+// License and a copy of the GNU General Public License along with
+// Eigen. If not, see <http://www.gnu.org/licenses/>.
+
+#include <bench/BenchUtil.h>
+#include <complex>
+#include <vector>
+#include <Eigen/Core>
+
+#include <unsupported/Eigen/FFT>
+
+using namespace Eigen;
+using namespace std;
+
+
+template <typename T>
+string nameof();
+
+template <> string nameof<float>() {return "float";}
+template <> string nameof<double>() {return "double";}
+template <> string nameof<long double>() {return "long double";}
+
+#ifndef TYPE
+#define TYPE float
+#endif
+
+#ifndef NFFT
+#define NFFT 1024
+#endif
+#ifndef NDATA
+#define NDATA 1000000
+#endif
+
+using namespace Eigen;
+
+template <typename T>
+void bench(int nfft,bool fwd,bool unscaled=false, bool halfspec=false)
+{
+    typedef typename NumTraits<T>::Real Scalar;
+    typedef typename std::complex<Scalar> Complex;
+    int nits = NDATA/nfft;
+    vector<T> inbuf(nfft);
+    vector<Complex > outbuf(nfft);
+    FFT< Scalar > fft;
+
+    if (unscaled) {
[…]

### 2018-02-27 courses/columbia-cg-animation/week02/FOSSSim/DragDampingForce.h

@@ -1,0 +1,32 @@
+#ifndef __DRAG_DAMPING_FORCE_H__
+#define __DRAG_DAMPING_FORCE_H__
+
+#include <Eigen/Core>
+#include <iostream>
+
+#include "Force.h"
+#include "MathDefs.h"
+
+class DragDampingForce : public Force
+{
+public:
+
+  DragDampingForce( const scalar& b );
+
+  virtual ~DragDampingForce();
+  
+  virtual void addEnergyToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, scalar& E );
+  
+  virtual void addGradEToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, VectorXs& gradE );
+  
+  virtual void addHessXToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, MatrixXs& hessE );
+  
+  virtual void addHessVToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, MatrixXs& hessE );
+  
+  virtual Force* createNewCopy();
+
+private:
+  scalar m_b;
+};
+
+#endif

### 2018-02-27 courses/columbia-cg-animation/week02/FOSSSim/GravitationalForce.cpp

@@ -1,0 +1,43 @@
+#include "GravitationalForce.h"
+
+void GravitationalForce::addEnergyToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, scalar& E )
+{
+  assert( x.size() == v.size() );
+  assert( x.size() == m.size() );
+  assert( x.size()%2 == 0 );
+  assert( m_particles.first >= 0 );  assert( m_particles.first < x.size()/2 );
+  assert( m_particles.second >= 0 ); assert( m_particles.second < x.size()/2 );
+
+  // Add milestone 2 code here.
+}
+
+void GravitationalForce::addGradEToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, VectorXs& gradE )
+{
+  assert( x.size() == v.size() );
+  assert( x.size() == m.size() );
+  assert( x.size() == gradE.size() );
+  assert( x.size()%2 == 0 );
+  assert( m_particles.first >= 0 );  assert( m_particles.first < x.size()/2 );
+  assert( m_particles.second >= 0 ); assert( m_particles.second < x.size()/2 );
+	
+  //GET PARTICLES
+  int size = 2;
+  int xistart = m_particles.first*2;
+  int xjstart = m_particles.second*2;  
+  VectorXs xi = x.segment(xistart, size);
+  VectorXs xj = x.segment(xjstart, size);
+	
+  //CALCULATE FORCE
+  VectorXs n = xi-xj;  
+  double lxixj = n.norm();
+  n /= lxixj;
+  double forceLength = m_G*m[xistart]*m[xjstart]/(lxixj*lxixj);
+  VectorXs dxiU = forceLength*n;
+  VectorXs dxjU = -forceLength*n;
+	
+  //CHANGE SYSTEM
+  gradE[xistart+0] += dxiU[0];
+  gradE[xistart+1] += dxiU[1];	
+  gradE[xjstart+0] += dxjU[0];
+  gradE[xjstart+1] += dxjU[1];
+}

### 2018-02-27 courses/columbia-cg-animation/week02/FOSSSim/GravitationalForce.h

@@ -1,0 +1,32 @@
+#ifndef __GRAVITATIONAL_FORCE_H__
+#define __GRAVITATIONAL_FORCE_H__
+
+#include <Eigen/Core>
+#include "Force.h"
+#include <iostream>
+
+class GravitationalForce : public Force
+{
+public:
+
+  GravitationalForce( const std::pair<int,int>& particles, const scalar& G );
+
+  virtual ~GravitationalForce();
+
+  virtual void addEnergyToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, scalar& E );
+
+  virtual void addGradEToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, VectorXs& gradE );
+
+  virtual void addHessXToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, MatrixXs& hessE );
+
+  virtual void addHessVToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, MatrixXs& hessE );
+
+  virtual Force* createNewCopy();
+
+private:
+  std::pair<int,int> m_particles;
+  // Gravitational constant
+  scalar m_G;
+};
+
+#endif

### 2018-02-27 courses/columbia-cg-animation/week02/FOSSSim/MathDefs.h

@@ -1,0 +1,17 @@
+#ifndef __MATH_DEFS_H__
+#define __MATH_DEFS_H__
+
+#include <Eigen/Core>
+#include <Eigen/StdVector>
+
+typedef double scalar;
+
+typedef Eigen::Matrix<scalar, 2, 1> Vector2s;
+typedef Eigen::Matrix<scalar, Eigen::Dynamic, 1> VectorXs;
+
+typedef Eigen::Matrix<scalar, 2, 2> Matrix2s;
+typedef Eigen::Matrix<scalar, Eigen::Dynamic, Eigen::Dynamic> MatrixXs;
+
+//typedef Matrix<int, 1, 2> RowVector2i;
+
+#endif

### 2018-02-27 courses/columbia-cg-animation/week02/FOSSSim/SpringForce.cpp

@@ -1,0 +1,47 @@
+#include "SpringForce.h"
+
+void SpringForce::addEnergyToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, scalar& E )
+{
+  assert( x.size() == v.size() );
+  assert( x.size()%2 == 0 );
+  assert( m_endpoints.first >= 0 );  assert( m_endpoints.first < x.size()/2 );
+  assert( m_endpoints.second >= 0 ); assert( m_endpoints.second < x.size()/2 );
+
+  // Add milestone 2 code here.
+}
+
+void SpringForce::addGradEToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, VectorXs& gradE )
+{
+  assert( x.size() == v.size() );
+  assert( x.size() == gradE.size() );
+  assert( x.size()%2 == 0 );
+  assert( m_endpoints.first >= 0 );  assert( m_endpoints.first < x.size()/2 );
+  assert( m_endpoints.second >= 0 ); assert( m_endpoints.second < x.size()/2 );
+
+  //GET PARTICLES
+  int size = 2;
+  int xistart = m_endpoints.first*2;
+  int xjstart = m_endpoints.second*2;  
+  VectorXs xi = x.segment(xistart, size);
+  VectorXs xj = x.segment(xjstart, size);
+	
+  //SPRING FORCE
+  VectorXs nhat = xi-xj;  
+  double lxixj = nhat.norm();
+  nhat /= lxixj;	
+  VectorXs dxiU = m_k*(lxixj-m_l0)*nhat;
+  VectorXs dxjU = -dxiU;  
+    
+  //SPRING DAMPING FORCE 
+  VectorXs vi = v.segment(xistart, size);
+  VectorXs vj = v.segment(xjstart, size);
+  double lvivj = (vi-vj).dot(nhat);
+  dxiU += m_b * nhat * lvivj; //F-
+  dxjU += -m_b * nhat * lvivj; //F+
+	
+  //CHANGE SYSTEM
+  gradE[xistart+0] += dxiU[0];
+  gradE[xistart+1] += dxiU[1];	
+  gradE[xjstart+0] += dxjU[0];
+  gradE[xjstart+1] += dxjU[1];
+}

### 2018-02-27 courses/columbia-cg-animation/week02/FOSSSim/SpringForce.h

@@ -1,0 +1,33 @@
+#ifndef __SPRING_FORCE_H__
+#define __SPRING_FORCE_H__
+
+#include <Eigen/Core>
+#include "Force.h"
+#include <iostream>
+
+class SpringForce : public Force
+{
+public:
+
+  SpringForce( const std::pair<int,int>& endpoints, const scalar& k, const scalar& l0, const scalar& b = 0.0 );
+
+  virtual ~SpringForce();
+  
+  virtual void addEnergyToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, scalar& E );
+  
+  virtual void addGradEToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, VectorXs& gradE );
+  
+  virtual void addHessXToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, MatrixXs& hessE );
+  
+  virtual void addHessVToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, MatrixXs& hessE );
+  
+  virtual Force* createNewCopy();
+
+private:
+  std::pair<int,int> m_endpoints;
+  scalar m_k;
+  scalar m_l0;
+  scalar m_b;
+};
+
+#endif

### 2018-02-27 courses/columbia-cg-animation/week02/include/eigen/bench/benchCholesky.cpp

@@ -1,0 +1,140 @@
+
+// g++ -DNDEBUG -O3 -I.. benchLLT.cpp  -o benchLLT && ./benchLLT
+// options:
+//  -DBENCH_GSL -lgsl /usr/lib/libcblas.so.3
+//  -DEIGEN_DONT_VECTORIZE
+//  -msse2
+//  -DREPEAT=100
+//  -DTRIES=10
+//  -DSCALAR=double
+
+#include <Eigen/Array>
+#include <Eigen/Cholesky>
+#include <bench/BenchUtil.h>
+using namespace Eigen;
+
+#ifndef REPEAT
+#define REPEAT 10000
+#endif
+
+#ifndef TRIES
+#define TRIES 10
+#endif
+
+typedef float Scalar;
+
+template <typename MatrixType>
+__attribute__ ((noinline)) void benchLLT(const MatrixType& m)
+{
+  int rows = m.rows();
+  int cols = m.cols();
+
+  int cost = 0;
+  for (int j=0; j<rows; ++j)
+  {
+    int r = std::max(rows - j -1,0);
+    cost += 2*(r*j+r+j);
+  }
+
+  int repeats = (REPEAT*1000)/(rows*rows);
+
+  typedef typename MatrixType::Scalar Scalar;
+  typedef Matrix<Scalar, MatrixType::RowsAtCompileTime, MatrixType::RowsAtCompileTime> SquareMatrixType;
+
+  MatrixType a = MatrixType::Random(rows,cols);
+  SquareMatrixType covMat =  a * a.adjoint();
+
+  BenchTimer timerNoSqrt, timerSqrt;
+
+  Scalar acc = 0;
+  int r = ei_random<int>(0,covMat.rows()-1);
+  int c = ei_random<int>(0,covMat.cols()-1);
+  for (int t=0; t<TRIES; ++t)
+  {
+    timerNoSqrt.start();
+    for (int k=0; k<repeats; ++k)
+    {
+      LDLT<SquareMatrixType> cholnosqrt(covMat);
+      acc += cholnosqrt.matrixL().coeff(r,c);
+    }
+    timerNoSqrt.stop();
+  }
+
+  for (int t=0; t<TRIES; ++t)
+  {
+    timerSqrt.start();
+    for (int k=0; k<repeats; ++k)
+    {
+      LLT<SquareMatrixType> chol(covMat);
+      acc += chol.matrixL().coeff(r,c);
+    }
+    timerSqrt.stop();
+  }
+
[…]

### 2018-02-27 courses/columbia-cg-animation/week02/include/eigen/blas/level1_impl.h

@@ -1,0 +1,344 @@
+// This file is part of Eigen, a lightweight C++ template library
+// for linear algebra.
+//
+// Copyright (C) 2009 Gael Guennebaud <gael.guennebaud@inria.fr>
+//
+// Eigen is free software; you can redistribute it and/or
+// modify it under the terms of the GNU Lesser General Public
+// License as published by the Free Software Foundation; either
+// version 3 of the License, or (at your option) any later version.
+//
+// Alternatively, you can redistribute it and/or
+// modify it under the terms of the GNU General Public License as
+// published by the Free Software Foundation; either version 2 of
+// the License, or (at your option) any later version.
+//
+// Eigen is distributed in the hope that it will be useful, but WITHOUT ANY
+// WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+// FOR A PARTICULAR PURPOSE. See the GNU Lesser General Public License or the
+// GNU General Public License for more details.
+//
+// You should have received a copy of the GNU Lesser General Public
+// License and a copy of the GNU General Public License along with
+// Eigen. If not, see <http://www.gnu.org/licenses/>.
+
+#include "common.h"
+
+int EIGEN_BLAS_FUNC(axpy)(int *n, RealScalar *palpha, RealScalar *px, int *incx, RealScalar *py, int *incy)
+{
+  Scalar* x = reinterpret_cast<Scalar*>(px);
+  Scalar* y = reinterpret_cast<Scalar*>(py);
+  Scalar alpha  = *reinterpret_cast<Scalar*>(palpha);
+
+//   std::cerr << "axpy " << *n << " " << alpha << " " << *incx << " " << *incy << "\n";
+
+  if(*incx==1 && *incy==1)    vector(y,*n) += alpha * vector(x,*n);
+  else if(*incx>0 && *incy>0) vector(y,*n,*incy) += alpha * vector(x,*n,*incx);
[…]

### 2018-04-24 texts/philosophy/introolavo.tex
.

@@
 Essa filosofia, por sua vez, é uma longa e rigososa dedução a partir de princípios universais abstratos -- precisamente o oposto do que penso que uma filosofia política deva ser.
+
+	O discurso da fé é sempre incompleto, semanticamente, porque aí não podemos ter o domínio cognitivo satisfatório dos objetos a que nos referimos.
+Eis por que nessa área é tão tentador cair no verbalismo oco, nos chavões e na busca de efeitos fáceis.
+A única substância que podemos dar a esse discurso é a da nossa própria busca de Deus, a dos nossos próprios tormentos interiores, a da nossa própria insuficiência, esperando que Ele mesmo complete, de algum modo, um sentido que nos escapa.
+
+	Como nos ensina o Professor Olavo de Carvalho, o poder, no sentido mais amplo e geral, é possibilidade de ação; no sentido estritamente político é a possibilidade de determinar as ações alheias.
+Os meios que os homens possuem para determinar a ação alheia podem ser reduzidos a três e apenas três poderes: escolher, gerar e destruir; respectivamente, o poder da inteligência humana, o poder da riqueza e o poder da violência.
+Esses poderes são exercidos, cada um a seu modo, em duas direções: numa direção passiva e numa direção ativa.
+
+	Segundo o Professor, o poder passivo da violência reside na justiça. Tende a dispersar-se, a nivelar o poder, a tudo resolver por livre acordo, a desacelerar a ação.
+
+	Já o poder ativo da violência reside na milícia. Tende a concentrar-se, à hierarquia vertical, à disciplina rígida, a instaurar a obediência automática que produz a máxima eficiência e rapidez.
+
+	A justiça e, em última instância, a milícia são o fundamento da autoridade esponsável pela manutenção da ordem social, podendo ser garantidos apenas pela capacidade efetiva de fazer uso legítimo da violência.
+
+	Diante dessa realidade inescapável, cabe a cada um de nós perguntar: (I) Quando a expressão passiva do poder responsável pela ordem social esgota seus recursos, qual é a única opção que nos resta?
+(II) Do mesmo modo, qual é a forma correta e mais inteligente de exercer esta opção para que ela não seja assimilada e voltada contra o próprio poder que a exerce, como em um golpe de judô?
+
+	Até respondermos essas perguntas só poderemos ter uma única certeza: a de que o poder real não está num prédio, num pedaço de papel, numa toga ou num fardamento, está na possibilidade de determinar as ações alheias -- e neste momento o chefe do maior esquema de corrupção de um país está determinando as ações de toda uma nação, mantendo os destinos de milhões e milhões de pessoas ao alcance do impacto de sua sanha por uma quantidade ainda maior de poder.
 \end{document}

### 2018-04-24 books/FiniteDifferenceComputingwithPDEs/vibration_tests.py

@@ -1,0 +1,12 @@
+from math import pi
+import numpy as np
+import matplotlib.pyplot as plt
+from vibration_undamped import *
+
+def test_three_steps():
+    I = 1; w = 2*pi; dt = 0.1; T = 1
+    u_by_hand = np.array([1.000000000000000, 0.802607911978213, 0.288358920740053])
+    u, t = solver(I, w, dt, T)
+    diff = np.abs(u_by_hand - u[:3]).max()
+    tol = 1E-14
+    assert diff < tol

### 2018-04-24 courses/columbia-cg-animation/week03/FOSSSim/ImplicitEuler.cpp

@@ -1,0 +1,63 @@
+#include "ImplicitEuler.h"
+
+bool ImplicitEuler::stepScene(TwoDScene& scene, scalar h)
+{
+  VectorXs& qn = scene.getX();
+  VectorXs& qn1 = scene.getX();
+  VectorXs& qdotn = scene.getV();
+  VectorXs& qdotn1 = scene.getV();
+    
+  const VectorXs& m = scene.getM();
+  const MatrixXs M = m.asDiagonal();
+  assert(qn.size() == qdotn.size());
+  assert(qn.size() == m.size());
+
+  int ndof = qn.size();
+
+  VectorXs stepqn = h*qdotn;
+  VectorXs& stepqn1 = stepqn;
+  VectorXs stepqdotn = VectorXs::Zero(ndof);
+  VectorXs& stepqdotn1 = stepqdotn;
+  
+  MatrixXs A(ndof,ndof);
+
+  VectorXs b(ndof);
+  VectorXs deltaqdoti1(ndof);
+  scalar stplen = std::numeric_limits<scalar>::infinity();
+
+  int iteration_i = 0;
+  int MAXITERATIONS = 1000;
+  while ((stplen >= 1.0e-9)&&(iteration_i < MAXITERATIONS))
+  {
+    //−M(qi˙n+1 − q˙n) + hF(qn + hqi˙n+1, qi˙n+1)
+    b.setZero();
+    scene.accumulateGradU(b,/*qn+*/stepqn,/*qdotn+*/stepqdotn);
+    b *= -h;
+    b += -M*stepqdotn;
+
+    zeroFixedDoFs(scene, b);
+
+    //M − (h2*∂F/∂qn+1 + h*∂F/∂q˙n+1 )
+    //where ∂F/∂qn+1 and ∂F/∂q˙n+1 are evaluated at (qn+hqi˙n+1, qi˙n+1).
+    A.setZero();
+    scene.accumulateddUdxdx(A,/*qn+*/stepqn,/*qdotn+*/stepqdotn);
+    A *= h;
+    scene.accumulateddUdxdv(A,/*qn+*/stepqn,/*qdotn+*/stepqdotn);
+    A *= -h;
+    A = M - A;
+    setFixedRowsAndColsToIdentity(scene, A);
+
+    deltaqdoti1 = A.fullPivLu().solve(b);
+
+    stepqdotn1 += deltaqdoti1;
+    stepqn1 = h*(qdotn+stepqdotn);
[…]

### 2018-04-24 courses/columbia-cg-animation/week03/FOSSSim/LinearizedImplicitEuler.cpp

@@ -1,0 +1,45 @@
+#include "LinearizedImplicitEuler.h"
+
+
+
+bool LinearizedImplicitEuler::stepScene(TwoDScene& scene, scalar h )
+{
+  VectorXs& qn = scene.getX();
+  VectorXs& qn1 = qn;
+  VectorXs& qdotn = scene.getV();
+  VectorXs& qdotn1 = qdotn; 
+  const VectorXs& m = scene.getM();
+  assert(qn.size() == qdotn.size());
+  assert(qn.size() == m.size());
+    
+  int ndof = qn.size();
+
+  // Ax = b
+  // b
+  VectorXs b = VectorXs::Zero(ndof);
+  VectorXs stepq = h*qdotn;
+  VectorXs stepqdot = VectorXs::Zero(ndof);
+  scene.accumulateGradU(b,/*qn+*/stepq, /*qdotn+*/stepqdot);
+  b *= -h;
+  zeroFixedDoFs(scene, b);
+
+  //A
+  MatrixXs partialFpartialq = MatrixXs::Zero(ndof,ndof);
+  scene.accumulateddUdxdx(partialFpartialq,/*qn+*/stepq,/*qdotn+*/stepqdot);
+    
+  MatrixXs partialFpartialqdot = MatrixXs::Zero(ndof,ndof);
+  scene.accumulateddUdxdv(partialFpartialqdot,/*qn+*/stepq,/*qdotn+*/stepqdot);
+  
+  MatrixXs M = m.asDiagonal();
+  MatrixXs A = M - (h*h*-partialFpartialq + h*-partialFpartialqdot);
+  setFixedRowsAndColsToIdentity(scene,A);
+
+  {
+      //Ax = b
+      VectorXs deltaqdot = A.fullPivLu().solve(b);
+      qdotn1 = qdotn + deltaqdot;
+      qn1 = qn + h*qdotn1;
+  }
+  
+  return true;
+}

### 2018-04-24 courses/columbia-cg-animation/week03/FOSSSim/LinearizedImplicitEuler.h

@@ -1,0 +1,42 @@
+#ifndef __LINEARIZED_IMPLICIT_EULER__
+#define __LINEARIZED_IMPLICIT_EULER__
+
+#include <Eigen/Dense>
+#include <iostream>
+
+#include "SceneStepper.h"
+
+class LinearizedImplicitEuler : public SceneStepper
+{
+public:
+  LinearizedImplicitEuler();
+  
+  virtual ~LinearizedImplicitEuler();
+  
+  virtual bool stepScene( TwoDScene& scene, scalar dt );
+  
+  virtual std::string getName() const;
+  
+  static void zeroFixedDoFs( const TwoDScene& scene, VectorXs& vec )
+{
+  int nprts = scene.getNumParticles();
+  for( int i = 0; i < nprts; ++i ) if( scene.isFixed(i) ) vec.segment<2>(2*i).setZero();
+}
+
+static void setFixedRowsAndColsToIdentity( const TwoDScene& scene, MatrixXs& mat )
+{
+  int nprts = scene.getNumParticles();
+  for( int i = 0; i < nprts; ++i ) if( scene.isFixed(i) )
+  {
+    mat.row(2*i).setZero();
+    mat.row(2*i+1).setZero();
+    mat.col(2*i).setZero();
+    mat.col(2*i+1).setZero();
+    // Set diagonal of fixed degrees of freedom to 1
+    mat(2*i,2*i) = 1.0;
+    mat(2*i+1,2*i+1) = 1.0;
+  }  
+}
+};
+
+#endif

### 2018-04-24 courses/columbia-cg-animation/week03/FOSSSim/MathDefs.h

@@ -1,0 +1,20 @@
+#ifndef __MATH_DEFS_H__
+#define __MATH_DEFS_H__
+
+#include <Eigen/Core>
+#include <Eigen/StdVector>
+
+typedef double scalar;
+
+typedef Eigen::Matrix<scalar, 2, 1> Vector2s;
+typedef Eigen::Matrix<scalar, Eigen::Dynamic, 1> VectorXs;
+
+typedef Eigen::Matrix<scalar, 2, 2> Matrix2s;
+typedef Eigen::Matrix<scalar, 4, 4> Matrix4s;
+typedef Eigen::Matrix<scalar, Eigen::Dynamic, Eigen::Dynamic> MatrixXs;
+
+//typedef Matrix<int, 1, 2> RowVector2i;
+//
+
+
+#endif

### 2018-04-24 courses/columbia-cg-animation/week03/FOSSSim/SimpleGravityForce.h

@@ -1,0 +1,30 @@
+#ifndef __SIMPLE_GRAVITY_FORCE_H__
+#define __SIMPLE_GRAVITY_FORCE_H__
+
+#include <Eigen/Core>
+#include "Force.h"
+#include <iostream>
+
+class SimpleGravityForce : public Force
+{
+public:
+
+  SimpleGravityForce( const Vector2s& gravity );
+
+  virtual ~SimpleGravityForce();
+  
+  virtual void addEnergyToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, scalar& E );
+  
+  virtual void addGradEToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, VectorXs& gradE );
+  
+  virtual void addHessXToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, MatrixXs& hessE );
+  
+  virtual void addHessVToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, MatrixXs& hessE );
+  
+  virtual Force* createNewCopy();
+
+private:
+  Vector2s m_gravity;
+};
+
+#endif

### 2018-04-24 courses/columbia-cg-animation/week04/FOSSSim/CollisionHandler.h

@@ -1,0 +1,79 @@
+#ifndef __COLLISION_HANDLER__
+#define __COLLISION_HANDLER__
+
+#include "TwoDScene.h"
+#include "MathDefs.h"
+#include <fstream>
+#include <vector>
+
+struct CollisionInfo
+{
+public:
+    enum collisiontype { PP, PE, PH };
+    
+    CollisionInfo(collisiontype type, int idx1, int idx2, const Vector2s &n, double time) : m_type(type), m_idx1(idx1), m_idx2(idx2), m_n(n), m_time(time) {}
+    
+    std::string toString() const
+    {
+        std::stringstream ss;
+        switch (m_type)
+        {
+            case PP:
+                ss << "Particle " << m_idx1 << " - Particle " << m_idx2 << " with normal = " << m_n.transpose();
+                break;
+            case PE:
+                ss << "Particle " << m_idx1 << " - Edge " << m_idx2 << " with normal = " << m_n.transpose();
+                break;
+            case PH:
+                ss << "Parnn   nv ticle " << m_idx1 << " - Halfplane " << m_idx2 << " with normal = " << m_n.transpose();
+                break;
+        }
+        return ss.str();
+    }
+    
+    bool operator == (const CollisionInfo & c) const { return m_type == c.m_type && m_idx1 == c.m_idx1 && m_idx2 == c.m_idx2; }
+
+    collisiontype m_type;
+    int m_idx1, m_idx2;
+    Vector2s m_n;
+    double m_time;
+};
+
+class CollisionHandler
+{
+public:
+    CollisionHandler(double COR) : m_COR(COR) {}
+    
+    virtual ~CollisionHandler() {}
+    
+    virtual void handleCollisions( TwoDScene& scene, const VectorXs &oldpos, VectorXs &oldvel, scalar dt ) = 0;
+    
+    virtual std::string getName() const = 0;
+    
+    // Returns the coefficient of restitution set in the scene XML
+    double getCOR() {return m_COR;}
+    
+    void clearImpulses() {m_impulses.clear();}
+    
+    const std::vector<CollisionInfo> &getImpulses() const {return m_impulses;}
+    
+    void serializeImpulses(std::ofstream &ofs);
+    
+    void loadImpulses(std::vector<CollisionInfo> &impulses, std::ifstream &ifs);
+    
+protected:
+    void addParticleParticleImpulse(int idx1, int idx2, const Vector2s &n, double time);
+    
[…]

### 2018-04-24 courses/columbia-cg-animation/week04/FOSSSim/MathDefs.h

@@ -1,0 +1,21 @@
+#ifndef __MATH_DEFS_H__
+#define __MATH_DEFS_H__
+
+#include <Eigen/Core>
+#include <Eigen/StdVector>
+
+typedef double scalar;
+
+typedef Eigen::Matrix<scalar, 2, 1> Vector2s;
+typedef Eigen::Matrix<scalar, Eigen::Dynamic, 1> VectorXs;
+
+typedef Eigen::Matrix<scalar, 2, 2> Matrix2s;
+typedef Eigen::Matrix<scalar, Eigen::Dynamic, Eigen::Dynamic> MatrixXs;
+
+//typedef Matrix<int, 1, 2> RowVector2i;
+template <typename T>
+T clamp(T n, T lower, T upper) {
+  return std::max(lower, std::min(n, upper));
+}
+
+#endif

### 2018-04-24 courses/columbia-cg-animation/week04/FOSSSim/PenaltyForce.cpp

@@ -1,0 +1,136 @@
+#include "PenaltyForce.h"
+#include "TwoDScene.h"
+
+void PenaltyForce::addEnergyToTotal( const VectorXs& x, const VectorXs& v, const VectorXs& m, scalar& E )
+{
+    // Feel free to implement if you feel like doing so.
+}
+
+// BEGIN STUDENT CODE
+
+
+// Adds the gradient of the penalty potential (-1 * force) for a pair of 
+// particles to the total.
+// Read the positions of the particles from the input variable x. Radii can
+// be obtained from the member variable m_scene, the penalty force stiffness 
+// from member variable m_k, and penalty force thickness from member variable
+// m_thickness.
+// Inputs:
+//   x:    The positions of the particles in the scene. 
+//   idx1: The index of the first particle, i.e. the position of this particle
+//         is ( x[2*idx1], x[2*idx1+1] ).
+//   idx2: The index of the second particle.
+// Outputs:
+//   gradE: The total gradient of penalty force. *ADD* the particle-particle
+//          gradient to this total gradient.
+void PenaltyForce::addParticleParticleGradEToTotal(const VectorXs &x, int idx1, int idx2, VectorXs &gradE)
+{
+    int index1 = 2*idx1;
+    int index2 = 2*idx2;
+    
+    VectorXs x1 = x.segment<2>(index1);
+    VectorXs x2 = x.segment<2>(index2);
+    
+    double r1 = m_scene.getRadius(idx1);
+    double r2 = m_scene.getRadius(idx2);
+    
+    VectorXs n = x2-x1;
+    scalar nnorm = n.norm();
+    
+    VectorXs nhat = n;
+    nhat.normalize();
+    
+    scalar size = r1 + r2 + m_thickness; 
+    if(nnorm < size)
+    {        
+        gradE.segment<2>(index1) -= m_k * (nnorm - size) * nhat;
+        gradE.segment<2>(index2) += m_k * (nnorm - size) * nhat;
+    }    
+}
+
+// Adds the gradient of the penalty potential (-1 * force) for a particle-edge
+// pair to the total.
+// Read the positions of the particle and edge endpoints from the input
+// variable x.
+// Inputs:
+//   x:    The positions of the particles in the scene.
+//   vidx: The index of the particle.
[…]

### 2018-04-24 courses/columbia-cg-animation/week04/include/eigen/bench/bench_gemm.cpp

@@ -1,0 +1,161 @@
+
+// g++-4.4 bench_gemm.cpp -I .. -O2 -DNDEBUG -lrt -fopenmp && OMP_NUM_THREADS=2  ./a.out
+// icpc bench_gemm.cpp -I .. -O3 -DNDEBUG -lrt -openmp  && OMP_NUM_THREADS=2  ./a.out
+
+#include <iostream>
+#include <Eigen/Core>
+#include <bench/BenchTimer.h>
+
+using namespace std;
+using namespace Eigen;
+
+#ifndef SCALAR
+#define SCALAR float
+#endif
+
+typedef SCALAR Scalar;
+typedef Matrix<Scalar,Dynamic,Dynamic> M;
+
+#ifdef HAVE_BLAS
+
+extern "C" {
+  #include <bench/btl/libs/C_BLAS/blas.h>
+}
+
+static float fone = 1;
+static float fzero = 0;
+static double done = 1;
+static double szero = 0;
+static char notrans = 'N';
+static char trans = 'T';
+static char nonunit = 'N';
+static char lower = 'L';
+static char right = 'R';
+static int intone = 1;
+
+void blas_gemm(const MatrixXf& a, const MatrixXf& b, MatrixXf& c)
+{
+  int M = c.rows(); int N = c.cols(); int K = a.cols();
+  int lda = a.rows(); int ldb = b.rows(); int ldc = c.rows();
+
+  sgemm_(&notrans,&notrans,&M,&N,&K,&fone,
+         const_cast<float*>(a.data()),&lda,
+         const_cast<float*>(b.data()),&ldb,&fone,
+         c.data(),&ldc);
+}
+
+void blas_gemm(const MatrixXd& a, const MatrixXd& b, MatrixXd& c)
+{
+  int M = c.rows(); int N = c.cols(); int K = a.cols();
+  int lda = a.rows(); int ldb = b.rows(); int ldc = c.rows();
+
+  dgemm_(&notrans,&notrans,&M,&N,&K,&done,
+         const_cast<double*>(a.data()),&lda,
+         const_cast<double*>(b.data()),&ldb,&done,
+         c.data(),&ldc);
+}
+
+#endif
+
+template<typename M>
+void gemm(const M& a, const M& b, M& c)
+{
+  c.noalias() += a * b;
+}
+
+int main(int argc, char ** argv)
+{
[…]

### 2018-04-24 courses/columbia-cg-animation/week04/include/eigen/demos/opengl/quaternion_demo.cpp

@@ -1,0 +1,670 @@
+// This file is part of Eigen, a lightweight C++ template library
+// for linear algebra.
+//
+// Copyright (C) 2008 Gael Guennebaud <gael.guennebaud@inria.fr>
+//
+// Eigen is free software; you can redistribute it and/or
+// modify it under the terms of the GNU Lesser General Public
+// License as published by the Free Software Foundation; either
+// version 3 of the License, or (at your option) any later version.
+//
+// Alternatively, you can redistribute it and/or
+// modify it under the terms of the GNU General Public License as
+// published by the Free Software Foundation; either version 2 of
+// the License, or (at your option) any later version.
+//
+// Eigen is distributed in the hope that it will be useful, but WITHOUT ANY
+// WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+// FOR A PARTICULAR PURPOSE. See the GNU Lesser General Public License or the
+// GNU General Public License for more details.
+//
+// You should have received a copy of the GNU Lesser General Public
+// License and a copy of the GNU General Public License along with
+// Eigen. If not, see <http://www.gnu.org/licenses/>.
+
+#include "quaternion_demo.h"
+#include "icosphere.h"
+
+#include <Eigen/Array>
+#include <Eigen/QR>
+#include <Eigen/LU>
+
+#include <QEvent>
+#include <QMouseEvent>
+#include <QInputDialog>
+#include <QGridLayout>
+#include <QButtonGroup>
+#include <QRadioButton>
+#include <QDockWidget>
+#include <QPushButton>
+#include <QGroupBox>
+
+using namespace Eigen;
+
+class FancySpheres
+{
+  public:
+    EIGEN_MAKE_ALIGNED_OPERATOR_NEW
+    
+    FancySpheres()
+    {
+      const int levels = 4;
+      const float scale = 0.33;
+      float radius = 100;
+      std::vector<int> parents;
+
+      // leval 0
+      mCenters.push_back(Vector3f::Zero());
+      parents.push_back(-1);
[…]

### 2018-04-24 courses/columbia-cg-animation/week04/include/eigen/test/determinant.cpp

@@ -1,0 +1,77 @@
+// This file is part of Eigen, a lightweight C++ template library
+// for linear algebra.
+//
+// Copyright (C) 2008 Benoit Jacob <jacob.benoit.1@gmail.com>
+// Copyright (C) 2008 Gael Guennebaud <gael.guennebaud@inria.fr>
+//
+// Eigen is free software; you can redistribute it and/or
+// modify it under the terms of the GNU Lesser General Public
+// License as published by the Free Software Foundation; either
+// version 3 of the License, or (at your option) any later version.
+//
+// Alternatively, you can redistribute it and/or
+// modify it under the terms of the GNU General Public License as
+// published by the Free Software Foundation; either version 2 of
+// the License, or (at your option) any later version.
+//
+// Eigen is distributed in the hope that it will be useful, but WITHOUT ANY
+// WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+// FOR A PARTICULAR PURPOSE. See the GNU Lesser General Public License or the
+// GNU General Public License for more details.
+//
+// You should have received a copy of the GNU Lesser General Public
+// License and a copy of the GNU General Public License along with
+// Eigen. If not, see <http://www.gnu.org/licenses/>.
+
+#include "main.h"
+#include <Eigen/LU>
+
+template<typename MatrixType> void determinant(const MatrixType& m)
+{
+  /* this test covers the following files:
+     Determinant.h
+  */
+  typedef typename MatrixType::Index Index;
+  Index size = m.rows();
+
+  MatrixType m1(size, size), m2(size, size);
+  m1.setRandom();
+  m2.setRandom();
+  typedef typename MatrixType::Scalar Scalar;
+  Scalar x = ei_random<Scalar>();
+  VERIFY_IS_APPROX(MatrixType::Identity(size, size).determinant(), Scalar(1));
+  VERIFY_IS_APPROX((m1*m2).eval().determinant(), m1.determinant() * m2.determinant());
+  if(size==1) return;
+  Index i = ei_random<Index>(0, size-1);
+  Index j;
+  do {
+    j = ei_random<Index>(0, size-1);
+  } while(j==i);
[…]

### 2018-04-24 courses/columbia-cg-animation/week05/FOSSSim/ContinuousTimeUtilities.h

@@ -1,0 +1,79 @@
+#ifndef CONTINUOUS_TIME_UTILITIES_H
+#define CONTINUOUS_TIME_UTILITIES_H
+
+#include <vector>
+#include <list>
+#include <cassert>
+#include <iostream>
+#include "rpoly.h"
+
+struct Interval
+{
+    Interval(double s, double e): m_s(s), m_e(e) {assert(m_s <= m_e);}
+    double m_s, m_e;
+    
+    bool operator<(const Interval &other) const {return m_s < other.m_s;}
+};
+
+bool overlap(const Interval &a, const Interval &b);
+Interval Iunion(const Interval &a, const Interval &b);
+Interval Iintersect(const Interval &a, const Interval &b);
+
+class Intervals
+{
+public:
+    Intervals(const std::vector<Interval> &intervals);
+    
+    double findNextSatTime(double t);
+    
+    friend Intervals intersect(const Intervals &i1, const Intervals &i2);
+    
+    friend std::ostream& operator<<(std::ostream &os, const Intervals &inter);
+    
+private:
+    std::list<Interval> m_intervals;
+    
+    void consolidateIntervals();
+    
+};
+
+Intervals intersect(const Intervals &i1, const Intervals &i2);
+std::ostream &operator<<(std::ostream &os, const Intervals &inter);
+
+class Polynomial
+{
+public:
+    Polynomial(const std::vector<double> &coeffs);
+    
+    double evaluate(double t) const ;
+    
+    const std::vector<double> &getCoeffs() const {return m_coeffs;}
+    
+private:
+    std::vector<double> m_coeffs;
+};
+
+class PolynomialIntervalSolver
+{
+public:
+    static double findFirstIntersectionTime(const std::vector<Polynomial> &polys);
+
+    static void writePolynomials(std::ostream & os);
+    static void readPolynomials(std::vector<Polynomial> & polynomials, std::istream & is);
+    
+    static std::vector<Polynomial> & getPolynomials() { return s_polynomials; }
+    static void clearPolynomials() { s_polynomials.clear(); }
+    
+private:
+    
+    static Intervals findPolyIntervals(const Polynomial &poly);
+    
+    static RootFinder rf;
+    
+private:
+    static std::vector<Polynomial> s_polynomials;
+    
+};
+
+
+#endif

### 2018-04-24 courses/columbia-cg-animation/week05/FOSSSim/HybridCollisionComparison.h

@@ -1,0 +1,43 @@
+#ifndef HYBRID_COLLISION_COMPARISON
+#define HYBRID_COLLISION_COMPARISON
+
+#include "HybridCollisionHandler.h"
+#include <vector>
+#include <iostream>
+
+struct ImpactZoneInfo
+{
+    ImpactZones Z;
+    VectorXs q;
+    VectorXs qdot;
+};
+
+class HybridCollisionComparison
+{
+public:
+    HybridCollisionComparison();
+    
+    void reset();
+    void load(std::ifstream &ifs);
+    void serialize(std::ofstream &ofs);
+    
+    void serializeImpactZones(const ImpactZones &Z, const VectorXs &q, const VectorXs &qdot, int iter);
+    void serializePostImpulses(const VectorXs &q, const VectorXs &qdot);
+    
+    bool comparePI(VectorXs &q, VectorXs &qdot);
+    
+    bool compareIZ(const ImpactZones &iz, const VectorXs &q, const VectorXs &qdot, int iter);
+    bool doneWithImpactZones(int iter);
+    
+    bool failed() {return fail;}
+    
+private:
+    VectorXs PIq;
+    VectorXs PIqdot;
+    std::vector<ImpactZoneInfo> IZiters;
+    
+    bool fail;
+    
+};
+
+#endif

### 2018-04-24 courses/columbia-cg-animation/week05/include/eigen/bench/vdw_new.cpp

@@ -1,0 +1,55 @@
+#include <Eigen/Array>
+
+using namespace Eigen;
+
+#ifndef SCALAR
+#define SCALAR float
+#endif
+
+#ifndef SIZE
+#define SIZE 10000
+#endif
+
+#ifndef REPEAT
+#define REPEAT 10000
+#endif
+
+typedef Matrix<SCALAR, Eigen::Dynamic, 1> Vec;
+
+using namespace std;
+
+SCALAR E_VDW(const Vec &interactions1, const Vec &interactions2)
+{
+  return (interactions2.cwise()/interactions1)
+         .cwise().cube()
+         .cwise().square()
+         .cwise().square()
+         .sum();
+}
+
+int main() 
+{
+  //
+  //          1   2   3   4  ... (interactions)
+  // ka       .   .   .   .  ...
+  // rab      .   .   .   .  ...
+  // energy   .   .   .   .  ...
+  // ...     ... ... ... ... ...
+  // (variables
+  //    for
+  // interaction)
+  //
+  Vec interactions1(SIZE), interactions2(SIZE); // SIZE is the number of vdw interactions in our system
+  // SetupCalculations()
+  SCALAR rab = 1.0;  
+  interactions1.setConstant(2.4);
+  interactions2.setConstant(rab);
+  
+  // Energy()
+  SCALAR energy = 0.0;
+  for (unsigned int i = 0; i<REPEAT; ++i) {
+    energy += E_VDW(interactions1, interactions2);
+    energy *= 1 + 1e-20 * i; // prevent compiler from optimizing the loop
+  }
+  cout << "energy = " << energy << endl;
+}

### 2018-04-24 sources/cpp/quadtree/quadtree/quadtree/resource.h

@@ -1,0 +1,14 @@
+//{{NO_DEPENDENCIES}}
+// Microsoft Visual C++ generated include file.
+// Used by quadtree.rc
+
+// Next default values for new objects
+// 
+#ifdef APSTUDIO_INVOKED
+#ifndef APSTUDIO_READONLY_SYMBOLS
+#define _APS_NEXT_RESOURCE_VALUE        101
+#define _APS_NEXT_COMMAND_VALUE         40001
+#define _APS_NEXT_CONTROL_VALUE         1001
+#define _APS_NEXT_SYMED_VALUE           101
+#endif
+#endif

### 2018-05-06 books/FundamentalsMatrixComputations/exercise.01.003.025.tex
Fundamentals of Matrix Computations

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{xcolor}
    \begin{document}
    Write down the numbers $1, 2, 3, ..., n-1$ on a line. Immediately below 
   these, write down the numbers $n - 1, n - 2, n - 3,..., 1$. Add these numbers up by 
   summing column-wise first. Conclude that 
   $$2*(1 + 2 + ... + n - 1) = n(n - 1)$$

   \begin{align*}
	A & = 1+2+3+...+(n-1)\\
	B &= (n-1) + (n-2) + (n-3) + ... + 1\\
	A + B &= [1 + (n - 1)] + [2 + (n-2)] + ... + [(n-1) + 1]\\
	A + B &= \sum_{i=1}^{n-1}{[i+(n-i)]}\\
	A + B &= \sum_{i=1}^{n-1}{n}\\
	A + B &= n*\sum_{i=1}^{n-1}{1}\\	
	A + B &= n*(n-1)\\
   \end{align*}

    \end{document}

### 2018-05-06 books/FundamentalsMatrixComputations/exercise.01.003.026.tex
Fundamentals of Matrix Computations

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{xcolor}
\begin{document}
	In this exercise you will use mathematical induction to draw the same\\
	conclusion as in the previous exercise. If you are weak on mathematical induction,\\ 
	you should definitely work this exercise.

	We wish to prove that\\
	$$\sum_{i=1}^{n-1} = \frac{n(n-1)}{2}$$
	\\
	for all positive integers n.\\
	\\
	Begin by showing that (1.3.27) holds when $n = 1$. The sum on the left-hand side is empty in this case. If you feel nervous about this, you can check the case $n = 2$ as well. Next show that if A.3.27) holds for $n = k$, then it holds also holds for $n ? k + 1$. That is, show that 
	$$\sum_{i=1}^{k} = \frac{(n+1)k}{2}$$
	is true, assuming that\\
	$$\sum_{i=1}^{k-1} = \frac{k(k-1)}{2}$$
	is true. This is just a matter of simple algebra. Once you have done this, you will 
	have proved by induction that A.3.27) holds for all positive integers n.\\
	Proof\\
	\\
	Step 1 (Base Case):
	\begin{align*}
		n = 1\\
		\sum_{i=1}^{1-1} &= \sum_{i=1}^{0} = 0\\
		\sum_{i=1}^{n-1} &= \frac{n(n-1)}{2}\\
		&= \frac{1(1-1)}{2}\\
		&= \frac{1(0)}{2}\\
		&= \frac{0}{2}\\
		&= 0\\
		\square
	\end{align*}
	\\
	Step 2\\
	\begin{align*}
		n &= n + 1\\
		\sum_{i=1}^{n}{i} &= \frac{(n+1)((n+1)-1)}{2}\\
		&= \frac{(n+1)(n+1-1)}{2}\\
		&= \frac{(n+1)n}{2}\\
		&= \frac{n^2+n}{2}\\
		&= \frac{n^2+n-n}{2}+\frac{n}{2}\\
		&= \frac{n(n-1)+n}{2}+\frac{n}{2}\\
		&= \frac{n(n-1)}{2}+\frac{n}{2}+\frac{n}{2}\\
		&= \frac{n(n-1)}{2}+\frac{2n}{2}\\
		&= \frac{n(n-1)}{2}+n\\
		&= (\sum_{i=1}^{n-1}{i})+n\\
		&= \sum_{i=1}^{n}{i}\\		
	\end{align*}
\end{document}

### 2018-05-06 books/FundamentalsMatrixComputations/exercise.01.004.015.tex
Fundamentals of Matrix Computations

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{systeme}
\usepackage{hyperref}
\begin{document}
	Exercise 1.4.15\\
	Let\\
	\begin{align*}
	A &= \begin{bmatrix}
		4 & 0\\
		0 & 9\\
		\end{bmatrix}
	\end{align*}
	(a) Prove that A is positive definite,\\
	(b) Calculate the Cholesky factor of $A$,\\
	(c) Find three other upper triangular matrices $R$ such that $A = R^TR$,\\
	(d) Let A be any $n \times n$ positive definite matrix. How many upper-triangular matrices $R$ such that $A = R^TR$ are there?\\
	\\
	Based on the work of \url{https://en.wikipedia.org/wiki/Andr\%C3\%A9-Louis_Cholesky}\\
	\\
	Proofs:\\
	(a)\\
	\begin{align*}
	x^TAx &= \begin{bmatrix}
	x_{11} & x_{21}\\
	\end{bmatrix} * \begin{bmatrix}
	4 & 0\\
	0 & 9\\
	\end{bmatrix} * \begin{bmatrix}
	x_{11}\\
	x_{21}\\
	\end{bmatrix}\\
	&= \begin{bmatrix}
	x_{11}*4 + x_{21}*0 & x_{11}*0 + x_{21}*9\\
	\end{bmatrix} * \begin{bmatrix}
	x_{11}\\
	x_{21}\\
	\end{bmatrix}\\
	&= \begin{bmatrix}
	x_{11}*4 & x_{21}*9\\
	\end{bmatrix} * \begin{bmatrix}
	x_{11}\\
	x_{21}\\
	\end{bmatrix}\\
	&= \begin{bmatrix}
	x_{11}*4*x_{11} & x_{21}*9*x_{21}\\
	\end{bmatrix}\\	
	&= \begin{bmatrix}
	4x_{11}^2 & 9x_{21}^2\\
	\end{bmatrix} \text{ necessarily} > 0\\	
	\end{align*}
	\\
	(b)\\
	\begin{align*}
		R &= \begin{bmatrix}
			r_{11} & r_{12}\\
			0 & r_{22}\\
			\end{bmatrix}\\
		A &= \begin{bmatrix}
		4 & 0\\
		0 & 9\\
		\end{bmatrix}\\
		R^TR &= A\\
		\begin{bmatrix}
		r_{11} & 0\\
		r_{12} & r_{22}\\
		\end{bmatrix} \begin{bmatrix}
		r_{11} & r_{12}\\
		0 & r_{22}\\
		\end{bmatrix} &= \begin{bmatrix}
		4 & 0\\
		0 & 9\\
		\end{bmatrix}\\
		\begin{bmatrix}
		r_{11}*r_{11}+0*0 & r_{11}*r_{12} + 0*r_{22}\\
		r_{12}*r_{11}+r_{22}*0 & r_{12}*r_{12} + r_{22}*r_{22}\\
		\end{bmatrix} &= \begin{bmatrix}
		4 & 0\\
		0 & 9\\
		\end{bmatrix}\\
		\\
		r_{11}*r_{11}+0*0 = 4\\
		r_{11}*r_{12} + 0*r_{22} = 0\\
		r_{12}*r_{11}+r_{22}*0 = 0\\
		r_{12}*r_{12} + r_{22}*r_{22} = 9\\
		\\
		r_{11}^2 = 4\\
		r_{11}*r_{12} = 0\\
		r_{12}*r_{11} = 0\\
		r_{12}^2 + r_{22}^2 = 9\\
		\\
		r_{11} = 2\\
		r_{11}*r_{12} = 0\\
		r_{12}*r_{11} = 0\\
		r_{12}^2 + r_{22}^2 = 9\\
		\\
		r_{11} = 2\\
		2*r_{12} = 0\\
		r_{12}*2 = 0\\
		r_{12}^2 + r_{22}^2 = 9\\	
	\end{align*}
	\begin{align*}
		r_{11} = 2\\
		r_{12} = 0\\
		r_{12} = 0\\
		r_{12}^2 + r_{22}^2 = 9\\
\\		
		r_{11} = 2\\
		r_{12} = 0\\
		r_{12} = 0\\
		0^2 + r_{22}^2 = 9\\
		\\
		r_{11} = 2\\
		r_{12} = 0\\
		r_{12} = 0\\
		r_{22}^2 = 9\\
		\\
		r_{11} = 2\\
		r_{12} = 0\\
		r_{12} = 0\\
		r_{22} = 3\\
		\\
		R = \begin{bmatrix}
			2 & 0\\
			0 & 3\\
		\end{bmatrix}\\
	\end{align*}
	\\
	(c)\\
	\\
	The Cholesky Factor must have all its diagonal entries greater than zero. That is what allowed us in (b) to choose $2$ and $3$ instead of $-2$ and $-3$ when finding the squares roots.\\
	But we can still find other matrices that satisfy the proposition $A=R^TR$ using this negative roots.\\
	\begin{align*}
		R = \begin{bmatrix}
		-2 & 0\\
		0 & 3\\
		\end{bmatrix}\\
		\\
		R = \begin{bmatrix}
		2 & 0\\
		0 & -3\\
		\end{bmatrix}\\
		R = \begin{bmatrix}
		-2 & 0\\
		\color{red}{0} & -3\\
		\end{bmatrix}
	\end{align*}
	All of them when "squared" generate the ogirinal matrix.\\
	\\
	(d) We can genralize this idea. For $A= n \times n$ matrix we can always find $N$ matrices where each one of them came from a permutation of the "signals". Given that we have $n$ elements in the diagonal and each of then can have 2 possible signals, we have $2^n$ possible matrices.
\end{document}

### 2018-05-07 books/FundamentalsMatrixComputations/exercise.01.004.052.tex
Fundamentals of COmputation Matrix - exercises - Cholesky

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\begin{document}
	Proposition 1.4.51\\
	If A is positive definite, then $a_{ii} > 0$ for $i = 1,..., n$. 
	\\
	Exercise 1.4.52\\
	Prove Proposition 1.4.51. Do not use the Cholesky decomposition in your 
	proof; we want to use this result to prove that the Cholesky decomposition exists.\\ 
	(Hint: Find a nonzero vector $x$ such that $x^TAx = a_{ii}$.)\\ 
	\\
	Proof:\\
	If $A$ is Positive Definite, then $x^TAx > 0$ for all $x$.
	\begin{align*}
		x^TAx = \begin{Bmatrix}x_1&x_2&...&x_n\end{Bmatrix}*\begin{Bmatrix}
		a_{11} & ... & a{1n}\\
		... & & ...\\
		a_{n1} & ... & a{nn}		
		\end{Bmatrix}*\begin{Bmatrix}x_1\\x_2\\...\\x_n\end{Bmatrix}
	\end{align*}
	But we know that "line vector and matrix multipliction" when the "line vector" is $e_i$ just selects one of the rows of the matrix.\\
	For example
	\begin{align*}
		e_1 = \begin{Bmatrix}1\\0\\...\\0\end{Bmatrix}\\
		e_1^T*\begin{Bmatrix}
		a_{11} & ... & a_{1n}\\
		... & & ...\\
		a_{n1} & ... & a_{nn}		
		\end{Bmatrix} = \begin{Bmatrix}a_{11} & ... & a_{1n} \end{Bmatrix}
	\end{align*}
	On the other hand, "matrix and column vector multiplication", when the "column vector" is $e_i$ we choose a column of $A$;
	\begin{align*}
	e_1 = \begin{Bmatrix}1\\0\\...\\0\end{Bmatrix}\\
	\begin{Bmatrix}
	a_{11} & ... & a_{1n}\\
	... & & ...\\
	a_{n1} & ... & a_{nn}		
	\end{Bmatrix}*e_i = \begin{Bmatrix}a_{11} \\ ... \\ a_{n1} \end{Bmatrix}
	\end{align*}
	So we can "choose" a element of the matrix by doing:
	\begin{align*}
		e_i^TAe_j = a_{ij}
	\end{align*}
	So we can easily "choose" the diagonal elements by doing:
	\begin{align*}
	e_i^TAe_i = a_{ii}
	\end{align*}
	But, given that A is "Positive Definite" this expression is always positive.
	So we have:\\
	\begin{align*}
	e_i^TAe_i > 0\\
	a_{ii} > 0\\
	\square	
	\end{align*}
\end{document}

### 2018-05-07 books/FundamentalsMatrixComputations/exercise.01.004.0023.m

@@ -1,0 +1,18 @@
+function isPositiveDefinite(A)
+    try
+        chol(A);
+        printf("Positive Definite\n")
+    catch
+        printf("Not Positive Definite\n")
+    end
+endfunction
+
+A = [9,3,3;3,10,7;3,5,9];
+B = [4,2,6;2,2,5;6,5,29];
+C = [4,4,8;4,04,1;8,1,6];
+D = [1,1,1;1,2,2;1,2,1];
+
+isPositiveDefinite(A);
+isPositiveDefinite(B);
+isPositiveDefinite(C);
+isPositiveDefinite(D);

### 2018-05-07 books/FundamentalsMatrixComputations/source/math.algebra.linear.hpp

@@ -336,6 +336,11 @@ namespace ma
 						}
 						return out;
 					}
+					bool isPositiveDefinite() const noexcept
+					{
+						auto[r, R] = factorCholeskyErasure();
+						return r;
+					}
 				private:
 					Matrix()
 					{

### 2018-05-07 books/FundamentalsMatrixComputations/Exercise.01.04.054.tex
Fundamentals of Computation Matrix - Cholesky Proof - preliminary exercises

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\begin{document}
	Proposition 1.4.53\\
	Let A be "Positive Definite", and consider a partition 
	$$A = \begin{Bmatrix}
	A_{11}&A_{12}\\
	A_{21}&A_{22}\\
	\end{Bmatrix}$$
	in which $A_{11}$ and $A_{22}$ are square. Then $A_{11}$ and $A_{22}$ are Positive Definite.\\ 
	Exercise 1.4.54\\
	Prove Proposition 1.4.53. As in the previous exercise, do not use the Cholesky 
	decomposition in your proof; use the fact that $x^TAx > 0$ for all nonzero x.\\
	\\
	Proof:\\
	\\
	\begin{align*}
		x^TAx = \begin{Bmatrix} x1^T & 0\end{Bmatrix}*\begin{Bmatrix}
			A_{11} & A_{12}\\
			A_{21} & A_{22}
		\end{Bmatrix}*\begin{Bmatrix} x1 \\ 0\end{Bmatrix}\\
		x^TAx = \begin{Bmatrix}
			x_1^T*A_{11} & x_1^T*A_{22}
		\end{Bmatrix}*\begin{Bmatrix} x1 \\ 0\end{Bmatrix}\\		
		x^TAx = x_1^T*A_{11}*x_1
	\end{align*}
	But given that A is "Positive Definite" it is necessary that $x^TAx >0$, but this imply that it is also necessary that $x^TA_{11}x > 0$.
	$$\square$$	
\end{document}

### 2018-05-09 books/FundamentalsMatrixComputations/Exercise.01.004.056.tex
Fundamentals of matrix Computations - spring system as positive definite matrix

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\begin{document}
	Theorem 1.4.4\\
	Let $M$ be any $n\times n$ nonsingular matrix, and let $A = M^TM$. Then 
	$A$ is positive definite.\\
	\\	
	Proposition 1.4.55\\
	If $A$ and $X$ are $n \times n$, A is "Positive Definite", and $X$ is nonsingular 
	then the matrix $B = X^TAX$ is also "Positive Definite".\\ 
	Considering the special case $A = I$ (which is clearly "Positive Definite"), we see that 
	this proposition is a generalization of Theorem 1.4.4.\\ 
	\\
	Exercise 1.4.56\\
	Prove Proposition 1.4.55.\\
	\\
	Proof:\\
	\\
	\begin{align*}
		z^TAz > 0 & \text { because A is "PD"}\\
		\\
		Xy=z\\
		(Xy)^TA(Xy)>0\\
		y^TX^TAXy>0\\
		y^TBy>0 & \text{ if } y > 0
	\end{align*}
	We already know that $z>0$ because of the "Positive Difiniteness" of A. So we need:
	\begin{align*}
		Xy=z\\
		z>0\\
		y>0\\
		Xy>0
	\end{align*}
	But if X is "Singular" it is possible that a $y>0$ that $Xy=0$. So to guarantee that $y>0$ and $Xy>0$ we need that $X$ be "NonSingular".
\end{document}

### 2018-05-09 books/FundamentalsMatrixComputations/Exercise.01.004.058.tex
Fundamentals of matrix Computations - spring system as positive definite matrix

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\begin{document}
	Proposition 1.4.53\\
	Let $A$ be positive definite, and consider a partition 
	$$A = \begin{bmatrix}	A_{11}&A_{12}\\A_{21}&A_{22}\end{bmatrix}$$ in which $A_{11}$ and $A_{22}$ are square. Then $A_{11}$ and $A_{22}$ are positive definite. 
	\\
	Equation 1.4.57\\
	\begin{align*}
		A = \begin{bmatrix}a_{11}&b^T\\b&\hat{A}\end{bmatrix}
	\end{align*}
	Proposition 1.4.51\\
	guarantees that $a_{11} > 0$. Using 1.4.27 and 1.4.28 as a guide, define 
	\begin{align*}
	r_{11} &= +\sqrt{a_{11}}\\
	s &= r_{11}^{-1}b\\ 
	\tilde{A} &= \hat{A}-ss^T
	\end{align*}

	Then, as one easily checks,

	\begin{align*}
	A=\begin{bmatrix}r_{11}&0\\s&I\end{bmatrix}\begin{bmatrix}1&0\\0&\tilde{A}\end{bmatrix}\begin{bmatrix}r_{11}&s^T\\0&I\end{bmatrix}
	\end{align*}
	\\
	Exercise 1.4.58\\
	Let $$A = \begin{bmatrix}A_{11} & A_{12}\\A_{21}&A_{22}\end{bmatrix}$$ be "Positive Definite", and suppose $A_{11}$ is $j \times j$ and 
	$A_{22}$ is $k \times k$.\\
	By Proposition 1.4.53, $A_{11}$ is "Positive Definite".\\
	Let $R_{11}$ be the Cholesky factor of $A_{11}$, let $R_{12} = 
	 R_{11}^{-T}A_{12}$, and let $\tilde{A}_{22} = A_{22} - R_{12}^TR_{12}$.\\
	The matrix $\tilde{A}_{22}$ is called the "Schur Complement" of $A_{11}$ in $A$.\\ 
	(a) Show that $\tilde{A}_{22} = A_{22} - A_{21}A_{11}^{-1}A_{12}$.\\ 
	(b) Establish a decomposition of A that is similar to 1.4.57 and involves $\tilde{A}_{22}$\\ 
	(c) Prove that $\tilde{A}_{22}$ is "Positive Definite".\\	
	\\
	Proof:\\
	(a)\\
	\begin{align*}
		\tilde{A}_{22} &= A_{22} - R_{12}^TR_{12}\\
		\\
		R_{12} &= R_{11}^{-T}A_{12}\\
		R_{12}^T &= A_{12}^TR_{11}^{-TT}\\
		&= A_{12}^{T}R_{11}^{-1}\\
		\\
		\tilde{A}_{22} &= A_{22} - (A_{12}^{T}R_{11}^{-1})(R_{11}^{-T}A_{12})\\
		\tilde{A}_{22} &= A_{22} - A_{12}^{T}R_{11}^{-1}R_{11}^{-T}A_{12}\\		
		\\
		A_{11} &= R_{11}^TR_{11}\\
		A_{11}^{-1} &= (R_{11}^TR_{11})^{-1}\\
		A_{11}^{-1} &= R_{11}^{-1}R_{11}^{-T}\\		
	\end{align*}	
	\begin{align*}
		\tilde{A}_{22} &= A_{22} - A_{12}^{T}A_{11}^{-1}A_{12}\\
		\\
		A_{21} &= A_{12}^T\\
		\\
		\tilde{A}_{22} &= A_{22} - A_{21}A_{11}^{-1}A_{12}\\
		\square
	\end{align*}
	(b)\\
	\begin{align*}
	A &= \begin{bmatrix}A_{11} & A_{12}\\A_{21}&A_{22}\end{bmatrix}\\
	\text{ using 1.4.57 }\\
	A&=X^TBX\\
	A&=\begin{bmatrix}R_{11}^T&0\\s&I\end{bmatrix}\begin{bmatrix}I&0\\0&\tilde{A}\end{bmatrix}\begin{bmatrix}R_{11}&s^T\\0&I\end{bmatrix}\\	
	&=\begin{bmatrix}R_{11}^T*I+0*0&R_{11}^T*0+0*\tilde{A}\\s*I+I*0&s*0+I*\tilde{A}\end{bmatrix}\begin{bmatrix}R_{11}&s^T\\0&I\end{bmatrix}\\
	&=\begin{bmatrix}R_{11}^T&0\\s&\tilde{A}\end{bmatrix}\begin{bmatrix}R_{11}&s^T\\0&I\end{bmatrix}\\	
	&=\begin{bmatrix}R_{11}^T*R_{11}+0*0&R_{11}^T*s^T+0*I\\s*R_{11}+\tilde{A}*0&s*s^T+\tilde{A}*I\end{bmatrix}\\
	&=\begin{bmatrix}R_{11}^TR_{11}&R_{11}^Ts^T\\sR_{11}&ss^T+\tilde{A}\end{bmatrix}\\
	\end{align*}
	\begin{align*}
	A_{11} &= R_{11}^TR_{11}\\
	A_{12} &= R_{11}^Ts^T\\
	A_{21} &= sR_{11}\\
	A_{22} &= ss^T+\tilde{A}\\
	\\
	A_{21} &= sR_{11}\\
	A_{21}R_{11}^{-1} &= sR_{11}R_{11}^{-1}\\	
	A_{21}R_{11}^{-1} &= sI\\	
	s &= A_{21}R_{11}^{-1}\\		
	s^T &= R_{11}^{-T}A_{21}^T\\			
	\\
	A_{22} &= ss^T+\tilde{A}\\
	-\tilde{A} &= ss^T-A_{22}\\
	\tilde{A} &= -ss^T+A_{22}\\	
	\tilde{A} &= A_{22} - ss^T\\
	\tilde{A} &= A_{22} - (A_{21}R_{11}^{-1})(R_{11}^{-T}A_{21}^T)\\
	...\\
	\tilde{A} &= A_{22} - A_{21}A_{11}^{-1}A_{12}\\	
	\\
	A&=\begin{bmatrix}R_{11}^T&0\\A_{21}R_{11}^{-1}&I\end{bmatrix}\begin{bmatrix}I&0\\0&A_{22} - A_{21}A_{11}^{-1}A_{12}\end{bmatrix}\begin{bmatrix}R_{11}&R_{11}^{-T}A_{21}^T\\0&I\end{bmatrix}\\
	&=\begin{bmatrix}R_{11}^TR_{11}&R_{11}^TR_{11}^{-T}A_{21}^T\\ A_{21}R_{11}^{-1}R_{11}&A_{21}R_{11}^{-1}R_{11}^{-T}A_{21}^T+A_{22} - (A_{21}R_{11}^{-1})(R_{11}^{-T}A_{21}^T)\end{bmatrix}\\
	&=\begin{bmatrix}R_{11}^TR_{11}&{-T}A_{21}^T\\ A_{21}&A_{21}R_{11}^{-1}R_{11}^{-T}A_{21}^T+A_{22} - (A_{21}R_{11}^{-1})(R_{11}^{-T}A_{21}^T)\end{bmatrix}\\
	\end{align*}
	\\
	(c)\\
	\\
	We know that $A = X^TBX$ is "Positive Definite", so if $B$ is "Positive Definite", $\tilde{A}$ will be "Positive Definite". To prove that $B$ is "Positive Definite" we need to prove that $X$ is nonsingular.\\
	So we need to prove that X is nonsingular and that B is "Positive Definite".\\
	\\
	(c.1) X is nonsingular\\
	\\
	\begin{align*}
		X &= \begin{bmatrix}R_{11}&s^T\\0&I\end{bmatrix}\\
		det(X) &= \prod{x_{ii}} \text { because X is Upper Triangular }\\
		x_{ii} &> 0\\
		det(x) &> 0\\
		\square
	\end{align*}\\
	\\
	(c.2) B is "Positive Definite".\\
	\\
	\begin{align*}
		A &= X^TBX\\
		AX^{-1} &= X^TBXX^{-1}\\
		AX^{-1} &= X^TBI\\		
		AX^{-1} &= X^TB\\				
		X^{-T}AX^{-1} &= X^{-T}X^TB\\						
		X^{-T}AX^{-1} &= IB\\		
		X^{-T}AX^{-1} &= B\\				
		B &= X^{-T}AX^{-1}\\
		\\
		Y = X^{-1}
		\\
		B &= Y^TAY\\
		\square
	\end{align*}
\end{document}

### 2018-05-09 books/FundamentalsMatrixComputations/Exercise.01.004.068.tex
Fundamentals of matrix Computations - spring system as positive definite matrix

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\begin{document}
	\begin{figure}
		\centering
		\includegraphics{1020010}
		\caption{}		
		\label{fig:1.4}
	\end{figure}
	Example 1.2.10\\
	\\
	Now suppose we have three masses attached by springs as shown 
	in Figure 1.4. Let $x_1$, $x_2$, and $x_3$ denote the amount by which carts 1, 2, and 3, 
	respectively, move when the forces are applied.\\
	\\
	For each cart the new equilibrium position is that point at which the sum of the forces on the cart is zero. Consider the second cart, for example. An external force of two newtons is applied, and there is 
the leftward force of the spring to the left, and the rightward force of the spring to the right. The amount by which the spring on the left is stretched is $x_2 - x_1$ meters.\\
	\\ 
	It therefore exerts a force $-4$ newtons/meter $\times (x_2 - x_1)$ meters $= -4(x_2 - x_1)$ newtons on the second cart. Similarly the spring on the right applies a force of $+4(x_3 - x_2)$ newtons.\\
	\\
	Thus the equilibrium equation for the second cart is 
	$$-4(x_2-x_1)+4(x_3-x_2)+2=0$$
	or
	$$-4x_1+8x_2-4x_3=2$$
	Similar equations apply to carts 1 and 3. Thus we obtain a system of three linear equations in three unknowns, which we can write as a matrix equation
	\begin{align*}
	\begin{bmatrix}8&-4&0\\-4&8&-4\\0&-4&8\end{bmatrix} \begin{bmatrix} x_1\\x_2\\x_3 \end{bmatrix} = 
	\begin{bmatrix}1\\2\\3\end{bmatrix}
	\end{align*}	
	\\
	Entering the matrix $A$ and vector $b$ into MATLAB, and using the command $x = A\backslash b$ (or simply solving the system by hand) we find that 
	$$b = \begin{bmatrix}0.625\\1.000\\0.875\end{bmatrix}$$
	\\
	Thus the first cart is displaced to the right by a distance of 0.625 meters, for example. The coefficient matrix A is called a stiffness matrix, because the values of its nonzero entries are determined by the stiffnesses of the springs.
	\\
	\\	
	Exercise 1.4.68\\
	\\
	(a) When a spring is stretched (or compressed) from its equilibrium position (0 
	meters) to some new position (x meters), the energy stored in the spring (strain 
	energy) is equal to the work required to move the spring to its new position.\\
	\\ 
	This is $\int_{0}^{x}{f(s)ds}$ joules, the integral of force with respect to distance, where 
	$f(s)$ is the force (in newtons) exerted against the spring that has been stretched 
	to $s$ meters.\\
	\\
	Show that for a linear spring with stiffness $k$ newtons/meter, the 
	strain energy is $\frac{1}{2}kx^2$ joules.\\ 
	\\
	(b) Show that if a spring is stretched or compressed by displacing its right and left 
	endpoints by $x_2$ and $x_1$ meters, respectively, the strain energy of the spring is 
	$\frac{1}{2}k(x_1 - x_2)^2$ joules, which is positive unless $x_1 = x_2$. Show that the strain 
	energy can also be written in the form
	$$\frac{1}{2} * \begin{bmatrix}x_1&x_2\end{bmatrix} \begin{bmatrix}k&-k\\-k&k\end{bmatrix} \begin{bmatrix}x_1\\x_2\end{bmatrix}$$\\
	\\
	(c) Show that the total strain energy of the mass-spring system in Example 1.2.10 
	is a sum of terms of the form $kx^2$ and $k(x_i - x_{i+1}$ and is positive unless all 
	of the displacements are zero.\\
	\\
	(d) Let $A$ be the coefficient matrix of the mass-spring system of Example 1.2.10. 
	Show that the strain energy of the system is $\frac{1}{2}x^TAx$. Deduce that A is positive 
	definite.\\ 
	\\
	(e) Show that the coefficient matrix of the mass-spring system of Exercise 1.2.20 is positive definite. 1.2.20 is the generalization of 1.2.10\\
	\begin{align*}
		\begin{bmatrix}
		k_1+k_2&-k_2&0&...&0\\
		-k_1&k_2+k_3&-k_3&...&0\\
		\vdots&\vdots&\vdots&\vdots&\vdots\\
		...&0&0&-k_{i-1}&k_{i-1}+k_i
		\end{bmatrix}
	\end{align*}
	\\
	Answers:\\
	\\
	(a)\\
	\\
	The applied force varies with the distance and the spring stiffness, so: $f(s)=ks$.
	\begin{align*}
		\int_{0}^{x}{ks\mathrm{d}s} &= k\int_{0}^{x}{s\mathrm{d}s} = k\frac{s^2}{2}\Big|_0^x = k(\frac{x^2}{2}-\frac{0^2}{2}) = k(\frac{x^2}{2})\\
		&=\frac{kx^2}{2}\\
		\square
	\end{align*}
	\\
	(b)\\
	\\
	\begin{align*}
		\int_{0}^{x1-x2}{ks\mathrm{d}s} = k\frac{s^2}{2}\Big|_{0}^{x_1-x_2} =
		k(\frac{(x_1-x_2)^2}{2}) - k(\frac{0^2}{2}) = \frac{k}{2}(x_1-x_2)^2
		\\
		\frac{k}{2}(x_1-x_2)^2\\
		\\
		\begin{bmatrix}x_1&x_2\end{bmatrix}
		\begin{bmatrix}1&-1\\-1&1\end{bmatrix}
		\begin{bmatrix}x_1\\x_2\end{bmatrix} =		
		\begin{bmatrix}x_1-x_2&-x_1+x_2\end{bmatrix}		\begin{bmatrix}x_1\\x_2\end{bmatrix}\\
		= (x_1-x_2)x_1+(-x_1+x_2)x_2\\
		= x_1^2-x_1x_2-x_1x_2+x_2^2\\
		= x_1^2-2x_1x_2+x_2^2\\
		= (x_1-x_2)^2\\
		\\
		\frac{k}{2}\begin{bmatrix}x_1&x_2\end{bmatrix}		\begin{bmatrix}1&-1\\-1&1\end{bmatrix}\begin{bmatrix}x_1\\x_2\end{bmatrix}\\
		= \frac{1}{2} \begin{bmatrix}x_1&x_2\end{bmatrix}	
		\begin{bmatrix}k&-k\\-k&k\end{bmatrix}\begin{bmatrix}x_1\\x_2\end{bmatrix}\\
		\square
	\end{align*}
	\\
	(c)\\
	\\
	We have four springs and the energy in each of them is given by $\frac{1}{2}kx^2$. Each spring has a stifness equal to $4$. So\\
	\begin{align*}
		\frac{1}{2}*4*0.625^2 + \frac{1}{2}*4*(1-0.625)^2+\frac{1}{2}*4*(0.875-1)^2+\frac{1}{2}*4*0.875^2\\
		= 5.25
	\end{align*}
	Stifness is alway positive.\\
	$(x_i)^2$ andd $(x_i - x_{i+1})^2$ are alwyas positive.
	The expression is a sum of positive numbers. The unique exception is when all displacements are zero, when the result is zero.\\
	\\
	(d.1)\\
	\\
	\begin{align*}
		\frac{1}{2}*k_1*x_1^2 + \frac{1}{2}*k_2*(x_2-x_1)^2+\frac{1}{2}*k_3*(x_3-x_2)^2+\frac{1}{2}*k_4*x_3^2\\
		\frac{1}{2}(k_1x_1^2+k_2(x_2-x_1)^2+k_3(x_3-x_2)^2+k_4x_3^2)\\	
	\end{align*}
		\\
	We can also rewrite this as\\
	\\
	\begin{align*}
	x_0 = 0\\
	x_4 = 0\\
	\frac{1}{2}(\sum_{1}^{4}{k_i(x_i-x_{i-1})^2})
	\end{align*}
	Using Octave and Sympy we have:\\
	\begin{verbatim}
	octave:1> pkg load Symbolic;
	octave:2> symbols x1 x2 x3 k1 k2 k3 k4;
	octave:3> expand(k1*x1**2+k2*(x2-x1)**2+k3(x3-x2)**2+k4*x3**2)
	ans = (sym)
     2        2                     2        2                     2        2
	k1*x1  + k2*x1  - 2*k2*x1*x2 + k2*x2  + k3*x2  - 2*k3*x2*x3 + k3*x3  + k4*x3
	octave:4> latex(ans)
	k_{1} x_{1}^{2} + k_{2} x_{1}^{2} - 2 k_{2} x_{1} x_{2} + k_{2} x_{2}^{2} 
	+ k_{3} x_{2}^{2} - 2 k_{3} x_{2} x_{3} + k_{3} x_{3}^{2} + k_{4} x_{3}^{2}
	\end{verbatim}
	Which gives us :\\
	\begin{align*}
	k_{1} x_{1}^{2} + k_{2} x_{1}^{2} - 2 k_{2} x_{1} x_{2} + k_{2} x_{2}^{2} + k_{3} x_{2}^{2} - 2 k_{3} x_{2} x_{3} + k_{3} x_{3}^{2} + k_{4} x_{3}^{2}
	\end{align*}
	Using Octave and Sympy again we see that we can rewrite this expression as:\\
	\begin{verbatim}
	octave:5> expand([x1,x2,x3]*[k1+k2,-k2,0;-k2,k2+k3,-k3;0,-k3,k3+k4]*[x1;x2;x3])
	ans = (sym)
		    2        2                     2        2                     2        2
	k1*x1  + k2*x1  - 2*k2*x1*x2 + k2*x2  + k3*x2  - 2*k3*x2*x3 + k3*x3  + k4*x3
	octave:6> latex(ans)
	k_{1} x_{1}^{2} + k_{2} x_{1}^{2} - 2 k_{2} x_{1} x_{2} + k_{2} x_{2}^{2}
	+ k_{3} x_{2}^{2} - 2 k_{3} x_{2} x_{3} + k_{3} x_{3}^{2} + k_{4} x_{3}^{2}
	\end{verbatim}
	Which is exactly what we had earlier.
	\begin{align*}
	k_{1} x_{1}^{2} + k_{2} x_{1}^{2} - 2 k_{2} x_{1} x_{2} + k_{2} x_{2}^{2}
	+ k_{3} x_{2}^{2} - 2 k_{3} x_{2} x_{3} + k_{3} x_{3}^{2} + k_{4} x_{3}^{2}
	\end{align*}
	So, we can write the Straing Energy of the system as\\
	\begin{align*}
	E &=
	\frac{1}{2} *
	\begin{bmatrix}x_1&x_2&x_3\end{bmatrix}
	\begin{bmatrix}k_1+k_2&-k_2&0\\-k_2&k_2+k_3&-k_3\\0&-k_3&k_3+k_4\end{bmatrix}
	\begin{bmatrix}x_1\\x_2\\x_3\end{bmatrix}\\
	E &= \frac{1}{2}x^TAx
	\end{align*}
	\\
	(d.2) and (e)\\
	\\
	Now we can show that A is "Positive Definite":\\
	\begin{align*}
		A = \begin{bmatrix}k_1+k_2&-k_2&0\\-k_2&k_2+k_3&-k_3\\0&-k_3&k_3+k_4\end{bmatrix}\\
	\end{align*}
	\\
	Using the summation expression from above, we can generalize A to the (e) part of the question and answer both at the same time.\\
	First the easy part:\\
	1) A is Square\\
	2) A is symmetric\\  we have:
	\begin{align*}
		x^tAx &> 0\\
		x^tAx &= \\
		&x_0 = 0\\
		&x_{i+1} = 0\\
		&\frac{1}{2}(\sum_{1}^{i+1}{k_i(x_i-x_{i-1})^2})
	\end{align*}
	But all $k_i$ are positive.\\
	All $(x_i-x_{i-1})^2$ are positive.\\
	So the summation of positive is positive.\\
	Half of positive is positive, so:
	\begin{align*}
		x^tAx &> 0\\
	\end{align*}
	What makes $A$ "Positive Definite".\\
	$\square$
\end{document}

### 2018-05-09 books/FundamentalsMatrixComputations/Exercise.01.004.069.tex
Fundamentals of Matrix Computations - Covariance matrix is Positive Definite

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\begin{document}
	Exercise 1.4.69\\
	Let $v$ be a vector whose entries represent some statistical data. For example, $v$ could be a vector with 365 entries representing the high temperature in Seattle on 365 consecutive days.\\
	\\
	We can normalize this vector by computing its mean and subtracting the mean from each of the entries to obtain a new vector with mean zero.\\
	\\ 
	Suppose now we have such a normalized vector. Then the variance of $v$ is 
	$$\sum_{i=1}^{n}{v_i^2}$$.\\
	This nonnegative number gives a measure of the variation in the data.\\
	\\
	Notice that if we think of $v$ as a column vector, the variance can be expressed as $v^Tv$.\\
	\\
	Now let $v$ and $w$ be two vectors with mean zero and variance (normalized to be) one. Then the correlation of $v$ and $w$ is defined to be 
	$$\sum_{i=1}^{n}{v_iw_i}=w^Tv=v^Tw$$\\
	\\
	This number, which can be positive or negative, measures whether the data in $v$ and $w$ vary with or against one another. For example, the temperatures in Seattle and Tacoma should have a positive correlation, while the temperatures in Seattle and Hobart, Tasmania, should have a negative correlation.\\
	\\
	Now consider $k$ vectors $v_1, ... , v_k$ with mean zero and variance one. The correlation matrix $C$ of the data $v_i, ..., v_k$ is the $k \times k$ matrix whose $(i,j)$ entry is $c_{ij} = v_j^Tv_i$ the correlation of $v_i$ with $v_j$.\\
	\\
	(a) Show that $C$ is a symmetric matrix whose main-diagonal entries are all ones.\\
	\\
	(b) Show that $C = V^TV$ for some appropriately constructed (nonsquare) matrix V.\\
	\\
	(c) Show that $C$ is positive definite if the vectors $v_i, ..., v_k$ are linearly independent.\\
	\\
	(d) Show that if $v_i,..., v_k$ are linearly dependent, then $C$ is not positive definite, but it is positive semidefinite, i.e. $x^TCx \ge 0$ for all x.\\
	\\
	Answers:\\
	\\
	(a.1) C is symmetric\\
	\\
	\begin{align*}
		c_{ij} = v_j^Tv_i
	\end{align*}
	Which is a line-column vector multiplication. Which is commutative. So:\\
	\begin{align*}
	c_{ij} = v_j^Tv_i = v_i^Tv_j = c_{ji}\\
	\square
	\end{align*}
	\\
	(a.2) $c_{ii} = 1$\\
	\\
	\begin{align*}
		c_{ii} = v_i^Tv_i
	\end{align*}
	But $v_i^Tv_i$ is the variance of $v$. Which we know is $1$ because the dataset was normalized to be so.
	\begin{align*}
		c_{ii} = v_i^Tv_i = \text{var}(v) = 1\\
		\square
	\end{align*}
	\\
	(b)\\
	\\
	We can define "Matrix Product" as:\\
	\begin{align*}
		C = A*B\\
		c_{ij} = \text{row}_i(a)*\text{col}_j(b)
	\end{align*}
	Given that covariance matrix $C$ is:
	\begin{align*}
		c_{ij} = v_j^Tv_i
	\end{align*}
	We can arrange a matrix $V$ such that:
	\begin{align*}
		C &= V^TV\\
		c_{ij} &= v_j^Tv_i\\
		c_{ij} &= v_i^Tv_j\\
		c_{ij} &= \text{row}_i(V^T)*\text{col}_j(V)\\
		c_{ij} &= \text{col}_i(V)*\text{col}_j(V)
	\end{align*}
	Which gives me that the covariance is just the dot-product of columns of $V$. So I can arrange the $V$ matrix as:
	\begin{align*}
	V &= 
	\begin{bmatrix}
		\begin{bmatrix}a_1\\b_1\\\vdots\end{bmatrix}&
		\begin{bmatrix}a_2\\b_2\\\vdots\end{bmatrix}&
		...&
		\begin{bmatrix}a_3\\b_3\\\vdots\end{bmatrix}
	\end{bmatrix}\\
	\square
	\end{align*}
	\\
	(c) and (d)\\
	\\
	\begin{align*}
		C&=V^TV\\
		x^TCx&=x^TV^TVx\\
		\\
		x^TV^T &= \begin{bmatrix}
		x_1a_1+x_2a_2+...+x_na_n&
		x_1b_1+x_2b_2+...+x_nb_n&
		...
		\end{bmatrix}\\
		Vx &= \begin{bmatrix}
		 a_1x_1+a_2x_2+...+a_nx_x\\		 
		 b_1x_1+b_2x_2+...+b_nx_x\\
		 \vdots
		\end{bmatrix}\\
		\\
		x^TV^TVx &= (x_1a_1+x_2a_2+...+x_na_n)*(a_1x_1+a_2x_2+...+a_nx_x)\\
			&+(x_1b_1+x_2b_2+...+x_nb_n)*(b_1x_1+b_2x_2+...+b_nx_x)\\
			&...\\
		 &= (x_1a_1+x_2a_2+...+x_na_n)^2\\
		&+(x_1b_1+x_2b_2+...+x_nb_n)^2\\
		&...\\
	\end{align*}
	Which will be positive because is a summation of positive values.\\
	With the addition that $C$ is square and symmetric, we can affirm that $C$ is "Positive Definite".\\
	The unique caveat is that if the $v_i$ are linear dependent, there are at least one $x$ that $$Vx=0$$\\
	In this particular case the summation above is not greater than zero, it is exactly zero. That is why we need that $v_i$s to be linear independent to $C$ be "Positive "Definite" and if $v_i$s are linear dependent $C$ is "Positive Semidefinite".\\
\end{document}

### 2018-05-12 books/FundamentalsMatrixComputations/Exercise.01.004.072.tex
Fundamentals of Matrix Computations - Solve matrix system using Cholesky factorization

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{pgfplots}
\begin{document}
	Exercise 1.4.72\\
	Figure out what the following MATLAB code does. 
	\begin{verbatim}
	n = 1000; 
	for jay = 1:4 
		if jay > 1; oldtime = time; end;
		M = randn(n); 
		A = M'*M; 
		t = cputime; 
		R = chol(A); 
		matrixsize = n
		time = cputime - t
		if time == 0; time = 1; end;
		if jay > 1; ratio = time/oldtime; end;
		n = 2*n; 
	end 	
	\end{verbatim}		
	If you put these instructions into a file named, say, zap.m, you can run the program by 
	typing zap from the MATLAB command line. The functions randn, cputime, 
	and chol are built-in MATLAB functions, so you can learn about them by typing 
	help randn, etc. You might find it useful to type more on before typing help 
	{topic}.\\ 
	(a) Does the code produce reasonable values of ratio when you run it? What 
	value would you expect in theory? Depending on the speed of the machine on 
	which you are running MATLAB, you may want to adjust $n$ or the number of 
	times the j ay loop is executed.\\ 
	(b) Why is the execution time of this code (i.e. the time you sit waiting for the 
	answers) so much longer than the times that are printed out?\\ 
	\\
	Execution:
	\begin{verbatim}
	> octave .\exercise.01.004.0072.m
	matrixsize =  1000
	time = 0
	matrixsize =  2000
	time =  1.0625
	matrixsize =  4000
	time =  10.125
	matrixsize =  8000
	time =  81.406
	\end{verbatim}
	Answers:\\
	\\
	(a) First we need to adjust $n$, because it is instantaneous to matrices smaller than 1000.\\
	By Proposition 1.4.24, the Cholesky decomposition should increase by $O(n^3)$.\\
	\\
	Proposition 1.4.24 Cholesky's algorithm 1.4.17 applied to an $n \times n$ matrix performs about $\frac{n^3}{3}$ flops.\\ 
	\\
	Which was exactly what happedned:\\
	\begin{verbatim}
	> 10.125 / 1.0625
	9.52941176470588
	> 81.406 / 10.150
	8.02029556650246
	\end{verbatim}
	(b) Because we are not counting the time spent generating $M$ and the time multiplying $M^TM$. Time needed to guarantee that we will pass a valid matrix to the "chol" method.
\end{document}

### 2018-05-12 books/FundamentalsMatrixComputations/Exercise.01.004.0072.m

@@ -1,0 +1,13 @@
+n = 1000; 
+for jay = 1:4 
+    if jay > 1; oldtime = time; end;
+    M = randn(n); 
+    A = M'*M; 
+    t = cputime; 
+    R = chol(A); 
+    matrixsize = n
+    time = cputime - t
+    if time == 0; time = 1; end;
+    if jay > 1; ratio = time/oldtime; end;
+    n = 2*n; 
+end 

### 2018-05-13 books/FundamentalsMatrixComputations/Exercise.01.005.009.tex
Fundamentals of Computation Matrix - Banded backward substitution complexity

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{pgfplots}
\begin{document}
	Exercise 1.5.9\\
	\\
	Let $R$ be an $n \times n$ upper-triangular matrix with semiband width $s$. Show that the system $Rx = y$ can be solved by back substitution in about $2ns$ flops. An analogous result holds for lower-triangular systems.\\
	\\
	\begin{align*}
	\begin{bmatrix}
	a_{11} & a_{12} & ...    & a_{1s} & 0      & ...    & 0\\
	0      & a_{22} & a_{23} & ...    & a_{2s} & ...    & 0\\
	0      & 0      & a_{33} & a_{34} & ...    & ...    & 0\\
	\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots\\
	0      & 0      & 0      & 0      & 0      & 0      & a_{nn}
	\end{bmatrix} \begin{bmatrix}
	x_1\\x_2\\x_3\\ \vdots \\ x_n
	\end{bmatrix} = \begin{bmatrix}
	b_1\\b_2\\b_3\\ \vdots \\ b_n
	\end{bmatrix}
	\end{align*}
	\\
	Proof:\\
	\\
	First step:\\
	\\
	$$x_n =  b_n / a_{nn}$$
	\\
	1 - flop, 2 - reads, 1 - write\\
	\\
	Next step would be:\\
	\\	
	$$x_{i} = (b_i - \sum_{j=i+1}^{n}(a_{ij}*x_{j})) / a_{ii}$$
	\\
	but, we now that from $a_{i,j+s+1}$ to $a_{in}$, all entries are zero because the matrix $A$ is banded with a semi-band of $s$. This will reflect in the sumation, so, in this case:
	\begin{align*}
		\sum_{j=i+1}^{n}(a_{ij}*x_{j}) &= \sum_{j=i+1}^{i+s}(a_{ij}*x_{j}) + \sum_{j=i+s+1}^{n}(0*x_{j})\\
		&= \sum_{j=i+1}^{i+s}(a_{ij}*x_{j})\\
	\end{align*}
	This will generate $(i+s) - (i+1) + 1 = i+s-i-1+1 = s$ iterations per line. Each iteration of the summation will perform:\\
	1 flop, 3 reads (we will read the accumulator), 1 write (updating the accumulator). Totalling:
	$s$ flops, $3s$ reads, $s$ writes.\\
	Plugging back in the original expression for line $i$ we have:
	(+1)Read $b_i$, (+1)flop $b_i - \text{acc}$, (+1)read $a_{ii}$, (+1)flop $/a_{ii}$, (+1)write $x_i$.
	In total we have:
	$s+2$ flops, $3s+2$ reads, $s+1$ writes for each line (worst case).
	Now we can calculate the cost for the whole matrix, just assuming (incorrectly) that each line takes the worst case and arrive at:\\
	$n*(s+2)=ns+2n$ flops,\\
	$n*(3s+2)=3ns+2n$ reads,\\
	$n*(s+1)=ns+n$ writes.\\
	In this banded matrix scenario s << n and it is not an absurd to approximate $s ~ 2$ that would gives us the $2ns$ flops of the exercise.
	$$\square$$
	\\\\
	But to better understand the cost of the algorithm we will need to reference Agner4
	\begin{verbatim}
	Latency:
	This is the delay that the instruction generates in a dependency chain.
	The numbers are 	minimum values. Cache misses, misalignment, and 
	exceptions may increase the clock counts considerably. Where 
	hyperthreading is enabled, the use of the same execution units in the 
	other thread leads to inferior performance. Denormal numbers, NAN's 
	and infinity do not increase the latency. The time unit used is core 
	clock cycles, not the reference	clock cycles given by the time stamp 
	counter.

	Throughput:
	The average number of core clock cycles per instruction for a series of 
	independent instructions of the same kind in the same thread.

	Instruction Operand 	Latency Throughput  
	FADD        Register    3       1
	FSUB        Register    3       1
	FADD        Memory      5       1
	FSUB        Memory      5       1	
	FMUL        Register    5       1
	FDIV        Register    16      5
	FDIV        Memory      16      5
	\end{verbatim}	
	\url{http://www.agner.org/optimize/instruction_tables.pdf}
	\\
	\\
	What we must analyse is that these are best-case scenarios. As long we have cache misses these values can,and will increase enormously. We can see the cost of cache misses, for example, at:\\
	\begin{verbatim}
		Level               Fastest Latency
		First Level Data    4 cycles
		Second Level        12 cycles
		Third Level         44 cycles
	\end{verbatim}
	\url{https://www.intel.co.uk/content/dam/www/public/us/en/documents/manuals/64-ia-32-architectures-optimization-manual.pdf}\\
	\\
	Tehese, again, are the best scenario. And we are not event touching the main system meory yet.\\
	Memory access is very difficult to stimate, but we will use the value used at:\\
	\begin{verbatim}
		Data Source                                 Latency
		L3 CACHE hit, line unshared                 ~40 cycles
		L3 CACHE hit, shared line in another core   ~65 cycles
		L3 CACHE hit, modified in another core      ~75 cycles
		remote L3 CACHE                             ~100-300 cycles
		Local Dram                                  ~60 ns
		Remote Dram                                 ~100 ns 
	\end{verbatim}
	\url{https://software.intel.com/sites/products/collateral/hpc/vtune/performance_analysis_guide.pdf}\\
	\\\\
	So, I think it is safe to say that today, the algorithm will be dominated by its memory access pattern, that is why we are also calculating read, and write patterns.
\end{document}

### 2018-05-21 books/FundamentalsMatrixComputations/Exercise.01.005.011.tex
Cholesky banded matrices and inverses

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{pgfplots}
\begin{document}
	\begin{figure}
		\centering
		\includegraphics[width=0.7\linewidth]{C:/github/sandbox/books/FundamentalsMatrixComputations/figure112}
	\end{figure}
	Exercise 1.5.11\\
	\\
	As in Exercise 1.5.4, consider the banded system of equations arising from an $m \times m$ network of nodes like Figure 1.12 but larger, with the nodes numbered by rows, as in Figure 1.12.\\
	\\ 
	(a) For the case m = 100 (for which $n = 10^4$) calculate the cost of solving the system $Ax = b$ (Cholesky decomposition plus forward and back substitution) with and without exploiting the band structure. Show that exploiting the band structure cuts the flop count by a factor of several thousand. Show that if only the semiband is stored, the storage space required is only about 1% of what 
	would be required to store the matrix naively.\\
	\\
	(b) Repeat part (a) with m = 1000. 
	\\
	Answers:\\
	\\		
	(a) Any link can theorically be linked to any other node, on a $100 \times 100$ this means we have a $n=10^4$ matrix.\\
	\\
	\\
	\\	
	Solving this system using naive Cholesky method will cost:\\
	Cholesky ($n^3/3$):$\frac{(10^4)^3}{3}=\frac{10^{12}}{3}$\\
	Foward Substitution ($n^2$):$(10^4)^2=10^8$\\
	Backward Substitution ($n^2$):$(10^4)^2=10^8$\\
	Total:\\
	\begin{align*}
		\frac{10^{12}}{3} + 10^8 + 10^8 = \frac{10^{12}}{3} + 2*10^8 \approx 10^{12}
	\end{align*}
	\\
	Solving using Banded-Matrix with band $s=100$:\\
	Banded Cholesky ($ns^2$): $ 10^4 * 100^2 = 10^4 * (10^2)^2 = 10^4 * 10^4 = 10^8  $\\
	Foward Substitution ($2ns$):$ 2*10^{4}*100 = 2*10^{4}*10^{2} = 2*10^{4}*10^{2} = 2*10^6$\\
	Backward Substitution ($2ns$):$ 2*10^{4}*100 = 2*10^{4}*10^{2} = 2*10^{4}*10^{2} = 2*10^6$\\
	\\
	Total:\\
	\begin{align*}
		10^8 + 2*10^6 + 2*10^6 = 10^8 + 4*10^6 \approx 10^{8}
	\end{align*}
	\\
	Using a Band optimized algorithms we gain:\\
	\begin{align*}
		\frac{10^8}{10^{12}} = 	\frac{10^8}{10^{8}*10^{4}} = \frac{1}{10^{4}} = 0.01 \%
	\end{align*}
	$1$ghz is $1.000.000.000$ of cycles per second, or $10^9$ cycles per second. In the naive scenario we are going to make $1^12$ operations. If we average that every operation takes:zz
	1 cycle per operation (ASM operation)\\
	50 cycles per operation (memory access of all variables)\\
	\\
	Which will be approximated to 50 cycles per operation.\\
	The naive approach.\\
	\begin{align*}
		10^{12} * 50 &=	10^{12} * 5*10 \text{ cycles}\\
		&= 5*10^{13} \text{ cycles}\\
		&= 5*10^{5}*10^{9} \text{ cycles}\\
		&= 5*10^{5}*10^{9} \text{ cycles} * \frac{1 \text{ sec}}{10^9 \text{ cycles}}\\
		&= 5*10^{5}*10^{9} \text{ cycles} * \frac{1 \text{ sec}}{10^9 \text{ cycles}}\\		
		&= 5*10^{5} \text{ sec}\\		
	\end{align*}
	The naive approach.\\
	\begin{align*}
	10^{12} * 50 &=	10^{12} * 5*10 \text{ cycles}\\
	&= 5*10^{13} \text{ cycles}\\
	&= 5*10^{5}*10^{9} \text{ cycles}\\
	&= 5*10^{5}*10^{9} \text{ cycles} * \frac{1 \text{ sec}}{10^9 \text{ cycles}}\\
	&= 5*10^{5}*10^{9} \text{ cycles} * \frac{1 \text{ sec}}{10^9 \text{ cycles}}\\		
	&= 5*10^{5} \text{ sec}\\		
	&\approx 8333 \text{ min}\\		
	&\approx 138 \text{ hours}\\			
	&\approx 6 \text{ days}\\	
	\end{align*}
	The banded optimized approach:\\
	\begin{align*}
	10^{8} * 50 &=	10^{8} * 5*10 \text{ cycles}\\
	&= 5*10^{9} \text{ cycles}\\
	&= 5*10^{9} \text{ cycles} * \frac{1 \text{ sec}}{10^9 \text{ cycles}}\\
	&= 5 \text{ sec}\\		
	\end{align*}
	\\
	(b) If we increase $m=1000$, $n$ will be $n=10^6$.\\\\
	Solving this system using naive Cholesky method will cost:\\
	Cholesky ($n^3/3$):$\frac{(10^6)^3}{3}=\frac{10^{18}}{3}$\\
	Foward Substitution ($n^2$):$(10^6)^2=10^{12}$\\
	Backward Substitution ($n^2$):$(10^6)^2=10^{12}$\\\\
	Solving using Banded-Matrix with band $s=1000$:\\
	Banded Cholesky ($ns^2$): $ 10^6 * 1000^2 = 10^6 * (10^3)^2 = 10^6 * 10^9 = 10^{15} $\\
	Foward Substitution ($2ns$):$ 2*10^{6}*1000 = 2*10^{6}*10^{3} = 2*10^9$\\
	Backward Substitution ($2ns$):$ 2*10^{6}*1000 = 2*10^{6}*10^{3} = 2*10^9$\\
	\\
	\begin{align*}
		\frac{10^{15}}{10^{18}} = \frac{10^{15}}{10^{15}*10^{3}} = \frac{1}{10^3} = 0.1 \%
	\end{align*}
\end{document}

### 2018-05-21 books/FundamentalsMatrixComputations/Exercise.01.005.012.tex
Cholesky banded matrices and inverses

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{pgfplots}
\begin{document}
	Exercise 1.5.12\\
	Consider a mass-spring system as in Figure 1.11 with six carts. Suppose each spring has a stiffness $k_i = 1$ newton/meter.\\ 
	(a) Set up the tridiagonal, positive definite, coefficient matrix $A$ associated with this problem.\\ 
	(b) Use the MATLAB chol command to calculate the Cholesky factor $R$. Notice that R inherits the band structure of A. (To learn an easy way to enter this particular A, type help toeplitz )\\ 
	(c) Use the MATLAB inv command to calculate $A^{-1}$. Notice that $A^{-1}$ does not inherit the band structure of $A$.
	\\
	Answers\\
	\\
	\begin{verbatim}
	octave:1> A = toeplitz([2,-1,0,0,0,0,0])
	A =

	2  -1   0   0   0   0   0
	-1   2  -1   0   0   0   0
	0  -1   2  -1   0   0   0
	0   0  -1   2  -1   0   0
	0   0   0  -1   2  -1   0
	0   0   0   0  -1   2  -1
	0   0   0   0   0  -1   2
	octave:2> chol(A)
	ans =

	1.41421  -0.70711   0.00000   0.00000   0.00000   0.00000   0.00000
	0.00000   1.22474  -0.81650   0.00000   0.00000   0.00000   0.00000
	0.00000   0.00000   1.15470  -0.86603   0.00000   0.00000   0.00000
	0.00000   0.00000   0.00000   1.11803  -0.89443   0.00000   0.00000
	0.00000   0.00000   0.00000   0.00000   1.09545  -0.91287   0.00000
	0.00000   0.00000   0.00000   0.00000   0.00000   1.08012  -0.92582
	0.00000   0.00000   0.00000   0.00000   0.00000   0.00000   1.06904
	octave:3> inv(A)
	ans =

	0.87500   0.75000   0.62500   0.50000   0.37500   0.25000   0.12500
	0.75000   1.50000   1.25000   1.00000   0.75000   0.50000   0.25000
	0.62500   1.25000   1.87500   1.50000   1.12500   0.75000   0.37500
	0.50000   1.00000   1.50000   2.00000   1.50000   1.00000   0.50000
	0.37500   0.75000   1.12500   1.50000   1.87500   1.25000   0.62500
	0.25000   0.50000   0.75000   1.00000   1.25000   1.50000   0.75000
	0.12500   0.25000   0.37500   0.50000   0.62500   0.75000   0.87500
	\end{verbatim}	
\end{document}

### 2018-05-21 books/FundamentalsMatrixComputations/Exercise.01.005.013.tex
Cholesky banded matrices and inverses

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{pgfplots}
\begin{document}
	Exercise 1.5.13\\
	In the previous exercise, the matrix $A^{-1}$ is full; none of its entries are zero.\\ 
	(a) What is the physical significance of this fact? (Think of the equation $x = A^{-1}b$, 
	especially in the case where only one entry, say the jth, of b is nonzero. If the 
	(i,j) entry of $A^{-1}$ were zero, what would this imply? Does this make physical 
	sense?)\\ 
	(b) The entries of $A^{-1}$ decrease in magnitude as we move away from the main 
	diagonal? What does this mean physically?\\	
	\\
	Answers:\\
	(a) $x = A^{-1}b$ means that $x_{i}$ is the inner product $\text{row}_i(A).b_i$ which means that the i-th displacement is the linear combination of a non-zeros coefficients and the applied forces, which means that every displacement influence every cart.\\
	In this special case that b is zero in all but one place, we would have only one force applied, and this force will cause a particular displacement in each cart.\\
	If for some reason the (in) entry of A were zero, that would mean that somehow a force applied to the j-th cart would not affect the i-th spring. Maybe they are not connected, so the energy apllied could not flow to that spring. One can easily see this imagining a extra, and disconnected, spring that will have its "influence factors" all zeroed beecaused it does not makes "part" of the system.\\
	\\
	(b) Yes! And this means that the displacement at the i-th cart will be more affected by the i-th force.
\end{document}

### 2018-05-21 books/FundamentalsMatrixComputations/source/math.algebra.linear.hpp

@@ -4,7 +4,38 @@
 #include <utility>
 #include <tuple>
 #include <iostream>
+#include <type_traits>
 
+#define TUPLE2(A,B) template <std::size_t N> \
+decltype(auto) get() const \
+{ \
+if constexpr (N == 0) return A; \
+else if constexpr (N == 1) return B; \
+}
+
+#define LAMBDA(i) [&](auto i) -> auto
+
+namespace ma
+{
+	template<typename T>
+	class task
+	{
+	public:
+		task() : failed(true), Value() {}
+		task(const T& value) : failed(false), Value(value) {}
+		task(bool failed, const T& value) : failed(failed), Value(value) {}
+
+		TUPLE2(failed, Value);
+	private:
+		bool failed;
+		T Value;
+	};
+}
+namespace std {
+	template<typename T> struct tuple_size<ma::task<T>> : std::integral_constant<std::size_t, 2> {};
+	template<std::size_t N, typename T>
+	struct tuple_element<N, ma::task<T>> { using type = decltype(std::declval<ma::task<T>>().get<N>()); };
+}
 namespace ma
 {
 	namespace math
@@ -15,24 +46,812 @@ namespace ma
 			namespace linear
 			{
 				using MatrixIndex = unsigned int;
+
+				// SPECIAL MATRIX TRAIT
 				class NONE {};
 				class IDENTITY {};
-				class UPPERTRIANGULAR {};
-				class LOWERTRIANGULAR {};
-				template <typename TNumber, NaturalNumber HEIGHT, NaturalNumber WIDTH, typename TAG = NONE> class Matrix;
-				template <NaturalNumber HEIGHT, NaturalNumber WIDTH, typename TAG = NONE> using Matrixf = Matrix<float, HEIGHT, WIDTH, TAG>;
-				template <typename TNumber, NaturalNumber HEIGHT> using MatrixIdentity = Matrix<TNumber, HEIGHT, HEIGHT, IDENTITY>;
-				template <NaturalNumber HEIGHT> using MatrixIdentityf = Matrix<float, HEIGHT, HEIGHT, IDENTITY>;
+				class UPPER {};
+				class UPPERBANDED {};
+				class LOWER {};
 
-				template <typename TNumber, NaturalNumber HEIGHT, typename TAG = NONE> using Vector = Matrix<TNumber, HEIGHT, 1, TAG>;
[…]

### 2018-05-25 books/FundamentalsMatrixComputations/Exercise.01.005.016.tex
Fundamentals of Matrix Computations exercises

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{pgfplots}
\begin{document}
	Exercise 1.5.16\\
	(d)\\
	\\
	Think about how your subroutines could be used to calculate the inverse of a 
	positive definite matrix. Calculate $A^{-1}$, where 
	\begin{align*}
	A = \begin{bmatrix}
	1 & 1/2 & 1/3 \\
	1/2 & 1/3 & 1/4\\ 
	1/3 & 1/4 & 1/5\\ 
	\end{bmatrix}	
	\end{align*}
	It turns out that the entries of $A^{-1}$ are all integers. Notice that your computed 
	solution suffers from significant roundoff errors. This is because A is (mildly) 
	ill conditioned. This is the 3x3 member of a famous family of ill-conditioned 
	matrices called Hilbert matrices; the condition gets rapidly worse as the size 
	of the matrix increases. We will discuss ill-conditioned matrices in Chapter 2.
	\\
	Answers\\
	\\
	We can calculate a inverse matrix using Cholesky factorization because:
	\begin{align*}
		A &= R^TR\\
		A*A^{-1} &= R^TR*A^{-1}\\
		I &= R^TR*A^{-1}\\
		\begin{bmatrix}
			e_1\\e_2\\\vdots\\e_n
		\end{bmatrix} &= R^TR*A^{-1}\\
		\begin{bmatrix}
		e_1\\e_2\\\vdots\\e_n
		\end{bmatrix} &= R^TR*\begin{bmatrix}
			a^{-1}_{1} &
			a^{-1}_{2} &
			... &
			a^{-1}_{n}
		\end{bmatrix}
	\end{align*}	
	Which can be simplified as:
	\begin{align*}
		\begin{bmatrix}
			e_1 = R^TR*a^{-1}_{1}\\
			e_2 = R^TR*a^{-1}_{2}\\
			\vdots \\
			e_n = R^TR*a^{-1}_{n}
		\end{bmatrix}\\		
	\end{align*}
	In this way we can find the inverse of a Matrix with $n$ "solves" using Cholesky. Each Cholesky solve makes one backward substitution and one foward substitution. They have the same complexity: $n^2$. Which gives us a solution in $n^3$.	
\end{document}

### 2018-05-25 books/FundamentalsMatrixComputations/Exercise.01.007.012.tex
Fundamentals of Matrix Computations exercises

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\author{Daniel Frederico Lins Leite}
\begin{document}
	We will transform the system by means of elementary operations of three types:\\ 
	1. Add a multiple of one equation to another equation.\\ 
	2. Interchange two equations.\\ 
	3. Multiply an equation by a nonzero constant.\\ 
	\\
	Exercise 1.7.2:\\
	\\
	Proposition 1.7.1\\
	If Ax = b is obtained from Ax = b by an elementary operation of type 1, 2, or 3, then the systems Ax = b and Ax = b are equivalent.\\
	\\
	Exercise 1.7.2\\
	Prove Proposition 1.7.1.\\
	Discussion: Suppose the system $Ax = b$ is transformed to $\hat{A}x = \hat{b}$ by an operation of type 1. You must show that\\
	(a) every solution of $Ax = b$ is a solution of $\hat{A}x = \hat{b}$ and\\
	(b) every solution of $\hat{A}x = \hat{b}$ is a solution of $Ax = b$.\\
	\\
	Part (a) should be easy. Part (b) becomes easy when you realize that $Ax = b$ can be recovered from $\hat{A}x = \hat{b}$ by an operation of type 1: If $\hat{A}x = b$ was obtained from $Ax = b$ by adding m times the j-th row to the i-th row, then $Ax = b$ can be recovered from $\hat{A}x = b$ by adding $-m$ times the j-th row to the i-th row. Analogous remarks apply to operations of types 2 and 3.\\
	\\
	Answers:\\
	\\
	(a)\\
	\\
	\begin{align*}
		Ax = b\\
		\forall{j} \big[ \text{row}_j(A) * x = b_j \big]\\
		\\
		\hat{A} = A + m*\text{row}_j(A)\\
		\hat{b} = b + m*b_j\\	
	\end{align*}
	\begin{align*}	
		Ax = b\\
		Ax + m*\text{row}_j(A)*x = b + m*\text{row}_j(A)*x\\		
		Ax + m*\text{row}_j(A)*x = b + m*b_j\\
		(A + m*\text{row}_j(A))*x = b + m*b_j\\
		(A + m*\text{row}_j(A))*x = \hat{b}\\
		\hat{A}*x = \hat{b}\\		
		\square
	\end{align*} 	
	\\
	(b)\\
	\\
	\begin{align*}
	Ax = b\\
	\forall{j} \big[ \text{row}_j(A) * x = b_j \big]\\
	\\
	\hat{A} = A + m*\text{row}_j(A)\\
	\hat{b} = b + m*b_j\\	
	\\
	\hat{A}x = \hat{b}\\
	(A + m*\text{row}_j(A))*x = b + m*b_j\\
	A*x + m*\text{row}_j(A)*x = b + m*b_j\\
	b + m*\text{row}_j(A)*x = b + m*b_j\\
	m*\text{row}_j(A)*x = b + m*b_j - b\\
	m*\text{row}_j(A)*x = m*b_j\\		
	\text{row}_j(A)*x = b_j\\
	\square	
	\end{align*} 	
\end{document}

### 2018-06-01 books/FundamentalsMatrixComputations/Exercise.01.007.032.tex
Fundamentals of Matrix Computations

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\author{Daniel Frederico Lins Leite}
\begin{document}
	Proposition 1.4.55\\
	If $A$ and $X$ are $n \times n$, $A$ is positive definite and $X$ is nonsingular, then the matrix $B = X^TAX$ is also positive definite.\\
	\\
	Theorem 1.7.31\\
	Let A be positive definite. Then A can be expressed in exactly one 
	way as a product $A = LDL^T$, such that L is unit lower triangular, and D is a 
	diagonal matrix whose main-diagonal entries are positive. \\
	\\
	Exercise 1.7.32\\
	Prove Theorem 1.7.31.\\
	\\
	To this end it suffices to show that A is positive definite if and only if the main-diagonal entries of D are positive. See Proposition 1.4.55.\\
	\\
	Proof:\\
	\\
	Part 1: If A is "Positive Definite" then main-diagonal entries of D are positive.
	\begin{align*}
		X^TAX = B\\
		X^{-T}X^TAXX^{-1} = X^{-T}BX^{-1}\\
		A = X^{-T}BX^{-1}\\
		\\
		L = X^{-1}\\
		\\
		A = L^TBL
	\end{align*}
	By the uniqueness of the factorization there is only one factorization of the form $A = L^TDL$. Which makes $B=D$. But from the "Positive Definiteness" of the matrix, $B$, and off course $D$ are "Positive Definite".
	Which implies that the main-diagonal entries of the matrix are positive $\square$.
	\\
	\\
	Part 2: If main-diagonal entries of D are positive then A is "Positive Definite"\\	
	\\
	If D is a diagonal matrix with  main-diagonal entries then D is "Positive Definite".
	\begin{align*}			
		B &= X^TDX\\
		\\
		L &= X\\
		\\
		B &= L^TDL\\
	\end{align*}	
	Again, by uniqueness of factorization, $B=A$, and given that $B$ is "Positive Definite", we conclude that $A$ is "Positive Definite". $\square$
\end{document}

### 2018-06-01 books/FundamentalsMatrixComputations/Exercise.01.007.034.tex
Fundamentals of Matrix Computations

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\author{Daniel Frederico Lins Leite}
\begin{document}
	Exercise 1.7.34\\
	\\
	In this exercise you will show that performing an elementary row operation of type 1 is equivalent to left multiplication by a matrix of a special type. Suppose $A$ is obtained from $A$ by adding $m$ times the j-th row to the i-th row.
	\\
	\\
	(a) Show that $\hat{A} = MA$, where $M$ is the triangular matrix obtained from the 
	identity matrix by replacing the zero by an $m$ in the $(i, j)$ position. For example, when $i > j$, $M$ has the form 
	$$
	\begin{bmatrix}
		1&0&0&0&0&...&0\\
		0&1&0&0&0&...&0\\
		0&0&1&0&0&...&0\\
		\vdots&\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		0&0&m&...&1&...&0\\
		\vdots&\vdots&\vdots&\vdots&\vdots&\ddots&\vdots\\		
		0&0&0&0&0&...&1
	\end{bmatrix}
	$$ 
	Notice that this is the matrix obtained by applying the type 1 row operation 
	directly to the identity matrix. We call $M$ an elementary matrix of type 1.\\
	\\
	(b) Show that $det(M) = 1$ and $det(\hat{A}) = det(A)$. Thus we see (again) that $\hat{A}$ is nonsingular if and only if A is. \\
	\\
	(c) Show that $M^{-1}$ differs from $M$ only in that it has $-m$ instead of m in the (i, j) 
	position. $M^{-1}$ is also an elementary matrix of type 1. To which elementary 
	operation does it correspond?\\
	\\
	(a)\\
	\\
	\begin{align*}
	\begin{bmatrix}
		1&...&0&...&0&...&0\\
		\vdots&\ddots&\vdots&\vdots&\vdots&\vdots&\vdots\\
		0&...&1&...&0&...&0\\
		\vdots&\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		0&...&m_{ab}&...&1&...&0\\
		\vdots&\vdots&\vdots&\vdots&\vdots&\ddots&\vdots\\		
		0&...&0&...&0&...&1
	\end{bmatrix} * \begin{bmatrix}
		a_{11}&...&a_{1j}&...&a_{1c}&...&a_{1n}\\
		\vdots&\ddots&\vdots&\vdots&\vdots&\vdots&\vdots\\
		a_{b1}&...&a_{bj}&...&a_{bc}&...&a_{bn}\\		
		\vdots&\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		a_{i1}&...&a_{ij}&...&a_{ic}&...&a_{in}\\		
		\vdots&\vdots&\vdots&\vdots&\vdots&\ddots&\vdots\\		
		a_{n1}&...&a_{nj}&...&a_{nc}&...&a_{nn}\\		
	\end{bmatrix} \\ = \begin{bmatrix}
		a_{11}&...&a_{1j}&...&a_{15}&...&a_{1n}\\
		\vdots&\ddots&\vdots&\vdots&\vdots&\vdots&\vdots\\
		\vdots&\vdots&\ddots&\vdots&\vdots&\vdots&\vdots\\		
		\vdots&\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		m_{ab}a_{b1}+a_{i1}&...&m_{ab}a_{bj}+a_{ij}&...&m_{ab}a_{bc}+a_{ic}&...&m_{ab}a_{bi}+a_{in}\\		
		\vdots&\vdots&\vdots&\vdots&\vdots&\ddots&\vdots\\		
		a_{n1}&...&a_{nj}&...&a_{n5}&...&a_{nn}\\		
	\end{bmatrix}
	\end{align*}
	 \\
	 (b)\\
	 \\
	 The unique multiplication that is not zero is the mais diagonal, so the determinant is 1.\\
	 \\
	 \begin{align*}
	 	det(A) = 1
	 \end{align*}
	 The determinant will be a multiplication of n-terms, one of each line.
	 For example, diagonal:
	 \begin{align*}
	 	det(A) &= ... + a_{11}a_{22}...a_{ii}...a_{nn} + ...\\
	 	det(\hat{A}) &= ... + a_{11}a_{22}...(m_{ab}a_{bc}+a_{ii})...a_{nn} + ...\\	 	
	 	&= ... + (a_{11}a_{22}...m_{ab}a_{bc}...a_{nn})+(a_{11}a_{22}...a_{ii}...a_{nn}) + ...\\	 	
	 \end{align*}
	 Which will give a term with $m_{ab}$ and term without. The sum of terms without will give the $det(A)$. The terms with $m_{ab}$ will appear in pairs, one positive and one negative, so the sum will be zero. Which will give us the $det(\hat{A})=det(A)$ $\square$.\\
	 \\
	 (c)\\
	 \\
	 From (a) we see that $\hat{A}$ is a copy of $A$ but on line $a$, so, if we want $\hat{A}$ as $I$, $A$ will be $I$ but on line $a$. This line will be the multiplication of line $a$ of M and all columns of $A$. This multiplication will be all zero but in two cases:\\
	 (1) when $m_{ab}$ is multiplied by the $1$ on the diagonal, and the $a_{ij}$ will be multiplied by the $1$ of that row, generating $m_{ab}+a_{ij}$. But we want this multiplication to be zero, because it is outside the diagonal. So we will have
	 $$
	 m_{ab}+a_{ij} = 0\\
	 m_{ab}=-a_{ij}
	 $$
	 Which will give us that in the posijion $(i,j)$ of the matrix $A$ in the same position that we have $m$ in the $M$ matrix in $A$ we will have $-m$.\\
	 \\
	 (2) The second multiplication will be in the main-diagonal entry of this line, we will have $m_{ab}$ multiplied by zero plus the entry $a_{ii}$ which will need to be $1$
	 \\
	 In conjuction we will have that $A$ will be:
	 \begin{align*}
	 	\begin{bmatrix}
		 1&...&0&...&0&...&0\\
		 \vdots&\ddots&\vdots&\vdots&\vdots&\vdots&\vdots\\
		 0&...&1&...&0&...&0\\
		 \vdots&\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		 0&...&-m_{ab}&...&1&...&0\\
		 \vdots&\vdots&\vdots&\vdots&\vdots&\ddots&\vdots\\		
		 0&...&0&...&0&...&1
		 \end{bmatrix}\\
		 \square
	 \end{align*}
\end{document}

### 2018-06-01 books/FundamentalsMatrixComputations/sourve2/la/stdafx.cpp

@@ -1,0 +1,8 @@
+// stdafx.cpp : source file that includes just the standard includes
+// la.pch will be the pre-compiled header
+// stdafx.obj will contain the pre-compiled type information
+
+#include "stdafx.h"
+
+// TODO: reference any additional headers you need in STDAFX.H
+// and not in this file

### 2018-06-01 texts/philosophy/introolavo.tex
Olavo philosophies

@@
 	Até respondermos essas perguntas só poderemos ter uma única certeza: a de que o poder real não está num prédio, num pedaço de papel, numa toga ou num fardamento, está na possibilidade de determinar as ações alheias -- e neste momento o chefe do maior esquema de corrupção de um país está determinando as ações de toda uma nação, mantendo os destinos de milhões e milhões de pessoas ao alcance do impacto de sua sanha por uma quantidade ainda maior de poder.
+
+	 Filosofia como unidade do conhecimento na unidade da consciência e vice-versa
+	- Só a consciência individual é capaz de conhecimento
+	- Atos sem testemunhas
+	- Definição de psique
+	- A autoconsciência (consciência da consciência) como fundamento da moral
+	- Conceito de Inteligência e verdade
+	- Os graus de Certeza
+	- Trauma de emergência da razão
+	- Teoria dos patamares de consciência
+	- Teoria das doze camadas da personalidade
+	- Princípio de autoria
+	- Método da confissão (método anamnético)
+	- Teoria dos Quatro Discursos
+	- Fundamentos metafísicos dos gêneros literários
+	- Astrocaracteriologia
+	- O princípio do conhecimento por presença
+	- Intuicionismo radical
+	- Teoria da tripla intuição fundamental
+	- Paralaxe cognitiva
+	- Mentalidade revolucionária
+	- Teoria política
+	- Teoria do Império 
+	- Conceito de Sujeito da História
+	- Técnica filosófica (Anamnese, Meditação, Exame dialético, Pesquisa histórico-filológica, Hermenêutica, Exame de consciência e Técnica expressiva)
+	- Elementos de Estudo de religião comparada
+	- Conceito de Contemplação Amorosa
+	- Teoria reformada das castas
+	- A natureza e formas do poder
+	- Conceito de proposição auto-evidente (univocidade)
+	- Crítica Cultural
+	- Educação Liberal
+	https://www.facebook.com/flavio.lindolfo.cof/posts/2125551407723175
 \end{document}

### 2018-06-19 books/IntroductionLinearALgebra/Exercise.01.001.tex
Gilbert Strang Linear Algebra Book

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\title{2D Graphics with Asymptote}
\author{The Asymptote Project}
\newcommand{\insertrep}[1]{%
	\hspace*{-2.4cm}
	\fbox{\includegraphics[page=1,scale=1]{#1}}

}
\begin{document}

Describe geometrically (line, plane, or all of $R^3$) all linear combinations of:\\\\
Linear combination is $a*A+b*B$ where $a \in R$ and $b \in R$.\\
\\
(a) $A = \begin{bmatrix}1\\2\\3\end{bmatrix}$ and $B = \begin{bmatrix}3\\6\\9\end{bmatrix}$\\
\\
Both points are on the same line, so their linear combination can only express a line. The blue line is the line that is formed by all linear combinations of $A$ and $B$. The red points are random linear combinations of $A$ and $B$ that we confirm that fall all in the line.\\
\begin{center}
\insertrep{exercise01001a.pdf}
\end{center}
\newpage
(b)  $A = \begin{bmatrix}1\\0\\0\end{bmatrix}$ and $B = \begin{bmatrix}0\\2\\3\end{bmatrix}$\\
It is obvious that we cannot have one line passing throught $(0,0,0)$ that also passes throught $(1,0,0)$ and $(0,2,3)$. So, the linear combinations of theses points forms a plane.\\
The blue plane represents all linear combinations of $A$ and $B$.\\
The red poins are, again, random linear combinations of $A$ and $B$. We can see in the second figure how all points fall perfectly in the plane.
\begin{center}
\insertrep{exercise01001b1.pdf}
\end{center}
\begin{center}
	\insertrep{exercise01001b2.pdf}
\end{center}
\newpage
(c) $\begin{bmatrix}2\\0\\0\end{bmatrix}$ and $\begin{bmatrix}0\\2\\2\end{bmatrix}$ and $\begin{bmatrix}2\\2\\3\end{bmatrix}$\\
\begin{center}
	\insertrep{exercise01001c1.pdf}
\end{center}
\begin{center}
	\insertrep{exercise01001c2.pdf}
\end{center}
\end{document}

### 2018-06-21 books/IntroductionLinearALgebra/Exercise.01.001.tex
Gilbert Strang Introduction to Linear Algebra

@@
 \begin{document}
-
+Exercise 1:\\
 Describe geometrically (line, plane, or all of $R^3$) all linear combinations of:\\\\
@@
 \newpage
-(c) $\begin{bmatrix}2\\0\\0\end{bmatrix}$ and $\begin{bmatrix}0\\2\\2\end{bmatrix}$ and $\begin{bmatrix}2\\2\\3\end{bmatrix}$\\
+(c) $A = \begin{bmatrix}2\\0\\0\end{bmatrix}$ and $B = \begin{bmatrix}0\\2\\2\end{bmatrix}$ and $C = \begin{bmatrix}2\\2\\3\end{bmatrix}$\\
+\\
+In this case it is also impossible to have a line passing through $(0,0,0)$, $(2,0,0)$ and $(0,2,2)$, but it is also impossible to have a plane passing through $(2,2,3)$.
+So, all linear combinations of $A$, $B$, $C$ span all possible points of $R^3$.\\
+Again, we show the blue dashed box as a representation of the space, but the linear combinations are not limited inside this blue box, they will span all $R^3$.\\
+Deceivingly, the random points appear to span a plane.
+That happens because $C$ is almost the sum of $A$ and $B$.
+The second picture show us that the points are not perfectedly in the plane.
+The third picture helps us to see the difference because it shows what happens when $C=(2,2,2)$ and the linear combination fall all in the plane.
 \begin{center}
@@
 \end{center}
+\begin{center}
+	\insertrep{exercise01001c3.pdf}
+\end{center}
 \end{document}

### 2018-06-21 books/IntroductionLinearALgebra/Exercise.01.004.tex
Gilbert Strang Introduction to Linear Algebra

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\title{2D Graphics with Asymptote}
\author{The Asymptote Project}
\newcommand{\insertrep}[1]{%
	\hspace*{-2.4cm}
	\fbox{\includegraphics[page=1,scale=0.8]{#1}}
}
\begin{document}
Exercise 4:\\
From $v=\begin{bmatrix}2\\1\end{bmatrix}$ and $w=\begin{bmatrix}1\\2\end{bmatrix}$, find the components of $3v+w$ and $cv+dw$.\\
\begin{align*}
	v&=\begin{bmatrix}2\\1\end{bmatrix}\\
	w&=\begin{bmatrix}1\\2\end{bmatrix}\\
	\\
	3v+w &= 3*\begin{bmatrix}2\\1\end{bmatrix} + \begin{bmatrix}1\\2\end{bmatrix}\\
	&=\begin{bmatrix}6\\3\end{bmatrix}+\begin{bmatrix}1\\2\end{bmatrix}\\
	&=\begin{bmatrix}7\\5\end{bmatrix}\\
	\\
	cv+dw &= c*\begin{bmatrix}2\\1\end{bmatrix} + d*\begin{bmatrix}1\\2\end{bmatrix}\\
	&= \begin{bmatrix}2c\\c\end{bmatrix} + \begin{bmatrix}d\\2d\end{bmatrix}\\
	&= \begin{bmatrix}2c+d\\c+2d\end{bmatrix}
\end{align*}
\newpage
Red dots are random linear combinations of $v$ and $w$.
\begin{center}
	\insertrep{exercise01004.pdf}
\end{center}
\end{document}

### 2018-06-21 books/IntroductionLinearALgebra/Exercise.01.005.tex
Gilbert Strang Introduction to Linear Algebra

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\title{2D Graphics with Asymptote}
\author{The Asymptote Project}
\newcommand{\insertrep}[1]{%
	\hspace*{-2.4cm}
	\fbox{\includegraphics[page=1,scale=2]{#1}}
}
\begin{document}
Exercise 5:\\
Compute $u+v+w$ and $2u+2v+w$. How do you know $u$, $v$, $w$ lie in a plane.\\
$$u = \begin{bmatrix}1\\2\\3\end{bmatrix}$$
$$v = \begin{bmatrix}-3\\1\\-2\end{bmatrix}$$
$$w = \begin{bmatrix}2\\-3\\-1\end{bmatrix}$$
One should expect that three vectors must awayls express any $R^3$ point as a linear combination, but in this example we can see, the linear combination of $u+v+w$ "only" express a plane.\\
One hint is that summing all vector we have the zero vector. This means that the third vector does not increase the expressiveness of the linear combination.\\
This happen because the vector $w$ can be written as a linear combination of $v$ and $w$.\\
\\
The following proof explains why $w$ does not increase the expressiveness of $u$ and $v$.
\begin{align*}
	u+v+w=0\\
	u+v=-w\\
	-u-v=w\\
	\\
	A = au + bv + cw\\
	A = au + bv + c(-u-v)\\
	A = au + bv - cu- cv\\	
	A = (a-c)u + (b-c)v\\
	A = a_2u + b_2v
\end{align*}
\newpage
In this image, the blue plane represents all possible linear combinations of all three vectors. The red dots are random linear combinations.
\begin{center}
	\insertrep{exercise01005a.pdf}
\end{center}
\newpage
In this image we see exactly how all random linear combinations fall in the plane.
\begin{center}
	\insertrep{exercise01005b.pdf}
\end{center}
\end{document}

### 2018-06-21 books/IntroductionLinearALgebra/Exercise.01.006.tex
Gilbert Strang Introduction to Linear Algebra

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\title{2D Graphics with Asymptote}
\author{The Asymptote Project}
\newcommand{\insertrep}[1]{%
	\hspace*{-2.4cm}
	\fbox{\includegraphics[page=1,scale=2]{#1}}
}
\begin{document}
Exercise 6:\\
Every combination of $v=(1,-2,1)$ and $w=(0,1,-1)$ has components that  add to? Find $d$ and $d$ so that $cv+dw=(3,3,-6)$.\\
(a)\\
\begin{align*}
	v+w &= \begin{bmatrix}1\\-2\\1\end{bmatrix} + \begin{bmatrix}0\\1\\-1\end{bmatrix}\\
	&= \begin{bmatrix}1\\-1\\0\end{bmatrix}
\end{align*}
(b)
\begin{align*}
cv+dw &= c*\begin{bmatrix}1\\-2\\1\end{bmatrix} + d*\begin{bmatrix}0\\1\\-1\end{bmatrix} = \begin{bmatrix}3\\3\\-6\end{bmatrix}\\
	&= \begin{bmatrix}c*1+d*0\\c*-2+d*1\\c*1+d*-1\end{bmatrix} = \begin{bmatrix}3\\3\\-6\end{bmatrix}\\
	\\
	c*1+d*0&=3\\
	c&=3\\
	\\
	c*-2+d*1 = 3\\
	3*-2+d*1 = 3\\	
	-6+d = 3\\		
	d = 3 + 6\\			
	d = 9\\		
	\\
	c*1+d*-1=-6\\
	3*1+9*-1=-6\\
	3-9=-6\\	
	-6=-6\\
\end{align*}
\end{document}

### 2018-06-21 books/IntroductionLinearALgebra/Exercise.01.009.tex
Gilbert Strang Introduction to Linear Algebra

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{lscape}
\title{2D Graphics with Asymptote}
\author{The Asymptote Project}
\newcommand{\insertrep}[1]{%
	\hspace*{-2.4cm}
	\fbox{\includegraphics[page=1,scale=0.6]{#1}}
}
\begin{document}
	Exercise 9:\\
	If three corners of a parallelogram are $(1,1)$, $(4,2)$ and $(1,3)$ what are all three of the possible fourth corners? Draw two of them.\\
	\\
	This question is a little bit tricky. If you have three points of a parallelogram, we definitely know the forth point. But with three points and no specific order, you actually have three possible orders, with means that you have actually three possible parallelograms.\\
	For example, we have $A$, $B$ and $C$, so wue actually have "partial-parallelograms": $ABC$, $ACB$, and $CAB$. We actually have six permutations: $3!=3*2*1=6$, but some permutation are actually the same. For example: $BAC$ and $CAB$, $ABC$ and $CBA$, $BCA$ and $ACB$. If you look carefully, you will see that the order of the first and the third point does not matter in this case, just the "middle" point matters.\\
	We can calculate one of the points using the pallelogram rule that its opposing sides are equal. In the parallelogram $ABCD$, we have that $AC=BD$. Others permutations will generate the other points.
	\begin{align*}
		C-A=D-B\\
		\\
		\begin{bmatrix}1\\3\end{bmatrix}-\begin{bmatrix}1\\1\end{bmatrix} = \begin{bmatrix}d_1\\d_2\end{bmatrix}-\begin{bmatrix}4\\2\end{bmatrix}\\
		d_1 - 4 = 1 - 1\\
		d_2 - 2 = 3 - 1\\
		\\
		d_1 - 4 = 0\\
		d_2 - 2 = 2\\
		\\
		d_1 = 4\\
		d_2 = 4\\
	\end{align*}
	\begin{landscape}
		\begin{center}
			\insertrep{exercise01009.pdf}
		\end{center}
	\end{landscape}
\end{document}

### 2018-06-23 books/IntroductionLinearALgebra/Exercise.01.010.tex
Introduction to Linear Algebra by Gilbert Strang

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{lscape}
\title{2D Graphics with Asymptote}
\author{The Asymptote Project}
\newcommand{\insertrep}[1]{%
	\hspace*{-2.4cm}
	\fbox{\includegraphics[page=1,scale=1]{#1}}
}
\begin{document}
	Exercise 10:\\
	Which point of the cube is $i+j$. Which point is the vector sum of $i=(1,0,0)$ and $j=(0,1,0)$ and $k=(0,0,1)$? Describe all points $(x,y,z)$ in the cube.\\
	We will generate random points using three random values $a$, $b$ and $c$ as:
	$$a*A+b*B+c*C$$
	In this figure we try some random linear combinations using unbounded values for $a$, $b$, $c$. We see that points are spread both inside and outside the unit cube.\\
	\begin{center}
		\insertrep{exercise01010a.pdf}
	\end{center}
	In the second attemp we try to normalize the three weights as their sum in 1.\\
	\begin{align*}
		a + b + c = 1\\
		\\
		a = \frac{a}{a+b+c}\\
		b = \frac{b}{a+b+c}\\
		c = \frac{c}{a+b+c}\\				
	\end{align*}
	We can see that altought all random points fall inside the but they are not as spread as possible. We have a filling that they do no span all possible cubes. Which makes sense given that as $x$ and $y$ approaches $0.5$, $z$ converges to zero.	
	\begin{center}
		\insertrep{exercise01010b1.pdf}
	\end{center}
	This figure is the same as above but with more random points.
	\begin{center}
		\insertrep{exercise01010b2.pdf}
	\end{center}
	\newpage
	And the following figure is when we bound the random points to the interval $[0,1]$.
	\begin{center}
		\insertrep{exercise01010c.pdf}
	\end{center}	
\end{document}

### 2018-06-24 books/IntroductionLinearALgebra/Exercise.01.011.tex
Introduction to Linear Algebra by GIlbert Strang

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{lscape}
\title{2D Graphics with Asymptote}
\author{The Asymptote Project}
\newcommand{\insertrep}[1]{%
	\hspace*{-2.4cm}
	\fbox{\includegraphics[page=1,scale=1.5]{#1}}
}
\begin{document}
	Exercise 11:\\
	Four corners of the cube are $(0,0,0)$,$(1,0,0)$,$(0,1,0)$,$(0,0,1)$. What are the other four corners? Find the coordinates of the center point of the cube. The center points of the six faces are?\\
	The other coordinates are the sum of the four known points.\\
	And the center point for each of the cube face's are the averaged sum of itts four corners.
	\begin{center}
		\insertrep{exercise01011.pdf}
	\end{center}
\end{document}

### 2018-06-24 books/IntroductionLinearALgebra/Exercise.01.012.tex
Introduction to Linear Algebra by GIlbert Strang

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{lscape}
\usepackage{hyperref}
\title{2D Graphics with Asymptote}
\author{The Asymptote Project}
\newcommand{\insertrep}[1]{%
	\hspace*{-2.4cm}
	\fbox{\includegraphics[page=1,scale=1.5]{#1}}
}
\begin{document}
	Exercise 12:\\
	How many corners does a cube have in 4 dimensions? How many 3D faces? How many edges?

	\section{Vertices}
	A typical corner is $(0,0,1,0)$. A typical edge goes to $(0,1,0,0)$.\\
	\\
	In 3D, all cube corners are:\\
	$(0,0,0)$\\
	$(0,0,1)$\\
	$(0,1,0)$\\
	$(0,1,1)$\\
	$(1,0,0)$\\
	$(1,0,1)$\\
	$(1,1,0)$\\
	$(1,1,1)$\\
	\\
	Which follows the permutation logic, and we know that in a set with three members (3D space), each with two possibilities (0 or 1) we have $2^3=8$ permutations.\\

	\section{Edges}
	In a 4D space we will have $2^4=16$ permutations, so we will have 16 corners.\\
	If we use the technique of imagining a 4D-Cube as a moving 3D Cube, we will have:\\
	1 - 12 edges from the "starting" cube;\\
	2 - 12 edges from the "final" cude;\\
	3 - 8 edges from the "moving vertices"\\
	\\
	What will give us 32 edges on a 4D-Cube.
	\newpage
	The recursive formula is: $f(N) = 2*f(N-1) + 2^{N-1}$
	\\
	\begin{align*}
		f(N) = 2f(N-1)+2^{N-1}\\
		f(N+1) = 2f(N)+2^{N}\\
		f(N+1) - 2f(N) = 2^{N}\\
		(E-2)f = 2^{N}\\
		(E-2)(E-2)f = (E-2)*2^{N}\\
		(E-2)^2f = 0\\
		\\
		(\alpha n + \beta)2^n\\
		\\
		(1\alpha + \beta)2^1 = 1\\
		(2\alpha + \beta)2^2 = 4\\
		(3\alpha + \beta)2^3 = 12\\
		\\
		2\alpha + 2\beta = 1\\
		8\alpha + 4\beta = 4\\
		24\alpha + 8\beta = 12\\
		\\
		-2(2\alpha + 2\beta) = -2*1\\			
		8\alpha + 4\beta = 4\\
		\\
		-4\alpha - 4\beta = -2\\			
		8\alpha + 4\beta = 4\\
		\\
		-4\alpha - 4\beta = -2\\			
		8\alpha + 4\beta = 4\\		
		\\
		4\alpha + 0\beta = 2\\
		\\
	\end{align*}
	\begin{align*}
		4\alpha = 2\\		
		\alpha = \frac{2}{4}\\
		\alpha = \frac{1}{2}\\
		\\
		2\frac{1}{2} + 2\beta = 1\\
		\frac{2}{2} + 2\beta = 1\\		
		1 + 2\beta = 1\\
		2\beta = 1 - 1\\
		2\beta = 0\\		
		\beta = 0
		\\
		(\frac{n}{2})2^n\\		
		\frac{n*2^n}{2}\\
	\end{align*}
	Which is a "closed form" for the quantities of edges of "cube" in any dimension:
	$$ \text{edges}(n) = \frac{n*2^n}{2}$$	
	Which can be interpreted as the dimension times half the vertices. This makes total sense because at each vertex there are three edges, one for each each axis in that dimension. This counts each edge twice, at the start and at the end, so we divide by two.
	\newpage
	\\
	Reference:\\
	\\
	Beyond the Third Dimension\\	
	by \\
	Thomas F. Banchoff \\
	\begin{quote}		
	It is helpful to think of cubes as generated by lower-dimensional cubes in motion. A point in motion generates a segment; a segment in motion generates a square; a square in motion generates a cube; and so on. From this progression, a pattern develops, which we can exploit to predict the numbers of vertices and edges.\\
	Each time we move a cube to generate a cube in the next higher dimension, the number of vertices doubles. That is easy to see since we have an initial position and a final position, each with the same number of vertices. Using this information we can infer an explicit formula for the number of vertices of a cube in any dimension, namely 2 raised to that power.\\
	What about the number of edges? A square has 4 edges, and as it moves from one position to the other, each of its 4 vertices traces out an edge. Thus we have 4 edges on the initial square, 4 on the final square, and 4 traced out by the moving vertices for a total of 12. That basic pattern repeats itself. If we move a figure in a straight line, then the number of edges in the new figure is twice the original number of edges plus the number of moving vertices. Thus the number of edges in a four-cube is 2 times 12 plus 8 for a total of 32. Similarly we find 32 + 32 + 16 = 80 edges on a five-cube and 80 + 80 + 32 = 192 edges on a six-cube.\\
	This presentation definitely suggests a pattern, namely that the number of edges of a hypercube of a given dimension is the dimension multiplied by half the number of vertices in that dimension. Once we notice a pattern like this, it can be proved to hold in all dimensions by mathematical induction.
	\end{quote}
	\\
	\url{http://www.math.brown.edu/~banchoff/Beyond3d/chapter4/section05.html}
	\\
	\section{Faces}
\end{document}

### 2018-06-24 books/IntroductionLinearALgebra/Exercise.01.012.tex
Introduction to Linear Algebra by Gilbert Strang

@@
 	\section{Faces}
+	The easiest way to calculate the quantity of faces of a 4D cube is to realize that from each vertex starts four edges and each face is a combination of two of theses edges.
+This gives us ${4 \choose 2}=6$ faces per vertex.\\
+	A 4D Cube has $2^4=16$ vertices each containing 6 faces. But this algotihm counts each face 4 times, so we actually have:
+	$$f(n) = \frac{2^n*{n \choose 2}}{4}$$
+	Which gives us the correct value for $R^4$, $\frac{2^4*{4 \choose 2}}{4}=24$.\\
+	\\	
+	Reference:\\
+	\begin{quote}
+		The hypercube is so highly symmetric that every vertex looks like every other vertex.
+If we know what happens at one vertex, we can figure out what is going to happen at all vertices.
+At each vertex there are as many square faces as there are ways to choose 2 edges from among the 4 edges at the point, namely 6.
+Since there are 16 vertices, we can multiply 6 by 16 to get 96, but this counts each square four times, once for each of its vertices.
+The correct number of squares in a hypercube is then 96/4, or 24.
+	\end{quote}
+	http://www.math.brown.edu/~banchoff/Beyond3d/chapter4/section07.html
 \end{document}

### 2018-06-24 books/IntroductionLinearALgebra/Exercise.01.013.tex
Introduction to Linear Algebra by Gilbert Strang

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{lscape}
\usepackage{hyperref}
\title{2D Graphics with Asymptote}
\author{The Asymptote Project}
\newcommand{\insertrep}[1]{%
	\hspace*{-2.4cm}
	\fbox{\includegraphics[page=1,scale=0.5]{#1}}
}
\begin{document}
	Exercise 13:\\
	(a) What us the sum V if the twelve vectors that go from the center of a clock to the hours 01:00, 02:00, ..., 12:00?\\
	(b) If the 02:00 vector is removed, why do the 11 remaining vectors add to0 8:00?\\
	(c) What are the components of that 02:00 vector $v = (cos \theta, sin \theta)$?
	\\
	(a) The sum is the zero vector because of the symmetry.\\
	(b) Because 08:00 is the vector that is symmetric to the 02:00 vector.\\
	(c) Each hour is $-\frac{\pi}{12}$, but our zero is actually at 03:00. So 2:00 is $(cos(\frac{2\pi}{12}),sin(\frac{2\pi}{12}))$\\
	\begin{align*}
		cos(\frac{2\pi}{12}) &= 0.866025403784439\\
		sin(\frac{2\pi}{12}) &= 0.5\\
	\end{align*}

	\begin{center}
		\insertrep{exercise01013.pdf}
	\end{center}
\end{document}

### 2018-08-01 books/IntroductionLinearALgebra/Exercise.01.014.tex
.

--- 2018-06-24 books/IntroductionLinearALgebra/Exercise.01.013.tex
@@
 \begin{document}
-	Exercise 13:\\
-	(a) What us the sum V if the twelve vectors that go from the center of a clock to the hours 01:00, 02:00, ..., 12:00?\\
-	(b) If the 02:00 vector is removed, why do the 11 remaining vectors add to0 8:00?\\
-	(c) What are the components of that 02:00 vector $v = (cos \theta, sin \theta)$?
+	Exercise 14:\\
+	Suppose the twelves vectors start from 06:00 at the bottom instead of $(0,0)$ at the center. The vector to 12:00 is doubled to $(0,2)$. Add the new twelve vectors.\\
 	\\
-	(a) The sum is the zero vector because of the symmetry.\\
-	(b) Because 08:00 is the vector that is symmetric to the 02:00 vector.\\
-	(c) Each hour is $-\frac{\pi}{12}$, but our zero is actually at 03:00. So 2:00 is $(cos(\frac{2\pi}{12}),sin(\frac{2\pi}{12}))$\\
-	\begin{align*}
-		cos(\frac{2\pi}{12}) &= 0.866025403784439\\
-		sin(\frac{2\pi}{12}) &= 0.5\\
-	\end{align*}
-
-	\begin{center}
-		\insertrep{exercise01013.pdf}
-	\end{center}
+	This is the same as adding $(0,1)$, wich will make the sum result in $(0,12)$ instaead of $(0,0)$.
 \end{document}

### 2018-08-01 courses/harvard-applied-calculus/PE.01.tex
.

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Daniel Frederico Lins Leite}
\begin{document}
	Here is the formula for price elasticity between two points $(p_1,q_1)$  and $(p_2,q_2)$:
	\begin{align*}
		\text{Price Elasticity} = \frac{\triangle q}{q_1} / \frac{\triangle p}{p_1}
	\end{align*}		
	Rearrange the formula and use the assumption that  to write a formula for price elasticity of demand at the point . Select the correct formula below.				
	\\
	Answer:\\
	\begin{align*}
		 \frac{\triangle q}{q_1} / \frac{\triangle p}{p_1}  &= \frac{\triangle q}{q_1} * \frac{p_1}{\triangle p}\\
		 &= \frac{\triangle q}{\triangle p} * \frac{p_1}{q_1}\\
 		 &= \frac{dq}{dp}\big|_{p_1} * \frac{p_1}{q_1}
	\end{align*}			
\end{document}

### 2018-08-01 texts/math/Brainstorm.Numbers.Infinite.tex
.

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Daniel Frederico Lins Leite}
\begin{document}
	Cantor's Diagonalization Proof start with the following assumptions.\\
	1 - Every decimal representation of a real number is unique.\\
	\\
	Cantor's Proof needs this assumption because it generates a new decimal representation that is not present in the chosen/constructed set. If for some reason exists multiple representations for the same real number, as we have in the rational numbers, having a new decimal representation is not necessary to Cantor's proof. We should get this new representation, normalize it to its canonical representation and test its set "is in" relation.\\
	For example, if we apply yhe Cantor's Diagonalization Proof for the canonized set of all rationals, a set that we know a bijection from the Natural numbers, we can find a evil twin that is not in the set using the generated representation, but we can use the rational normalization algorithm, to find its canonical representation and actually find the number in the list.	\\
	\\
	Example:\\
	$$0.999... = 1$$
	\\
	2 - Every decimal representation of a real number is valid.\\
	\\
	This is obvious because the twin number must be a valid real number to be considered is the real number set, but Cantor does not give this proof, he only assumes that every decimal representation is valid, which is not the case.\\
	\\
	For example, we know that $0.999... = 1$, which implies that $0.00000...1$ does not exist.\\
	A possible proof that $0.000...1$ does exist can be said that:\\
	\begin{align*}
		A &= 0.000...1\\
		A &< 1/10\\
		A &< 1/100\\
		A &< 1/1000\\		
		...
	\end{align*}
	//TODO improve this
	Which is impossible.\\
	If there is a representation of an impossible real number, the question is... is this the unique impossible number? Are all other representations following a same pattern?\\
	\\
	The question can be summarized as, is there a finite representations of irrational numbers? This is different than asking if there are infinite irrational numbers.\\
	For example, we know that all roots, greater than one, of two are irrational.
	Assume $\sqrt[x]{2}}$ is rational with $p$ and $q$ as coprimes (normalized rational representation).
	\newpage
	\begin{align*}
		\sqrt[x]{2} &= \frac{q}{p}}\\
		(\sqrt[x]{2})^n &= (\frac{q}{p}})^n\\
		2 &= \frac{q^n}{p^n}}\\		
		2p^n &= q^n\\	
		2p^n &= (2k)^n\\		
		2p^n &= 2^nk^n\\				
		p^n &= \frac{2^nk^n}{2}\\						
		p^n &= 2^{n-1}k^n\\								
		p^n &= 2*2^{n-2}k^n\\										
		p^n &= 2*X\\												
	\end{align*}
	Given that multiplication is closed on parity (odd times odd is odd, and even times even is even), we must have p as even. If p is even it is a multiple of two. If it is a multiple of two. If $p$ and $q$ are multiple of two are not coprimes.\\
	If they are not coprimes we can reduce the original fraction and try again. Until we come to conclusion that the is no $q$ and $p$ that satisfy the assumption and that the root is not rational.\\
	So we have infinite irrational numbers, but we must ask if they have infinite representations.
\end{document}

### 2018-08-01 texts/philosophy/introolavo.tex
.

@@
 	https://www.facebook.com/flavio.lindolfo.cof/posts/2125551407723175
+
+	O objeto da religião cristã não são verdades gerais teoréticas, mas fatos concretos da ordem real, dos quais alguns já sucederam no tempo histórico desde o nascimento de Nosso Senhor até hoje, outros abrangem e transcendem o suceder temporal e outos destinam-se a suceder num futuro anunciado pela profecia.
+Dito de outro modo, não se trata de verdades formais, e sim materiais.
+Esta distinção deve ser enfatizada sobretudo no que diz respeito às verdades atemporais, extratemporais ou supratemporais, que tão frequentemente (por efeito da confusão entre a ordem do ser e a ordem do conhecer) se deixam tomar como verdades puramente formais a exemplo das verdades lógicas e matemáticas.
+É que estas refletem apenas a estrutura da possibilidade e são indiferentes ao suceder (ou não-suceder) real, ao passo que as verdades atemporais da religião não são desse tipo, não são meras relações entre conjuntos de possibilidades e sim FATOS QUE ACONTECEM O TEMPO TODO, sem descontinuidade, transcendendo o suceder temporal não porque lhe sejam indiferentes (como 2 + 2 = 4) e sim porque são constantes e continuados como a existência mesma,
+	https://www.facebook.com/olavo.decarvalho/posts/10156363216842192
+
+	W. R. Inge, no clássico ?Christian Mysticism?(New York, 1956), afirma:
+	?O misticismo é a tentativa de realizar, no pensamento e no sentimento, a imanência do temporal no eterno, e do eterno no temporal...
+Mas, uma vez que a nossa consciência do além é ela própria desprovida de forma, ela não pode ser trazida diretamente a uma relação com as formas do nosso pensamento.
+Em decorrência disso, ela tem de se expressar por símbolos.?
+	Tudo isso está certo, mas deixa de fora o principal: Se os símbolos são apenas instrumentos da linguagem humana, eles são criados pelo homem e nada mais expressam do que o pensamento humano mesmo.
+A famosa ?imanência do temporal no eterno e do eterno no temporal?
+não passa, aí, de um fenômeno interno da mente humana, sendo inteiramente temporal e nada tendo de eterno exceto uma pretensão nominal que atesta a sua própria impotência.
+	Ou os símbolos são a linguagem do próprio eterno e o canal do seu ingresso na esfera temporal, ou toda pretensão de falar do eterno só nos aprisiona mais e mais na esfera temporal.
+	https://www.facebook.com/olavo.decarvalho/posts/10156376101727192
+
+	Só o mais presunçoso dos idiotas negaria que há conhecimentos valiosos e essenciais espalhados em todas as tradições científicas, literárias.
+artísticas, religiosas e esotéricas milenares.
+A forma do conjunto, no entanto, é caótica e inapreensível, e toda tentativa de colocar nele alguma ordem esbarra não só na quantidade inabarcável do material e na multiplicidade dos códigos lingüísticos e simbólicos envolvidos, mas na dificuldade invencível de encontrar o nexo, a chave de abóbada desde a qual a unidade se revele por trás e por cima (ou por baixo) da massa, entre luminosa e obscura, que se oferece como supremo enigma à inteligência humana.
+Uma chave propriamente cognitiva ( isto é, doutrinal ou teórica) é inalcançável por definição, já que sua posse corresponderia ao domínio intelectual da "ciência divina?
+que só Deus possui.
+Mas uma chave heurística e prática pode ser encontrada pela busca da PRIORIDADE REAL capaz de separar os conhecimentos que são valiosos para o ser humano e aqueles que expressam somente uma ambição satanicamente desmedida.
+Essa chave, por sua vez, tem de emanar do reconhecimento da finalidade mais vital e dramática da nossa existência, que é a SALVAÇÃO DA ALMA, o salto da individualidade humana da vida temporal para a vida eterna.
+A rigor, a única tradição espiritual que tem essa meta como seu objetivo central e único, enquanto as outras se diversificam em finalidades múltiplas e variadas, é o cristianismo.
+Logo, só o cristianismo pode recolher, articular e ordenar, não numa impossível síntese teórica, mas na perspectiva da racionalidade prática, o máximo volume abarcável dos dados da sabedoria tradicional, separando o joio do trigo e retribuindo a cada uma das fontes a sua parcela da verdade.
+Se existe alguma ?unidade transcendente?
+acessível à consciência do homem temporal, é a unidade que só o cristianismo, absorvendo, depurando e ordenando, confere a tudo o que não é ele.
+
+	NB ? Esse é um dos temas que desenvolverei no meu próximo curso, ?Simbolismo e ordem cósmica, ontem e hoje?. A ementa e o programa serão divulgados nos próximos dias.
+	https://www.facebook.com/olavo.decarvalho/posts/10156402650257192
 \end{document}

### 2018-08-01 sources/games/html5/BoxManager.index.js

@@ -1,0 +1,26 @@
+import start from 'Game.js';
+import Graphics from 'Graphics.js';
+import BoxManager from 'BoxManager.js';
+import boxConfig from "BoxConfig.js";
+
+var boxManager = new BoxManager(boxConfig, x => {
+  if(x.type == "exit") console.log("enter");
+});
+start({
+  graphics: new Graphics(),
+  init: x => {
+    return {
+      assets: [
+        x.loadImage("http://localhost:8081/mi3/Room009/00.png")
+      ],
+      components: [
+        boxManager
+      ],
+    };
+  },
+  update: (dt, data) => {
+  },
+  render: (ctx, data) => {
+    ctx.drawImage(data.assets[0], 0, 0);
+  }
+});

### 2018-08-01 sources/games/html5/Bus.js

@@ -1,0 +1,50 @@
+export default function Bus()
+{
+  this.subscribes = [];
+  this.newSubscribe = function(f, callback) {
+    this.subscribes.push({
+      predicate: f,
+      publish: function(x){
+        callback(x);
+      }
+    });
+  };
+  this.newTopic = function(f) {
+    var topicSubscribers = [];
+    const topic = {
+      then: function(x){
+        topicSubscribers.push({
+          callback: x
+        });
+      }
+    };
+    this.subscribes.push({
+      predicate: f,
+      publish: function(x){
+        for(var i=0;i<topicSubscribers.length;++i)
+        {
+          topicSubscribers[i].callback(x);
+        }
+      }
+    });
+    return topic;
+  };
+  this.publish = function(msg) {
+    const immutableMsg = new Proxy(msg, {
+      get: function(target, prop) {
+        return target[prop];
+      }
+    });
+    for(var i=0;i<this.subscribes.length;++i){
+      let x = this.subscribes[i];
+      if(x.predicate){
+        try{
+          if(x.predicate(msg)) {
+            x.publish(immutableMsg);
+          }
+        }
+        catch(e){}
+      }
+    }
+  }
+}

### 2018-08-01 sources/games/html5/GameScene.js

@@ -1,0 +1,362 @@
+import Sprite from 'Sprite.js';
+import buildIncidence from 'BuildIncidence.js';
+import WalkGraph from 'WalkGraph.js';
+import BoxManager from 'BoxManager.js';
+import GetNearestPoint from 'GetNearestPoint.js';
+
+export default function GameScene() {
+  const data = {};
+  const lastBoxManager;
+  const lastObject;
+  const lastGraph;
+  const lastClick;
+  const userStack;
+  const zero = (x) => {
+    lastBoxManager = null;
+    lastObject = null;
+    lastGraph = null;
+    lastClick = null;
+    userStack = [];
+    data = {
+      firstTime: true,
+      scripts: {
+        entry: ""
+      },
+      objects: {
+
+      },
+      objectTable: x.objects || []
+    };
+    if (x && x.scripts) {
+      Object.keys(x.scripts)
+        .forEach(k => data.scripts[k] = x.scripts[k]);
+    }
+  };
+  zero({});
+  const obj2asset = {
+
+  };
+  const getPos = id => {
+    var obj = data.objects[id];
+    console.log(obj);
+    if (obj.def.type == "Picture") {
+      return obj.drawData.pos;
+    }
+  }
+  const setPos = (id, x, y) => {
+    const obj = data.objects[id];
+    if (obj.gateway.d && obj.gateway.d.data) {
+      obj.gateway.d.data.pos = [x, y];
+    }
+    else {
+      obj.drawData.pos = [x, y];
+    }
+  }
+  const getValue = (name, gamedata) => {
+    if (name == "click.x") {
+      return lastClick[0];
+    } else if (name == "click.y") {
+      return lastClick[1];
+    } else if (name == "lastObject") {
+      return lastObject.name;
+    } else if (name == "lastObject.x") {
+      return getPos(lastObject.name)[0];
+    } else if (name == "lastObject.y") {
+      return getPos(lastObject.name)[1];
+    } else if (name == "userPop") {
+      var top = userStack.pop();
+      console.log("userStack", userStack);
+      return top;
+    }
+    return name;
+  },
+  const runScript = (name, gamedata) => {
+    var stopped = false;
+    const script = data.scripts[name];
+    if (!script) {
+      console.log("runningScript", name, "notFound");
+      return stopped;
+    }
+    console.log("runningScript", name, script.code);
+    var lines = script.code;
+    const operandTable = {
+      loadObj: x => {
[…]

### 2018-08-01 sources/games/html5/Graphics.js

@@ -1,0 +1,113 @@
+export default function Graphics() {
+  this.context = null;
+  this.overlay = [];
+  this.toDraw = [];
+  this.queue = [];
+  this.clearRect = () => { };
+  this.beginPath = () => {
+    var a = arguments;
+    this.overlay.push(() => this.context.beginPath(...a))
+  };
+  this.arc = () => {
+    var a = arguments;
+    this.overlay.push(() => this.context.arc(...a))
+  };
+  this.rect = () => {
+    var a = arguments;
+    this.overlay.push(() => this.context.rect(...a))
+  };
+  this.fill = () => {
+    var a = arguments;
+    var style = this.fillStyle;
+    this.overlay.push(() => {
+      this.context.fillStyle = style;
+      this.context.fill(...a);
+    })
+  };
+  this.stroke = () => {
+    var a = arguments;
+    var style = this.strokeStyle;
+    this.overlay.push(() => {
+      this.context.strokeStyle = style;
+      this.context.stroke(...a);
+    })
+  };
+  this.scale = () => {
+    var a = arguments;
+    this.overlay.push(() => this.context.scale(...a))
+  };
+  this.restore = () => {
+    var a = arguments;
+    this.overlay.push(() => this.context.restore(...a))
+  };
+  this.save = () => {
+    var a = arguments;
+    this.overlay.push(() => this.context.save(...a))
+  };
+  this.translate = () => {
+    var a = arguments;
+    this.overlay.push(() => this.context.translate(...a))
+  };
+  this.fillText = () => {
+    var a = arguments;
+    var style = this.fillStyle;
+    var font = this.font;
+    this.overlay.push(() => {
+      this.context.fillStyle = style;
+      this.context.font = font;
+      this.context.fillText(...a);
+    });
+  };
+  this.moveTo = () => {
+    var a = arguments;
+    this.overlay.push(() => this.context.moveTo(...a))
+  };
+  this.lineTo = () => {
+    var a = arguments;
+    this.overlay.push(() => this.context.lineTo(...a))
+  };
+  this.drawImage = () => {
+    const a = arguments;
+    var getCommand = () => {
+      if (a.length == 3) this.context.drawImage(a[0], a[1], a[2]);
[…]

### 2018-08-01 sources/games/html5/Math.js

@@ -1,0 +1,43 @@
+export function myclamp(x, min, max) {
+  if (x < min) return min;
+  if (x > max) return max;
+  return x;
+}
+
+export function vecscal(x, s) {
+  return [x[0] * s, x[1] * s];
+}
+
+export function vecdot(x, y) {
+  return x[0] * y[0] + x[1] * y[1];
+}
+
+export function vecminus(x, y) {
+  return [x[0] - y[0], x[1] - y[1]];
+}
+
+export function vecLength(x) {
+  return Math.sqrt(x[0] * x[0] * 1.0 + x[1] * x[1] * 1.0);
+}
+
+export function vecNormalize(v) {
+  var l = vecLength(v) * 1.0;
+  return [v[0] * 1.0 / l, v[1] * 1.0 / l];
+}
+
+export function vec(from, to, normalize) {
+  if (!normalize)
+    return [to[0] - from[0], to[1] - from[1]];
+  else {
+    return vecNormalize([to[0] - from[0], to[1] - from[1]]);
+  }
+}
+
+export function vecDraw(ctx, pos, v, color) {
+  color = color || "green"
+  ctx.strokeStyle = color;
+  ctx.beginPath();
+  ctx.moveTo(pos[0], pos[1]);
+  ctx.lineTo(pos[0] + v[0], pos[1] + v[1]);
+  ctx.stroke();
+}

### 2018-08-01 sources/games/html5/Nodes.js

@@ -1,0 +1,358 @@
+import {myclamp, vec, vecscal, vecdot, vecminus, vecLength, vecNormalize, vecDraw} from 'Math.js';
+
+export default function Nodes(setf, endf) {
+  this.data = {
+    dt: 0,
+    path: [],
+    pos: [0, 0, 0],
+    dirCode: "",
+    target: [340, 350],
+    nodes: [
+      [450, 440],
+      [340, 350],
+      [250, 450]
+    ],
+    edges: [
+      { nodes: [0, 1], vel: 1, end: [[1, 0]] },
+      { nodes: [1, 2], vel: 1, begin: [[0, 1]] }
+    ],
+    mousePos: null
+  };
+  this.astar = (from, to) => {
+    var getNeighbors = (x) => {
+      var edgeNum = x.node[0];
+      var edge = this.data.edges[0];
+      var neighbors = [];
+      if (x.node[1] != 0) neighbors.push({ node: [edgeNum, 0] });
+      if (x.node[1] != 1) neighbors.push({ node: [edgeNum, 1] });
+
+      if(edgeNum == to[0]){
+        neighbors.push({ node: [edgeNum, to[1]] });
+      }
+
+      if (x.node[1] == 0) {
+        if (edge.begin) {
+          edge.begin.forEach(x => {            
+            neighbors.push({ node: [x[0], x[1]] });
+          });
+        }
+      }
+      if (x.node[1] == 1) {
+        if (edge.end) {
+          edge.end.forEach(x => {            
+            neighbors.push({ node: [x[0], x[1]] });
+          });
+        }
+      }
+
+      //console.log("getneighbors", x.node, neighbors);
+      return neighbors;
+    };
+    var heuristic = (x) => {
+      var edge = this.data.edges[x.node[0]];
+      var n1 = this.data.nodes[edge.nodes[0]];
+      var n2 = this.data.nodes[edge.nodes[1]];
+      var v = [n2[0] - n1[0], n2[1] - n1[1]];
+      var vl = Math.sqrt(v[0] * v[0] + v[1] * v[1]);
+      v[0] = v[0] * x.node[1] / vl;
+      v[1] = v[1] * x.node[1] / vl;
+
+      var tedge = this.data.edges[to[0]];
+      var tn1 = this.data.nodes[tedge.nodes[0]];
[…]

### 2018-08-01 sources/games/html5/WalkGraph.Index.js

@@ -1,0 +1,180 @@
+// Import stylesheets
+import './style.css';
+import start from 'Game.js';
+import AStar from 'AStar.js';
+import WalkGraph from 'WalkGraph.js';
+import buildIncidence from 'BuildIncidence.js';
+import log from 'Console.js';
+import { myclamp, vec, vecscal, vecdot, vecminus, vecLength, vecNormalize, vecDraw } from 'Math.js';
+import GetNearestPoint from 'GetNearestPoint.js';
+import Sprite from 'Sprite.js';
+import guybrushConfig from 'GuybrushConfig.js';
+import cannonConfig from 'CannonConfig.js';
+import Graphics from 'Graphics.js';
+
+var el = document.getElementById("console");
+const log = (x) => {
+  if (el.children.length >= 5) {
+    el.removeChild(el.firstChild);
+  }
+  var ellog = document.createElement('pre');
+  if (arguments.length == 1)
+    ellog.innerHTML = JSON.stringify(x);
+  else
+    ellog.innerHTML = JSON.stringify(Array.from(arguments));
+  el.appendChild(ellog);
+}
+
+function NearestPoint(config) {
+  const Point = [10, 10];
+  this.update = (dt, data) => {
+    if (data.mouseClicks.length > 0) {
+      
+      Point = data.mouseClicks[0].pos;
+    }
+  };
+  const getXY = (edge, t) => {
+    if (t < 0) t = 0;
+    if (t > 1) t = 1;
+    var e = config.edges[edge];
+    var n0 = config.nodes[e.nodes[0]];
+    var n1 = config.nodes[e.nodes[1]];
+    var v = [n1.pos[0] - n0.pos[0], n1.pos[1] - n0.pos[1]];
+    return [
+      v[0] * t + n0.pos[0],
+      v[1] * t + n0.pos[1]];
+  };
+  this.render = (ctx, data) => {
+    ctx.fillStyle = "Green";
+    ctx.beginPath();
+    ctx.arc(Point[0], Point[1], 4, 0, 2 * Math.PI);
+    ctx.fill();
+
+    var best = GetNearestPoint(Point, config, ctx);
+    var nearest = getXY(best[0], best[4]);
+    ctx.beginPath();
+    ctx.arc(nearest[0], nearest[1], 2, 0, 2 * Math.PI);
+    ctx.fill();
+  };
+}
+
+const config = buildIncidence([
[…]

### 2018-08-01 sources/games/html5/pong.js

@@ -1,0 +1,150 @@
+<!DOCTYPE html>
+<html>
+<head>
+  <meta charset="utf-8">
+  <meta name="viewport" content="width=device-width">
+  <title>JS Bin</title>
+</head>
+<body>
+  <canvas id="backbuffer" width="800" height="500">
+  </canvas>
+  <script>
+    function random(){ return (Math.random()-0.5)*2.0; }
+    function isInsideAABB(pos, posAABB, sizeAABB){
+      if(pos[0] < posAABB[0]) return false;
+      if(pos[1] < posAABB[1]) return false;
+      if(pos[0] > (posAABB[0] + sizeAABB[0])) return false;
+      if(pos[1] > (posAABB[1] + sizeAABB[1])) return false;
+      return true;
+    }
+    function GameState (){
+      this.constants = {
+        ballSize: 10,
+        courtHeight: 500,
+        minVel: 100,
+        incVel: 1.05,
+        paddleSize: [20,50],
+        paddleX: [0, 500]
+      }
+      this.world = Object.create(this.constants);
+      this.world.right = 250;
+      this.world.rightScore = 0;
+      
+      this.resetMatch();
+      this.you = Object.create(this.world);
+      this.you.left = 250;
+      this.you.leftScore = 0;
+     
+      var x = this;
+      var handler = {
+        get: function(obj, prop){                
+          return x.you[prop];
+        },
+        set: function(obj, prop, value){          
+          throw "Read-Only"
+        }
+      };
+      this.commands = [];
+      this.Data = Object.create(this.you);
+    };
+    GameState.prototype.resetMatch = function(){
+      this.world.ball = {
+          startPosition: [250.0, 250.0],
+          pos: [250.0,250.0],
+          vel: [random()*500,
+                0]
+      };
+    }
+    GameState.prototype.addCommand = function(c){
+      this.commands.push(c);
+    }
+    GameState.prototype.stepLeft = function(f){
+      this.you.left = Math.min(
+          Math.max(0, this.you.left + f), 300
+      );
+    };
+    GameState.prototype.step = function(dt){      
+      var startPosition = this.world.ball.startPosition;
+      var ballPos = this.world.ball.pos;      
+      var ballVel = this.world.ball.vel;      
+      ballPos[0] += this.world.ball.vel[0]*dt;
+      ballPos[1] += this.world.ball.vel[1]*dt;      
+      
[…]

### 2018-11-14 texts/dev/DIY - Database.tex
.

\documentclass[10pt,a4paper]{book}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\lstset{
	frame=tb, % draw a frame at the top and bottom of the code block
	tabsize=4, % tab space width
	showstringspaces=false, % don't mark spaces in strings
	numbers=left, % display line numbers on the left
	commentstyle=\color{green}, % comment color
	keywordstyle=\color{blue}, % keyword color
	stringstyle=\color{red} % string color
}
\author{Daniel Frederico Lins Leite}
\title{DIY - Database}
\begin{document}
	\chapter{REPL}

	\begin{lstlisting}[language=C++, caption={C++ code using listings}]
	#include <stdio.h>
	#include <stddef.h>
	#include <stdint.h>
	#include <stdlib.h>
	#include <string>
	#include <sstream>
	#include <iostream>
	#include <functional>
	#include <tuple
	\end{lstlisting}

	\begin{lstlisting}[language=C++, caption={C++ code using listings}]
	int main(int argc, char* argv[]) 
	{
		REPL repl;
		repl.run([](auto str, auto& ss) {
			if (str == ".exit") return -1;
			else 
			{
				ss << "Unrecognized command [" 
				   << str << "]";
				return 0;
			}
		});
		exit(EXIT_SUCCESS);
		return 0;
	}
	\end{lstlisting}

	\pagebreak

	\begin{lstlisting}[language=C++, caption={C++ code using listings}]
	using PREPLCallback = int(
		const std::string&,
		std::stringstream& ss);
	using REPLCallback = std::function<PREPLCallback>;
	class REPL
	{
	public:
		REPL() :
			in(std::cin),
			out(std::cout)
		{ }
		REPL(std::istream& in, std::ostream& out) :
			in(in),
			out(out)
		{ }

		void run(REPLCallback f) { ... }
	private:
		std::istream& in;
		std::ostream& out;

		std::string read_input() { ... }	
	};
	\end{lstlisting}

	\begin{lstlisting}[language=C++, caption={C++ code using listings}]
	void run(REPLCallback f)
	{
		std::stringstream ss;
		while (true) 
		{
			out << "db> ";

			ss.str("");
			ss.clear();

			auto str = read_input();
			auto status = f(str, ss);
			if (status > 0)
			return exit(status);
			else if (status < 0)
			break;

			out << ss.str() << std::endl;
		}
	}
	\end{lstlisting}

	\begin{lstlisting}[language=C++, caption={C++ code using listings}]
	std::string read_input() 
	{
		std::string str;
		std::getline(in, str);
		if (str.size() <= 0)
		{
			out << "Error reading input." << std::endl;
			exit(EXIT_FAILURE);
		}
		return str;
	}
	\end{lstlisting}
\end{document}

### 2018-11-14 sources/cpp/allocators/source/allocators.h

@@ -1,7 +1,7 @@
 #ifndef ALLOCATORS_H
 #define ALLOCATORS_H
 
-//using size_t = unsigned long long;
+using size_t = unsigned long long;
 using uint8_t = unsigned char;
 using uint32_t = unsigned int;
 

### 2018-11-14 sources/cpp/coroutines/main.all.cpp

@@ -1,0 +1,126 @@
+// namespace std::experimental
+// {
+//     template <typename... T> struct coroutine_traits;
+
+//     template <typename T = void> struct coroutine_handle;
+//     template <>
+//     struct coroutine_handle<void>
+//     {
+//         static coroutine_handle from_address(void* ptr)
+//         {
+//             return {ptr};
+//         }
+//         template <class _Tp, bool _CallIsValid = false>
+//         static coroutine_handle from_address(_Tp*) {
+//             // static_assert(_CallIsValid, "coroutine_handle<void>::from_address cannot be called with non-void pointers");
+//         }
+
+//         constexpr coroutine_handle() :ptr(nullptr) {}
+//         constexpr coroutine_handle(void* p) :ptr(p) {}
+
+//         void* address() const { return ptr; }        
+//         constexpr explicit operator bool() const { return ptr; }
+//         void operator()() { resume(); }
+
+//         void resume() {
+//             __builtin_coro_resume(ptr);
+//         }
+//         void destroy() {
+//             __builtin_coro_destroy(ptr);
+//         }
+//         bool done() const {
+//             return __builtin_coro_done(ptr);
+//         }
+//     private:
+//         template <class _PromiseT> friend class coroutine_handle;
+//         void* ptr;
+//     };
+
+//     template <typename _Promise>
+//     class coroutine_handle : public coroutine_handle<> {
+//         using _Base = coroutine_handle<>;
+//     public:
+//         static coroutine_handle from_address(void* ptr) {
+//             return {ptr};
+//         }
+
+//         _Promise& promise() const 
+//         {
+//             return *static_cast<_Promise*>(
+//                 __builtin_coro_promise(this->ptr, __alignof(_Promise), false));
+//         }
+
+//         static coroutine_handle from_promise(_Promise& __promise)
+//         {
+//             using _RawPromise = _Promise;
+//             //auto h = __builtin_coro_promise(::std::addressof(const_cast<_RawPromise&>(__promise)), __alignof(_Promise), true);
+//             auto h = __builtin_coro_promise(&(const_cast<_RawPromise&>(__promise)), __alignof(_Promise), true);
+//             return {h};
+//         }
+//     };
+// }
+
+// struct suspend_never
+// {   
+//     bool await_ready() { return false; } 
+//     void await_suspend( std::experimental::coroutine_handle<void> ) { }
+// };
+
+// struct suspend_always
+// {
[…]

### 2018-11-14 sources/cpp/timer/sources/main.cpp

@@ -1,0 +1,121 @@
+#define CATCH_CONFIG_MAIN
+#include "catch.hpp"
+
+#include "timer.h"
+
+using Timer1 = LinkedListTimer<NewAllocator>;
+using Timer2 = PriorityQueueTimer<NewAllocator>;
+
+//////////////////////////////////////////////////// Binary Heap
+
+TEST_CASE("Must insert first node in a empty bh", "[BinaryHeap]")
+{
+	auto heap = BinaryHeap<int, NewAllocator>();
+	heap.emplace(1, 1);
+	auto r = heap.pop();
+	REQUIRE(r == 1);
+}
+
+TEST_CASE("Must insert smaller than bigger and remove them", "[BinaryHeap]")
+{
+	auto heap = BinaryHeap<int, NewAllocator>();
+
+	heap.emplace(1, 1);
+	heap.emplace(2, 2);
+
+	auto r = heap.pop();
+	REQUIRE(r == 1);
+
+	r = heap.pop();
+	REQUIRE(r == 2);
+}
+
+//////////////////////////////////////////////////// TIMER TESTS
+
+#define TIMERTEST template <typename TTimer> void 
+
+TIMERTEST EmptyTimer(TTimer& timer)
+{
+	auto& experied = timer.tick(1);
+	REQUIRE(experied.size() == 0);
+}
+
+TIMERTEST AddTick(TTimer& timer)
+{
+	timer.add(1);
+	auto& expired = timer.tick(1);
+
+	REQUIRE(expired.size() == 1);
+	REQUIRE(expired[0] == 0);
+}
+
+TIMERTEST AddTwoItemsTickTwice(TTimer& timer)
+{
+	timer.add(1);
+	timer.add(2);
+	auto& experied = timer.tick(1);
+
+	REQUIRE(experied.size() == 1);
+	REQUIRE(experied[0] == 0);
+
+	auto& experied2 = timer.tick(2);
+
+	REQUIRE(experied.size() == 1);
+	REQUIRE(experied[0] == 1);
+}
+
+TIMERTEST AddRemoveTick(TTimer& timer)
+{
+	auto id = timer.add(1);
+	auto r = timer.remove(id);
+	
+	REQUIRE(r);
+
+	auto& experied = timer.tick(1);
+
+	REQUIRE(experied.size() == 0);
+}
+
+//////////////////////////////////////////////////// LINKED LIST TIMER TESTS
+
[…]

### 2018-11-14 sources/games/html5/scummanim.js

@@ -1,0 +1,107 @@
+
+
+var canvas = document.getElementById("canvas");
+var ctx = canvas.getContext("2d");
+
+var imgs = {
+}
+var limbs = [];
+var ianim = 27;
+var anim;
+var draw = false;
+var iframe = 0;
+var tframe = 0;
+fetch("http://127.0.0.1:8080/aksq_json.txt")
+  .then(x => x.json())
+  .then(x => {
+    var defs = x[ianim].Defs;
+    console.log(defs);
+    defs = Object.keys(defs)
+      .map(x => defs[x])
+      .filter(x => x.Mode == 6 || x.Mode == 5);
+    var ps = defs.map(d => {
+      console.log(d);
+      var url = "http://127.0.0.1:8080/anim_" + d.Start + ".json";
+      return fetch(url);
+    });
+    return Promise.all(ps);
+  })
+  .then(defs => Promise.all(defs.map(x => x.json())))
+  .then(defs => {
+    var i = 0;
+    var ps = defs.map(x => {
+      x.Operations = x.Operations
+        .filter(o => o && o.Name && o.Items && o.Items[0].Frame);
+      var frames = x.Operations
+        .map(o => o.Items[0].Frame)
+        .filter((x, i, a) => a.indexOf(x) == i);
+
+      limbs.push({
+        def: x,
+        tframe: 0,
+        iframe: 0
+      });
+
+      var ps = frames.map(f => {
+        var res, rej;
+        var p = new Promise((a, b) => { res = a; rej = b; });
+        var img = new Image();
+        img.onload = function () {
+          imgs[f] = img;
+          res(img);
+        };
+        img.src = 'http://127.0.0.1:8080/costume_2_frame_' + f + '_.png';
+        return p;
+      });
+      return Promise.all(ps);
+    });
+    return Promise.all(ps);
+  })
+  .then(x => {
+    console.log(limbs);
+    draw = true;
+  });
+
+var pos = [100, 300];
+
+var lastTimestamp;
+
+function render(timestamp) {
+  ctx.clearRect(0, 0, canvas.width, canvas.height);
+
+  if (!lastTimestamp) lastTimestamp = timestamp - 16;
+  var dt = (timestamp - lastTimestamp) / 1000;
+  lastTimestamp = timestamp;
+
+  limbs.forEach(x => {
+    x.tframe += dt;
+    if (draw) {      
+      if (x.tframe >= 0.1) {
[…]

### 2018-12-29 books/IntroductionToProbability/Solutions.tex
.

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\author{Daniel Frederico Lins Leite}
\begin{document}

\textbf{Introduction to Probability}\\
Dimitri P. Bertsekas and John N. Tsitsiklis\\
2nd edition\\
2008\\
ISBN: 9781886529236\\
\\
SECTION 5.1. Some Useful Inequalities\\
Problem 1
\paragraph{Problem 1.}	
	 A statistician wants to estimate the mean height h (in meters) of a 
	population, based on n independent samples $X_i, ... , X_n$, chosen uniformly from the 
	entire population. He uses the sample mean $M_n = (X_1 + ... + X_n)/n$ as the estimate 
	of h, and a rough guess of 1.0 meters for the standard deviation of the samples $X_i$.
	\\
	(a) How large should $n$ be so that the standard deviation of $M_n$ is at most 1 centimeter? 	
	\\
	(b) How large should $n$ be so that Chebyshev's inequality guarantees that the estimate is within 5 centimeters from $h$, with probability at least 0.99? 
	\\
	(c) The statistician realizes that all persons in the population have heights between 
	1.4 and 2.0 meters, and revises the standard deviation figure that he uses based 
	on the bound of Example 5.3. How should the values of n obtained in parts (a) 
	and (b) be revised?\\
	\\
	\newpage
	\textbf{Solution:}\\
	\\
	(a)
	\begin{align*}
		var[M_n] &= var \bigg[\frac{(X_1 + ... + X_n)}{n} \bigg] && \text{definition $X_n$}\\
		&= \frac{1}{n^2} var [X_1 + ... + X_n ]\\
		&= \frac{1}{n^2} \bigg[ var [X_1] + ... + var [X_n] \bigg]\\
		&= \frac{1}{n^2} \bigg[ var [X_i] + ... + var [X_i] \bigg]\\
		&= \frac{1}{n^2} \bigg[ n*var [X_i] \bigg]\\		
		&= \frac{n*var [X_i]}{n^2}\\
		var[M_n] &= \frac{var [X_i]}{n}\\
		\\	
		sd[M_n] &= \sqrt{var[M_n]}\\
		&= \sqrt{ \frac{var [X_i]}{n} }\\
		&= \frac{\sqrt{var [X_i]}}{\sqrt{n}}\\
	\end{align*}
	\begin{align*}
		&= \frac{\sqrt{10.000cm^2}}{\sqrt{n}}\\
		&= \frac{100cm}{\sqrt{n}}\\
		\\		
		\frac{100cm}{\sqrt{n}} &< 1cm\\
		\frac{100cm}{1cm} &< \sqrt{n}\\
		100 &< \sqrt{n}\\
		\sqrt{n} &> 100\\
		(\sqrt{n})^2 &> (100)^2\\
		n &> 10.000\\
	\end{align*}
	\newpage
	\textbf{Free Material:}\\
	\\
	\cite[section 19.3, page 798]{MIT6042}\\
	\url{http://crosslinks.mit.edu/topic/variance/}\\
	\\
	\textbf{Books:}\\
	\\
	\cite[section 2.4, page 81]{dimitriIntro}\\
	\cite[section 4.5, page 132]{sheldonrossIntroProb}\\
	\\
	(b)\\
	Although the problem asks to use Chebyshev, we can start using Markov, just to see their difference. "Markov Inequality" states that:\\
	\\
	\begin{align*}
		P(M_n \ge a) &\le \frac{E[M_n]}{a}\\
		\\
		E[M_n] &= E\bigg[\frac{(X_1 + ... + X_n)}{n} \bigg]\\
		&= \frac{1}{n} E[X_1 + ... + X_n]\\
		&= \frac{1}{n} \bigg[ E[X_1] + ... + E[X_n] \bigg]\\
		&= \frac{1}{n} \bigg[ E[X_i] + ... + E[X_i] \bigg]\\
		&= \frac{1}{n} \bigg[ n*E[X_i] \bigg]\\
		&= \frac{n*E[X_i]}{n}\\
		&= E[X_i]\\
		\\
		P(M_n \ge a) &\le \frac{E[X_i]}{a}\\
	\end{align*}	
	\\
	Now it is clear that we cannot derivate anything using just the "Markov Inequality", because $E[M_n]$ does not depends on $n$. So let us try using "Chebyshev Inequality".\\
	\newpage
	\textbf{Expected Value:}\\
	\\
	\textbf{Free Material:}\\
	\\
	\cite[section 18.4, page 751]{MIT6042}\\
	\url{http://crosslinks.mit.edu/topic/expected-value/}\\
	\\
	\textbf{Books:}\\
	\\
	\cite[section 2.4, page 81]{dimitriIntro}\\
	\cite[section 4.4, page 128]{sheldonrossIntroProb}\\
	\\
	\textbf{Markov Inequality:}\\
	\\
	\textbf{Free Material:}\\
	\\
	\cite[section 19.1, page 789]{MIT6042}\\
	\url{http://crosslinks.mit.edu/topic/markovs-theorem/}\\
	\\
	\textbf{Books:}\\
	\\
	\cite[section 5.1, page 265]{dimitriIntro}\\
	\cite[section 8.2, page 388]{sheldonrossIntroProb}\\
	\\	
	"Chebyshev Inequality" is just a simple derivation from "Markov Inequality", but will help us in this problem.\\
	\\
	\begin{align*}
	P(|M_n - E[M_n]| \ge a) &\le \frac{var[M_n]}{a^2}\\
	& \le \frac{10000cm^2}{n} * \frac{1}{a^2}\\
	\\
	P(|M_n - E[M_n]| \ge 5cm) &\le \frac{10000cm^2}{n} * \frac{1}{(5cm)^2}\\
	&\le \frac{10000cm^2}{n} * \frac{1}{25cm^2}\\
	&\le \frac{10000cm^2}{25cm^2} * \frac{1}{n}\\
	&\le 400 * \frac{1}{n}\\	
	&\le \frac{400}{n}\\		
	\end{align*}

	But the problem asks the probability of being withing 5cms and not outside. So we need to "invert" the probability. And we want this probability to be at least 0.99.

	\begin{align*}
	P(|M_n - E[M_n]| \le 5cm) &= 1 - P(|M_n - E[M_n]| \ge 5cm)
	\\
	0.99 &<= P(|M_n - E[M_n]| \le 5cm)\\
	0.99 &<= 1 - P(|M_n - E[M_n]| \ge 5cm)\\	
	0.99 &\le 1 - \frac{400}{n}\\
	0.99 - 1&\le [1 - \frac{400}{n}] - 1\\
	-0.01 &\le -\frac{400}{n}\\
	0.01 &\ge \frac{400}{n}\\	
	n &\ge \frac{400}{0.01}\\	
	n &\ge 40.000\\
	\end{align*}
	\\
	\\
	\textbf{Free Material:}\\
	\\
	\cite[section 19.2, page 792]{MIT6042}\\
	\url{http://crosslinks.mit.edu/topic/chebyshevs-inequality/}\\
	\\
	\textbf{Books:}\\
	\\
	\cite[section 5.1, page 267]{dimitriIntro}\\
	\cite[section 8.2, page 389]{sheldonrossIntroProb}\\
	\\
	(c)\\
	Given that all sampled heights are bounded, we can use the "variance definition" to find a bound to the variance. If this bound is smaller than the initial variance of $1m^2$ maybe we can have a better approximation to the probability. We start with the "variance definition".\\
	\\
	Gamma ($\gamma$), in the following equations, has no special meaning, it is real number.\\
	\\
	\begin{align*}
		E[(X-\gamma)^2] = E[X^2] - 2\gamma E[X] + \gamma^2
	\end{align*}
	We know that this equation is minimized when $\gamma=E[x]$. Wich means that when $\gamma$ is different than $E[x]$ the value of the equation is greater.
	\begin{align*}
		var[X] = E[(X-E[X])^2] \le E[(X-\gamma)^2]
	\end{align*}

	If we choose $\gamma$ as $\frac{a+b}{2}$ with $a$ and $b$ as the lower and higher bounds.

	\begin{align*}
	var[X] &= E[(X-E[X])^2] \le E \bigg[ \bigg(X-\frac{a+b}{2} \bigg)^2 \bigg]
	\\
	E \bigg[ \bigg(X-\frac{a+b}{2} \bigg)^2 \bigg] &= E \bigg[ X^2 - 2X\bigg( \frac{a+b}{2} \bigg) + \bigg(\frac{a+b}{2} \bigg)^2 \bigg]\\
	&= E \bigg[ X^2 - 2X\frac{a}{2} -2X\frac{b}{2} + \bigg(\frac{a+b}{2} \bigg)^2 \bigg]\\
	&= E \bigg[ X^2 -Xa -Xb + \bigg(\frac{a+b}{2} \bigg)^2 \bigg]\\
	&= E \bigg[ X^2 -Xa -Xb + \bigg(\frac{a^2+2ab+b^2}{4} \bigg) \bigg]\\	
	&= E \bigg[ X^2 -Xa -Xb + \frac{2ab}{4} + \bigg(\frac{a^2+b^2}{4} \bigg)\\
	&= E \bigg[ X^2 -Xa -Xb + \frac{ab}{2} + \bigg(\frac{a^2+b^2}{4} \bigg)	 \bigg]\\		
	&= E \bigg[ X^2 -Xa -Xb + \frac{ab}{2} + (\frac{ab}{2}) + \bigg(\frac{a^2+b^2}{4} \bigg) - (\frac{ab}{2}) \bigg]\\
	\end{align*}
	\begin{align*}
	&= E \bigg[ X^2 -Xa -Xb + \frac{2ab}{2} + \bigg(\frac{a^2+b^2}{4} \bigg) - (\frac{2ab}{4}) \bigg]\\
	&= E \bigg[ X^2 -Xa -Xb + ab + \bigg(\frac{a^2+b^2-2ab}{4} \bigg) \bigg]\\	
	&= E \bigg[ X^2 -Xa -Xb + ab \bigg] + \bigg(\frac{a^2+b^2-2ab}{4} \bigg)\\	
	&= E [ (X-a)(X-b) ] + \frac{(a-b)^2}{4}\\	
	\end{align*}
	The interesting part now is that $a$ and $b$ are the bounds of the variable. So $X-b$ is always negative, because $X$ must be smaller than $b$. Wich makes
	$$(X-a)(X-b) < 0$$.

	And the expected value will be negative, which will always decrease $\frac{(a-b)^2}{4}$. Giving us.

	\begin{align*}
		&= E [ (X-a)(X-b) ] + \frac{(a-b)^2}{4} \le \frac{(a-b)^2}{4}
	\end{align*}

	Which gives us the expectacular result that:
	\begin{align*}
		var[x] \le \frac{(a-b)^2}{4}
	\end{align*}

	Going back to the problem, the statistician realized that the bound is 1.4 and 2.0. So we have that the maximum possible variance is:

	\begin{align*}
	var[X] \le \frac{(a-b)^2}{4} &= \frac{(1.4m-2.0m)^2}{4}\\
	& = \frac{(0.6m)^2}{4}\\
	& = \frac{0.36m^2}{4}\\	
	& = 0.09m^2\\	
	& = 900cm^2
	\\
	sd[x] &= \sqrt{var[X]}\\
	&= \sqrt{900cm^2}\\
	&= 30cm\\
	\end{align*}

	Doing parts (a) and (b) again we have.

	(new a)

	\begin{align*}
	\frac{30cm}{\sqrt{n}} &< 1cm\\
	\frac{30cm}{1cm} &< \sqrt{n}\\
	30 &< \sqrt{n}\\
	(30)^2 &< n\\
	n &> 900\\	
	\end{align*}

	(new b)

	\begin{align*}
		0.01 &\ge \frac{900cm^2}{25cm^2} * \frac{1}{n}\\
		0.01 &\ge 36 * \frac{1}{n}\\		
		n &\ge \frac{36}{0.01}\\		
		n &\ge 3.600\\				
	\end{align*}

	\begin{thebibliography}{9}		
		\bibitem{dimitriIntro}
		Dimitri P. Bertsekas and John N. Tsitsiklis,
		Introduction to Probability,
		2nd edition,
		2008,
		ISBN: 9781886529236,
		\url{http://www.athenasc.com/probbook.html}
		\bibitem{sheldonrossIntroProb}
		Sheldon Ross
		A First Course in Probability,
		5th edition,
		2012,
		ISBN: 9780137463145	
		\bibitem{MIT6042}
		Mathematics for Computer Science,
		\url{https://courses.csail.mit.edu/6.042/spring18/}
	\end{thebibliography}
\end{document}

### 2018-12-29 sources/cpp/cheerp/main.cpp

@@ -1,0 +1,23 @@
+#include <string>
+
+#include <cheerp/client.h>
+#include <cheerp/clientlib.h>
+
+// We need to extend the client namespace to declare our
+// custom JavaScript function
+namespace client
+{
+    // The name should be the same as the JavaScript one
+    // The parameters needs to be a const client::String reference
+    // so that implicit conversion from const char* is supported
+    void changeTitle(const String& str);
+}
+
+using namespace client;
+
+void webMain()
+{
+    auto titleElement = document.getElementById("pagetitle");
+    auto oldText = titleElement->get_textContent();
+    changeTitle(oldText + "Literal C++ string");
+}

### 2018-12-29 sources/cpp/cheerp/main.js

@@ -1,0 +1,1 @@
+"use strict";/*Compiled using Cheerp (R) by Leaning Technologies Ltd*/var y=Math.imul;var z=Math.fround;var aSlot=null;var oSlot=0;var nullArray=[null];var nullObj={d:nullArray,o:0};function s(){var f=null;f="pagetitle";f=document.getElementById(f);f.textContent;f="Literal C++ string";changeTitle(f);return;}function n(v,w){var h=0,i=0,f=null,x=null;f=String();h=v[w]|0;if((h&255)===0){return f;}else{i=0;}while(1){x=String.fromCharCode(h<<24>>24);f=f.concat(x);i=i+1|0;h=v[w+i|0]|0;if((h&255)===0){break;}}return f;}function j(f,g){var h=null;h=n(f,g);return String(h);}var u=new Uint8Array([112,97,103,101,116,105,116,108,101,0]);var t=new Uint8Array([76,105,116,101,114,97,108,32,67,43,43,32,115,116,114,105,110,103,0]);s();

### 2019-01-09 texts/philosophy/introolavo.tex
.

@@
 	\subsection{Scientist versus Agent}
+
+	TRÊS ELEMENTOS DA FILOSOFIA POLÍTICA DE OLAVO DE CARVALHO
+	https://www.youtube.com/watch?v=T2TLrnathAU&list=PL2wuZQFPMbL8e1QLKJZVKKoawroT-Lv3O
+
+	Definição de agente histórico (agente político):
+	Agente político é todo projeto que consegue se perpetuar no tempo dada alguma consistência.
+Uma pessoa obviamente pode ser um agente, mas tendo no máximo 50-60 anos de ação, mesmo que seja muito influente, como o Soros, um dia morrerá.
+E não tem um projeto para continuar o seu plano, a sua agência será forte, porém breve.
+
+	Por conta disso o Estado-Nação não pode ser um agente, pois apesar de possuir a duração, não possui consistência necessária.
+Um dia está numa mão fazendo A, no outro está noutra mão fazendo B, ou até mesmo não-A (crítica direta ao Hans Morgenthal).
+
+	O Olavo em si não cita, mas estudos interessantes aos agentes políticos reais e mais claros é feita pelo Antony Sutton.
+O que era considerado como Império America/Inglês-Atlântico e hoje é associado ao projeto do Cecil Rodhes, muito bem documento pelo Edward Griffin é um exemplo de uma agente político.
+Dos mais complexos, inclusive.
+
+	MAIS SOBRE AGENTE HISTÓRICO
+
+		Artigos do conceito "agente histórico"/"agente político" do Olavo de Carvalho.
+
+		Definição:
+
+		"Para ser um agente histórico, o grupo ou entidade tem de:
+
+		(a) Acalentar objetivos permanentes ou de longo prazo.
+		(b) Ser capaz de prosseguir a consecução desses objetivos para além da duração de seus agentes individuais;
+		(c) Ser, portanto, capaz de reproduzir agentes individuais aptos a prosseguir a ação ao longo dos séculos;
+
+		Somente as seguintes entidades obedecem a essas condições:
+
+		(1) As grandes religiões universais.
+		(2) As organizações iniciáticas e esotéricas.
+		(3) As dinastias reais e nobiliárquicas e suas similares.
+		(4) Os movimentos e partidos ideológicos revolucionários.
+		(5) Os agentes espirituais: Deus, anjos e demônios."
+
+		http://www.olavodecarvalho.org/debate-com-duguin-ii/
+
+		Diferença entre o agente histórico e filósofo/cientista.
+
+		"Há mais de dois séculos a casta dos intelectuais ativistas espalha terror e sofrimento por toda parte, sempre sob a desculpa de conduzir a humanidade a um reino de justiça igualitária.
+Não há genocídio, não há violência, não há brutalidade que não tenha por trás a criatividade incansável desses tagarelas iluminados, cujo maior talento é o de jogar os demais grupos humanos uns contra os outros enquanto mantêm oculta sua própria existência de agentes históricos principais, dirigentes máximos do processo e mandantes últimos de todos os crimes.
+
+		O intelectual ativista distingue-se do filósofo, do erudito, do cientista, do escritor, embora possa atuar sob a camuflagem de um ou vários desses papéis sociais, confundindo a platéia.
+A diferença é que, enquanto estes se esforçam para tentar compreender e expressar a realidade, ele só se ocupa de condená-la e de tentar transformá-la em outra coisa.
+O homem de estudos tem diante de si um mundo que já lhe parece complicado demais para a sua pobre cabecinha.
+O intelectual ativista tem na cabeça inchada um projeto de mundo, o plano integral de uma nova humanidade, que ele acha infinitamente superior a tudo quanto já existiu ou existe neste universo desmasiado estreito para a sua grandiosa imaginação."
+		http://www.olavodecarvalho.org/casta-de-malditos/
+
+		Aplicações:
+
+		1 - Foro de São Paulo como agente histórico mais poderoso da América Latina.
+
+		"Quando o Foro de São Paulo foi criado, um só país dessa região era governado por um partido pertencente a ele, e hoje são mais de dez.?
+( http://forodesaopaulo.org/declaracion-final-del-xx-encuentro-del-foro-de-sao-paulo/).
+Para um agente histórico que ?não existe na prática?, essas vitórias são mais do que espetaculares: são mágicas.
+Na verdade, o Foro continua sendo a maior, mais poderosa e mais eficiente organização política que já existiu no continente latino-americano."
+		http://www.olavodecarvalho.org/extinguindo-o-inexistente/
+
+		2 - Globalismo, agente histórico extremamente complexo (ver mais http://www.joeplummer.com/)
+
+		"Abortismo, casamento gay, quotas raciais, desarmamento civil, regulamentos ecológicos draconianos, liberação das drogas, controle estatal da conduta religiosa, redução da idade de consentimento sexual para doze anos ou menos: tais são, entre alguns outros, os ideais que fazem bater mais forte o coração de estudantes, professores, políticos, jornalistas, ongueiros, empresários ?esclarecidos?
+e demais pessoas que monopolizam o debate público neste país.
+
+		Nenhuma dessas propostas veio do povo brasileiro ou de qualquer outro povo.
+Nenhuma delas tem a sua aprovação.
+Isso não importa.
+Elas vêm sendo e continuarão sendo impostas de cima para baixo, aqui como em outros países.
+
+		De onde vêm essas idéias, a técnica com que se disseminam e o dinheiro que subsidia a sua implantação forçada?
+
+		A fonte desses três elementos é única e sempre a mesma: a elite bilionária fabiana e globalista que domina a rede bancária mundial e tem nas suas mãos o controle das economias de dezenas de países, assim como da totalidade dos organismos internacionais reguladores.
+
+		Em geral, nem seus adeptos e servidores, nem a população que se horroriza ante os resultados visíveis da sua política têm a menor idéia de quem é o agente histórico por trás do processo.
+Os primeiros deixam-se levar pelo atrativo aparente das metas nominais proclamadas e acreditam piamente ?
+ó céus!
+?
+estar lutando contra a ?elite capitalista?.
+A população vê o mundo piorando e de vez em quando se revolta contra esta ou aquela mudança em particular."
+		http://www.olavodecarvalho.org/conduzidos-a-forca/
+
+		3 - Agente histórico do Eurasianismo do Dugin. Me parece a conclusão mais "arriscada" do Olavo. Hoje vejo o próprio Olavo dizendo como o Putin/Dugin mais usam a religião Russa do que o contrário.
+
+		"Um exemplo de força histórica que transcende infinitamente as fronteiras e a duração de Estados e Impérios é a Igreja Ortodoxa, da qual o prof.
+Dugin se diz um crente.
+A força da Igreja Ortodoxa como agente histórico penetrou fundo no cérebro do próprio prof.
+Dugin, moldando a sua noção ?holista?
+do império teocrático.
+
+		[Dugin] qualifica de ?heresia?
+a distinção de Igreja e Império que moldou a civilização do Ocidente.
+Sem essa separação, a única hipótese que resta é de as fronteiras da expansão religiosa coincidirem milimetricamente com o mapa do Império.
+Neste caso, a religião imperial torna-se apenas uma religião nacional ampliada.
+
+		O projeto eurasiano é a única saída que a Igreja Ortodoxa tem se não quiser ficar confinada aos limites da nação russa, falhando à sua missão declarada de religião universal.
+
+		Foi isso, de fato, o que aconteceu, enquanto a Igreja Ortodoxa, através do prof.
+Dugin, ainda está buscando uma saída para o mundo e não vê outro meio de encontrá-la senão constituir-se em Império Mundial."
+		http://www.olavodecarvalho.org/debate-com-duguin-ii/
+
+		Pequena nota sobre gerações:
+
+		"De uma fase até a outra decorreram aproximadamente quinze anos ?
+o prazo que, em La Teoría Historica de las Generaciones, Julián Marías diz marcar o trânsito entre duas gerações de agentes históricos."
+		http://www.olavodecarvalho.org/capitulos-de-historia-bestial/
+
+	Marxismo como Cultura:
+	Cultura = Sistema de Valores que estrutura o imaginado coletivo.
+	Como subcultura vive como um parasita da cultura oficial.
+	Horizonte de Consciência - Eric Voegelin
+
+	Teoria da Mentalidade Revolucionária:
+
 	\subsection{Inversion of the Concepts}

### 2019-01-09 courses/kth-high-performance-finite-element-modeling/FEM in Science and Industry/heat.py

@@ -1,0 +1,138 @@
+#%matplotlib inline
+#%run /home/fenics/fenics-matplotlib.py
+from dolfin import *; 
+from mshr import *; 
+import matplotlib.pyplot as plt
+from IPython.display import display, clear_output; 
+import time
+import logging; 
+logging.getLogger('FFC').setLevel(logging.WARNING)
+from dolfin import *
+import matplotlib.pyplot as plt
+import matplotlib.tri as tri
+
+def mesh2triang(mesh):
+    xy = mesh.coordinates()
+    return tri.Triangulation(xy[:, 0], xy[:, 1], mesh.cells())
+
+def mplot_cellfunction(cellfn):
+    C = cellfn.array()
+    tri = mesh2triang(cellfn.mesh())
+    return plt.tripcolor(tri, facecolors=C)
+
+def mplot_function(f):
+    mesh = f.function_space().mesh()
+    if (mesh.geometry().dim() != 2):
+        raise AttributeError('Mesh must be 2D')
+    # DG0 cellwise function
+    if f.vector().size() == mesh.num_cells():
+        C = f.vector().array()
+        return plt.tripcolor(mesh2triang(mesh), C)
+    # Scalar function, interpolated to vertices
+    elif f.value_rank() == 0:
+        C = f.compute_vertex_values(mesh)
+        return plt.tripcolor(mesh2triang(mesh), C, shading='gouraud')
+    # Vector function, interpolated to vertices
+    elif f.value_rank() == 1:
+        w0 = f.compute_vertex_values(mesh)
+        if (len(w0) != 2*mesh.num_vertices()):
+            raise AttributeError('Vector field must be 2D')
+        X = mesh.coordinates()[:, 0]
+        Y = mesh.coordinates()[:, 1]
+        U = w0[:mesh.num_vertices()]
+        V = w0[mesh.num_vertices():]
+        return plt.quiver(X,Y,U,V)
+
+# Plot a generic dolfin object (if supported)
+def plot(obj):
+    plt.gca().set_aspect('equal')
+    if isinstance(obj, Function):
+        return mplot_function(obj)
+    elif isinstance(obj, CellFunctionSizet):
+        return mplot_cellfunction(obj)
+    elif isinstance(obj, CellFunctionDouble):
+        return mplot_cellfunction(obj)
[…]

### 2019-02-13 texts/philosophy/introolavo.tex
.

@@
 	\subsubsection{Reality Unification}
+
+	INTUICIONISMO RADICAL
+	por Olavo de Carvalho
+
+	?Intuição é conhecimento imediato, isto é, sem intermediações.
+Se ela não existisse, não existiria conhecimento nenhum, pois o conhecimento dos intermediários precisaria de outros intermediários, e estes de outros ainda, e assim por diante ilimitadamente.
+Se falamos, por exemplo, da intuição sensível, dizer ?
+a sério, e não como mera abreviatura verbal ?
+que só conhecemos os objetos do mundo físico "por intermédio" dos sentidos, portanto não diretamente, é como dizer que uma arma de fogo não atira diretamente mas "por intermédio" do cano, como se o cano não fosse parte dela e sim um ajudante externo; pior ainda, além dos sentidos não temos nenhum outro órgão capaz de captar as qualidades sensíveis, de modo que, se os sentidos fossem apenas "intermediários", estariam mediando entre os objetos sensíveis e um nada.
+
+	Quando apreendemos a conclusão de um silogismo, essa apreensão é também direta e intuitiva, caso contrário precisaríamos de um intermediário entre nós e essa conclusão, e esse intermediário precisaria de outro, etc.
+etc.
+
+	A intuição é a apreensão de uma evidência.
+Evidência é presença imediata à consciência, o correlato objetivo da intuição.
+O que é evidente não requer prova.
+Prova é evidência indireta, ou deficiente, obtida por uma articulação de representações mentais.
+Quando atinamos com a veracidade de uma prova lógica, temos a apreensão intuitiva só da prova enquanto tal, não dos objetos correspondentes.
+
+	Só a intuição é critério cabal da verdade, seja na apreensão dos dados sensíveis, seja no próprio raciocínio lógico.
+
+	Quem diz que algum conhecimento bem provado é "contra-intuitivo" usa a palavra "intuição" para designar a simples expectativa de uma percepção possível; dito de outro modo, uma crença do senso comum sem intuição nenhuma.
+
+	É isso o que eu chamo ?intuicionismo radical?.?
+	https://www.facebook.com/photo.php?fbid=10215093755150845&set=a.3036833753418&type=3&theater
+
 	\subsubsection{Conscience Unification}
@@
 	\subsection{Scientist versus Agent}
+
+	Já expliquei mil vezes que a ciência política começou quando Platão e Aristóteles criaram a distinção entre o discurso do agente político e o do observador científico.
+A objetividade das opiniões do cientista político não vem de nenhum isentismo, mas do simples fato de ele JAMAIS se rebaixar à função de porta-voz de um grupo político.
+É a minha total independência de quaisquer grupos que me torna incompreensível e escandaloso para muita gente num pais em que praticamente TODO pensamento é grupal.
+
+	https://www.facebook.com/olavo.decarvalho/posts/10156896956572192
 

### 2019-03-06 texts/math/AsymptoticStatistics.tex
.

\documentclass[10pt,a4paper]{book}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Daniel Frederico Lins Leite}
\title{Asymptotic Statistics}
\begin{document}
\maketitle
\tableofcontents

\chapter {Introduction}

The idea of this crash course on asymptotic Statistics is to have all proofs and ideas related with the one of the three most important aspects of statistics, being estimation. The other two being confidence interval and hypothesis testing, off course.\\

The idea is to present as gentle as possible the needed concepts to follow a more thorough course. Here one will find the concepts of "asymptotic", "estimators", Markov and Chebyshevs inequalities, convergnce in the sense for Statistics, characteristic functions, the weak law of large numbers and the Central Limit Theorem.

\chapter{Asymptotic Behaviour of Estimators}
\section{Introduction}

As "Asymptotic Statistics" we understand the study of Probabilities and Statistics as one of its parameters go to infinity. We will study for example:

\begin{align}
	\lim_{n->\infty}{P(X_n \in A)}
\end{align}

or

\begin{align}
	\lim_{n->\infty}{P((X_n - X) \in A)}
\end{align}

Here $P(x \in A) = \int_{A}{f(x)dx}$. The lower-case $f$ has a especial meaning because that is how we label the PDF of a distribution. We use upper-case $F$ to mean de CDF. We also know that to be a valid "random variable":

\begin{align}
	\int_{-\infty}^{\infty}{f(x)dx} = 1 && f(x) >= 0
\end{align}

Where $X_n$ means off course a "random variable", pure in the sense that is obeys a known distribution or a "transformed random variable". We will be interested to know if a "random variable" converge to a constant, to another "random variable" of if it diverge. Throughout this book we will see that we can conclude different things if any of these cases are proved as true.

One of the most interesting, or one the most useful, "random variables" is the "estimator". We call "estimator" any "statistic" that does not depend on any of the "population parameters" an possible estimator. If on top of that we define that this "statistic" will be used as an "estimation" of the "population parameter", we have a "estimator".

A famous statistic is the "sample mean" that we will define as:

\begin{align*}
	X_i \sim P_{\theta}\\
	S_n = \sum_{\forall i}{X_i}\\
	\bar{X_{n}} = \frac{S_n}{n}\\
\end{align*}

We understand the expressions above as:
\begin{itemize}
	\item {$X_i$ is a "random variable" that follows a distribution described with a parameter $\theta$, that can be a number or various numbers;}
	\item {The set of all $X_i$ are i.i.d.}
	\item {$S_n$ is another "random variable". Being the sum of $n$ "random variables" allows us to know the distribution of $S_n$ in some cases}
	\item {$\bar{X_{n}}$ is another "random variable" that applies the "transformation" $1/x$ to the "random variable" $S_n$}
\end{itemize}

Being random variables, $X_i$, $S_n$, $\bar{X_{n}}$, allow them to have "expected values", "variations" and any other statistics themselves. This is a powerfull source of confusion. So we can have:

\begin{align*}
	E[X_i] = a \text{ or } f_a(i)\\	
	E[S_n] = b \text{ or } f_b(n)\\
	E[\bar{X_{n}}] = c \text{ or } f_c(n)\\
\end{align*}

In these cases, $a$, $b$, $c$ are not "random variables". They are constants, or functions that depend on the "random variables" "parameter". The same can be said about their "variance" and other statistics.

Remember that "Expected Value" is:

\begin{align}
	E[X] = \int_{-\infty}^{\infty}{x*f(x)dx}
\end{align}

Actually this is just the "First Moment" of $X$. We can the n-th "moment" as:

\begin{align}
	\int_{-\infty}^{\infty}{x^n*f(x)dx}
\end{align}

or

\begin{align*}
	E[X^1] = \int_{-\infty}^{\infty}{x^1*f(x)dx}\\
	E[X^2] = \int_{-\infty}^{\infty}{x^2*f(x)dx}\\
	...\\
	E[X^n] = \int_{-\infty}^{\infty}{x^n*f(x)dx}\\
\end{align*}

And this allows us to calculate the variance as, the "second moment" minus the square of the "first moment":

\begin{align}
	\text{VAR}[X] = E[X^2] - E[X]^2
\end{align}

\section{Markov's Inequality Intuition}

What can you say about a "Probbility distribution" if you only have its mean? Probably not much. But not much is more than nothing. If we imagine a standard dice with six faces, but not necessarily fair, each face having the same probability. The question is, knoning just the mean, can we affirm with a 100\% certainity that the dice is not fair?

For example, if someone tell us that the $E[X_i]$, $X_i$ being a roll of the dice is $6$. We know that the only way of this happening is when $P(X = 6) = 1$ and $P(X < 6) = 0$ because of the "Expected Value" definition.

\begin{align*}
	E[X] &= \sum_{i=1}^{6}{i*P(X=i)} = 6\\
	&= 6*P(X=6) = 6\\
	& P(X=6) = \frac{6}{6}\\
	& P(X=6) = 1\\
\end{align*}

So it seems that knowing only the $E[X]$ allows us to take some conclusions of the distribution. But this is a extreme case. Can we take conclusions if for example the $E[X]$ is the same as the "expected value" when the dice is fair? Let us see.

We know that the $E[X]$ is:

\begin{align*}
	E[X] &= \sum_{i=1}^{6}{i*P(X=i)}\\
\end{align*}

And we know that $i \in {1,2,3,4,5,6}$ or $i > 0$. We know that $i$ is positive. We also know that $P(X = i) \in [0,1]$. It is also positive. The multiplication of two positive values is also positive. And the sum of two positive values is also positive.

\begin{align*}
	i &> 0\\
	P(X = i) &> 0\\
	a * b &> 0 \text{, if } a > 0 \text{ and } b > 0\\
	a + b &> 0 \text{, if } a > 0 \text{ and } b > 0	
\end{align*}

Which give us that

\begin{align*}
	E[X] &= \sum_{i=1}^{6}{i*P(X=i)}\\
	&= \sum_{i=1}^{5}{i*P(X=i)} + 6*P(X=6)
\end{align*}

We know that this summuation is going to be greater than zero. Whick make the $E[X]$ greater than or equal $6*P(X=6)$. In the extreme case above, it was equal because the summation was zero. But the summation can be greater than zero (never lower).

\begin{align*}
	E[X] &= \sum_{i=1}^{6}{i*P(X=i)}\\
	E[X] &= \sum_{i=1}^{5}{i*P(X=i)} + 6*P(X=6)\\
	E[X] &>= 6*P(X=6)\\
	\frac{E[X]}{6} &>= P(X=6)\\
	P(X=6) &<= \frac{E[X]}{6}
\end{align*}

Which is quite surprising if you think. But looking from another perspective, it is quite obvious that there is a relationship with the $P(X=6)$ and the "expected value".

\section{Markov's Inequality}

This relationship was discovered by two mathematicians:\\	
Andrey Markov\\
\includegraphics[width=50px]{AAMarkov}\\

and Pafnuty Chebyshev\\
\includegraphics[width=50px]{Chebyshev}\\

And it is generalized as:
\begin{itemize}
	\item {$X$ is a nonnegative random variable;}
	\item {$a > 0$}
\end{itemize}

We now that:

\begin{align*}
	E[X] &= \int_{-\infty}^{\infty}{x*f(x)dx}\\
	&= \int_{0}^{\infty}{x*f(x)dx} && \text{because of } X > 0\\
	&= \int_{0}^{a}{x*f(x)dx} + \int_{a}^{\infty}{x*f(x)dx} && \text{because of } a > 0\\	
\end{align*}

We know that $\int_{0}^{a}{x*f(x)dx} > 0$, so

\begin{align*}
	E[X] &= \int_{0}^{a}{x*f(x)dx} + \int_{a}^{\infty}{x*f(x)dx}\\
	E[X] &= b + \int_{a}^{\infty}{x*f(x)dx} && b > 0\\
	E[X] - b &= \int_{a}^{\infty}{x*f(x)dx}\\
	E[X] &>= \int_{a}^{\infty}{x*f(x)dx} && b > 0\\
\end{align*}

Before the next step, we must realize that:

\begin{align*}
	\int_{a}^{\infty}{x*f(x)dx}&\\
	&=\int_{a}^{\infty}{(a+(x-a))*f(x)dx}\\
	&=\int_{a}^{\infty}{a*f(x)dx}+\int_{a}^{\infty}{(x-a)*f(x)dx}\\
\end{align*}

We must realize the in the second integration, $x>=a$ and $f(x) > 0$ which makes the second integration greater than or equal to zero. This allow us to:

\begin{align*}
	\int_{a}^{\infty}{x*f(x)dx} &=\int_{a}^{\infty}{a*f(x)dx}+\int_{a}^{\infty}{(x-a)*f(x)dx}\\
	\int_{a}^{\infty}{x*f(x)dx}	&=\int_{a}^{\infty}{a*f(x)dx}+c\\
	\int_{a}^{\infty}{x*f(x)dx}	- c &=\int_{a}^{\infty}{a*f(x)dx}\\
	\int_{a}^{\infty}{x*f(x)dx}	&>= \int_{a}^{\infty}{a*f(x)dx}\\	
\end{align*}

We can use this fact with the fact that if $a>b$ and $b>c$ then $a>c$, and finish our proof

\begin{align*}
	E[X] &>= \int_{a}^{\infty}{x*f(x)dx} && b > 0\\
	E[X] &>= \int_{a}^{\infty}{a*f(x)dx} && \text{see above}\\
	E[X] &>= a*\int_{a}^{\infty}{f(x)dx}\\
	E[X] &>= a*P(X>a)\\
	\frac{E[X]}{a} &>= P(X>a)\\
\end{align*}
\begin{align}
	P(X>a) &<= \frac{E[X]}{a}	
\end{align}

Which is the obivious generalization we did in the intuition section. But remember that we are studying "Asymptotic Statistics", this is useful for us, because in some cases, the right side will depend on $n$, and in the limit the right side will converge or diverge. This will give even more information about the "random variable". All of this with just its "expected value".

	\section{Chebyshev's Inequality}

	\chapter{Convergence}
	\section{Convergence in probability of a random variable}
	\section{Convergence in probability to a random variable}
	\section{Convergence in probability of a random variable to a constant}
	\section{Convergence in distribution of a random variable}

	\chapter{Characteristic Functions}
	\section{Introduction}

	\chapter{Weak Law of Large Numbers}
	\section{Introduction}
	\section{Proof of the weak law of large numbers}
	\section{Proof using characteristic functions}

	\chapter{Central Limit Theorems}
	\section{Introduction}
	\section{Proof}
	\section{The Characteristic Function of a Normal Random Variable}
\end{document}

### 2019-03-06 texts/math/AsymptoticStatistics.tex
.

@@
 \begin{align}
-	\int_{-\infty}^{\infty}{f(x)dx} = 1 && f(x) >= 0
+	\int_{-\infty}^{\infty}{f(x)dx} = 1 && f(x) \ge 0
 \end{align}
@@
 \begin{align}
-	\text{VAR}[X] = E[X^2] - E[X]^2
+	\text{VAR}[X] = E[X^2] - E[X]^2\\
+\end{align}
+
+or
+
+\begin{align}
+\text{VAR}[X] = E[(X-E[X])^2]
+\end{align}
+
+And we also have the "standard deviation".
+
+\begin{align}
+	\text{SD}[X] = \sqrt{\text{VAR}[X]}
 \end{align}
@@
 	E[X] &= \sum_{i=1}^{5}{i*P(X=i)} + 6*P(X=6)\\
-	E[X] &>= 6*P(X=6)\\
-	\frac{E[X]}{6} &>= P(X=6)\\
-	P(X=6) &<= \frac{E[X]}{6}
+	E[X] &\ge 6*P(X=6)\\
+	\frac{E[X]}{6} &\ge P(X=6)\\
+	P(X=6) &\le \frac{E[X]}{6}
 \end{align*}
@@
 	E[X] - b &= \int_{a}^{\infty}{x*f(x)dx}\\
-	E[X] &>= \int_{a}^{\infty}{x*f(x)dx} && b > 0\\
+	E[X] &\ge \int_{a}^{\infty}{x*f(x)dx} && b > 0\\
 \end{align*}
@@
 
-We must realize the in the second integration, $x>=a$ and $f(x) > 0$ which makes the second integration greater than or equal to zero. This allow us to:
+We must realize the in the second integration, $x \ge a$ and $f(x) > 0$ which makes the second integration greater than or equal to zero. This allow us to:
 
@@
 	\int_{a}^{\infty}{x*f(x)dx}	- c &=\int_{a}^{\infty}{a*f(x)dx}\\
-	\int_{a}^{\infty}{x*f(x)dx}	&>= \int_{a}^{\infty}{a*f(x)dx}\\	
+	\int_{a}^{\infty}{x*f(x)dx}	&\ge \int_{a}^{\infty}{a*f(x)dx}\\	
 \end{align*}
@@
 \begin{align*}
-	E[X] &>= \int_{a}^{\infty}{x*f(x)dx} && b > 0\\
-	E[X] &>= \int_{a}^{\infty}{a*f(x)dx} && \text{see above}\\
-	E[X] &>= a*\int_{a}^{\infty}{f(x)dx}\\
-	E[X] &>= a*P(X>a)\\
-	\frac{E[X]}{a} &>= P(X>a)\\
+	E[X] &\ge \int_{a}^{\infty}{x*f(x)dx} && b > 0\\
+	E[X] &\ge \int_{a}^{\infty}{a*f(x)dx} && \text{see above}\\
+	E[X] &\ge a*\int_{a}^{\infty}{f(x)dx}\\
+	E[X] &\ge a*P(X \ge a)\\
+	\frac{E[X]}{a} &\ge P(X \ge a)\\
 \end{align*}
 \begin{align}
-	P(X>a) &<= \frac{E[X]}{a}	
+	P(X \ge a) &\le \frac{E[X]}{a}	
 \end{align}
@@
 \section{Chebyshev's Inequality}
+
+One of the interesting aspects of the "Markov Inequality" is that it only contains two assumptions and both are very generic.
+It only depends on X being non-negative and a being nonnegative.
+We know that a nonnegative function, when sifted on the X-Axis is still nonnegative.
+So $X-a$ is still non-negative and the "Markov Inequality" still apllies.
+
+\begin{align*}
+P((X-b) \ge a) &\le \frac{E[X-b]}{a}	
+\end{align*}
+
+Another "transformation" that keeps the non-negativiness of the function is squaring its value.
+
+\begin{align*}
+P((X-b)^2 \ge a^2) &\le \frac{E[(X-b)^2]}{a^2}	
+\end{align*}
+
+But we do not have any restriction on $b$ here, and we can easily choose the "expected value" of $X$.
+
+\begin{align*}
+P((X-E[X])^2 \ge a^2) &\le \frac{E[(X-E[X])^2]}{a^2}
+\end{align*}
+
+Which gives us the $\text{VAR}[X]$. Although this inequality is often writen in a different form.
+
+\begin{align*}
+P((X-E[X])^2 \ge a^2) &\le \frac{\text{VAR}[X]}{a^2}\\	
+\end{align*}
+
+But this is still not the most "famous" way this formula is written, and the reason is going to be appear in future chapters.
+To derive the most famous form we are going to apply some transformations only to the left side, because they will not change the boundness of the inequality.
+
+\begin{align*}
+P(\sqrt{(X-E[X])^2}\ge\sqrt{a}) &\le \frac{\text{VAR}[X]}{a^2}\\
+P(|X-E[X]| \ge a) &\le \frac{\text{VAR}[X]}{a^2} && \text{ no modulus on a because } a>0
+\end{align*}
+
+\begin{align}
+	P(|X-E[X]| \ge a) &\le \frac{\text{VAR}[X]}{a^2}
+\end{align}
+
+Which is quite fascinating, because it gives you a know bound when you know the distribution "expected value" and "variance".
+This formula will demonstrate itself very powerfull and useful in the study of sampling and convergence.
+
+We can also interpret that it is "harder", less probable, of being $n$ "standard deviations" from the "expected value".
+What is very intuitive, if you stop to think about it.
+What you can not do, is forget the "standard deviation" and say that it is "harder" to be far from the "expected value".
+This is not true.
+Without the "standard deviation", or "variance" this phrase, does not make any send.
+Stop to think of a distribution with "infinite" "variance".
+It is very "easy" to be "infinitilly" far from the "expected value".
+
+\section{Markov's and Chebyshev's Inequalities}
+
+If you search you will probably find another formula for both inequalities. They are all equivalent, off course.
+
+\begin{align*}
+	P(X \ge a) \le \frac{E[X]}{a}\\	
+	P(X \ge a*E[X]) \le \frac{E[X]}{a*E[X]} && E[X] > 0
+\end{align*}
+\begin{align}
+	P(X \ge a*E[X]) \le \frac{1}{a}
+\end{align}
+
+\begin{align*}
+P((X-E[X])^2 \ge a^2) &\le \frac{E[(X-E[X])^2]}{a^2}\\
+P((X-E[X])^2 \ge a^2*\text{VAR}[X]) &\le \frac{E[(X-E[X])^2]}{a^2*\text{VAR}[X]}\\
+P((X-E[X])^2 \ge a^2*\text{VAR}[X]) &\le \frac{\text{VAR}[X]}{a^2*\text{VAR}[X]}\\
+P((X-E[X])^2 \ge a^2*\text{VAR}[X]) &\le \frac{1}{a^2}\\
+P(\sqrt{(X-E[X])^2}\ge\sqrt{a^2*\text{VAR}[X]}) &\le \frac{1}{a^2}\\
+\end{align*}
+\begin{align}
+P(|(X-E[X])| \ge a*\text{SD}[X]) &\le \frac{1}{a^2}
+\end{align}
+
+\section{68-95-99.7 rule}
+
+\section{Summary}
+
+\subsection{Markov's Inequality}
+
+\begin{align}
+P(X \ge a) &\le \frac{E[X]}{a}
+\end{align}
+
+or
+
+\begin{align}
+P(X \ge aE[X]) &\le \frac{1}{a}
+\end{align}
+
+\subsection{Chebyshev's Inequality}
+
+\begin{align}
+P(|X - E[X] \ge a) &\le \frac{\text{VAR}[X]}{a^2}
+\end{align}
+
+or
+
+\begin{align}
+P(|X - E[X] \ge a*\text{SD}[X]) &\le \frac{1}{a^2}
+\end{align}
 

### 2019-05-26 texts/philosophy/DesconstruindoODesconstrucionismo.tex
.

\documentclass[10pt,a4paper]{book}
\usepackage[utf8]{inputenc}
\usepackage{fontspec}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xltxtra} 
\usepackage{xgreek}  
\usepackage{polyglossia}
\setdefaultlanguage{Portuguese}
\title{Desconstruindo o Descontrucionismo}
\author{Pierre Magnard}
\date{10 de julho de 2017}
\begin{document}
	\maketitle

	\chapter{Desconstruindo o Descontrucionismo}	
	\section{Video}

	\url{https://youtu.be/kJ1AntkVcq4}

	Tradução:\\
	Fabrício Soares de Souza\\
	\\
	Pierre Yves:\\
	Professor Pierre Magnard veio compartilhar conosco esta apresentação sobre como desconstruir a desconstrução.\\
	\\
	Pierre Magnard:\\
	Muito obrigado. É realmente uma imensa honra e uma grande alegria recebê-lo.\\
	\\
	Pierre Yves:\\
	Muito obrigado, professor.\\
	\\
	Pierre Magnard: \\
	Sou eu quem agradeço Pierre Yves a este  convite tão amável. Eu não poderia faltar com o seu chamado, mesmo sendo às pressas. E eu me comprometo de fazer então, com muito prazer, uma improvisação que não é uma qualquer pois ela é mais do que isso: uma confidência.\\
	\\
	A luta contra os "desconstrutores" eu fiz durante toda minha vida universitária. Desde a minha chegada ao Liceu Henri IV em 1947 até os dias de hoje. E a luta não acabou. Porque podemos colocar na conta desses senhores uma palavra esplêndida, uma palavra que nos faria acreditar na inteligência de seu autor. Se ela não foi pronunciada por desprezo ou por acaso.\\
	\\
	"Em uma multidão, há aqueles que têm êxito e há aqueles que não são nada."\\
	\\
	Eu acolhi isto com uma alegria no coração. Eu me reconheci no grupo daqueles que não são nada. \\
	E que nunca quiseram ser outra coisa do que isso. Nada, é no nada que Deus se esconde.\\
	\\
	Meu antigo aluno e amigo, Christian Bobin, o repete ao longo de páginas:\\
	\\
	"Deus se esconde no nada".\\
	\\
	E, nós mesmos, se somos capazes de reencontrar a virtude essencial que fez o Homem, isto é, a humildade. Se nós somos capazes de partir do personagem vilão que a sociedade gostaria de nos fazer representar. Nós somos, exatamente, o que Homero chamou oυδείς (U'dis), isto é, ninguém. Nem mesmo um oυδείς (U'dis), mas ninguém, ou seja, nada. É este nada que transcende todos os personagens e que nos dá a capacidade de encontrar um outro na amizade e no amor e, também, de aspirar encontrar Deus.\\
	\\
	Mas, a título de preâmbulo, tentemos ver como eu me deparei com a desconstrução\\
	\\
	Eu iniciarei de um texto que mereceria ser recolocado à moda, hoje. É o romance "A Náusea" de Sartre de 1937. O Liceu do Havre, como por acaso, é um lugar onde o gênio maléfico passeia. No Liceu do Havre, há um grande pátio no qual nos deparamos com um imponente castanheiro. E alguns de vocês que já leram esse livro de Sartre se lembram da parte surpreendente sobre a raiz do castanheiro que desperta em Sartre uma sensação de nojo a tal ponto que ele tem vontade de vomitar diante do que ele chama: "o surgimento de um ser que é sempre demasiado".\\
	\\
	Eis aí, no fundo, a primeira manifestação do espírito moderno.\\
	\\
	Pois onde eu encontro a náusea, a tradição metafísica, desde a Grécia antiga, falava de "espanto/perplexidade", θαυμαζείν (thaumazein) de maravilhamento, de contentamento. Alegria diante do mistério da aparição do Ser. O Ser dava-lhe contentamento.\\
	\\
	Ora, a grande novidade do homem moderno é que o Ser lhe causa náusea. E o Ser, como um acréscimo, é vivido como algo demasiado. É a palavra que utilizará Sartre em "O Ser e o Nada" quando ele retoma esta memorável análise:\\
	\\
	"O Ser é sempre demasiado."\\
	\\
	E é a partir daí que começa esse caminho da destruição ou desconstrução que almejará gerir, nada menos que, a metafísica enterrando a metafísica.\\
	\\
	Quando eu cheguei ao Liceu Henri IV para me preparar à École Normale Supérieur. O que eu encontrei? Eu encontrei, precisamente, o grande debate aberto, no qual se podia ser metafísico sem ser absolutamente medíocre, ultrapassado. E pensar, hoje em dia, não exige essa renúncia à metafísica.  Portanto, vou tentar dizer-lhes, de modo bem simples, o que isto pode significar pois vocês não são, provavelmente, metafísicos experientes. Do que se trata?\\
	\\
	Eu diria que há duas palavras que a tradição metafísica, desde os gregos, associa, a saber: Deus e o Ser. Duas palavras entre as quais parece se estabelecer uma nuvem sem que sejamos constrangidos de identificar Deus ao Ser e fazer do Ser a expressão mesma de Deus. Mas temos esta noção de Ser na referência a Deus e na nominação mesma de Deus.\\
	\\
	Vocês sabem como um grande filósofo francês, Étienne Gilson, vai sinalizar no desenvolvimento do que ele chamará de metafísica do Êxodo fundada a partir do texto do Êxodo 3,14 no qual Deus guardando seu nome responde a Moisés:\\
	\\
	"Eu sou o que sou"\\
	\\
	Eu estou de minha parte, dado que sou uma cria da desconstrução, pelo fato da minha chegada em 1947 ao Liceu Henri IV, reservado no lugar do gilsonismo que fora minha filosofia provisória até então. Reservado no sentido que eu não estou seguro que Deus se nomeia (revela) na sarça ardente e que o Ser seja a designação mesma de Deus. Mas, seguindo o caminho de Gilson, o que vocês podem compreender bem, é que ele vai da afirmação de Deus saber qual é a relação entre Deus e o Ser.\\
	\\
	Qual é a relação entre Deus e o Ser?\\
	\\
	Vamos então para 1947. Isto não nos diz nada? A maioria de vocês não tinha nascido. Eu posso lhes dizer que foi um período sombrio. Um período inquietante. Um período em que os franceses não eram franceses. Um período em que se podia denunciar por nada e arrastar para o tribunal qualquer um por um dizer, por pouca coisa. 1947 é a época da corte marcial. 1947 é a época da depuração.\\
	\\
	Logo, imaginem vocês como era. Um período, portanto, em que falar poderia ter sérias consequências. E era preciso saber o que se poderia avançar. Deus, o Ser mas, afinal, o Ser o que é?\\
	\\
	Se se admite que é o conceito mais vasto. O mais compreensível. O mais capaz de abraçar a realidade e de captá-la em seu sentido. O Ser seria ser, talvez, a operatividade divina. Se não for o próprio Deus. Seria, talvez, a criação. Seria, talvez, o Reino de Deus. Seria, talvez, a energia divina. Ou como dizem os ortodoxos: as energias divinas. Eu creio que ninguém recusará esta asserção.\\
	\\
	Assim mesmo, não se faria do Ser um nome de Deus mas seríamos levados a estabelecer uma relação entre o Deus onipotente e o Ser. O Ser sendo, exatamente, a expressão da operatividade criadora. Ora, o que se professa naqueles anos de 1947, 1948, 1949? Professa-se, precisamente, a inconsistência de um mundo que se fragmenta. E a ausência total de significação à esse destino do mundo. Dito de outro modo, vive-se uma crise do sentido. Vive-se uma crise da significação.\\
	\\
	Como repete meu amigo George Steiner: "é o sentido do sentido que parece se subtrair" a partir dessa época o sentido do sentido, o sentido de que se nutre.\\
	\\
	Mais perto de nós, um dos meus amigos jovens, Richard Millet, o qual vocês conheçam, talvez, os panfletos completamente formidáveis, fala de uma exaustão do sentido para caracterizar a nova  mentalidade. Entramos em uma era de exaustão do sentido. O que quer dizer por exaustão do sentido? Richard Millet tem uma expressão absolutamente correta:\\
	\\
	"Vivemos a exaustão do sentido até experimentarmos a vertigem do nada."\\
	\\
	O que acontece é que naquele momento há uma espécie de má consciência de toda a intelligentsia francesa para com o seu passado, para com sua história vivida. Gosto de citar o poeta René Char que retomará nas páginas de Hypnos de 1948, num discurso que ele proferiu em 1943:\\
	\\
	"Nossa herança não nos foi dada por nenhum testamento."\\
	\\
	E ele vai tentar analisar esta negação geral dos franceses para com sua cultura. Ele vai tentar analisar esse desleixo geral para com todas as tradições por essa ausência de testamento. E se  compreendemos, René Char nos diz em 1943: "Nossa herança não nos foi dada por nenhum testamento." Em outras palavras, nós somos herdeiros encarregados de  guardar um patrimônio intelectual e espiritual. Este patrimônio, de repente, é atingido por um desinteresse. Ele parece caduco. Como se a nova geração não quisesse assumi-lo.\\
	\\
	De quem se trata? De René Bazin, Henry Bordeaux, Paul Bourget\\
	Ainda de quem se trata? De Charles Maurras\\
	De quem se trata? uma vez mais: De Maurice Barrès\\
	\\
	Resumindo, trata-se de toda uma literatura que se dizia francesa e que nos inscrevia em nossas raízes, em nosso passado. Ora, voltem às revistas dos anos de 1946, 47, 48 e vejam como são tratados estes autores. Há uma espécie de negação geral de reconhecer os mesmos. Até do gentil Jean Giraudoux que é condenado por causa da sua situação complexa e seu papel controverso frente à ocupação alemã. Eles são todos estigmatizados porque eles não teriam compreendido ou porque não teriam tido consciência da reviravolta dos anos sombrios. E eles não teriam percebido os novos ventos da História.\\
	\\
	Portanto, tentar compreender a situação da inteligência francesa naqueles anos é que, de algum modo, era indecente reivindicar o nobre passado da França, sua precedência, a fortiori, de se nutrir.\\
	\\
	Deve-se rejeitar tudo isto.\\
	\\
	E aparecem novos autores que ganharão reputação durante esse período de negação. Se penso num destes que conheci, citarei - que eu encontrei - François Mauriac. \\
	\\
	Sobre o caminho de Chartres. Eu era estudante. Acabamos de nos interpelar, com consciência pesada,\\
	explicando que nossa vontade de ser fiel a nossa tradição é uma recusa de humanidade e que deveríamos 'cortar o nosso pescoço'. Eis o que nos ensinavam. Recusa de humanidade porque gostaríamos de ser fiéis a nossos valores franceses.\\
	\\
	Além de Mauriac, eu citarei André Malraux. Foi um pouco mais tarde quando eu o encontrei em Mendig(?) para uma apresentação dele que já era um homem célebre. Então, eu entro na pequena cabine na qual ele se preparava para sua intervenção, forço a porta e digo-lhe: "mestre, diga-nos, o que devemos entender por Gaullismo?"\\
	\\
	Ele disse estas palavras sublimes: "O Gaullismo é a fidelidade à oportunidade de fidelidade." Foi André Malraux que me disse, pessoalmente.\\
	\\
	Heidegger\\
	\\
	A partir disso, então, vocês podem imaginar como era aquele momento bem difícil dos anos que vieram após a guerra. Foi o momento, no qual precisamente, vai aparecer a tentação da desconstrução. Então, como a tentação da desconstrução se manifesta?\\
	\\
	Na khâgne do liceu Henri-IV, isto é, classe preparatória para os cursos superiores (universitários) nós tínhamos como professor de filosofia, Jean Beaufret. Jean Beaufret era aluno de Martin Heidegger. E Jean Beaufret ia todo final de semana levar a Heidegger as questões que lhe colocavam os alunos do curso preparatório do liceu Henri-IV.\\
	\\
	Era eu, portanto, que, às terças-feiras de manhã, tinha as respostas diretas de Heidegger às nossas perguntas. Eu, portanto, garanti a conversação entre os estudantes de Paris e Heidegger durante dois anos. E tenho bastante orgulho de ter orientado o debate já que era eu quem fazia as perguntas. Portanto, isso, posso talvez, enfim, dizer-lhes, pois eu nunca relatei a ninguém durante toda minha vida. Mas tendo a necessidade de dizê-lo no período, digamos, particularmente desastroso que vivemos hoje em dia.\\
	\\
	Eu tive a honra de, durante dois anos, ser o responsável por transcrever as aulas de Jean Beaufret para juntar todas as perguntas dos meus colegas e daí colocá-las a Heidegger. Então, que questões colocávamos a Heidegger? Essencialmente, queríamos saber o que era o Ser? E Heidegger nos respondia pelo seu livro de 1927: \\
	\\
	"o Ser deve ser interpretado segundo todas as modalidades do tempo." Ser e Tempo (Sein und Zeit).\\
	\\
	Em outras palavras, o Ser não era mais a denominação do estável, do imutável, do eterno, do absoluto como dizia Étienne Gilson que eu citei anteriormente. Ele não era mais, portanto, a denominação do próprio Deus. O Ser era a conotação de um evento, de um surgimento na História da própria divindade. Por que não? Pois, de fato, Heidegger que tinha abandonado seu catolicismo de origem para aderir ao protestantismo de sua esposa, via, essencialmente, Deus em sua manifestação no tempo. O tempo é o acontecimento em que se dá, em que se desvela o divino. Dito de outra maneira, se eu digo "é", "foi", "será" estas são as conotações de um evento, de uma aparição, de uma produção do divino na história. E, assim, se se considerava Deus como determinação do Absoluto, do incondicionado, do Princípio passa-se a considerar o divino em sua eventualidade (como um acontecimento, como aquilo que se mostra no presentificar, em seu desvelamento).\\
	\\
	Isto é algo que sempre me deu muito trabalho: ver como Heidegger mudou a visão ainda tomista da teologia, que a classe preparatória do liceu Henri-IV tinha, para uma visão barthiana (de Karl Barth) da teologia. Isto é, para uma concepção protestante.\\
	\\
	Era a tentação de todos os meus colegas e, também, minha, evidentemente. E nós dávamos uma grande atenção àquela proposta de Heidegger. Esta preocupação me levou a estudar durante toda minha vida os textos de Heidegger sobre o Ser. E encontrei num número bem grande desses textos que todos insistem sobre o fato de que o Ser não é, necessariamente, uma designação de Deus porém, não obstante, seja a afirmação de Deus na história. Eu cito o próprio Heidegger:\\
	\\
	"Ser e Deus não são idênticos e nunca conceberei pensar o sentido de Deus através do Ser. Alguns de vocês talvez saibam que eu venho da teologia. Assim, eu guardei um amor antigo por ela. E compreendo alguma coisa. Se eu escrevesse ainda uma obra de teologia, foi porque fui tentado de fazê-la. Por isso, a palavra Ser não deveria intervir. Ao mesmo tempo, o pensamento do Ser não é necessário. Quando se tem necessidade dele, já não é mais a fé. Ou seja, quando se tem a necessidade do Ser já não é mais fé. É o que Lutero compreendeu. Mesmo em sua própria igreja parece-se esquecer. Meu pensamento é muito modesto para aqueles que têm a aptidão de pensar com o Ser o sentido de Deus de maneira teológica. Do Ser nós não podemos obter nada para esta ciência. Eu creio que o Ser jamais poderá ser pensando como fundamento e sentido de Deus. Mas que, todavia, a experiência de Deus se fazer uma revelação possível. Advém, em sentido próprio, da dimensão do Ser. O que não significa, entretanto, que o Ser possa valer como predicado possível de Deus."\\
	\\
	Foi para mim que ele endereçou este texto. Já que ele era no início seminarista no seminário católico antes de seu esgotamento rumo ao luteranismo. "Ao mesmo tempo, o pensamento do Ser não é necessário". Mas o que significa "ao mesmo tempo" para Heidegger? "Ao mesmo tempo" é uma maneira de habitar o incognoscível. Não é nada além disso. Pois uma vez que ele se constitui sem a razão. Esta não é a fé de Joseph Ratzinger.\\
	\\
	Portanto, o Ser não é um predicado de Deus. O Ser não designa Deus. Mas ele vai fazer uso da palavra Ser no ato de dizer o acontecimento da revelação. Isto é exatamente o protestantismo barthiano. Ora, é isto que vai estar na origem da famosa desconstrução. Por quê e como?\\
	\\
	Bem, o que é preciso é que eu utilize com vocês a pedagogia de Martin Heidegger para nossa própria situação. Heidegger, como procuramos explicar a partir do que significou a remoção da noção do Ser, que fora excluído do discurso teológico, por sua iniciativa - nos dizia isso, ao nos reenviar ao capítulo 6 de Ser e Tempo (Sein und Zeit) de 1927. E nesse capítulo 6, está a questão, no fundo, da destruição ou como traduzirá Gérard de Granel: desconstrução.\\
	\\
	O texto mereceria ser aqui analisado, mas seria necessário toda a noite para fazê-lo. Vou dizer, simplesmente, o que ele contém. Heidegger nos diz:\\
	\\
	"Eu proponho uma desconstrução da linguagem comum e do pensamento usual. O pensamento usual desde Aristóteles conjuga Ser e Deus. A oposição de identidade destes dois conceitos, eu demonstro que se pratique uma disjunção entre Deus e Ser. E esta disjunção eu a chamo: desconstrução. Não pratiquemos nenhuma desconstrução mais pois todos os outros binômios da linguagem comum antiga são binômios que portam uma sabedoria que nós devemos alcançar. Todo o pensamento estruturado de antônimos, sinônimos, identidades e suas identidades como suas oposições,  [devem ser] conservados. A desconstrução deve, portanto, ser concebida de uma maneira crítica."\\
	\\
	Como dirá Léon Brunschvicg:\\
	\\
	"Herança de Palavras; Herança de Ideias" \\
	\\
	Em outras palavras, vocês sabem que em todos esses binômios têm uma sabedoria que não devemos renunciar. "A desconstrução deve, portanto, ser concebida de uma maneira crítica." É a palavra que Heidegger utilizava. E fazer a crítica da desconstrução quer dizer em qual circunstância ela é permitida. E ela é permitida, unicamente, para efetuar a disjunção entre Deus e o Ser.\\
	\\
	É algo de muito significativo esta insistência.\\
	\\
	Então, prosseguindo, para manter certa reserva e cuidado, principalmente face a alguns outros desconstrutores que utilizaram Heidegger de maneira indecente, insolente e, completamente, inaceitável. Até nos fazer 'colocar nele um uniforme da SS' e tratá-lo como um nazista. Passemos por cima dessa calúnia absolutamente gratuita.\\
	\\
	Eu me permiti de ter relações pessoais com o padre abade de Saint Martin de Beuron. A abadia que fica a 4 quilômetros de Messkirch, a cidade natal de Heidegger. A abadia aonde Heidegger, acompanhado dos pais, ia, todos os domingos, à missa no tempo em que ele era ainda fiel ao catolicismo. A abadia onde ele também fez conferências magistrais em 1931, 1932 e mesmo em 1933 até o dia em que ele mudou de ideia e se tornou reitor de sua universidade (Universidade de Friburgo).\\
	\\
	Ele era talvez...ele não merecesse ser persona grata em uma abadia beneditina. Estávamos em todos os debates mas ele não estava mais habilitado a dar conferências magistrais. "Heidegger", disse-me o atual padre abade, "permanecerá fiel a abadia de Beuron até o fim de seus dias. Mas ele não [vai] mais à missa na parte da manhã. Ele a frequentava somente ao anoitecer. No serviço litúrgico vespertino do conflito." No qual ele declarará, numa carta que ficou famosa, que esse serviço de Liturgia das horas da Véspera, no limiar da noite, é o serviço litúrgico no qual o mundo morre e no qual ele via, à sua maneira, a morte de Deus.\\
	\\
	Eis, portanto, um tipo de Heidegger romântico que guarda da fé cristã uma certa nostalgia. Mas que, no entanto, vai do desespero à desconstrução. \\
	\\
	Dito isto, o que será a desconstrução? E como ela vai se desenvolver?\\
	\\
	Bem, eu diria que a desconstrução vai ser realizada dia a dia na universidade da minha geração. O que quer dizer que eu recebi o forte choque desde seu início e que foi muito difícil aguentá-lo. Quem foram os quatro cavaleiros negros do apocalipse do mal?\\
	\\
	O primeiro, eu diria que foi Gilles Deleuze; o segundo, Michel Foucault; o terceiro, Pierre Bourdieu e o quarto, Jacques Derrida.\\
	\\
	Eu pego somente estes quatro simplesmente porque eu tive a honra de ser o desafiante deles, de ser o antípoda dos mesmos, de ser o adversário deles. E de ter sido em toda a minha vida o fraternal adversário dos quatro. Amaldiçoando suas doutrinas enquanto procurava conservar um mínimo de relação amigável com eles. De tal modo que seria, talvez, interessante que um dia eu revelasse minhas lembranças desses quatro cavaleiros negros.\\
	\\
	O que eles representam? Comecemos pelo primeiro:\\
	\\
	Gilles Deleuze\\
	\\
	Eu o conheci melhor. Ele era mais velho do que eu dois anos. Ele entrara na École Normale Supérieur quatro anos antes de mim porque eu era mais meticuloso e ele era um fardón (fanfarrão, exibido), precoce. Mas lá na École Normale Supérieur nós criamos uma espécie de confraria que nos tornou solidários uns aos outros. Para o melhor e para o pior. Portanto, eu frequentei bastante Gilles Deleuze e tentei compreender o que nos levou ao seminário Alquié (Ferdinand) no qual ele era o protagonista.\\
	\\
	Então, o intuito de Deleuze de retomar a operação de desconstrução e de prolongá-la foi muito rápido. Prolongar a desconstrução, quer dizer, efetuá-la sobre todos os binômios reputados sacrossantos e que não mereceriam talvez essa reputação.\\
	\\
	Eu me explico: o que significa fazer a desconstrução?\\
	\\
	Se se considera a vulgata filosófica, a filosofia tradicional, ela é fundada naquilo que se chama convertibilidade do sentido da expressão onto (Ser). Ou seja, é de bom tom dizer que o Bem, o Belo e o Verdadeiro são convertíveis. Portanto, não se procurará a Beleza no mal. As flores do mal não funcionam. Não se procurará a Beleza no sacrilégio. Não se procurará a Beleza na profanação como faz a arte contemporânea. Já que a Beleza é o esplendor do Bem e, ao mesmo tempo, é o esplendor da Verdade. Quer dizer que não se procurará a Beleza na mentira. Em suma, há aí identidades notáveis, como se diz na filosofia, que visam que o Bem seja o Belo e que o Belo seja o Verdadeiro.\\
	\\
	Ora, a primeira tese de Gilles Deleuze busca refutar estas identidades notáveis. E de declarar que seria, talvez, inteiramente interessante de procurar a Beleza na linhagem (?), na perversão... procurar a Beleza no mal. Vejam como é feita a inversão e como a penetração, com força de uma literatura de uma ética completamente perversa, se efetua em favor da rejeição de identidades notáveis.\\
	\\
	Eis aí a desconstrução em curso.\\
	\\
	E essa desconstrução vai nos conduzir a um reexame de tudo o que a linguagem nos impõe. Gilles Deleuze era muito sedutor e inteligente, é preciso dizer, quando ele tentava nos convencer que nosso modo de pensar era, essencialmente, condicionado por estruturas...  estruturas gramaticais que impunham que o sujeito fosse o pivô da proposição e, de acordo com entendimento dele, os epítetos ou os atributos sejam, em conjunto, conjugados e distribuídos.\\
	\\
	Ora, isto tratará de tentar subverter, perverter a ordem gramatical levando-nos a imaginar um tipo de frase cujo sujeito não seria mais o princípio ao propor que todos os atributos podem  tornar-se sujeitos. E isto Deleuze toma, incansavelmente, como a imagem da árvore. A árvore é um paradigma falso pois ele nos impõe um princípio e consequências. Ele nos impõe um ponto de partida e um ponto de chegada. Ele nos impõe uma genealogia de nosso pensamento como também de nossas vidas e nossas ações. Ele nos impõe a consideração de uma paternidade que o princípio simboliza.\\
	\\
	Ora, ele concebe, a partir daí, uma imagem de um mundo que não seria feito de árvores mas de rizomas. O rizoma vocês sabem o que é? É a batata. É o efeito de um desenvolvimento sem raízes por radículas que partem do tubérculo e que permitem um outro tubérculo nascer, e assim por diante, sem que haja um tronco.\\
	\\
	Ora, para Deleuze, é preciso renunciar a imagem do tronco e raízes e pensar segundo a imagem das radículas. Portanto, a imagem do rizoma (rizot?) que faz tábula rasa de tudo o que é raiz e de tudo que é enraizamento. Deleuze vai recrudescer nesse tipo de crítica. Ele vai recrudescer porque ele começa aplicá-la à nossa sociedade.\\
	\\
	Há uma sociedade na qual nós vivemos que é uma sociedade fundada a partir da família. E ele defenderá que a sociedade seja calcada sobre a multidão, o bando. Sobre a multidão e não mais sobre a família.\\
	\\
	Separo algumas páginas absolutamente impressionantes, nesse livro que venho lhes mostrar - Mil Platôs de Gilles Deleuze -, com a apologia da multidão.\\
	\\
	"É preciso que a humanidade não seja fundada sobre a família mas sobre a multidão."\\
	\\
	E para isto que o leva à entender, mais uma vez, sua desconstrução e querer imaginar que a crítica que se efetua ao nível da sociedade seja efetuada ao nível do próprio ser vivo. Daí sua noção de um corpo sem órgãos. É preciso renunciar a organicidade. Deve-se considerar que em um corpo qualquer órgão pode fazer qualquer coisa... em uma vicariância geral. \\
	\\
	Mas a organicidade foi proibida. Por que querer que em um corpo tenha órgãos de nutrição, de locomoção, de movimento e para a reprodução? É preciso acabar com esta divisão através de um tipo de erotização geral de todo o corpo que seria inteiramente órgão de luxúria para um tipo de jubilação geral para aquele que se entregar à essa espécie de perversão, dando uma finalidade sexual ou afrodisíaca a todos elementos de seu corpo.\\
	\\
	O corpo sem órgãos...e a ideia do corpo sem órgãos vai levar a reflexões que, a meu ver, completamente interessantes. Eu creio que ele sabia - porque um dia pressionei-o contra à parede e interroguei-o sobre a questão - inspirado em um poeta patético que se pode gostar ou não, a saber: Antonin Artaud.\\
	\\
	As blasfêmias de Antonin Artaud contra Deus e a ordem divina tinham impressionado muito Deleuze. E havia na obra de Antonin Artaud, precisamente, diatribes contra o corpo. Antonin Artaud, no fim da sua vida, deteriorado pelo câncer... Antonin Artaud no qual nenhum órgão funciona corretamente...tudo é disfunção. Antonin Artaud vai se insurgir contra essa modelização do corpo à qual ele foi submetido em sua infância, e que lhe deu durante anos, assim ele diz, um corpo não-cristificado.\\
	\\
	Por que? Porque constituído segundo a Christi-formitas. Ora, é preciso libertar o corpo de toda Christi-formitas, dizia Artaud, e Deleuze vai retomar esta visão, é preciso libertar o corpo. É preciso "afrouxar" o corpo. Então, o que é "afrouxar" o corpo? O corpo sem órgãos.\\
	\\
	Eu cito:\\
	\\
	"Um corpo sem órgãos grita. Fizeram de mim um organismo. Forçaram-me indevidamente. Roubaram-me meu corpo. O julgamento de Deus o  arranca de sua imanência e faz dele um organismo, uma significação, um sujeito. Consideremos estes três estratos em sua relação conosco, isto é, aqueles que nos amarram mais diretamente: o organismo, o significante, a subjetivação. Tu serás um organismo. Tu articularás teu corpo senão tu não passarás de um depravado. Tu serás significante e significado, intérprete e interpretado senão tu não passarás de um desviado. Tu serás sujeito e fixado como tal. Sujeito denunciação rebatido por um sujeito denunciado senão tu não passarás de um vagabundo."\\
	\\
	As imprecações de Deleuze são realmente significativas. Fizeram dele... Precisamente porque ele recebeu uma educação cristã por parte de pais normais e sensatos. Fizeram dele, precisamente, o que ele recusou ser: um depravado, um desviante, um vagabundo. Pois, para ele, é são viver o corpo sem órgãos. Isto é, sem especificação, em cujo corpo todos os órgãos são polivalentes e podem preencher todas as funções que desejar fazer preenchê-las.\\
	\\
	Então, vejam! Não estamos longe da época moderna. Nada de novo foi inventado. A "queridinha" Najat Belkacem (ministra da educação no 2o. governo de Manuel Valls) não descobriu nada novo. E foi buscar na fonte, pois, de fato, foi essa gente lá que fez a escola e que se tornou maîtres à penser (mentores) da universidade. É claro... Era vosso servidor... (?) e mesmo contusões; e até braço quebrado (?) (Parece se referir a maio de 68 quando Pierre Magnard dava aulas em Dijon). Isso pelo fato dos mal feitos que vinham de Strasbourg até Dijon para pregar seu desgosto e golpear entre as cadeiras destruídas daquela pobre sala de aula que fora arrasada porque era a última escola onde se dedicava ainda a função de professores, apesar da greve que se tornaria geral. Eu ainda fui a única exceção a greve geral. Bom, isso não é um argumento filosófico. Mas temos outros argumentos.\\
	\\
	Então, eu continuo com o problema da desconstrução.\\
	\\
	Vocês viram um pouco o que representa nosso prezado Gilles Deleuze. Para ele, a multidão está no lugar da família.\\
	\\
	"O espaço sedentário é estriado por 'torres' [sic] (muros no texto original), cercas e caminhos entre cercas ao passo que o espaço nômade é liso (igual se fala de músculo liso e músculo estriado já que se trata, precisamente, de desorganizar o próprio organismo), somente marcado por traços que se apagam e se deslocam 'no panorama' (dans le sujet) [sic]."['com o trajeto' (avec le trajet)  no texto original e não 'dans le sujet']. Enquanto o migrante deixa um meio que se tornou amorfo e ingrato, o nômade é aquele que não pode e que não quer partir. Agarra-se a esse espaço liso onde a floresta recua, onde a estepe e o deserto crescem e inventa o nomadismo como resposta a esse desafio."\\
	\\
	É tudo o que nos oferece o autor de Mil Platôs. Transformar nossa amada França num deserto.\\
	\\
	Mas isso ele diz, ele trama e ele diz que é preciso fazer isso. É o preço a se pagar: essa grande revolução do ser humano. Então está aí o cerne dos desconstrutores. É ele, Gilles Deleuze.\\
	\\
	Mas eu gostaria de acrescentar ainda algumas palavras dele próprio. Pois é a ele que se deve a fórmula muito bonita de uma humanidade sem lugar de origem e sem história (hors-sol).\\
	\\
	"Humanidade sem lugar de origem como há endívias sem lugar de origem como há galinhas sem lugar de origem...é preciso uma humanidade sem lugar de origem porque não é necessário mais enraizamento."\\
	\\
	Pois há algo que ele teme absolutamente, a saber: a determinação pela terra natal (terroir). Ou seja, ser determinado por sua terra. A terra tem uma memória. A terra tem uma vontade. Ela não é apenas devaneio. A terra nos impõe sua lei. A terra é a única lei que devemos aceitar. Onde todos batalham.\\
	Então, ele quer recusar essa determinação pela terra. Essa determinação pelo enraizamento. Para ele, é preciso suprimi-la para todo sempre.\\
	\\
	Então, humanidade sem lugar de origem que não se lembra de suas proveniências. Sem lugar de origem quer dizer sem terra mas quer dizer, também, sem paternidade. Ele tem páginas terríveis sobre o que ele chama La Ceifal, que era uma revista que tinha sido criada por André Breton uns dez anos antes. \\
	\\
	La Ceifal. Cabeça cortada. Eu me lembro ainda da sua capa La Ceifal  - Cabeça cortada. Então, a cabeça cortada é a cabeça de Luís XVI, evidentemente. Era a cabeça do pai. Pois não há mais paternidade...cabeça cortada. E a La Ceifal queria que se produzisse uma humanidade que não requeresse mais a mínima filiação. Nossos Clowns de hoje, nossos legisladores atuais estão nessa mesma linha de pensamento. Eles não fazem nada mais do que disseminar aquilo que foi desenvolvido em um livro nos idos 1968 por Gilles Deleuze que foi meu desafiante desde os ano de 1947, 48, 49, 50.\\
	\\
	Eu entrei na Universidade em 1950. Eu o conheci somente em 1950 na universidade. Portanto, foi nessa época que ele já desenvolvia esse nobre pensamento. \\
	\\
	Portanto...avancemos na nossa apresentação dos desconstrutores.\\
	\\
	Michel Foucault\\
	\\
	O segundo será Michel Foucault. Ele é exatamente contemporâneo de Gilles Deleuze. Eles são da mesma idade. Ambos nasceram em 1925. Eles eram mais velhos do que eu dois anos. Michel Foucault, eu o conheci em Clermont-Ferrand. Eu era professor em khâgne em Clermont-Ferrand, Liceu Blaise Pascal e ele era professor da faculdade. Ele era um homem gentil, amigável. Permanecendo muito aceitável com quem não compartilha de seus hábitos.\\
	\\
	Eu não sentia nenhum constrangimento em ir ao bufê da estação de trem, tomar um copo de cerveja, na companhia de Foucault que me pedia para explicar-lhe que tinham sido os pensadores do XV e XVI séculos que ele incrivelmente ignorava.\\
	\\
	E Michel Foucault, portanto, encontrava-me todas as semanas quando ele voltava à Paris no bufê da estação de trem de Clermont-Ferrand para que eu lhe falasse sobre Raimondi, Colus (?) e de outros pensandores da renascença e da pré-renascença.\\
	\\
	E ele escrevia nessa época As palavras e as Coisas. E como ele podia fazer tudo - porque ele queria ir muito rápido. Ele me pegava, em alguns anos que lecionava no liceu, a quem ele pagava, para viajar à Paris e fosse até a biblioteca nacional recopiar as citações dos autores que eu citava abundantemente no meu curso. Pois ele não conhecia minhas anotações. Fiquei espantado quando As Palavras e as Coisas foi publicado de ver nos dois primeiros capítulos d'As Palavras e as Coisas uma quantidade de citações fora de contexto tomadas todas em sentido contrário porque ele não verificou em qual contexto elas estavam.\\
	\\
	Ele se contentava de recopiar as partes marcadas e puramente copiar e colar simplesmente. Mas não se deve espantar pois Michel Foucault vai a partir d'As Palavras e as Coisas [se tornar] um anti-intelectual(?). Mas Michel Foucault tinha uma particularidade, ele gostava muito de Deleuze e ele intencionava desenvolver o pensamento de Deleuze. E sua particularidade o tomava depois do segundo copo de cerveja. Ele se tornava um louco enfurecido quando ele falava do que lhe parecia dever ser eliminado para sempre da linguagem dos seres humanos: a palavra filiação.\\
	\\
	Não havia nada pior aos seus olhos do que ter um pai. Para ele, é o opróbrio por excelência. É preciso se desfazer da filiação. Libertar a humanidade é libertá-la da filiação. Não temos mais paternidade a partir de Foucault. Então não podemos nos espantar do que acontece, hoje em dia, com a GPA (Gestação para outrem, barriga de aluguel) e a PMA (Procriação médica assistida) estão em consonância com o que Foucault sempre ensinou.\\
	\\
	Foucault não cessava de dizer seu horror de que representava para ele o fato de ter nascido em Poitiers, vejam vocês, de um pai médico em Poitiers.\\
	\\
	"Ter tido um pai, ele me dizia, é o pior dos opróbrios."\\
	\\
	Um louco! [Mas foi] este louco que [se tornou o] maître à penser (intelectual orientador) para as gerações que seguiram. Pois, de fato, tudo que conhecemos, hoje, como crítica de filiação foi o que Foucault   preparou para esse mercado de ideias baratas. \\
	\\
	Então, eu não tenho tempo de seguir Foucault em todas suas elucubrações e eu gostaria de dizer algumas palavras sobre os outros dois desconstrutores.\\
	\\
	Pierre Bourdieu\\
	\\
	Pierre Bourdieu e Jacques Derrida. Então, Pierre Bourdieu é muito simples. É o mais simpático, o mais gentil do grupo. Ele foi para a Argélia prestar o serviço militar. Ele procurava o que poderia torná-lo diferenciado, o que poderia impulsioná-lo. E ele entra na residência geral (sede do representante do governo francês). Isto é, a direção fazendária e militar da Argélia.\\
	\\
	Ele foi à Argélia francesa com muita determinação. Depois ele volta e dois [anos] mais tarde parte novamente para a Argélia porque ele é convocado pelo comando militar ao qual pertencia e lá ele se torna membro do FLN (Frente de Libertação Nacional, partido político nacionalista argelino).\\
	\\
	Então, uma mutação brusca.\\
	\\
	Evidentemente, na biologia admite-se mutações bruscas mas, enfim, mesmo assim, é algo - e Jules Jean-Pierre me escuta - isso não impede de passar os atritos de um lado a outro. Ele me disse: \\
	\\
	"mas eu não era sensato porque eu era um filho do povo. Meu pai era jornaleiro e agricultor e é necessário que eu pense nas consequências e foi assim que eu passei para o lado do FLN."\\
	\\
	Então vai ser ele que vai escrever Os Herdeiros. Os Herdeiros, livro que, hoje, tratam como se fosse um tipo de bíblia no meio dos ditos "bem pensantes". O meio dos ditos "bem pensantes" fez de Os Herdeiros o livro imprescindível, indispensável. A tese de Os Herdeiros é muito simples: enquanto não se puder renunciar ao privilégio que a família pode dar na transmissão dos saberes não se terá uma sociedade igualitária.\\
	\\
	Portanto, se se vive numa sociedade verdadeiramente igualitária, e numa sociedade de homens livres, é preciso que não haja, em nenhum lugar, nenhuma família para a transmissão dos saberes.\\
	\\
	Este pensamento vai se tornar um inimigo íntimo para mim porque eu me fizera, já na época, o campeão da transmissão e ele era realmente o adversário da transmissão. Nós nos opúnhamos frequentemente sobre o tema da transmissão. E eu chegarei ao quarto desconstrutor que é Jacques Derrida.\\
	\\
	Jacques Derrida\\
	\\
	Então, a carreira de Derrida vocês a conhecem. Jacques Derrida estava à khâgne (classe preparatória) comigo no liceu Louis-le-Grand no último ano. Ele estava lá, como Bourdieu e eu, no mesmo ano. Em 1950. E Jacques Derrida indicava ser um fervoroso proponente da desconstrução custasse o que custasse. Foi assim que ele conheceu alguns descontentes quando ele quis se candidatar à universidade.\\
	\\
	Eu era do conselho consultivo que selecionava os professores universitários e, por duas vezes, fui levado à votar para que ele não fosse selecionado. O que não me impedia de ter boas relações com ele porque eu me expliquei por telefone. Eu lhe disse que se talvez cessasse de ser como era, gostaria de aprová-lo. Mas que aquela pose, aquela impostura que ele mantinha para um posto filosófico era algo absolutamente detestável. Mas, todavia, ele ia conhecer a fortuna. Foi em 1981.\\
	\\
	A fortuna ele a conheceu por sua prisão por tráfico de drogas na fronteira ao retornar de uma viagem da Europa Central. Mala com fundo falso, drogas pesadas...ele vivia disso já que ele não tinha posto na universidade e ele não queria dar aulas no liceu. E ele sucumbiria a ação da justiça se uma "divina" surpresa não tivesse intervindo em sua carreira: a eleição "miraculosa" de um certo François Mitterrand. Do qual ele se tornará, de um dia para o outro, membro do conselho filosófico e que, por isto, será ilibado de seus crimes.\\
	\\
	Mitterrand funda o Colégio Internacional de Filosofia para Derrida. E Derrida, a partir daí, com a situação tranquila frente a justiça, será até mesmo colocado numa situação de superioridade para julgar seus colegas de universidade que ele voltará a encontrar. Portanto, a fortuna de Derrida é menos suas obras que são todas ineptas - uns mais que outras - e rudemente mal redigidas do que a "graça" presidencial que fez dele o pensador (filósofo) oficial.\\
	\\
	Então o que ele acrescentou a desconstrução?\\
	\\
	Nada. A não ser que ele a generaliza. Ele a praticou sistematicamente e em toda parte. Quer dizer que todos os binômios constituídos de um tipo, de uma maneira canônica devem ser destruídos. Deve-se colocar por desígnio que o mal é belo e que o bem deve-se procurar precisamente nos antípodas dos locais onde se procura habitualmente. E, então, seu desafio será de desenvolver isso em um plano de um tipo de erotização geral da palavra escrita e da ação que lhe permitirá de justificar essa desconstrução generalizada.\\
	\\
	Então está aí o que eu tinha de dizer sobre os quatro cavaleiros do apocalipse.\\
	\\
	O Desastre\\
	\\
	O que eu gostaria é de tentar tirar uma sombra, mais o sonho do que eu lhes apresentei sobre o modo conflitual e, deliberadamente, opositivo. Eu o farei por uma ficção que não é imaginária, já que é a relação de uma lembrança muito precisa. Vocês poderiam me perguntar se, fora da camaradagem ocasional que eu tive com esses quatro personagens, tive a possibilidade de encontrá-los todos juntos e debater com eles. Isto aconteceu em Saint-Germain-des-Prés na casa de Marguerite Duras que recebia Maurice Blanchot.\\
	\\
	Este nome não lhes diz, talvez, mais nada. Ele foi um pensador muito sensato, muito distinto e muito sutil. Mas talvez, hoje, completamente esquecido. E, no entanto, ele é, talvez, aquele que sem querer foi o que mais me ajudou no meu combate. \\
	\\
	Maurice Blanchot era um crítico literário muito mais velho do que nós, já que ele tinha nascido, se eu não me engano, em 1907 - ele era vinte anos mais velho do que eu. E ele reunia o que eles acreditavam ser as cabeças pensantes da universidade da época, de maneira que eu tive a honra de reunir na casa de Marguerite Duras, que nos ofereceu seu apartamento, com Bourdieu, com Derrida, com Deleuze e com Foucault.\\
	\\
	O que se destacou de suas reflexões?\\
	\\
	O que eu guardei foi o silêncio de Blanchot que nunca tomava partido no debate. E que tinha a honestidade de impor minha presença enquanto eu estava dissonante e mal visto naquele meio. É preciso dizer que Maurice Blanchot fazia a grande diferença. Ele fora discípulo de Maurras. E foi com este "título" que ele tinha por mim alguma simpatia, digamos assim, ou alguma indulgência. E ele tinha durante a guerra colaborado com os comunistas, não por marxismo, mas porque ele tinha ajudado a passar judeus para a Suíça. E como ele era de um grande generosidade, sua casa era um pouco uma casa de acolhimento.\\
	\\
	Ora, o que eu guardo de Blanchot?\\
	\\
	Toda uma literatura que aparecerá bem depois e que terá por tema fundamental o desastre. E se você quiser conhecer algo de Blanchot, hoje, compre A Escritura do Desastre.\\
	\\
	O que é o desastre?\\
	\\
	Quando Blanchot nos recebe entre 1947 e 1952, vivíamos naquele período em que a ameaça comunista era grande sobre a França. Período em que tememos, precisamente, a tomada do poder pelo partido - lembrem-se do próprio ano de 1947! E nosso admirável Blanchot num tom monocórdico com uma atonia absolutamente surpreendente, escritor de uma escrita que eu qualifico de uma escrita sóbria - pois ele não manifesta nenhuma paixão -, nos explica o que é o desastre.\\
	\\
	Ele nos dizia para permanecermos calmo: \\
	\\
	"não vós impressionai! Vós viveis um desastre, quer dizer que o homem da vossa geração perdeu seu astro."\\
	\\
	O desastre é isto.\\
	\\
	"A marcha para a estrela chegou ao fim. O lavrador de outrora caminhava em direção à estrela para ir ao seu primeiro campo arado. Hoje não há mais caminho para a estrela. O céu se escureceu, o céu ficou turvo. Não há mais sentido para buscar ou algo que seja. É o desastre."\\
	\\
	Mas, então, o que fazer nesse desastre?\\
	\\
	\\
	Mas no desastre é bom aceitar prudentemente que nada mais manifesta um sentido. Nem sobre a terra nem no céu já que as constelações, elas mesmas, parecem  estar apagadas. Quanto ao perfume das flores e as cores da folhagem elas não lhes diz mais nada, pois o sentido desapareceu. O sentido do sentido - a capacidade de sentir está, de alguma maneira, extinta em nossa humanidade. Por isso, nós vivemos o desastre. Mas o desastre jamais foi tão certo do que isso.\\
	\\
	Por quê?\\
	\\
	Acredita-se que a casa se desmoronou. Acredita-se que ela já pereceu. Todos as outras desapareceram. Elas são fantasmagóricas. E, no entanto, você, fiel, último rebento com atributos, você bate a porta e você vê, você se coloca nos velhos muros... nos velhos muros que você não sabe absolutamente ao certo se eles ainda existem, ou se eles são puramente e simplesmente ilusórios e nos dizia Blanchot: \\
	\\
	"vós entrais no reino da precariedade."\\
	\\
	Ora, o que é o reino da precariedade?\\
	\\
	É aquele cujos edifícios, as fundações das construções não aguentam mais suas vigas mas, simplesmente, em virtude de nossa oração, nosso pedido. Précarité, pré carré, prier [Precariedade, o que é só da nossa alçada, rezar (há uma aliteração e parece haver um jogo de palavras].\\
	\\
	Ele nos dizia: \\
	\\
	"Então, é o último recurso que vos resta. Não pergunteis vós se a casa está ainda lá, ide servi-la como se ela jamais estivesse derrubada. Ela se mantém apenas por vossa oração."\\
	\\
	Aí está a lição que nos deu Maurice Blanchot, naqueles anos, diante de nossos quatro desconstrutores que não tinham nenhuma consideração por isso.\\
	\\
	Eu jamais esquecerei o olhar terno de Blanchot sobre seu empregado quando ele lhe dizia:\\
	\\
	"Não deixe, meu caro amigo, de rezar." \\
	\\
	Obrigado.
\end{document}

### 2019-05-26 sources/cpp/watch/watch.cpp

@@ -98,14 +98,6 @@ namespace w32
 	//io
 	unique_handle CreateFile(_In_ LPCSTR lpFileName, _In_ DWORD dwDesiredAccess, _In_ DWORD dwShareMode, _In_opt_ LPSECURITY_ATTRIBUTES lpSecurityAttributes, _In_ DWORD dwCreationDisposition, _In_ DWORD dwFlagsAndAttributes, _In_opt_ HANDLE hTemplateFile){return ::CreateFileA(lpFileName, dwDesiredAccess, dwShareMode, lpSecurityAttributes, dwCreationDisposition, dwFlagsAndAttributes, hTemplateFile);}
 
-	//http
-	unique_handle WinHttpOpen(_In_opt_z_ LPCWSTR pszAgentW, _In_ DWORD dwAccessType, _In_opt_z_ LPCWSTR pszProxyW, _In_opt_z_ LPCWSTR pszProxyBypassW, _In_ DWORD dwFlags){return ::WinHttpOpen(pszAgentW, dwAccessType, pszProxyW, pszProxyBypassW, dwFlags); }
-	unique_handle WinHttpConnect(IN HINTERNET hSession, IN LPCWSTR pswzServerName, IN INTERNET_PORT nServerPort, IN DWORD dwReserved){return ::WinHttpConnect(hSession,pswzServerName, nServerPort, dwReserved);}
-	
-	//websocket
-	HRESULT WINAPI WebSocketCreateServerHandle(_In_reads_(ulPropertyCount) const PWEB_SOCKET_PROPERTY pProperties, _In_ ULONG ulPropertyCount, _Out_ WEB_SOCKET_HANDLE *phWebSocket) { return WebSocketCreateServerHandle(pProperties, ulPropertyCount, phWebSocket); }
-	DWORD WinHttpWebSocketReceive(_In_ HINTERNET hWebSocket, _Out_writes_bytes_to_(dwBufferLength, *pdwBytesRead) PVOID pvBuffer, _In_ DWORD dwBufferLength, _Out_range_(0, dwBufferLength) DWORD *pdwBytesRead, _Out_ WINHTTP_WEB_SOCKET_BUFFER_TYPE *peBufferType){return ::WinHttpWebSocketReceive(hWebSocket, pvBuffer, dwBufferLength, pdwBytesRead, peBufferType);}
-
 	struct OVERLAPPED
 	{
 		property<unique_handle, HANDLE> hEvent;
[…]

### 2019-06-22 texts/dev/PapersILove.tex
.
some c++ papers

@@
 \documentclass{article}
+\usepackage{lmodern}
+\usepackage[utf8]{inputenc}
 \usepackage{hyperref}
-
 \begin{document}
@@
 \url{http://venus.cs.qc.edu/~waxman/cs211%20spring%202009/why%20is%20recursive%20fibonacci%20so%20slow.pdf}}
-	\item {Binomial Coefﬁcient Computation: Recursion or Iteration?\\
+	\item {Binomial Coefficient Computation: Recursion or Iteration?\\
+\url{http://delab.csd.auth.gr/papers/SBI02m.pdf}}	\item {Binomial Coefficient Computation: Recursion or Iteration?\\
 \url{http://delab.csd.auth.gr/papers/SBI02m.pdf}}
@@
 \begin{enumerate}
+	\item {Algorithm for computer control of a digital plotter by J. E. Bresenham\\\url{https://www.cse.iitb.ac.in/~paragc/teaching/2013/cs475/papers/bresenham_line.pdf}}
 	\item {Bresenham's Algorithm\\
 \url{http://graphics.idav.ucdavis.edu/education/GraphicsNotes/Bresenhams-Algorithm.pdf}}
+	\item {Simplex noise demystified\\\url{http://webstaff.itn.liu.se/~stegu/simplexnoise/simplexnoise.pdf}}
 \end{enumerate}
@@
 \url{http://www-db.cs.wisc.edu/cidr/cidr2007/papers/cidr07p15.pdf}}
-	\item {Conﬂict-free Replicated Data Types\\ \url{https://hal.inria.fr/inria-00609399/document}}
+	\item {Conflict-free Replicated Data Types\\
+\url{https://hal.inria.fr/inria-00609399/document}}
 \end{enumerate}
@@
 
-\subsection{Programming Paradigms}
+\subsection{Programming}
 \subsubsection{Language Analysis}
@@
 	\item {Evaluating the Design of the R Language\\ \url{http://r.cs.purdue.edu/pub/ecoop12.pdf}}
+	\item{A Modest Proposal: C++ Resyntaxed\\
+\url{http://users.monash.edu/~damian/papers/HTML/ModestProposal.html}}
+	\item{Meta-Compilation for C++\\
+\url{http://www.computing.surrey.ac.uk/research/dsrg/fog/FogThesis.pdf}}
 \end{enumerate}
@@
 \section{Mathematics}
+
 \subsection{Geometry}
@@
 \end{enumerate}
+
 \subsection{Linear Algebra}
@@
 \url{https://ntrs.nasa.gov/archive/nasa/casi.ntrs.nasa.gov/19780018835.pdf}}
+\item {An Extended Set of FORTRAN Basic Linear Algebra Subprograms\\\url{http://www.ma.man.ac.uk/~sven/pubs/Level2BLAS-1-TOMS14-88.pdf}}
 	\item{FLAME: Formal Linear Algebra Methods Environment\\
@@
 \end{enumerate}
+
 \subsection{Real Analysis}
@@
 \end{enumerate}
+
 \subsection {Statistics}
@@
 \end{enumerate}
+
+\subsection{Differential Equations}
+\begin{enumerate}
+	\item {Euler Methods, Explicit, Implicit, Symplectic\\
+\url{https://www.researchgate.net/publication/302468139_Euler_Methods_Explicit_Implicit_Symplectic}}
+\end{enumerate}
+
+\subsection {Matrix Calculus}
+\begin{enumerate}
+	\item {The Matrix Calculus You Need For Deep Learning\\
+		\url{https://arxiv.org/abs/1802.01528}}
+\end{enumerate}
+
 \subsection{Forecast}

### 2019-07-06 texts/dev/PapersILove.tex
.

@@
 \begin{enumerate}
+\item{A Universal Algorithm for Sequential Data Compression\\ \url{	http://citeseer.ist.psu.edu/viewdoc/download?doi=10.1.1.118.8921}}
 \item {Data Compression Using Long Common Strings\\
@@
 \begin{enumerate}
+	\item{Hashed and Hierarchical Timing Wheels: Data Structures for the Efficient Implementation of a Timer Facility\\ \url{https://web.archive.org/web/20130319034954/https://www.cs.columbia.edu/~nahum/w6998/papers/sosp87-timing-wheels.pdf}}
 \item {Bitlist New Full-Text Index for Low Space Cost and Efficient Keyword Search\\

### 2019-07-06 courses/UTAustinX UT.PHP.16.01x/Assignments/Week2/C/Gemm_12x2Kernel.c

@@ -1,0 +1,57 @@
+#define alpha( i,j ) A[ (j)*ldA + (i) ]   // map alpha( i,j ) to array A
+#define beta( i,j )  B[ (j)*ldB + (i) ]   // map beta( i,j ) to array B
+#define gamma( i,j ) C[ (j)*ldC + (i) ]   // map gamma( i,j ) to array C
+
+#include<immintrin.h>
+
+void Gemm_MRxNRKernel( int k, double *A, int ldA, double *B, int ldB,
+		double *C, int ldC )
+{
+  /* Declare vector registers to hold 8x6 C and load them */
+  __m256d gamma_0123_0 = _mm256_loadu_pd( &gamma( 0,0 ) );
+  __m256d gamma_0123_1 = _mm256_loadu_pd( &gamma( 0,1 ) );
+  __m256d gamma_4567_0 = _mm256_loadu_pd( &gamma( 4,0 ) );
+  __m256d gamma_4567_1 = _mm256_loadu_pd( &gamma( 4,1 ) );
+  __m256d gamma_891011_0 = _mm256_loadu_pd( &gamma( 8,0 ) );
+  __m256d gamma_891011_1 = _mm256_loadu_pd( &gamma( 8,1 ) );
+   	
+  for ( int p=0; p<k; p++ ){
+    /* Declare vector register for load/broadcasting beta( p,j ) */
+    __m256d beta_p_j;
+    
+    /* Declare vector registersx to hold the current column of A and load
+       them with the eight elements of that column. */
+    __m256d alpha_0123_p = _mm256_loadu_pd( &alpha( 0,p ) );
+    __m256d alpha_4567_p = _mm256_loadu_pd( &alpha( 4,p ) );
+    __m256d alpha_891011_p = _mm256_loadu_pd( &alpha( 8,p ) );
+
+    /* Load/broadcast beta( p,0 ). */
+    beta_p_j = _mm256_broadcast_sd( &beta( p, 0) );
+    
+    /* update the first column of C with the current column of A times
+       beta ( p,0 ) */
+    gamma_0123_0 = _mm256_fmadd_pd( alpha_0123_p, beta_p_j, gamma_0123_0 );
+    gamma_4567_0 = _mm256_fmadd_pd( alpha_4567_p, beta_p_j, gamma_4567_0 );
+    gamma_891011_0 = _mm256_fmadd_pd( alpha_891011_p, beta_p_j, gamma_891011_0 );
+    
[…]

### 2019-07-06 courses/UTAustinX UT.PHP.16.01x/Assignments/Week2/C/Gemm_12x6Kernel.c

@@ -1,0 +1,117 @@
+#define alpha( i,j ) A[ (j)*ldA + (i) ]   // map alpha( i,j ) to array A
+#define beta( i,j )  B[ (j)*ldB + (i) ]   // map beta( i,j ) to array B
+#define gamma( i,j ) C[ (j)*ldC + (i) ]   // map gamma( i,j ) to array C
+
+#include<immintrin.h>
+
+void Gemm_MRxNRKernel( int k, double *A, int ldA, double *B, int ldB,
+		double *C, int ldC )
+{
+  /* Declare vector registers to hold 8x6 C and load them */
+  __m256d gamma_0123_0 = _mm256_loadu_pd( &gamma( 0,0 ) );
+  __m256d gamma_0123_1 = _mm256_loadu_pd( &gamma( 0,1 ) );
+  __m256d gamma_0123_2 = _mm256_loadu_pd( &gamma( 0,2 ) );
+  __m256d gamma_0123_3 = _mm256_loadu_pd( &gamma( 0,3 ) );
+  __m256d gamma_0123_4 = _mm256_loadu_pd( &gamma( 0,4 ) );
+  __m256d gamma_0123_5 = _mm256_loadu_pd( &gamma( 0,5 ) );
+  __m256d gamma_4567_0 = _mm256_loadu_pd( &gamma( 4,0 ) );
+  __m256d gamma_4567_1 = _mm256_loadu_pd( &gamma( 4,1 ) );
+  __m256d gamma_4567_2 = _mm256_loadu_pd( &gamma( 4,2 ) );
+  __m256d gamma_4567_3 = _mm256_loadu_pd( &gamma( 4,3 ) );
+  __m256d gamma_4567_4 = _mm256_loadu_pd( &gamma( 4,4 ) );
+  __m256d gamma_4567_5 = _mm256_loadu_pd( &gamma( 4,5 ) );
+  __m256d gamma_891011_0 = _mm256_loadu_pd( &gamma( 8,0 ) );
+  __m256d gamma_891011_1 = _mm256_loadu_pd( &gamma( 8,1 ) );
+  __m256d gamma_891011_2 = _mm256_loadu_pd( &gamma( 8,2 ) );
+  __m256d gamma_891011_3 = _mm256_loadu_pd( &gamma( 8,3 ) );
+  __m256d gamma_891011_4 = _mm256_loadu_pd( &gamma( 8,4 ) );
[…]

### 2019-07-06 courses/UTAustinX UT.PHP.16.01x/Assignments/Week2/C/Gemm_8x6Kernel.c

@@ -1,0 +1,98 @@
+#define alpha( i,j ) A[ (j)*ldA + (i) ]   // map alpha( i,j ) to array A
+#define beta( i,j )  B[ (j)*ldB + (i) ]   // map beta( i,j ) to array B
+#define gamma( i,j ) C[ (j)*ldC + (i) ]   // map gamma( i,j ) to array C
+
+#include<immintrin.h>
+
+void Gemm_MRxNRKernel( int k, double *A, int ldA, double *B, int ldB,
+		double *C, int ldC )
+{
+  /* Declare vector registers to hold 8x6 C and load them */
+  __m256d gamma_0123_0 = _mm256_loadu_pd( &gamma( 0,0 ) );
+  __m256d gamma_0123_1 = _mm256_loadu_pd( &gamma( 0,1 ) );
+  __m256d gamma_0123_2 = _mm256_loadu_pd( &gamma( 0,2 ) );
+  __m256d gamma_0123_3 = _mm256_loadu_pd( &gamma( 0,3 ) );
+  __m256d gamma_0123_4 = _mm256_loadu_pd( &gamma( 0,4 ) );
+  __m256d gamma_0123_5 = _mm256_loadu_pd( &gamma( 0,5 ) );
+  __m256d gamma_4567_0 = _mm256_loadu_pd( &gamma( 4,0 ) );
+  __m256d gamma_4567_1 = _mm256_loadu_pd( &gamma( 4,1 ) );
+  __m256d gamma_4567_2 = _mm256_loadu_pd( &gamma( 4,2 ) );
+  __m256d gamma_4567_3 = _mm256_loadu_pd( &gamma( 4,3 ) );
+  __m256d gamma_4567_4 = _mm256_loadu_pd( &gamma( 4,4 ) );
+  __m256d gamma_4567_5 = _mm256_loadu_pd( &gamma( 4,5 ) );
+   	
+  for ( int p=0; p<k; p++ ){
+    /* Declare vector register for load/broadcasting beta( p,j ) */
+    __m256d beta_p_j;
+    
+    /* Declare vector registersx to hold the current column of A and load
+       them with the eight elements of that column. */
+    __m256d alpha_0123_p = _mm256_loadu_pd( &alpha( 0,p ) );
+    __m256d alpha_4567_p = _mm256_loadu_pd( &alpha( 4,p ) );
+
+    /* Load/broadcast beta( p,0 ). */
+    beta_p_j = _mm256_broadcast_sd( &beta( p, 0) );
+    
[…]

### 2019-07-06 courses/UTAustinX UT.PHP.16.01x/Assignments/Week2/C/Gemm_JI_PJI.c

@@ -1,0 +1,38 @@
+#include <stdio.h>
+#include <stdlib.h>
+
+#define alpha(i, j) A[(j)*ldA + (i)] // map alpha( i,j ) to array A
+#define beta(i, j) B[(j)*ldB + (i)]  // map beta( i,j ) to array B
+#define gamma(i, j) C[(j)*ldC + (i)] // map gamma( i,j ) to array C
+
+#define min(x, y) ((x) < (y) ? (x) : (y))
+
+#define MB 100
+#define NB 100
+#define KB 100
+
+void Gemm_PJI(int, int, int, double *, int, double *, int, double *, int);
+
+void MyGemm(int m, int n, int k, double *A, int ldA,
+            double *B, int ldB, double *C, int ldC)
+{
+  for (int j = 0; j < n; j += NB)
+  {
+    int jb = min(n - j, NB); /* Size for "finge" block */
+    for (int i = 0; i < m; i += MB)
+    {
+      int ib = min(m - i, MB); /* Size for "finge" block */
+      Gemm_PJI(ib, jb, k, &alpha(i, 0), ldA, &beta(0, j), ldB,
+               &gamma(i, j), ldC);
+    }
+  }
+}
+
+void Gemm_PJI(int m, int n, int k, double *A, int ldA,
+              double *B, int ldB, double *C, int ldC)
+{
+  for (int p = 0; p < k; p++)
+    for (int j = 0; j < n; j++)
+      for (int i = 0; i < m; i++)
+        gamma(i, j) += alpha(i, p) * beta(p, j);
+}

### 2019-07-06 courses/UTAustinX UT.PHP.16.01x/Assignments/Week2/C/Gemm_JI_P_Ger.c

@@ -1,35 +1,39 @@
 #include <stdio.h>
 #include <stdlib.h>
 
-#define alpha( i,j ) A[ (j)*ldA + (i) ]   // map alpha( i,j ) to array A
-#define beta( i,j )  B[ (j)*ldB + (i) ]   // map beta( i,j ) to array B
-#define gamma( i,j ) C[ (j)*ldC + (i) ]   // map gamma( i,j ) to array C
+#define alpha(i, j) A[(j)*ldA + (i)] // map alpha( i,j ) to array A
+#define beta(i, j) B[(j)*ldB + (i)]  // map beta( i,j ) to array B
+#define gamma(i, j) C[(j)*ldC + (i)] // map gamma( i,j ) to array C
 
-#define min( x, y ) ( (x) < (y) ? (x) : (y) )
+#define min(x, y) ((x) < (y) ? (x) : (y))
 
 #define MB 4
 #define NB 4
 #define KB 4
 
-void Gemm_P_Ger( int, int, int, double *, int, double *, int, double *, int );
-void Ger( int, int, double *, int, double *, int, double *, int );
+void Gemm_P_Ger(int, int, int, double *, int, double *, int, double *, int);
+void Ger(int, int, double *, int, double *, int, double *, int);
 
-void MyGemm( int m, int n, int k, double *A, int ldA,
-	     double *B, int ldB, double *C, int ldC )
+void MyGemm(int m, int n, int k, double *A, int ldA,
+            double *B, int ldB, double *C, int ldC)
 {
-  for ( int j=0; j<n; j+=NB ){
-    int jb = min( n-j, NB );    /* Size for "finge" block */ 
-    for ( int i=0; i<m; i+=MB ){
-      int ib = min( m-i, MB );    /* Size for "finge" block */ 
-      Gemm_P_Ger( ib, jb, k, &alpha( i,0 ), ldA, &beta( 0,j ), ldB,
-		           &gamma( i,j ), ldC );
+  for (int j = 0; j < n; j += NB)
+  {
+    int jb = min(n - j, NB); /* Size for "finge" block */
+    for (int i = 0; i < m; i += MB)
+    {
+      int ib = min(m - i, MB); /* Size for "finge" block */
+      Gemm_P_Ger(ib, jb, k,
+                 &alpha(i, 0), ldA,
+                 &beta(0, j), ldB,
+                 &gamma(i, j), ldC);
[…]

### 2019-07-06 courses/UTAustinX UT.PHP.16.01x/Assignments/Week2/C/data/output_JIP_P_Ger.m

@@ -1,0 +1,18 @@
+% number of repeats:% 3
+% enter first, last, inc:% 48 480 48 
+data = [
+%  n          reference      |         current implementation 
+%        time       GFLOPS   |    time       GFLOPS     diff 
+   480 9.7380e-03 2.2713e+01    1.5993e-01 1.3830e+00 1.1369e-13
+   432 7.2350e-03 2.2287e+01    1.0731e-01 1.5026e+00 7.1054e-14
+   384 5.7230e-03 1.9788e+01    7.6928e-02 1.4721e+00 7.1054e-14
+   336 3.2360e-03 2.3444e+01    5.0597e-02 1.4994e+00 7.1054e-14
+   288 2.0530e-03 2.3271e+01    3.1830e-02 1.5010e+00 5.6843e-14
+   240 1.1910e-03 2.3214e+01    1.8096e-02 1.5279e+00 4.2633e-14
+   192 6.2100e-04 2.2795e+01    9.1420e-03 1.5484e+00 2.8422e-14
+   144 2.7000e-04 2.2118e+01    3.9330e-03 1.5184e+00 2.8422e-14
+    96 2.1900e-04 8.0798e+00    2.8420e-03 6.2262e-01 1.4211e-14
+    48 4.1000e-05 5.3947e+00    3.4400e-04 6.4298e-01 7.1054e-15
+];
+
+% Maximum difference between reference and your implementation: 1.136868e-13.

### 2019-07-06 courses/UTAustinX UT.PHP.16.01x/Assignments/Week2/C/data/output_JI_4x1Kernel.m

@@ -1,0 +1,39 @@
+% number of repeats:% 3
+% enter first, last, inc:% 48 1488 48 
+data = [
+%  n          reference      |         current implementation 
+%        time       GFLOPS   |    time       GFLOPS     diff 
+  1488 3.0855e-01 2.1356e+01    2.6763e+00 2.4621e+00 1.8190e-12
+  1440 2.7141e-01 2.2003e+01    2.7589e+00 2.1646e+00 1.8190e-12
+  1392 2.5534e-01 2.1126e+01    2.2270e+00 2.4223e+00 1.6485e-12
+  1344 2.2473e-01 2.1606e+01    2.2105e+00 2.1966e+00 1.5348e-12
+  1296 2.0067e-01 2.1695e+01    1.7417e+00 2.4995e+00 1.3642e-12
+  1248 1.7961e-01 2.1644e+01    1.7514e+00 2.2197e+00 1.4211e-12
+  1200 1.5779e-01 2.1903e+01    1.3620e+00 2.5375e+00 1.1369e-12
+  1152 1.4142e-01 2.1621e+01    1.3892e+00 2.2009e+00 9.6634e-13
+  1104 1.2938e-01 2.0800e+01    1.0037e+00 2.6812e+00 6.8212e-13
+  1056 1.0899e-01 2.1609e+01    9.1234e-01 2.5815e+00 5.1159e-13
+  1008 9.6670e-02 2.1189e+01    6.0841e-01 3.3668e+00 2.2737e-13
+   960 8.2157e-02 2.1538e+01    4.6048e-01 3.8427e+00 1.7053e-13
+   912 7.4076e-02 2.0480e+01    3.4746e-01 4.3662e+00 1.1369e-13
+   864 5.9965e-02 2.1512e+01    2.7592e-01 4.6750e+00 1.1369e-13
+   816 5.1059e-02 2.1283e+01    2.1935e-01 4.9541e+00 1.4211e-13
+   768 4.1544e-02 2.1807e+01    2.3579e-01 3.8423e+00 1.4211e-13
+   720 3.5687e-02 2.0918e+01    1.4644e-01 5.0978e+00 1.1369e-13
+   672 2.9790e-02 2.0374e+01    1.1928e-01 5.0883e+00 1.1369e-13
+   624 2.2850e-02 2.1267e+01    9.5310e-02 5.0985e+00 1.1369e-13
[…]

### 2019-07-06 courses/UTAustinX UT.PHP.16.01x/Assignments/Week2/C/data/output_JI_8x2Kernel.m

@@ -1,0 +1,39 @@
+% number of repeats:% 3
+% enter first, last, inc:% 48 1488 48 
+data = [
+%  n          reference      |         current implementation 
+%        time       GFLOPS   |    time       GFLOPS     diff 
+  1488 2.7766e-01 2.3731e+01    1.2696e+00 5.1900e+00 1.8190e-12
+  1440 2.5322e-01 2.3584e+01    1.1816e+00 5.0540e+00 1.8190e-12
+  1392 2.3082e-01 2.3371e+01    8.8122e-01 6.1216e+00 1.6485e-12
+  1344 2.0546e-01 2.3633e+01    8.4766e-01 5.7280e+00 1.5348e-12
+  1296 1.8480e-01 2.3558e+01    6.8408e-01 6.3641e+00 1.3642e-12
+  1248 1.6690e-01 2.3292e+01    7.2391e-01 5.3702e+00 1.4211e-12
+  1200 1.4675e-01 2.3551e+01    5.3259e-01 6.4890e+00 1.1369e-12
+  1152 1.3022e-01 2.3481e+01    5.2521e-01 5.8218e+00 9.6634e-13
+  1104 1.1458e-01 2.3488e+01    3.6119e-01 7.4508e+00 6.8212e-13
+  1056 1.0182e-01 2.3131e+01    3.5488e-01 6.6366e+00 5.1159e-13
+  1008 8.7680e-02 2.3362e+01    2.9442e-01 6.9573e+00 2.2737e-13
+   960 7.4669e-02 2.3698e+01    2.1888e-01 8.0841e+00 1.7053e-13
+   912 6.4469e-02 2.3532e+01    1.3572e-01 1.1178e+01 1.1369e-13
+   864 5.6097e-02 2.2995e+01    1.0083e-01 1.2794e+01 1.1369e-13
+   816 4.6415e-02 2.3412e+01    7.9830e-02 1.3612e+01 1.4211e-13
+   768 3.8685e-02 2.3419e+01    7.2446e-02 1.2505e+01 1.4211e-13
+   720 3.2709e-02 2.2822e+01    5.4094e-02 1.3800e+01 1.1369e-13
+   672 2.6546e-02 2.2863e+01    4.3126e-02 1.4073e+01 1.1369e-13
+   624 2.1570e-02 2.2529e+01    3.4559e-02 1.4061e+01 1.1369e-13
[…]

### 2019-07-06 courses/UTAustinX UT.PHP.16.01x/Assignments/Week2/C/data/output_JI_8x4Kernel.m

@@ -1,0 +1,39 @@
+% number of repeats:% 3
+% enter first, last, inc:% 48 1488 48 
+data = [
+%  n          reference      |         current implementation 
+%        time       GFLOPS   |    time       GFLOPS     diff 
+  1488 2.9897e-01 2.2040e+01    7.0103e-01 9.3994e+00 1.8190e-12
+  1440 2.5209e-01 2.3690e+01    7.0570e-01 8.4625e+00 1.8190e-12
+  1392 2.2707e-01 2.3757e+01    5.5115e-01 9.7877e+00 1.6485e-12
+  1344 2.0512e-01 2.3672e+01    5.3954e-01 8.9993e+00 1.5348e-12
+  1296 1.8698e-01 2.3284e+01    4.2624e-01 1.0214e+01 1.3642e-12
+  1248 1.6621e-01 2.3389e+01    4.2945e-01 9.0522e+00 1.4211e-12
+  1200 1.4728e-01 2.3465e+01    3.4151e-01 1.0120e+01 1.1369e-12
+  1152 1.4752e-01 2.0727e+01    3.0762e-01 9.9397e+00 9.6634e-13
+  1104 1.1486e-01 2.3429e+01    2.5370e-01 1.0608e+01 6.8212e-13
+  1056 1.0033e-01 2.3473e+01    2.0205e-01 1.1656e+01 5.1159e-13
+  1008 8.8358e-02 2.3183e+01    4.2338e-01 4.8382e+00 2.2737e-13
+   960 7.6101e-02 2.3252e+01    2.4571e-01 7.2016e+00 1.7053e-13
+   912 6.5648e-02 2.3110e+01    9.0008e-02 1.6855e+01 1.1369e-13
+   864 5.5691e-02 2.3163e+01    7.5168e-02 1.7161e+01 1.1369e-13
+   816 4.6651e-02 2.3294e+01    5.7373e-02 1.8941e+01 1.4211e-13
+   768 3.9291e-02 2.3058e+01    4.7827e-02 1.8943e+01 1.4211e-13
+   720 3.2364e-02 2.3066e+01    3.7228e-02 2.0052e+01 1.1369e-13
+   672 2.6448e-02 2.2948e+01    3.4147e-02 1.7774e+01 1.1369e-13
+   624 2.1347e-02 2.2764e+01    2.4316e-02 1.9984e+01 1.1369e-13
[…]

### 2019-07-06 sources/cpp/http/main.cpp

@@ -1,0 +1,269 @@
+#define UNICODE
+
+#include <io.h>
+#include <stdio.h>
+#include <winsock2.h>
+#include <Mswsock.h>
+
+#include <iostream>
+ 
+#pragma comment(lib,"ws2_32.lib")
+
+const int MAX_RIO_THREAD = 1;
+const int MAX_SEND_RQ_SIZE_PER_SOCKET = 32;
+const int MAX_RECV_RQ_SIZE_PER_SOCKET = 32;
+const int SESSION_BUFFER_SIZE = 65536;
+const int MAX_CLIENT_PER_RIO_THREAD = 2560;
+const int MAX_CQ_SIZE_PER_RIO_THREAD =
+    (MAX_SEND_RQ_SIZE_PER_SOCKET + MAX_RECV_RQ_SIZE_PER_SOCKET) 
+    * MAX_CLIENT_PER_RIO_THREAD;
+const int MAX_RIO_RESULT = 1000;
+
+RIO_EXTENSION_FUNCTION_TABLE mRioFunctionTable = { 0, };
+RIO_CQ mRioCompletionQueue[MAX_RIO_THREAD+1] = { 0, };
+
+struct IOCPLoopData {HANDLE iocp;};
+DWORD WINAPI IOCPLoop(LPVOID lpParam)
+{
+    auto& data = *(IOCPLoopData*)lpParam;
+    std::cout << "IOCPloop " << data.iocp << std::endl;
+    unsigned long bytes = 0;
+    unsigned long long cKey = 0;
+    OVERLAPPED* overlapped;
+    std::cout << "IOCPloop waiting" << std::endl;
+    auto r = GetQueuedCompletionStatus(
+        data.iocp,
+        &bytes,
+        &cKey,
+        &overlapped,
+        INFINITE
+    );
+    if(r){
+        std::cout << "IOCPloop " << bytes << " " << cKey;
+    }
+
+    return 0;
+}
+
+int main(int argc, char** argv)
+{    
+    int LISTEN_PORT = 5000;
+
+    //////////////////////////////////////////// init
+
+    WSADATA wsa;
+	WSAStartup(MAKEWORD(2, 2), &wsa);
+
+	/// create TCP socket with RIO mode
+	SOCKET mListenSocket = WSASocket(AF_INET, 
+        SOCK_STREAM, 
+        IPPROTO_TCP, 
+        NULL, 
+        0, 
+        WSA_FLAG_REGISTERED_IO);
[…]

### 2019-07-06 sources/cpp/timer/sources/NewAllocator.h

@@ -1,0 +1,15 @@
+class NewAllocator
+{
+protected:
+	template <typename T, typename... TArgs>
+	T* alloc(TArgs&&... args)
+	{
+		return ::new T{std::forward<TArgs>(args)...};
+	}
+
+	template <typename T>
+	void del(T* item)
+	{
+		delete item;
+	}
+};

### 2019-07-06 sources/cpp/timer/sources/NodeBinaryHeap.h

@@ -1,0 +1,304 @@
+// Heap
+//https://cacm.acm.org/magazines/2010/7/95061-youre-doing-it-wrong/fulltext#F1
+//http://theoryofprogramming.com/2015/02/01/binary-heaps-and-heapsort-algorithm/
+// emplace - O(log2(n))
+// pop - O(log2(n))
+// remove - O(n)
+// TAOCP - page 334
+//		2.3.2. Binary Tree Representation of Trees 
+template <typename T, typename TAlloc>
+class NodeBinaryHeap : protected TAlloc
+{
+	struct Node
+	{
+		Node* parent;
+		Node* left;
+		Node* right;
+		ui32 id;
+		ui64 p;
+		T data;
+	};
+
+	ui32 Id;
+	ui32 Size;
+	Node* Root;
+
+	unsigned leading_zero_naive3(ui32 x)
+	{
+// #ifdef _MSC_VER
+// 		unsigned long index;
+// 		auto isNonzero = _BitScanReverse(&index, (unsigned long)x);
+// 		if (isNonzero)
+// 			return (sizeof(x) * 8) - index - 1;
+// 		else return sizeof(x) * 8;
+// #else
+		int n;
+		if (x == 0) return 32;
+		for (n = 0; ((x & 0x80000000) == 0); n++, x <<= 1);
+		return n;
+//#endif
+	}
+
+	template <typename... TArgs>
+	Node* emplaceAtInsertionPoint(ui64 priotity, TArgs&&... args)
+	{
+		// While inserting itself we could keep a track of the heap size. So,
+		// this takes constant time. While inserting, we must search for the
+		// appropriate location. For this, we will convert the size into its
+		// binary representation and begin the traversal from the root. How?
+		// Keep reading the bits of the binary representation you just
+		// generated, if you encounter ‘0’ go to the left child of the parent,
+		// if it is a ‘1’ go to the right child of the parent. I know it
+		// sounds really weird, but that’s the best thing we can do. 
+		//http://theoryofprogramming.com/2015/02/01/binary-heaps-and-heapsort-algorithm/
+		auto path = ++Size;
+		auto pos = leading_zero_naive3(path) + 1;
+
+		Node* parent = nullptr;
+		Node* current = Root;
+
+		while (current != nullptr && pos < 32)
+		{
+			parent = current;
[…]

### 2019-07-06 sources/javascript/pptx2html/index.js

@@ -1,0 +1,12 @@
+let { AirParser } = require("airppt-parser");
+
+let pptParser = new AirParser("../../webassembly/wasm.pptx");
+waitForParsing();
+
+async function waitForParsing() {
+	//pass in the slide number and wait
+	let result = await pptParser.ParsePowerPoint(1);
+
+	//returns an array of Powerpoint Elements and some extra MetaData
+	console.log(result.powerPointElements[1]);
+}

### 2019-07-06 sources/webassembly/emscriptexample/em.main.js

@@ -1,0 +1,1 @@
+var Module=typeof Module!=="undefined"?Module:{};var moduleOverrides={};var key;for(key in Module){if(Module.hasOwnProperty(key)){moduleOverrides[key]=Module[key]}}Module["arguments"]=[];Module["thisProgram"]="./this.program";Module["quit"]=function(status,toThrow){throw toThrow};Module["preRun"]=[];Module["postRun"]=[];var ENVIRONMENT_IS_WEB=false;var ENVIRONMENT_IS_WORKER=false;var ENVIRONMENT_IS_NODE=false;var ENVIRONMENT_HAS_NODE=false;var ENVIRONMENT_IS_SHELL=false;ENVIRONMENT_IS_WEB=typeof window==="object";ENVIRONMENT_IS_WORKER=typeof importScripts==="function";ENVIRONMENT_HAS_NODE=typeof process==="object"&&typeof require==="function";ENVIRONMENT_IS_NODE=ENVIRONMENT_HAS_NODE&&!ENVIRONMENT_IS_WEB&&!ENVIRONMENT_IS_WORKER;ENVIRONMENT_IS_SHELL=!ENVIRONMENT_IS_WEB&&!ENVIRONMENT_IS_NODE&&!ENVIRONMENT_IS_WORKER;var scriptDirectory="";function locateFile(path){if(Module["locateFile"]){return Module["locateFile"](path,scriptDirectory)}else{return scriptDirectory+path}}if(ENVIRONMENT_IS_NODE){scriptDirectory=__dirname+"/";var nodeFS;var nodePath;Module["read"]=function shell_read(filename,binary){var ret;if(!nodeFS)nodeFS=require("fs");if(!nodePath)nodePath=require("path");filename=nodePath["normalize"](filename);ret=nodeFS["readFileSync"](filename);return binary?ret:ret.toString()};Module["readBinary"]=function readBinary(filename){var ret=Module["read"](filename,true);if(!ret.buffer){ret=new Uint8Array(ret)}assert(ret.buffer);return ret};if(process["argv"].length>1){Module["thisProgram"]=process["argv"][1].replace(/\\/g,"/")}Module["arguments"]=process["argv"].slice(2);if(typeof module!=="undefined"){module["exports"]=Module}process["on"]("uncaughtException",function(ex){if(!(ex instanceof ExitStatus)){throw ex}});process["on"]("unhandledRejection",abort);Module["quit"]=function(status){process["exit"](status)};Module["inspect"]=function()
[…]

### 2019-07-11 sources/cpp/memory/source/allocators.h
.

@@ -1,9 +1,18 @@
 #ifndef ALLOCATORS_H
 #define ALLOCATORS_H
 
-using size_t = unsigned long long;
+#include <Windows.h>
+
+//using size_t = unsigned long long;
 using uint8_t = unsigned char;
 using uint32_t = unsigned int;
+
+template <typename T>
+void* operator new(size_t size, T& allocator)
+{
+	auto block = allocator.allocate(size);
+	return block.Pointer;
+}
 
 namespace ma
 {
@@ -78,12 +87,33 @@ namespace ma
 		{
 		}
 
+		template <typename T, typename... TArgs>
+		T& emplace(TArgs... args)
+		{
+			return *(new (Pointer) T{ args... });
+		}
+
+		uint8_t* end() const { return (uint8_t*)Pointer + Size; }
+		template<typename T> bool owns(T* ptr) const { return (uint8_t*)ptr < ((uint8_t*)Pointer + Size); }
+		template<typename T> int position(T* ptr) const
+		{
+			auto p = (uint8_t*)ptr;
+			auto end = (uint8_t*)Pointer + Size;
+
+			if (p >= Pointer && p < end) return 0;
+			if (p >= end) return 1;
+			if (p <= Pointer) return -1;
+			return 0; //impossible
+		}
+
 		static const Block Null;
 	};
 	const Block Block::Null{ nullptr, 0 };
 
 	bool operator == (const Block& l, const Block& r) { return l.Pointer == r.Pointer; }
 	bool operator != (const Block& l, const Block& r) { return l.Pointer != r.Pointer; }
+
+	////////////////////////////////////////////////////////////////////////////////////// NULL ALLOCATOR
 
 	class NullAllocator
 	{
@@ -107,6 +137,8 @@ namespace ma
 			return Block::Null;
 		}
 	};
+	
+	////////////////////////////////////////////////////////////////////////////////////// FALLBACK ALLOCATOR
 
 	template <typename Primary, typename Fallback>
 	class FallbackAllocator : private Primary,
@@ -136,6 +168,8 @@ namespace ma
 				Fallback::deallocate(block);
 		}
 	};
+
+	////////////////////////////////////////////////////////////////////////////////////// STACK ALLOCATOR
 
 	template <size_t SIZE>
 	class StackAllocator
@@ -183,6 +217,8 @@ namespace ma
 		char *Top;
 	};
 
[…]

### 2019-08-08 courses/NewYorkBuffalo-ComputerVision/colorTransfer.m
.

@@ -1,0 +1,30 @@
+
+% based on
+% Reinhard, Erik, et al. "Color transfer between images." 
+% IEEE Computer graphics and applications 21.5 (2001): 34-41.
+% https://ieeexplore.ieee.org/abstract/document/946629
+
+function outChannel = colortransfer(sourceChannel,targetChannel)
+    sourceMean = mean(sourceChannel(:));
+    sourceStDev = std(sourceChannel(:));
+    
+    targetMean = mean(targetChannel(:));    
+    targetStDev = std(targetChannel(:));
+    
+    a = sourceChannel - sourceMean;
+    b = targetStDev / sourceStDev;
+    outChannel = (a * b) + targetMean;
+end
+
+img1 = imread('source.jpg');
+img2 = imread('target.jpg');
+
+[SL,SA,SB] = imsplit(rgb2lab(img1));
+[T1,T2,T3] = imsplit(rgb2lab(img2));
+
+OL = colortransfer(SL, T1);
+OA = colortransfer(SA, T2);
+OB = colortransfer(SB, T3);
+
+newImg = lab2rgb(cat(3, OL, OA, OB));
+montage({img1, img2, newImg}, 'Size', [1, 3])

### 2019-12-01 texts/dev/PapersILove.tex
.

@@
 \begin{enumerate}
+	\item{Lists and why they are useful\\ \url{https://academic.oup.com/comjnl/article-pdf/7/4/278/1013051/7-4-278.pdf}}
 	\item{Hashed and Hierarchical Timing Wheels: Data Structures for the Efficient Implementation of a Timer Facility\\ \url{https://web.archive.org/web/20130319034954/https://www.cs.columbia.edu/~nahum/w6998/papers/sosp87-timing-wheels.pdf}}
@@
 	\item {Simplex noise demystified\\\url{http://webstaff.itn.liu.se/~stegu/simplexnoise/simplexnoise.pdf}}
+
+	\item{Pose Space Deformation: A Unified Approach to Shape Interpolation and
+		Skeleton-Driven Deformation \\\url{http://scribblethink.org/Work/PSD/PSD.pdf}}
 \end{enumerate}
@@
 \url{http://langvillea.people.cofc.edu/MCapps7.pdf}}
+	\item{Linear Algebra for Computer Vision \\\url{http://buzzard.ups.edu/courses/2014spring/420projects/math420-UPS-spring-2014-wills-computer-vision.pdf}}
 \end{enumerate}

### 2019-12-01 sources/game/vulkan/src/main.cpp

@@ -5,431 +5,8 @@
 #include <algorithm>
 #include <string>
 #include <sstream>
-std::vector<std::string> split(const std::string& s, char delimiter)
-{
-    std::vector<std::string> tokens;
-    std::string token;
-    std::istringstream tokenStream(s);
-    while (std::getline(tokenStream, token, delimiter))
-        tokens.push_back(token);
-    return tokens;
-}
-
-#include <vulkan/vulkan.h>
-#include <vulkan/vulkan_win32.h>
-
-template <typename T>
-struct unique_handle
-{
-    using THANDLE = typename T::HandleType;
-    unique_handle(THANDLE h) : handle(h) {}
-
-    //NON COPYABLE
-    unique_handle(const unique_handle&) = delete;
-    unique_handle& operator=(const unique_handle&) = delete;
-
-    //MOVEABLE
-    unique_handle(unique_handle&& other) 
-        : handle(other.handle)
-    {
-        other.handle = T::INVALID_HANDLE;
-    }   
-
-    unique_handle& operator = (unique_handle&& other)
-    {
-        if (this != &other) {
-            handle = other.handle;
-            other.handle = T::INVALID_HANDLE;
-        }
-        return *this;
-    }
-
-    ~unique_handle()
-    {
-        if(handle != T::INVALID_HANDLE)
-            T::CloseHandle(handle);
-    }
-
-    operator THANDLE() const & noexcept { return handle; }
-private:
-    THANDLE handle;
-};
-
-#define UNIQUEHANDLE(Name) struct Vk##Name##Methods \
-{ \
-    using HandleType = Vk##Name; \
-    static constexpr Vk##Name INVALID_HANDLE = nullptr; \
-    static void CloseHandle(Vk##Name& handle) { \
-        vkDestroy##Name(handle, NULL); \
-    } \
-}; \
-using Vk##Name##Handle = unique_handle<Vk##Name##Methods>;
-
-#define GETINSTANCE_FUNC_PTR(instance, entrypoint) (PFN_vk##entrypoint) vkGetInstanceProcAddr(instance, "vk"#entrypoint)
-#define GETDEVICE_FUNC_PTR(dev, Entrypoint) (PFN_vk##Entrypoint)vkGetDeviceProcAddr(dev, "vk"#Entrypoint)
-
-UNIQUEHANDLE(Instance) //https://www.khronos.org/registry/vulkan/specs/1.1-extensions/man/html/VkInstance.html
[…]

### 2019-12-01 sources/game/vulkan/src/uniqueHandle.h

@@ -1,0 +1,36 @@
+template <typename T>
+struct unique_handle
+{
+    using THANDLE = typename T::HandleType;
+    unique_handle(THANDLE h) : handle(h) {}
+
+    //NON COPYABLE
+    unique_handle(const unique_handle&) = delete;
+    unique_handle& operator=(const unique_handle&) = delete;
+
+    //MOVEABLE
+    unique_handle(unique_handle&& other) 
+        : handle(other.handle)
+    {
+        other.handle = T::INVALID_HANDLE;
+    }   
+
+    unique_handle& operator = (unique_handle&& other)
+    {
+        if (this != &other) {
+            handle = other.handle;
+            other.handle = T::INVALID_HANDLE;
+        }
+        return *this;
+    }
+
+    ~unique_handle()
+    {
+        if(handle != T::INVALID_HANDLE)
+            T::CloseHandle(handle);
+    }
+
+    operator THANDLE() const & noexcept { return handle; }
+private:
+    THANDLE handle;
+};

### 2019-12-01 sources/javascript/videoscrapper/start.js

@@ -1,0 +1,65 @@
+const chrome = require('puppeteer');
+const firefox = require('puppeteer-firefox');
+const argv = require('yargs').argv;
+
+var exec = require('child_process').exec;
+exec('pwd', function callback(error, stdout, stderr){
+    // result
+});
+
+function sleep(ms) {
+    return new Promise(resolve => setTimeout(resolve, ms));
+}
+
+async function exe(cmd)
+{
+    var p = new Promise((ok,rej) =>
+    {
+        exec(cmd, ok);
+    });
+    return p;
+}
+
+var videos = [];
+var i = 0;
+function logRequest(r) {
+    var url = r.url();
+    if(url.includes(".m3u8")) {
+        videos.push(`ffmpeg -y -i "${r.url()}" -c copy -bsf:a aac_adtstoasc "${argv.path}/${argv.title}${++i}.mp4"`);
+    }    
+  }
+
+  async function processQueue()
+  {
+    var nowork = 5;
+    while(nowork > 0)
+    {
+        if(videos.length > 0)
+        {
+            console.log("");
+            var cmd = videos.pop();
+            console.log(cmd);
+            process.stdout.write("running...");
+            await exe(cmd);
+            process.stdout.write(" Done!");
+            nowork = 5;
+        }        
+        await sleep(1000);
+        nowork--;
+        process.stdout.write(".");
+    }
+  }
+
+(async () => {
+  const browser = await firefox.launch({
+      headless: (argv.headless || "true") == "true",
+      //executablePath: 'C:/Program Files (x86)/Google/Chrome/Application/chrome.exe'
+      //executablePath: "C:/Program Files/Mozilla Firefox/firefox.exe"
+  });
+  const page = await browser.newPage();
+  page.on('request', logRequest);
+
+  await page.goto(argv.url);
+  await processQueue();
+  await browser.close();
+})();
